### 2022-07-21 Paper1.tex
First draft 21.07.2022

 \documentclass[aps,prb,groupedaddress,showpacs,twocolumn,superscriptaddress,10pt]{revtex4-2}

\setlength{\paperheight}{11in}

\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bbm}
\usepackage{bm}
\usepackage{cancel}
\usepackage{xspace}
\usepackage{braket}
\usepackage{xcolor}   
\usepackage{calrsfs}
\usepackage{comment}
\usepackage{placeins}%enables \FloatBarier
\usepackage{hyperref}

\usepackage{units}

\synctex=1

\DeclareMathAlphabet{\pazocal}{OMS}{zplm}{m}{n} % capital letters for Re and Im parts 
\newcommand{\capcali}{\pazocal{I}}
\newcommand{\capcalr}{\pazocal{R}}

\newcommand{\ee}{\mathrm{e}}  % Euler number 
\DeclareMathOperator*{\ii}{i} % imaginary unit
\newcommand*\dd{\mathop{}\!\mathrm{d}}

\renewcommand{\vec}[1]{\bm{#1}} % vectors in bold
\newcommand{\mat}[1]{\bm{#1}} % matrices in bold 
\newcommand{\kel}[1]{\underline{#1}} % objects on Keldysh contour

\newcommand{\defeq}{\overset{\mathrm{def}}{=\joinrel=}} % definition symbol ":="

%% REFERENCE
\newcommand{\fig}[1]{Fig.\thinspace{}\ref{#1}}
\newcommand{\figs}[1]{Figs.\thinspace{}\ref{#1}} 
\newcommand{\Fig}[1]{Figure \ref{#1}}
\newcommand{\eq}[1]{Eq.\thinspace{}(\ref{#1})}
\newcommand{\Eq}[1]{Eq.\thinspace{}(\ref{#1})}
\newcommand{\eqs}[1]{Eqs.\thinspace{}(\ref{#1})}
\newcommand{\Eqs}[1]{Eqs.\thinspace{}(\ref{#1})}
\newcommand{\feqs}{eqs.\@\xspace}
\newcommand{\fEqs}{Eqs.\@\xspace}
\newcommand{\ch}{Ch.\@\xspace}
\newcommand{\Ch}{Ch.\@\xspace}
\newcommand{\pa}{par.\@\xspace}
\newcommand{\Pa}{Par.\@\xspace}
\newcommand{\se}{Sec.\@\xspace}
\newcommand{\Se}{Sec.\@\xspace}
\newcommand{\app}{App.\@\xspace}
\newcommand{\App}{App.\@\xspace}

%% CITE
\newcommand{\etal}[0]{\textit{et al.}}
\newcommand{\tcite}[1]{Ref.~~\cite{#1}}
\newcommand{\tcites}[1]{Refs.~~\cite{#1}}
\newcommand{\Tcite}[1]{Ref.~~\cite{#1}}
\newcommand{\Tcites}[1]{Refs.~~\cite{#1}}

%Defs
\newcommand{\und}{\underline}
\newcommand{\iim}{\Im{}\,}
\newcommand{\li}{\mathcal L}
\newcommand{\ga}[1]{\Gamma^{(#1)}}
\newcommand{\up}{\ensuremath{\uparrow}}
\newcommand{\dw}{\ensuremath{\downarrow}}
\newcommand{\vv}[1]{\boldsymbol{#1}}
\newcommand{\Dph}{\underline{\Delta}_\mathrm{ph}(\omega)}
\newcommand{\Daux}{\underline{\Delta}_\mathrm{aux}(\omega)}
\newcommand{\DRph}{\Delta^R_\mathrm{ph}(\omega)}
\newcommand{\DRaux}{\Delta^R_\mathrm{aux}(\omega)}
\newcommand{\DKph}{\Delta^K_\mathrm{ph}(\omega)}
\newcommand{\DKaux}{\Delta^K_\mathrm{aux}(\omega)}

%choose
%\newcommand{\phys}{\text{phys}}
%\newcommand{\phys}{\text{DMFT}}
\newcommand{\phys}{} %my preference

\def\bra#1{\mathinner{\langle{#1}|}}
\def\ket#1{\mathinner{|{#1}\rangle}}
\def\braket#1{\mathinner{\langle{#1}\rangle}}
\def\Bra#1{\left<#1\right|}
\def\Ket#1{\left|#1\right>}

\newcommand{\nag}{{\phantom{\dagger}}}

\newcommand{\pim}{IM$_\mathrm{ph}$ }
\newcommand{\aim}{IM$_\mathrm{aux}$ }
\newcommand{\pimns}{IM$_\mathrm{ph}$} 
\newcommand{\aimns}{IM$_\mathrm{aux}$}

\newcommand{\mscomm}[1]{{\color{blue} MS Comment: #1}}
%\newcommand{\kh}[1] {\textcolor{green}{KH comment: #1}}

\definecolor{orange}{RGB}{252,77,6}
\definecolor{brown}{RGB}{200,127,50}

\definecolor{ao(english)}{rgb}{0.0, 0.5, 0.0}

\newcommand{\pgcomm}[1]{{\color{ao(english)} [PG COMMENT: #1]}}
\newcommand{\pgch}[1]{{\color{ao(english)} #1}}

\begin{document}

\title{Impact ionization processes in driven Mott insulating layer: influence of fermion baths and phonons}

\author{Paolo Gazzaneo}
\email[]{paolo.gazzaneo@tugraz.at}
\affiliation{Institute of Theoretical and Computational Physics, Graz University of Technology, 8010 Graz, Austria}
\author{Tommaso Maria Mazzocchi}
\affiliation{Institute of Theoretical and Computational Physics, Graz University of Technology, 8010 Graz, Austria}
\author{Jan Lotze}
\affiliation{Institute of Theoretical and Computational Physics, Graz University of Technology, 8010 Graz, Austria}
\author{Enrico Arrigoni}
\email[]{arrigoni@tugraz.at}
\affiliation{Institute of Theoretical and Computational Physics, Graz University of Technology, 8010 Graz, Austria}

\date{\today}

\begin{abstract}

We study a model for photovoltaic energy collection consisting of a Mott insulating layer coupled to local acoustic phonons between two wide-band fermion baths at different chemical potentials, driven to the non-equilibrium steady state by an external AC field. We treat electron correlations with non-equilibrium dynamical mean field theory (DMFT) using the so-called auxiliary master equation approach as impurity solver, incuding phonons via the Migdal approximation.

We show that with a small coupling to fermion baths, the peak of the photocurrent is mainly due to impact ionization processes, while with higher coupling is due primarily to direct excitations. This occurs also for higher electric field amplitudes, that boost overall the photocurrent and the double occupation. Acoustic phonons slightly enhance the photocurrent for small driving frequencies and suppress it at higher values, in correspondence to the peak, disregarding the dominant electronic scattering process taking place. Their effect is independent of the bath-layer coupling value and the electric field amplitude.

\end{abstract}

% insert suggested PACS numbers in braces on next line
%71.10.-w Theories and models of many-electron systems
%71.15.-m Methods of electronic structure calculations
%71.27+a Strongly correlated electron systems; heavy fermions
% 71.38.−k Polarons and electron-phonon interactions
% 72.20.Jv Charge carriers: generation, recombination, lifetime, and trapping
% 73.21.−b Electron states and collective excitations in multilayers, quantum wells, mesoscopic, and nanoscale systems
%73.21.La Quantum dots (Electron states and collective excitations in multilayers, quantum wells, mesoscopic, and nanoscale systems)
% 73.50.Pz Photoconduction and photovoltaic effects
\pacs{71.10.Fd,71.15.-m,71.27+a,71.38.-k,72.20.Jv,73.21.-b,73.21.La,73.50.Pz}

\maketitle

\section{Introduction} 
\label{sec:intro}

\pgcomm{IS FERMION BATHS THE APPROPRIATE TERM?}

The idea of designing photovoltaic devices exploiting the Mott gap to convert electromagnetic radiation into energy has become popular in the recent years \cite{mano.10,li.ch.13,gu.gu.13,co.ma.14,wa.li.15}. In particular, it has been
suggested that in strongly correlated materials, highly excited charge carriers could use their extra energy to excite additional carriers across the Mott gap via impact ionization \cite{mano.10,co.ma.14}, thus
potentially improving their efficiency beyond the Shockley-Queisser limit \cite{sh.qu.61}. Although impact ionization is also present in conventional semiconductor devices, the time scales for electron-electron scattering are typically much longer than in correlated materials, so that highly excited electrons will mostly dissipate their energy to phonons.

Experimentally, evidence for fast carrier multiplication processes has indeed been detected via pump-probe experiments in VO$_2$ \cite{ho.bi.16}. Oxide heterostructures based on LaVO$_3$/SrTiO$_3$ have been identified as promising candidates, due to the ideal band gap and the strong polar field, able to separate the excited charge carriers \cite{as.bl.13}. There are however some drawbacks, such as the low mobility of the carriers \cite{wa.li.15,je.re.18}, which still question these materials’ applicability as efficient solar cells. In this regard, it has to be mentioned that, while a large-scale application of Mott-based solar cells may be hard to achieve, the employment of such systems as photodetectors may be more promising on the long run, due to their high photoresponsivity.

Therefore, the properties of the Mott-based photovoltaic mechanism deserve to be investigated further, from the scientific point of view and for future applications in order to explore, whether alternative unexpected paths could be opened. And in fact, a lot of theoretical work has been done, in order to understand the impact ionization process (see, e.g. \cite{co.ma.14,ec.we.11,ec.we.13,we.he.14,pe.be.19,so.do.18,ka.wo.20,ma.ev.22}).

The effects of the coupling to metallic leads and of phonons dissipation are essential features to properly establish the occurrence of impact ionization in Mott-based photovoltaic setups. They haven't been taken into account up to now and in this article we address such issues.

% First, because the effect of phonons on impact ionization is still to clarify completely and therefore there are still questions regarding the physical mechanisms to be answered. Once such questions are answered, a more detailed treatment of phonons, together with DFT may address more accurately the precise entity of the their effect.

\begin{figure}[ht]
% \captionsetup{width=\textwidth} 
\includegraphics[width=0.9\linewidth]{./figures_Paper1/setup.pdf}
\caption{(Colour online) Schematic representation of the considered setup. A correlated layer with local Hubbard interaction $U$ and electron-phonon coupling $g$ (green) is sandwiched between two non-interacting layers (red) via the coupling $v$ (black). The latter are in turn coupled via $\Gamma$ (orange) to wide-band fermion reservoirs (blue) at different chemical potentials $\mu_{l/r}$.}
\label{fig:setup}
\end{figure}

The setup used is depicted in Fig.\ref{fig:setup}: a Hubbard insulating layer with local acoustic phonons under AC driving is put between two intermediate non-interacting layers coupled to wide-band fermion reservoirs at different chemical potentials, acting as metallic leads. For sake of simplicity, we refer for the rest of the article to the non-interacting layers and fermion reservoirs together simply as fermion baths. We address the non-equilibrium steady state situation under an external AC field, treated via nonequilibrium Floquet dynamical mean-field theory (F-DMFT).

Our goal is to show for which values of the bath-layer coupling impact ionization clearly occurs and how is influenced by the effect of phonons.

We limit our analysis to qualitative and semi-quantitative features of the influence of fermion baths and phonons on photocurrent, double occupation and spectral properties. 
An accurate quantitative analysis of such effects and their relative signatures in possible experimental setups of Mott solar cells is outside the scope of this work.

We find that a small coupling to fermion baths clearly enhances impact ionization respect to a bigger coupling, for which direct excitations are dominant. Impact ionization therefore plays a crucial role, compensating the smaller charge injection and giving the same magnitude in the photocurrent of the case with a bigger coupling. Such results remain the same considering higher values of electric field amplitude, although the current and double occupation are greatly increased. The phonons slightly enhance the photocurrent for small driving frequencies, while suppressing it at higher values, in corrispondence to the peak, disregarding the dominant electron scattering process taking place. Such influence of phonons on the photocurrent is substantially unaltered sweeping over different values of the bath-layer coupling and of electric field amplitude.

The structure of the paper is the following: in Sec.\ref{sec:Model} we describe the model Hamiltonian. Methods, formalism and observables used are explained in Sec.\ref{sec:Method_formalism}. We discuss our results in Sec.\ref{sec:results}. We present our conclusions in Sec.\ref{sec:conclusions}.

\section{Model}
\label{sec:Model}

Our setup (Fig.\ref{fig:setup}) consists of a central Hubbard layer at half filling with local phonon coupling, under an external AC driving,attached to fermionic baths:

\begin{equation}
\label{eq:Hamiltonian}
\begin{split} 
\hat{H}(t)&=\varepsilon_c \sum_{i\sigma}\hat{n}_{i\sigma} -\sum_{\sigma}\sum_{(i,j)} t_{ij}(t) \hat{c}^{\dagger}_{i\sigma} \hat{c}_{j\sigma}
\\ & + U \sum_{i} \hat{n}_{i\uparrow} \hat{n}_{i\downarrow}+\hat{H}_{e-ph} + \hat{H}_{ph}+\hat{H}_{bath}
\end{split}
\end{equation}

The operator $\hat{c}^{\dagger}_{i\sigma}$ ($\hat{c}_{i\sigma}$) creates (annihilates) an electron with spin $\sigma= \lbrace \uparrow,\downarrow \rbrace$ on the \emph{i-th} lattice site, with $\hat{n}_{i\sigma}\equiv \hat{c}^{\dagger}_{i\sigma} \hat{c}_{i\sigma}$. We denote with $(i,j)$ the sum over next neighbour sites and with $\varepsilon_c \equiv -U/2$ the electron onsite energy. The AC field consists of a time-periodic, homogeneous and monochromatic electric field with frequency $\Omega$. It enters via the Peierl's substitution in the time-dependent hopping in Eq. (\ref{eq:Hamiltonian}) \cite{peie.33}:
\begin{equation}\label{eq:peierls} 
t_{ij}(t) = t_{c} \ e^{-i \frac{q}{\hbar} \left( \vec{r}_j - \vec{r}_i \right) \cdot \vec{A}(t)}, 
\end{equation} 
where $t_{c}$ is the intra-lattice hopping, $\vec{A}$(t) is the time-dependent vector potential, $\hbar$ the Planck's constant and $q$ the charge of the electron. Here $\vec{A}(t)=\vec{e}_{0} A(t)$ is along the lattice body diagonal, i.e. $\vec{e}_{0}=(1,1,\dots,1)$. For the AC field, $A(t)=\frac{\hbar}{qa}A\sin\Omega t$, with $A=-\frac{qE_0a}{\hbar\Omega}$, being $E_0$ the electric field amplitude and $a$ the lattice spacing ~\cite{ts.ok.08}. Therefore in the temporal gauge $\vec{E}= -\partial_{t}\vec{A}(t) = \vec{e}_{0}E_0 \cos\Omega t$.

The local electron-phonon coupling is included as in Ref.\cite{ma.ga.22u}, considering an acoustic phonon branch attached to each lattice site via the Hamiltonian 
\begin{equation}\label{eq:e-ph_ham} 
\hat{H}_{e-ph} = g \sum_{i\sigma} \hat{n}_{i\sigma} \hat{x}_{i},  
\end{equation}
with $g$ the electron-phonon coupling and $\hat{x}_{i} \equiv \frac{1}{\sqrt{2}} \left( \hat{b}^{\dagger}_{i} + \hat{b}_i \right)$, where $\hat{b}^{\dagger}_{i}$ ($\hat{b}_{i}$) creates (annihilates) a phonon of the acoustic branch at site $i$, with dispersion relation in $\hat{H}_{ph}$ \cite{ma.ga.22u}.

Details on the baths are provided in \ref{sec:Dyson_equation}.

In this paper we consider the correlated system as a $d$-dimensional layer in $d+1$ dimensions and we take the limit of infinite dimensions $d \rightarrow \infty$ by rescaling the hopping as $t_{c}=t^{*}/2\sqrt{d}$ \footnote{We tune $t^*$ such that we reproduce as best as possible the DOS of a 2D layer with $t_c$ = 1, following Ref.\cite{so.do.18}.}. With $a=1$, sums over crystal momentum ${\bf k}$ of a generic quantity $\chi$ read $\sum_{{\bf k}} \chi(\omega,{\bf k}) \rightarrow \int d\epsilon \int   d\overline{\epsilon} \ \rho(\epsilon,\overline{\epsilon}) \chi(\omega;\epsilon,\overline{\epsilon})$ with $\rho(\epsilon,\overline{\epsilon}) = (1/\pi t^{* 2}) \ exp(-( \epsilon^{2} + \overline{\epsilon}^{2})/t^{* 2})$ the joint density of states (JDOS) ~\cite{ts.ok.08}, with  
\begin{align}\label{eq:d-dim_crystal_dep}
\begin{split}  
\epsilon & = -2t_{c} \sum_{i=1}^{d} cos(k_i a) \\  
\overline{\epsilon}& = -2t_{c}\sum_{i=1}^{d} sin(k_i a). \\
\end{split}  
\end{align}

In this paper we set $\hbar = k_B = a = 1 = -q$, so that every physical quantity is in units of $t^{*}$.

\section{Method and formalism}    
\label{sec:Method_formalism}

\subsection{Floquet Green's Function method}   
\label{sec:GFs_Dyson_Floquet}

To correctly describe the nonequilibrium periodic steady-state (NESS), we use the Floquet generalization of non-equilibrium Green's function (NEGF) approach \cite{ts.ok.08}. Every function $G(t;t{'})$ satisfying the periodicity relation $G(t;t{'})=G(t+\tau;t{'}+\tau)$, with $\tau=2\pi/\Omega$ the period related to the external driving frequency $\Omega$, may be represented as \cite{ts.ok.08,sc.mo.02u,jo.fr.08}

\begin{equation}
\label{eq:FloquetGF} 
\underline{G}_{mn}(\omega) =\int dt_{rel} \int_{-\tau/2}^{\tau/2} \frac{dt_{av}}{\tau} e^{i[\left(\omega+m\Omega\right) t -\left( \omega+n\Omega\right)t{'}]} \underline{G}(t,t'),
\end{equation}

known as the the \emph{Keldysh-Floquet} GF, and

\begin{equation}\label{eq:WignerGF}
\underline{G}_{l}(\omega) =\int dt_{rel} \int_{-\tau/2}^{\tau/2} \frac{dt_{av}}{\tau} e^{i\omega t_{rel} + il\Omega t_{av}} \underline{G}(t,t'),
\end{equation}

the \emph{Wigner} GF ~\cite{ts.ok.08}. $t_{rel} = t-t{'}$ and $t_{av} = (t+t{'})/2$ are the relative and average-time variables. Eqs. (\ref{eq:FloquetGF}) and (\ref{eq:WignerGF}) are related via the relation

\begin{equation}\label{eq:Wig2Fl}
\underline{G}_{mn}(\omega)=\underline{G}_{m-n}\left(\omega+\frac{m+n}{2}\Omega \right),
\end{equation}

We denote in the rest of this work a Floquet-represented matrix as either $X_{mn}$, with the explicit indices, or using a boldface letter, $\bf{X}$. A single index as subscript, $X_{l}$, is reserved for the Wigner representation. The underline indicates the overall structure 
\begin{equation}\label{eq:Keld-structure}
\underline{{\bf G}} \equiv 
\begin{pmatrix}
{\bf G}^{R} & {\bf G}^{K}\\
{\bf 0}         & {\bf G}^{A} \\
\end{pmatrix},
\end{equation}

which contains the \emph{retarded}, \emph{advanced} and \emph{Keldysh} components $\textbf{G}^{\text{R,A,K}}$, where $\textbf{G}^{\text{A}}=(\textbf{G}^{\text{R}})^{\dagger}$. The \emph{Keldysh} component is defined as $\textbf{G}^{K} \equiv \textbf{G}^{>} + \textbf{G}^{<}$, with $\textbf{G}^{\lessgtr}$ the \emph{lesser} and \emph{greater} components~\cite{schw.61,keld.65,ra.sm.86,ha.ja}

\subsection{Dyson equation}
\label{sec:Dyson_equation}

The lattice Floquet GF of our setup obeys the Dyson equation

\begin{equation}\label{eq:FullDysonEq}
\underline{{\bf G}}^{-1}(\omega_n;\epsilon,\overline{\epsilon}) = \underline{{\bf G}}^{-1}_{0}(\omega_n;\epsilon,\overline{\epsilon}) - \underline{{\bf \Sigma}}(\omega_n;\epsilon,\overline{\epsilon}) - \underline{{\bf \Sigma}}_{e-ph}(\omega_n;\epsilon,\overline{\epsilon}),
\end{equation}

The lattice GF of the non-interacting part of the Hamiltonian, Eq. (\ref{eq:Hamiltonian}), is

\begin{equation}\label{eq:non-int_InvGF} 
\underline{G}^{-1}_{0,mn}(\omega_n;\epsilon,\overline{\epsilon}) =  \underline{g}^{-1}_{0,mn}(\omega_n;\epsilon,\overline{\epsilon}) - \sum_{\rho\in\{l,r\}}v^2_{\rho}\underline{g}_{b,\rho}(\omega_n;\epsilon)\delta_{mn},
\end{equation}

 with $v_{l/r}$ the bath-layer coupling, $\omega_n \equiv \omega + n\Omega$, $n\in\mathbbm{Z}$, and

 \begin{align}\label{eq:inv_non-int_lat_GF_comps}
\begin{split}
\left[ g^{-1}_{0}(\omega_n;\epsilon,\overline{\epsilon})) \right]^{R}_{mn} & = \left( \omega_n + i0^{+} -\varepsilon_c \right)\delta_{mn} - \varepsilon_{mn}(\epsilon,\overline{\epsilon})) \\
\left[ g^{-1}_{0}(\omega_n;\epsilon,\overline{\epsilon})) \right]^{K}_{mn} & = 0 \\
\end{split}.
\end{align}

In the steady-state, the inverse Keldysh component is negligible \cite{so.do.18}. The Floquet dispersion relation, $\varepsilon_{mn}$, for the AC field in a hyper-cubic lattice is \cite{ts.ok.08}

\begin{equation}
\label{eq:Floquet_disp}
\varepsilon_{mn}(\epsilon,\overline{\epsilon}) = \left\{
                \begin{array}{ll}
                  \epsilon J_{m-n}(A) \quad m-n:\textrm{even} \\
                  i\overline{\epsilon}J_{m-n}(A) \quad m-n:\textrm{odd}
                \end{array}
              \right  .
\end{equation}

with $J_n$ denoting the $n$-th order Bessel function of the first kind, with argument $A$ defined in \se\ref{sec:Model}.  $\underline{g}_{b,l/r}$ is the GF of the bath, composed by a $d$-dimensional layer, coupled to an infinite fermion reservoir via the hopping term $\Gamma$ (see Fig.\ref{fig:setup}). 
Its \emph{retarded} and \emph{Keldysh} components are

\begin{equation}
\label{eq:retarded_bath_GF}
g^{R}_{b,l/r}(\omega;\epsilon) = \frac{1}{\omega-\varepsilon_{l/r}(\epsilon)+i\Gamma_{l/r}}
\end{equation}

\begin{equation}
\label{eq:keldysh_bath_GF}
g^{K}_{b,l/r}(\omega;\epsilon) = 2i \Im g_{b,l/r}^{R}(\omega;\epsilon)[1-2f(\omega,\mu_{l/r},\beta)]
\end{equation}

with dispersion $\varepsilon_{l/r}(\epsilon)=\varepsilon_{l/r} +\frac{t_{l/r}}{t^*}\epsilon$, where $f(\omega,\mu_{l/r},\beta)=1/(\ee^{\beta(\omega-\mu_{l/r})}+1)$ is the Fermi-Dirac distribution function at inverse temperature $\beta \equiv 1/T$, $\varepsilon_{l/r}$ is the onsite energy and $t_{l/r}$ is the hopping within the $d$-dimensional layer of the bath.

The electron self-energy (SE) $\underline{\bf{\Sigma}}$ is obtained from F-DMFT and is therefore independent of the crystal momentum, i.e., $\underline{\bf{\Sigma}}(\omega;\epsilon,\overline{\epsilon}) \simeq \underline{\bf{\Sigma}}(\omega)$. Further details are given in Sec. \ref{sec:FDMFT_implementation}.

The e-ph SE is also included locally, $\underline{\bf{\Sigma}}_{e-ph}(\omega;\epsilon,\overline{\epsilon}) \simeq \underline{\bf{\Sigma}}_{e-ph}(\omega)$. In terms of the contour time arguments $z,z^\prime$ it has the form

\begin{equation}\label{eq:backbone_e-ph_SE}
\Sigma_{\text{e-ph}}(z,z^{\prime}) = ig^{2} G(z,z^{\prime}) D_{\text{ph}}(z,z^{\prime}).
\end{equation}

The Keldysh components ~\cite{ao.ts.14} of the non-interacting phonon GF $\kel{D}_{\text{ph}}(t,t^{\prime})$ are given by
\begin{align}\label{eq:Ph_Prop_time}
\begin{split} 
D^{\text{R}}_{\text{ph}}(t,t^{\prime}) & = -i \theta(t-t^{\prime}) \int \dd\omega \ \ee^{-i\omega\left(t-t^{\prime}\right)} A_{\text{ph}}(\omega), \\
D^{>}_{\text{ph}}(t,t^{\prime}) & = -i \int \dd\omega \ \ee^{-i\omega\left(t-t^{\prime}\right)} A_{\text{ph}}(\omega) \left( 1 + b(\omega) \right) \\
D^{<}_{\text{ph}}(t,t^{\prime}) & = -i \int \dd\omega \ \ee^{-i\omega\left(t-t^{\prime}\right)} A_{\text{ph}}(\omega) \ b(\omega), \\
\end{split},
\end{align}
where $b(\omega)=1/(\ee^{\beta\omega}-1)$ is the Bose-Einstein distribution function at inverse temperature $\beta$. We focus on acoustic phonons, with $A_{\text{ph}}(\omega) = \omega/(\omega^{2}_{\text{ph}}) \ee^{-| \omega|/\omega_{\text{ph}}}$ the phonon spectral function and $\omega_{\text{ph}}$ a soft cutoff frequency \cite{pi.li.21}. The retarded and Keldysh components of Eq.~\eqref{eq:backbone_e-ph_SE} can be found in Ref.\cite{ma.ga.22u}.

\subsection{Floquet DMFT}
\label{sec:FDMFT_implementation}

We compute the electron SE in the Dyson equation Eq.\eqref{eq:FullDysonEq} using DMFT approach~\cite{me.vo.89,ge.ko.92,ge.ko.96}, and in particular its nonequilibrium Floquet (F-DMFT) extension~\cite{ts.ok.08,sc.mo.02u,jo.fr.08}. \pgcomm{(I CAN CANCEL IT MAYBE, UNUSEFUL?) The DMFT approximation consists in neglecting the crystal momentum dependence of the electron SE, i.e. $\kel{\mat{\Sigma}}(\omega,\epsilon,\overline{\epsilon}) \to \kel{\mat{\Sigma}}(\omega)$. This allows us to map the original problem into a single-site impurity model with a bath hybridization function, $\kel{\mat\Delta}(\omega)$ encoding the effect of all other lattice sites.} We briefly describe now the self-consistent F-DMFT scheme used.
(i) We start from an initial guess for electron SE $\kel{\mat{\Sigma}}(\omega)$. (ii) We compute the local electron Green's function as

\begin{equation}\label{eq:Lat_LocGF}
\begin{split}
\kel{\mat G}_{\text{loc}}(\omega) &= \int \dd\epsilon \int \dd\overline{\epsilon} \ \rho(\epsilon,\overline{\epsilon}) \times \\ 
&\times \left[ \left( \kel{\mat G}^{-1}_{0}(\omega,\epsilon,\overline{\epsilon}) - \kel{\mat\Sigma}(\omega) - \kel{\mat \Sigma}_{\text{e-ph}}(\omega) \right)^{-1} \right].
\end{split}
\end{equation}

(iii) We compute $\kel{\mat{\Sigma}}_{\text{e-ph}}(\omega)$
from Eq.\eqref{eq:backbone_e-ph_SE}.
(iv) We map the problem into a in a single-site impurity one, with $\kel{\mat\Delta}(\omega)$ given by

\begin{equation}\label{eq:imp_Dyson_eq}
\kel{\mat{\Delta}}(\omega) = \kel{\mat{g}}^{-1}_{\text{0,site}}(\omega) - \kel{\mat{G}}^{-1}_{\text{loc}}(\omega) - \kel{\mat{\Sigma}}(\omega)
\end{equation}

where $\kel{\mat{g}}^{-1}_{\text{0,site}}(\omega)$ is defined as in Eq.~(\ref{eq:inv_non-int_lat_GF_comps}) but without $\varepsilon_{mn}(\epsilon,\overline{\epsilon})$. (v) We map the impurity problem to an auxiliary one, we solve the many body problem and determine the new $\kel{\mat{\Sigma}}(\omega)$(see \ref{sec:amea}). (vi) We plug the obtained SEs in step (ii) and we iterate the steps (ii)-(vi) until convergence.

\subsubsection{Floquet-diagonal self-energy approximation}
\label{sec:FDSA}

Eq.\eqref{eq:imp_Dyson_eq} gives a periodic time-dependent bath hybridization function $\kel{\mat\Delta}(\omega)$. We want to address photovoltaic effects, therefore following Ref.\cite{so.do.18}, we consider only the $(0,0)$-Floquet matrix element of Eq.\eqref{eq:imp_Dyson_eq} (corresponding to the time-average over a period $\tau$) and  we employ the Floquet-diagonal self-energy approximation (FDSA) for $\kel{\mat{\Sigma}}(\omega)$.  We employ the FDSA in Eq.\eqref{eq:FullDysonEq} also for $\underline{\bf{\Sigma}}_{e-ph}(\omega)$, namely $\kel{\Sigma}_{mn,e-ph}(\omega_n) = \kel{\Sigma}_{00,e-ph}(\omega_n)\delta_{mn}$ \footnote{In the range in which FDSA is justified for $\kel{\Sigma}$, $\kel{\Sigma}_{00,e-ph}$ is orders of magnitude bigger than the other Floquet matrix elements $\kel{\Sigma}_{mn,e-ph}$.}.  Therefore Eq.\eqref{eq:imp_Dyson_eq} reads

\begin{equation}\label{eq:imp_Dyson_eq_av}
\kel{\Delta}(\omega) = \kel{g}^{-1}_{\text{0,site}}(\omega) - \kel{G}^{-1}_{\text{loc}}(\omega) - \kel{\Sigma}(\omega)
\end{equation}

where all the quantities are time-averaged. Once we obtain the new $\kel{\Sigma}(\omega)$, we reconstruct the Floquet dependence of SEs via the translation property $\kel{\Sigma}_{mn}(\omega) = \kel{\Sigma}_{00}(\omega+m\Omega)\delta_{mn}$.

\subsubsection{Auxiliary master equation approach}
\label{sec:amea}

We briefly summarize the impurity solver used in step (v) of DMFT self-consistent loop (Sec.\ref{sec:FDMFT_implementation}).

We solve the many-body problem using the auxiliary master equation approach (AMEA)~\cite{ar.kn.13,do.nu.14,do.ga.15,do.so.17}. It maps the impurity problem in an open quantum system consisting of a finite number of bath sites $N_{\text{B}}$ attached to Markovian reservoirs described by the Lindblad equation. The corresponding hybridization function $\kel{\Delta}_{\text{aux}}(\omega)$ is obtained by fitting the original DMFT one. We reach convergence once $\kel{\Delta}_{\text{aux}}$ agrees with $\kel{\Delta}$ with a sufficient accuracy. With the parameters obtained from $\kel{\Delta}_{\text{aux}}$, we solve the auxiliary problem using standard many-body-diagonalization methods for open quantum systems, obtaining the new $\kel{\Sigma}(\omega)$.

\subsection{Observables}
\label{sec:observables}

In this article, we consider time-averaged observables, defined as follows.

The photocurrent (or simply current, without any ambiguity) flowing from the left fermion bath to the right one, passing through the correlated layer is given by

\begin{align}
 j_{L\rightarrow R}&=v^2\int_{-\frac{\Omega}{2}}^{\frac{\Omega}{2}}\frac{d\omega}{2\pi} \int d\epsilon \int d\overline{\epsilon} \rho(\epsilon,\overline{\epsilon}) \text{Re Tr} \boldsymbol{J}\label{eq: Current furmula_Omega}\\
  &= v^2\int_{-\infty}^{+\infty}\frac{d\omega}{2\pi} \int d\epsilon \int d\overline{\epsilon} \rho(\epsilon,\overline{\epsilon}) \text{Re} J_{00}\label{eq: Current furmula_00}
  \end{align} 
where $\boldsymbol{J}$ is given by the following expression
\begin{equation}
  \boldsymbol{J}=\left[\boldsymbol{G}^{\text{R}}(\boldsymbol{g}_{b,l}^{\text{K}}-\boldsymbol{g}_{b,r}^{\text{K}})+\boldsymbol{G}^{\text{K}}(\boldsymbol{g}_{b,l}^{\text{A}}-\boldsymbol{g}_{b,r}^{\text{A}})\right]
\end{equation}

obtained directly from Ref.\cite{so.do.18}. The two equivalent formulas Eq.\eqref{eq: Current furmula_Omega}-\eqref{eq: Current furmula_00} are used for consistency and they agree over all the chosen parameter space.

The electronic spectral function (or density of states, DOS) reads

\begin{equation}
\label{eq:el_spectral_function}
 A(\omega)=-\frac{1}{\pi}\Im G_{loc,00}^{R}(\omega).
\end{equation}

where $G^{\text{R}}_{\text{loc,00}}$ is the time-averaged retarded component of the GF given in Eq.~\eqref{eq:Lat_LocGF}. The non-equilibrium distribution function is defined via

\begin{equation}
\label{eq:NEFD-dist}
F_{\text{neq}}(\omega) = \frac{1}{2} \left\{1 - \frac{1}{2}\frac{\Im[G^{\text{K}}_{\text{loc}}(\omega)]}{\Im[G^{\text{R}}_{\text{loc}}(\omega)]} \right\}
\end{equation}

and the related occupation function is

\begin{equation}
\label{eq:Filling_func}
N(\omega) \equiv A(\omega)F_{\text{neq}}(\omega).
\end{equation}

\section{Results}
\label{sec:results}

We want to study the occurrence of impact ionization in a Mott insulating layer. Therefore following \cite{so.do.18}, we choose $U=12$. We work with fermion baths and acoustic phonons at temperature $T=0.02$. We consider a particle-hole symmetric system with $\Gamma_l=\Gamma_r=0.37$, $t_l=t_r=1.7$ \footnote{The value of the hopping within the baths layers is consistent with the choice of metallic reservoirs, commonly used for photovoltaic applications.}\footnote{The values of the baths parameters are chosen such that they reproduce best the bandwidth of metallic leads at the same temperature $T$}, $\varepsilon_{l/r}=\mp 6$ and $v_l=v_r=v$.

To reproduce a realistic situation \footnote{ Real metallic leads usually have a wide bandwidth and are only partially filled}, we choose the baths bandwidth $W_b$ to be roughly the same of the correlated layer (see Fig.\ref{fig:energy_setup}(a)) as $W_b\approx8$ and we set the baths chemical potentials to $\mu_{l/r} =\mp 1$. The left/right bath band is centered at the same energy of the Lower Hubbard Band (LHB)/Upper Hubbard Band (UHB) (Fig.\ref{fig:energy_setup}(a)) and the effective gap is $\Delta_{\textrm{eff}} \approx 4$.

All the simulations are carried out with parameter $\alpha=t^{*}E_0/\Omega^{2}<0.5$, range in which FDSA is justified \cite{so.do.18}. We consider for the phonons parameters $g=0.8$ and $\omega_{ph}=0.1$.

With the help of preliminary considerations in Sec.\ref{sec:explicative_scheme}, we discuss the occurrence of impact ionization for $E_0=2$ at different $v$, considering only the fermion baths in Sec.\ref{sec:E0_2_only_electrons} and additionally the acoustic phonons in Sec.\ref{sec:E0_2_electrons_phonons}. In the same way, we consider the effect of higher electric field amplitudes in Sec.\ref{sec:higher_E0_only_electrons} and \ref{sec:higher_E0_electrons_phonons}.

\begin{figure}[ht]
% \captionsetup{width=\textwidth} 
\includegraphics[width=0.9\linewidth]{./figures_Paper1/energy_setup.pdf}
\caption{(Colour online) Energy scheme and physical processes occuring in the considered setup. The baths bands are in red, the Hubbard bands in green and the vertical axis represents the energy. Panel (a) shows the quantities mentioned in Sec.\ref{sec:results}. Panel (b) illustrates a direct excitation process, in which an electron is excited  by a photon with energy $\Omega$ (yellow arrow) to the upper Hubbard band and escapes into the right bath (red arrow). Panel (c) displays an impact ionization process, where the photoexcited electron in the upper Hubbard band excites a second electron from the lower to the upper Hubbard band (black arrows) and they both escape into the right bath.}
\label{fig:energy_setup}
\end{figure}

\subsection{Energy considerations and physical processes}
\label{sec:explicative_scheme}

We propose here a scheme, based on energy considerations, to describe the occurrence of impact ionization (IO) in our setup. We partially follow Ref.\cite{so.do.18,ma.ev.22} for the \emph{only-electron} case, extending it to the case with electron-phonon interaction. It holds at non-equilibrium steady state (NESS), where energy and particles conservation have to be respected and therefore no charge accumulation in the correlated layer is allowed.

We assume that only first-order photon absorption processes occur. This is in fact the case for the chosen $\alpha$-values (see above) \cite{so.do.18}. We neglect also higher-order processes as multi-scattering IO processes.

The essential condition to meet to have IO is that the bandwidth of the UHB is twice the effective gap $\Delta_{\textrm{eff}}$ \cite{so.do.18}. Only in this case, the photoexcited electron has enough energy to excite a second one across the gap.

\subsubsection{Only electrons}
\label{sec:scheme_only_electrons}

\begin{itemize}

\item For $\Omega<\Delta_{\textrm{eff}}$, we don't have any current if the DOS of the correlated layer has a true gap \footnote{To overcome the effective gap with $\Omega<\Delta_{\textrm{eff}}$ multiple-photon absorption processes should take place, but as written in the main text, such effects are negligible in the studied parameter range.}. If $\Delta_{\textrm{eff}}$ is a partial gap, we have a clear suppression of the current.

\item For $\Delta_{\textrm{eff}}<\Omega<\Delta_{\textrm{eff}}+2W_b$, an electron coming from the left bath into the LHB is photoexcited to the UHB and can escape directly into the right bath without additional scattering (Fig.\ref{fig:energy_setup}(b)). From now on, we refer to such processes as direct excitations (DE).

\item For $2\Delta_{\textrm{eff}}<\Omega<\Delta_{\textrm{eff}}+2W_b$, a photoexcited electron in the UHB can excite via IO a second electron from LHB to the UHB, before being both dragged into the right bath (Fig.\ref{fig:energy_setup}(c)).

\item For $\Omega>\Delta_{\textrm{eff}}+2W_b$, there are no final states available for a photoexcited electron and the transition shouldn't occur.

\end{itemize}

From these considerations, we notice that in the energy window $\Delta_{\textrm{eff}}<\Omega<2\Delta_{\textrm{eff}}$ the only scattering processes taking place are DE, instead for $2\Delta_{\textrm{eff}}<\Omega<\Delta_{\textrm{eff}}+2W_b$ both DE and IO can occur.

We point out that the boundaries of such energy ranges aren't strict and the separation of these physical processes can't be net, due to the influence of the various complicated mechanisms involved.

\subsubsection{Electron and phonons}
\label{sec:scheme_electrons_phonons}

With the inclusion of electron-phonon scattering, the outlined scheme remains valid except for the modification of the effective gap $\Delta_{\textrm{eff}}$. As shown in Sec.\ref{sec:E0_2_electrons_phonons}, the phonons broaden the DOS of the correlated layer and slightly close the gap. Therefore the effective gap is reduced by a small amount $\Delta_{\textrm{diss}}$ indicating the dissipation by phonons, i.e. $\Delta_{\textrm{eff,ph}}=\Delta_{\textrm{eff}}-\Delta_{\textrm{diss}}$.

\subsection{$E_0=2$}
\label{sec:E0_2}

\begin{figure*}[ht]
\includegraphics[width=\textwidth]{./figures_Paper1/j_vs_omega_mu1_v_0.4_0.8_eph.pdf}
% \captionsetup{width=\textwidth}
\caption{(Colour online) $\Omega$-dependence of time-averaged steady-state current $j$ (in units of $j_0=\frac{qt^*}{\hbar a^2}$) (a), double occupancy $N_D$ (b) and time-averaged current $j$ rescaled by $v^2$ (c), for $v=0.4$ and $v=0.8$, when electron-phonon interaction is switched off and on. The electron-phonon coupling is set to $g=0.8$ and the phonon cutoff frequency to $\omega_{ph}=0.1$. Default parameters are specified at the beginning of section~\ref{sec:results}.} 
\label{fig:j_vs_omega_mu1_v_0.4_0.8_eph}
\end{figure*}

\subsubsection{Only electrons}
\label{sec:E0_2_only_electrons}

\begin{figure}[ht] 
% \captionsetup{width=\textwidth} 
\includegraphics[width=\linewidth]{./figures_Paper1/spec_filling_mu1_v_0.4_0.8_O_5_11_e.pdf}
\caption{(Colour online) Spectral function $A(\omega)/t^{* -1}$ (solid) and occupation function $N(\omega)/t^{* -1}$ (shaded area), at $\Omega=5$ (a) and $\Omega=11$ (b) for $v=0.4,0.8$, when electron-phonon interaction is switched off. Default parameters are specified at the beginning of section~\ref{sec:results}.}
\label{fig:spec_filling_mu1_v_0.4_0.8_O_5_11_e}
\end{figure}

We start from the analysis of the results obtained considering the electron-phonon interaction switched off, to describe the behaviour of the observables in terms of the bath-layer coupling $v$ only.

In Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(a) the photocurrent $j$ as a function of the driving frequency $\Omega$ shows an increase for both $v$ in the region $4\lesssim\Omega\lesssim8$ due to DE creating an electron-holon pair. Such range corresponds in fact, with our choice of parameters (see Sec.\ref{sec:results} and \ref{sec:scheme_only_electrons}), to the $\Omega$-region in which only DE can occur. For the same $\Omega$, $j_{v=0.8}>j_{v=0.4}$, clearly due to bigger value of $v$. In this region, the double occupation (Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(b)) shows accordingly an increase for both $v$.

For $\Omega\gtrsim8$, the current increases further reaching for both $v$ its peak, located at $\Omega\approx 11$ \footnote{The position of the current peak roughly correspond to the resonant driving frequency $\Omega=U$.}. The magnitude of the peak is approximately the same for both $v$, despite the bath-layer couplings are one the double of the other. The double occupation in this region shows a similar behaviour for $v=0.4$, with a peak around $\Omega\approx 11$, while exhibits for $v=0.8$ a plateau.

This region corresponds (see \ref{sec:scheme_only_electrons}) to the one in which both DE and IO can occur. Therefore what described above strongly suggests that for $v=0.4$ the dominant process taking place is IO, while for $v=0.8$ the dominant one is DE. In fact, for $v=0.4$ there is a clear increase in $N_D$ \footnote{
We point out that the increase of $N_D$ in Fig.\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}, in comparison with Ref.\cite{so.do.18} isn't so steep and big in magnitude because in our setup choice, every photoexcited carrier can escape in the right bath.}, well-known signature for IO \cite{so.do.18,ma.ev.22} and the magnitude of the current peak is comparable with $v=0.8$: given the current formula Eq. \eqref{eq: Current furmula_00}, the prefactor $v^2$ for $v=0.4$ is four time smaller than the one for $v=0.8$, therefore such result should imply a different electronic scattering, as IO, doubling the number of carriers for a single photon absorption. On the other hand, the plateau in $N_D$ for $v=0.8$ means that a double occupation of a site doesn't increase with $\Omega$, signalizing that photoexcited electrons simply arrive in UHB and escape. An additional strong confirmation to such picture comes from Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(c): the current $j$ rescaled by $v^2$ shows that the net contribution of the integral in $\eqref{eq: Current furmula_00}$ for $v=0.4$ is much bigger (roughly four times) than for $v=0.8$ and therefore the enhancement of the current has to come from a mutiplying-carriers electronic process.

Such behaviour is extremely interesting: smaller $v$ means smaller probability amplitude of electrons entering in the LHB from the left bath and escaping from the UHB in the right bath. Despite that the magnitude of the photocurrent is roughly the same and IO process compensates almost completely this injection/drag deficency.

The spectral features corroborate such hypotesis. In Fig.~\ref{fig:spec_filling_mu1_v_0.4_0.8_O_5_11_e}(a)-(b) the occupation function for $\Omega=5$, in the DE region, is almost the same for both $v$, while for $\Omega=11$ where the $j$-peak current occurs, the occupation of the UHB for $v=0.4$ is clearly bigger, in line with the peak of $N_D$.

Finally, increasing further $\Omega$ the current and double occupation decrease until they approach their minimum for $\Omega\approx20$ \footnote{The current $j$ doesn't go to zero as it should for $\Omega>20$ because of a background current intrinsic in the AMEA approach in presence of a gap or a band edge \cite{so.do.18}. This background current depends on $v$, $\mu_{l/r}$ and $g$, therefore we have different offsets according to the chosen parameters. Since we are interested in the qualitative behavior of the current and not stricly on the magnitude, we don't show these background currents, which don't affect our analysis.}.

\subsubsection{Electrons and phonons}   
\label{sec:E0_2_electrons_phonons}

\begin{figure}[ht]
% \captionsetup{width=\textwidth} 
\includegraphics[width=\linewidth]{./figures_Paper1/spec_filling_mu1_v_0.4_0.8_O_11_eph.pdf}
\caption{(Colour online) Spectral function $A(\omega)/t^{* -1}$ (solid line) and occupation function $N(\omega)/t^{* -1}$ (dashed line) at $\Omega=11$ when electron-phonon interaction is switched off and on, for $v=0.4$ (a) and $v=0.8$ (b). The electron-phonon coupling is set to $g=0.8$ and the phonon cutoff frequency to $\omega_{ph}=0.1$. Default parameters are specified at the beginning of section~\ref{sec:results}.} 
\label{fig:spec_filling_mu1_v_0.4_0.8_O_11_eph}
\end{figure}

We discuss now the effect of acoustic phonons on the results obtained in the previous section, switching on the electron-phonon coupling $g$.

The current $j$ in presence of phonons in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(a) is slighty bigger than the \emph{only-electron} one for both $v$ when $\Omega\lesssim7$. This difference decreases increasing $\Omega$, until $\Omega\approx7$,  where a crossing takes place and the \emph{only-electron} current becomes bigger. Between $7\lesssim\Omega\lesssim14$, the current in presence of phonons follows the same behaviour of the \emph{only-electron} one, reaching for both $v$ its maximum, also located at $\Omega\approx 11$, but it shows a clear suppression in magnitude, occuring especially around the peak at $\Omega\approx 11$. For $\Omega\gtrsim14$ the current with phonons for both $v$ goes down until the minimum for $\Omega\approx20$ as before.

The double occupation $N_D$ with phonons (Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(b)) for both $v$ remains bigger and follows the behaviour of the corresponding \emph{only-electron} counterpart within all the $\Omega$-range considered.

The spectral features including electron-phonon interaction shown in Fig.\ref{fig:spec_filling_mu1_v_0.4_0.8_O_11_eph} display a redistribution of the spectral weight towards the edges of the LHB and UHB, closing the gap and a suppression of the peaks of the bands. Consequently, the occupation of positive energy states is slightly shifted to the bottom of the UHB respect to the case without phonons, as the occupation function shows. The spectral function with phonons is then more broadened and tends to fill the effective gap $\Delta_{\textrm{eff}}$, as anticipated in Sec.\ref{sec:scheme_electrons_phonons}.

Such feature explains why the current in presence of phonons in (Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(a)) is slighty bigger in magnitude respect to the \emph{only-electron} one for both $v$ for $\Omega\lesssim7$. Such driving frequencies can excite across the gap only electrons coming from the upper edge of the LHB and due to $\Delta_{\textrm{eff,ph}}<\Delta_{\textrm{eff}}$, for the same $\Omega$ more photoexcited electrons end up in the UHB respect to the \emph{only-electron} case, with a consequent increase of the photocurrent. For example, Fig.\ref{fig:spec_filling_mu1_v_0.4_0.8_O_11_eph}(a)-(b) shows that an electron excited with $\Omega=4-5$ from the upper edge of the LHB ends close to the lower edge of UHB where $A(\omega)$ with phonons is slightly bigger than the \emph{only-electron} one.

We explain instead the suppression of the current with phonons respect to \emph{only-electron} one in the range $7\lesssim\Omega\lesssim14$, for both $v$, observing that for driving frequencies around the $j-$peak at $\Omega\approx 11$ the photoexcited electron in the UHB can come from three regions of LHB. Looking at Fig. \ref{fig:spec_filling_mu1_v_0.4_0.8_O_11_eph}(a)-(b), an electron can in fact be excited from the lower edge of LHB to lower edge of the UHB, from the middle of the LHB to the middle of UHB or from upper edge of LHB to the upper edge of the UHB. In the first and third case the electron comes and ends up in $\omega$-regions where the spectral function in presence of phonons has slightly more spectral weight than the \emph{only-electron} one, while in the second case the electron is excited between $\omega$-regions in which the \emph{only-electron} $A(\omega)$ is clearly bigger in magnitude than the one in presence of phonons. Overall, the dominant scattering process is the second one, yielding an higher current when only electrons are taken into account.

\pgcomm{Maybe this explanation above related to tunneling current}

Regarding the trend of double occupation $N_D$ with phonons for both $v$ in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(b), we notice from Fig.\ref{fig:spec_filling_mu1_v_0.4_0.8_O_11_eph} that, for positive energies,  the occupation function in presence of phonons is almost always bigger than the \emph{only-electron} one.

We discuss now the effect of phonons on DE/IO processes, as outlined in Sec.\ref{sec:E0_2_only_electrons}.

The presence of phonons enhances slightly the current in almost all the region in which only DE take place (until $\Omega\lesssim7$, while the DE region ends at $\Omega\approx8$). They suppress the current in the range $7\lesssim\Omega\lesssim14$, where IO is the dominant electronic scattering process for $v=0.4$ and DE for $v=0.8$. This is confirmed by Fig.\ref{fig:j_vs_omega_mu1_v_0.4_0.8_E0_2_sweep_omegaph}, that shows that the effect of acoustic phonons on the observables is slightly boosted decreasing the soft cutoff phonon frequency $\omega_{ph}$, as the comparison with Fig.\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph} highlights \footnote{Decreasing $\omega_{ph}$, the acoustic phonon modes linear dispersion is always more truncated and increased in magnitude. Therefore the maximal value of the reciprocal lattice vector $\vec{q}_{\text{max}}$ such that $\omega_{\text{ph}}=\omega(\vec{q}_{\text{max}})$ \cite{ma.ga.22u} is reduced and consequently the dissipation by acoustic phonons is more effective.}.

The results above suggest that the effect of acoustic phonons on the electronic scattering processes is the same, independently from their DE or IO origin, in fact they don't change drastically the interaction between the electrons.

Moreover, their effect is independent of $v$, therefore independent of "how many" carriers are injected/dragged into/from the layer. Fig.\ref{fig:j_vs_omega_mu1_sweep_v_E0_2_eph} confirms such behaviour for the intermediate bath-layer couplings $v=0.5,0.6,0.7$, for which DE and IO at $\Omega\gtrsim8$ are even more mixed and hard to identify, together with their features \footnote{We don't consider smaller $v$ and smaller $E_0$ because they give a really slow convergence of DMFT loop. Moreover, the observables' magnitude becomes comparable with numerical fluctuations caused by numerical precision issues.}.

\pgcomm{Are there some confirmations in literature regarding the effects of the phonons I observed?}

\begin{figure}[ht] 
% \captionsetup{width=\textwidth} 
\includegraphics[width=\linewidth]{./figures_Paper1/j_vs_omega_mu1_sweep_v_E0_2_eph.pdf}
\caption{(Colour online) $\Omega$-dependence of time-averaged steady-state current $j$ (in units of $j_0=\frac{qt^*}{\hbar a^2}$) (a) and double occupancy $N_D$ (b), for $v=0.5,0.6,0.7$, when electron-phonon interaction is switched off and on. The electron-phonon coupling is set to $g=0.8$ and the phonon cutoff frequency to $\omega_{ph}=0.1$. Default parameters are specified at the beginning of section~\ref{sec:results}.} 
\label{fig:j_vs_omega_mu1_sweep_v_E0_2_eph}
\end{figure}

\begin{figure}[ht] 
% \captionsetup{width=\textwidth} 
\includegraphics[width=\linewidth]{./figures_Paper1/j_vs_omega_mu1_v_0.4_0.8_E0_2_sweep_omegaph.pdf}
\caption{(Colour online) $\Omega$-dependence of time-averaged steady-state current $j$ (in units of $j_0=\frac{qt^*}{\hbar a^2}$) (a) and double occupancy $N_D$ (b), for $v=0.4,0.8$, at  phonon cutoff frequencies $\omega_{ph}=0.025,0.05$. The electron-phonon coupling is set to $g=0.8$. Default parameters are specified at the beginning of section~\ref{sec:results}.} 
\label{fig:j_vs_omega_mu1_v_0.4_0.8_E0_2_sweep_omegaph}
\end{figure}

\newpage

\subsection{Higher $E_0$}
\label{sec:higher_E0}

\begin{figure*}[ht] 
\includegraphics[width=\textwidth]{./figures_Paper1/j_vs_omega_mu1_v_0.4_0.8_eph_E0_3_4.pdf}
% \captionsetup{width=\textwidth}
\caption{(Colour online) $\Omega$-dependence of time-averaged steady-state current $j$ (in units of $j_0=\frac{qt^*}{\hbar a^2}$) (a) and double occupancy $N_D$ (b), for $v=0.4,0.8$ at different electric field amplitudes $E_0=3,4$, when electron-phonon interaction is switched off and on. The electron-phonon coupling is set to $g=0.8$ and the phonon cutoff frequency to $\omega_{ph}=0.1$. Default parameters are specified at the beginning of section~\ref{sec:results}.} 
\label{fig:j_vs_omega_mu1_v_0.4_0.8_eph_E0_3_4}
\end{figure*}

\subsubsection{Only electrons}
\label{sec:higher_E0_only_electrons}

As for Sec.\ref{sec:E0_2_only_electrons}, we analyze first the results obtained without the electron-phonon interaction.

The trend of the current as a function of $\Omega$ for the two different $v$ at increasing $E_0$ in Fig.\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph_E0_3_4}(a) follows the one outlined in Sec. \ref{sec:E0_2_only_electrons}.

For both $E_0=3,4$ the current maximum, located around $\Omega\approx11.5$, is due mainly to IO for $v=0.4$ and mainly to DE for $v=0.8$, as the double occupation in Fig.\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph_E0_3_4}(b) clearly shows. These results are in accordance with Sec.\ref{sec:E0_2_only_electrons}. This is confirmed also by Fig.\ref{fig:spec_filling_mu1_v_0.4_0.8_E3_4_O_11.5_e}(a)-(b) in which is evident the bigger occupation of the UHB for $v=0.4$.

There are however some features to be discussed more in detail.

The magnitude of the current clearly increases with $E_0$ and there is a steeper increase of $j$ in the $\Omega$-region after $\Omega\approx8$ for both $v$ respect to $E_0=2$ (Fig.\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}). The current peak for $v=0.8$ becomes bigger than the corresponding one for $v=0.4$ increasing the electric field amplitude $E_0$. A small bump develops at $E_0=4$ for $v=0.4$ around $\Omega\approx6$. Its position, directly in the middle of DE region (Sec.\ref{sec:scheme_only_electrons}) suggests an origin due to DE \cite{so.do.18}.

\pgcomm{The position of the current peaks seem to have a linear dependence on $E_0$. (see mail). Putting here the plots would have taken really long time and maybe we don't even insert this part.}

Also the double occupation as a function of $\Omega$ for the two $v$ at increasing $E_0$ in Fig.\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph_E0_3_4}(b) follows the one outlined in Sec. \ref{sec:E0_2_only_electrons}. However, the magnitude of $N_D$ is enhanced clearly with $E_0$, especially the $N_D$ peaks for $v=0.4$, in comparison with the $E_0=2$ case in Fig.\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(b). Moreover, the difference in $N_D$ between the two $v$ at the same $E_0$ increases with $E_0$, as Fig.\ref{fig:spec_filling_mu1_v_0.4_0.8_E3_4_O_11.5_e} also shows.

Therefore, increasing $E_0$, we have an overall enhancement of the photocurrent and of double occupation. The current for $v=0.8$ in which DE play a major role is enhanced respect to the one $v=0.4$ coming mainly from IO. However, the latter experiences an extreme increase in both the observables $j$ and $N_D$, confirmed by Fig.\ref{fig:spec_filling_mu1_v_0.4_0.8_E3_4_O_11.5_e}.

\begin{figure}[ht]
% \captionsetup{width=\textwidth} 
\includegraphics[width=\linewidth]{./figures_Paper1/spec_filling_mu1_v_0.4_0.8_E3_4_O_11.5_e.pdf}
\caption{(Colour online) Spectral function $A(\omega)/t^{* -1}$ (solid line) and occupation function $N(\omega)/t^{* -1}$ (shaded area) at $\Omega=11.5$ for $v=0.4,0.8$ when electron-phonon interaction is switched off, for $E_0=3$ (a) and $E_0=4$ (b). Default parameters are specified at the beginning of section~\ref{sec:results}.} 
\label{fig:spec_filling_mu1_v_0.4_0.8_E3_4_O_11.5_e}
\end{figure}

\subsubsection{Electrons and phonons}
\label{sec:higher_E0_electrons_phonons}

As in Sec.\ref{sec:E0_2_electrons_phonons}, we discuss now the results obtained including the acoustic phonons.

The $\Omega$-dependence of the current with phonons respect to the \emph{only-electron} one follows for both $v$ and $E_0$ the behaviour outlined in Sec.\ref{sec:E0_2_electrons_phonons}, with two minor differences, namely the crossing between the currents with and without phonons, occurring in this case at $\Omega\approx8$ and the current peaks slighly shifted at $\Omega\approx11.5$. For the small bump at $E_0=4$, $v=0.4$ around $\Omega\approx6$ there is no difference whether the phonons are taken into account or not.

The double occupation $N_D$ with phonons (Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph_E0_3_4}(b)) for both $v$ and $E_0$ is bigger and goes like the corresponding \emph{only-electron} one over all the $\Omega$-range, similarly to Sec.\ref{sec:E0_2_electrons_phonons}.

However, for increasing $E_0$, the $N_D$-peak in presence of phonons for $v=0.4$, around $\Omega\approx11.5$, is clearly flattened on the relative \emph{only-electron} one. There is this tendency (even though really small) also for $v=0.8$.

The spectral features with the electron-phonon interaction remain the same as described in Sec.\ref{sec:E0_2_electrons_phonons}(see Fig.\ref{fig:spec_filling_mu1_v_0.4_0.8_O_11_eph}).

The effect of phonons on DE/IO processes as $E_0$ is increased is the same as discussed in Sec.\ref{sec:E0_2_electrons_phonons}. Overall, as Fig.\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph_E0_3_4}(a)-(b) show, their effect is independent of the electric field amplitude $E_0$, therefore independent of "how strong" electrons are driven from the external AC field.

\section{Conclusions}
\label{sec:conclusions}

We investigated the influence of fermion baths and phonons dissipation on electron transport and spectral properties of a Mott insulating layer driven to the non-equilibrium
steady state by an external AC field. In order to reproduce a possible Mott-based photovoltaic setup between metallic leads, we considered partially filled wide-band fermion baths, addressing the issue regarding how acoustic phonons dissipate the energy carried by photoexcited electrons. We demonstrated the importance of the coupling to fermion baths on the electron scattering process occurring at different driving frequencies and observed how the dissipation by phonons influences the photocurrent and the double occupation. We found a strong evidence that the dominant electron scattering mechanism responsible for the photocurrent peak is impact ionization at small couplings to the fermion baths, almost absent at higher couplings. Higher electric field amplitudes substantially boost the photocurrent and the double occupation, without modifying the picture above. Acoustic phonons dissipation slightly boosts the photocurrent for small driving frequencies and suppresses it at higher ones, in correspondence to the peak, disregarding the dominant electron scattering process taking place. Phonons effect isn't influenced from the bath-layer coupling value and the electric field amplitude.

These results suggest that in correlated layers weakly coupled to single layers or quantum dots, in turn connected to metallic leads, impact ionization may occur significantly. From the experimental point of view, such realization is employed, for example, to bridge semiconductor quantum dots to reservoirs through small molecules \cite{wa.mc.13,wa.bo.17}, to extract hot photoexcited carriers \cite{ti.ke.10,ca.wa.16}.

A positive aspect towards the future research in this direction is that a moderate electron-phonon coupling doesn't seem to suppress drastically the current, as our results show, and therefore in real materials, impact ionization might contribute consistently to overcome the Schockley-Queisser limit \cite{sh.qu.61}.

However, in order to address the occurrence of impact ionization in realistic setups, one should take into account the feedback of the electrons on the phonon dynamics with a self-consistent treatment and the effect of impurities scattering. Another step forward would be the extension to multiorbital systems \cite{pe.be.19} in a multilayer setup, to model oxide heterostructures \cite{as.bl.13,pe.be.19}, where the correlated region is made of multiple layers and photoexcited carriers are separated via an electric field gradient.

%  For electric field amplitudes in the sunlight range the generated photocurrent, even though small, could yield an efficiency exploitable for some applications. On the the other side, for experimental setups or scientific-based devices, a strong AC electric field, realized with a more concentrated light source like laser, would give a much bigger photocurrent with a broader range of future applications.

% In second instance, such model misses still some ingredients as impurities/defects scatterings, long-range Coulomb effects, a multilayer structure with an intrinsic electric field gradient separating the charges. All these additional elements are present in Mott materials as oxide heterostructures proposed as a prototype for Mott solar cells. At the present level there's no point in considering now such features towards a more realistic description, because all these additional ingredients would complicate and hide the basic mechanisms still to be clarified completely.

\section*{Acknowledgements}
This work was supported by the Austrian Science Fund (FWF) within Project P 33165-N, as well as NaWi Graz. The computational results presented have been obtained using the Vienna Scientific Cluster (VSC) and the D-Cluster Graz.

\bibliographystyle{prsty}   
% references in Phys Rev style
\bibliography{footnotes,references_database}

% \bibliographystyle{/afs/itp.tugraz.at/user/arrigoni/noneq-group/bibtex/prsty} 
%\bibliography{New_References,/afs/itp.tugraz.at/user/arrigoni/noneq-group/bibtex/references_database.bib}
% \bibliography{Additional_Refs.bib,references_database.bib}
%\bibliography{New_References,references_database.bib}

\end{document}

### 2022-07-21 figures_Paper1/energy_setup.tex
First draft 21.07.2022

\documentclass{standalone}

\usepackage{braket}   % braket notation
\usepackage{amsmath}  % math features
\usepackage{bm}       % bold greek letters

\usepackage{graphicx} % include images
\usepackage{xcolor}   % colors

\usepackage{pgfplots}
\pgfplotsset{compat=1.13}
\usetikzlibrary{math}
\usetikzlibrary{calc}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{decorations.pathmorphing}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{positioning}
\usetikzlibrary{fit}
\usetikzlibrary{matrix}
\usetikzlibrary{intersections}
\usetikzlibrary{bending}
\usepgfplotslibrary{fillbetween}

\pgfmathsetmacro{\PI}{3.141592654}

\renewcommand{\vec}[1]{\bm{#1}} % vectors in bold
\newcommand{\mat}[1]{\bm{#1}} % matrices in bold
\DeclareMathOperator*{\Tr}{Tr} % trace
\DeclareMathOperator{\TT}{T} % time-ordering operator
\DeclareMathOperator*{\RRe}{Re} % real part
\DeclareMathOperator*{\IIm}{Im} % real part
\DeclareMathOperator*{\sgn}{sgn} % sign function
\DeclareMathOperator*{\dd}{d} % differential
\DeclareMathOperator*{\ii}{i} % imaginary unit
\DeclareMathOperator*{\const}{const.} % constant
\DeclareMathOperator*{\DD}{D} % differential operator
\DeclareMathOperator*{\stat}{stat} % stationary
\DeclareMathOperator*{\sad}{sad} % saddlepoint
\DeclareMathOperator*{\linspan}{linspan} % saddlepoint
\newcommand{\irchi}[2]{\raisebox{\depth}{$#1\chi$}}      % inline chi
\DeclareRobustCommand{\rchi}{{\mathpalette\irchi\relax}}
\newcommand{\irpsi}[2]{\raisebox{\depth}{$#1\psi$}}      % inline psi
\DeclareRobustCommand{\rpsi}{{\mathpalette\irpsi\relax}}
\newcommand{\equalhat}{\mathrel{\stackon[1.5pt]{=}{\stretchto{%
    \scalerel*[\widthof{=}]{\wedge}{\rule{1ex}{3ex}}}{0.5ex}}}}

\definecolor{colorOne}{HTML}{323232}   % Anthrazit
\definecolor{colorTwo}{HTML}{004191}   % Mittelblau
\definecolor{colorThree}{HTML}{00BEFF} % Hellblau
% Helper Colors
\definecolor{hblue}{RGB}{0,112,255}    % Brandeis blue
\definecolor{hred}{RGB}{199,44,72}     % raspberry red
\definecolor{hgreen}{RGB}{50,205,50}   % lime green
\definecolor{horange}{RGB}{255,127,0}  % orange
\definecolor{hpurple}{RGB}{111,45,168} % grape
\definecolor{hyellow}{RGB}{255,211,0}  % cyber yellow
\definecolor{hgray}{HTML}{323232}      % anthrazit gray
\definecolor{hbrown}{RGB}{128,70,27}   % russet brown

% circled
\DeclareRobustCommand\circled[1]{\tikz[baseline=(char.base),scale=0.3]{
\node[shape=circle,draw,thick,inner sep=0.5pt,fill=white] (char) {#1};}}

\tikzstyle directmin=[postaction={decorate,decoration={markings,
    mark=at position .5 with {\arrow{stealth}}}}]
\tikzstyle directed=[postaction={decorate,decoration={markings,
    mark=at position .65 with {\arrow{stealth[color=black]}}}}]
\tikzstyle bluedirected=[postaction={decorate,decoration={markings,
    mark=at position .65 with {\arrow{stealth[color=hblue]}}}}]
\tikzstyle reddirected=[postaction={decorate,decoration={markings,
    mark=at position .65 with {\arrow{stealth[color=hred]}}}}]
\tikzstyle flatdirected=[postaction={decorate,decoration={markings,
    mark=at position .65 with {\arrow{Stealth[color=black,flex=0.75,length=5pt,width=10pt]}}}}]
\tikzstyle directmax=[postaction={decorate,decoration={markings,
    mark=at position .85 with {\arrow{stealth}}}}]

\tikzset{
    cheating dash/.code args={on #1 off #2}{
        % Use csname so catcode of @ doesn't have do be changed.
        \csname tikz@addoption\endcsname{%
            \pgfgetpath\currentpath%
            \pgfprocessround{\currentpath}{\currentpath}%
            \csname pgf@decorate@parsesoftpath\endcsname{\currentpath}{\currentpath}%
            \pgfmathparse{\csname pgf@decorate@totalpathlength\endcsname-#1}\let\rest=\pgfmathresult%
            \pgfmathparse{#1+#2}\let\onoff=\pgfmathresult%
            \pgfmathparse{max(floor(\rest/\onoff), 1)}\let\nfullonoff=\pgfmathresult%
            \pgfmathparse{max((\rest-\onoff*\nfullonoff)/\nfullonoff+#2, #2)}\let\offexpand=\pgfmathresult%
            \pgfsetdash{{#1}{\offexpand}}{0pt}}%
    }
}

\begin{document}

\begin{tikzpicture}[>=stealth]

% Figure 1

% \path[>=stealth,<->,shorten >=0.15cm,shorten <=0.15cm,out=-30,in=-150,line width=2pt] (2.5,0.5) edge (5,0.5);

% \filldraw[fill=hblue!50!white,draw=hblue,xshift=-2cm,rotate=-90] (-1,0) parabola[bend pos=0.5] bend +(0,2) +(3,0) -- cycle;

\path[>=stealth,<->,shorten >=0.5cm,shorten <=0.5cm,line width=2pt] (4.7,2.5) edge (4.7,5.5);

\filldraw[draw=hred,fill=hred!20!white] (2.5,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;

\filldraw[draw=hgreen,fill=hgreen!20!white] (0,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas

\path[>=stealth,line width=1pt] (2.5,2.75) edge (4.5,2.75);

\path[>=stealth,<->,shorten >=0.5cm,shorten <=0.5cm,line width=2pt] (0,1.5) edge (0,3.5);

\path[>=stealth,line width=1pt] (-2.5,2.25) edge (-0.5,2.25);

\filldraw[draw=hgreen,fill=hgreen!20!white] (0,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas

\filldraw[draw=hred,fill=hred!20!white] (-2.5,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;

\path[>=stealth,<->,shorten >=0.5cm,shorten <=0.5cm,line width=2pt] (-2.7,-0.5) edge (-2.7,2.5);

% text

\node at (3.5,4) [minimum size = 0.1 cm]{\textcolor{hred}{r-bath}}; 
\node at (1,4) [minimum size = 0.1 cm]{\textcolor{hgreen}{UH band}};
\node at (1,1) [minimum size = 0.1 cm]{\textcolor{hgreen}{LH band}};
\node at (-1.5,1) [minimum size = 0.1 cm]{\textcolor{hred}{l-bath}};

\node at (5.1,4) {\textcolor{black}{$W_{b}$}};

\node at (3.5,2.6) {\textcolor{black}{$\mu_r$}};  
\node at (-1.5,2.4) {\textcolor{black}{$\mu_l$}};

\node at (-3.1,1) {\textcolor{black}{$W_{b}$}};

\node at (1,2.5) {\textcolor{black}{$\Delta_{\textrm{eff}}$/$\Delta_{\textrm{eff,ph}}$}};

\node at (-2.7,5) {\bfseries(a)};

% Figure 2

\filldraw[draw=hred,fill=hred!20!white] (2.5,-3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;

\filldraw[draw=hgreen,fill=hgreen!20!white] (0,-3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas

\draw [->,>=Stealth,line width=1pt,decorate,decoration={snake,amplitude=0.2cm,segment length=0.4cm,pre length=0.4cm,post length=0.4cm},draw=hyellow] (-2.5,-2.5) -- (0,-3.5);

\filldraw[draw=hgreen,fill=hgreen!20!white] (0,-6) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas

\filldraw[draw=hred,fill=hred!20!white] (-2.5,-6) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;

% text

\node at (3.5,-2) [minimum size = 0.1 cm]{\textcolor{hred}{r-bath}}; 
\node at (1,-2) [minimum size = 0.1 cm]{\textcolor{hgreen}{UH band}};
\node at (1,-5) [minimum size = 0.1 cm]{\textcolor{hgreen}{LH band}};
\node at (-1.5,-5) [minimum size = 0.1 cm]{\textcolor{hred}{l-bath}};

\node at (-1,-2.7) {\textcolor{hyellow}{$\Omega$}};

\node at (-2.7,-1) {\bfseries(b)};

\draw[dotted,color=black,fill=white] (0.5,-5) circle[radius=3pt];

\path[color=hyellow,>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=120,in=210,line width=1pt] (0.5,-5) edge (0.8,-2);

\draw[color=black,fill=hgreen] (0.8,-2.1) circle[radius=3pt];

\path[color=hred,>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=-30,in=-150,line width=1pt] (0.8,-2.2) edge (3.2,-2);

% Figure 3

\filldraw[draw=hred,fill=hred!20!white] (2.5,-9) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;

\filldraw[draw=hgreen,fill=hgreen!20!white] (0,-9) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas

\draw [->,>=Stealth,line width=1pt,decorate,decoration={snake,amplitude=0.2cm,segment length=0.4cm,pre length=0.4cm,post length=0.4cm},draw=hyellow] (-2.5,-8.5) -- (-0.2,-9.5);

\filldraw[draw=hgreen,fill=hgreen!20!white] (0,-12) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas

\filldraw[draw=hred,fill=hred!20!white] (-2.5,-12) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;

% text

\node at (3.5,-8) [minimum size = 0.1 cm]{\textcolor{hred}{r-bath}}; 
\node at (1,-8) [minimum size = 0.1 cm]{\textcolor{hgreen}{UH band}};
\node at (1,-11) [minimum size = 0.1 cm]{\textcolor{hgreen}{LH band}};
\node at (-1.5,-11) [minimum size = 0.1 cm]{\textcolor{hred}{l-bath}};

\node at (-1,-8.7) {\textcolor{hyellow}{$\Omega$}};

\node at (-2.7,-7) {\bfseries(c)};

\draw[dotted,color=black,fill=white] (0.5,-11.3) circle[radius=3pt];

\path[color=hyellow,>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=120,in=240,line width=1pt] (0.5,-11.3) edge (0.4,-7.2);

\draw[dotted,color=black,fill=white] (0.4,-7.3) circle[radius=3pt];

\path[>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=-60,in=-180,line width=1pt] (0.4,-7.3) edge (1.6,-8);

\draw[color=black,fill=hgreen] (1.6,-8) circle[radius=3pt];

\path[color=hred,>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=30,in=150,line width=1pt] (1.6,-8) edge (3.6,-8);

\draw[dotted,color=black,fill=white] (0.9,-10.3) circle[radius=3pt];

\path[>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=120,in=-150,line width=1pt] (0.9,-10.3) edge (0.7,-8.8);

\draw[color=black,fill=hgreen] (0.67,-8.75) circle[radius=3pt];

\path[color=hred,>=stealth,->,shorten >=0.15cm,shorten  <=0.15cm,out=-30,in=210,line width=1pt] (0.7,-8.7) edge (3.6,-8.4);

% \path[>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=-30,in=-150,line width=1pt] (0.8,-2.2) edge (3.2,-2);

\end{tikzpicture}

\end{document}

### 2022-07-21 figures_Paper1/setup.tex
First draft 21.07.2022

\documentclass{standalone}

\usepackage{amsmath}
\usepackage{pgfplots}
\pgfplotsset{compat=1.16}
\usepackage{tikz-3dplot}
\usetikzlibrary{calc}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{decorations.pathmorphing}

\usepackage{xcolor}
\usepackage{amsmath}

\definecolor{hblue}{RGB}{0,112,255}    % Brandeis blue
\definecolor{hred}{RGB}{199,44,72}     % raspberry red
\definecolor{hgreen}{RGB}{50,205,50}   % lime green
\definecolor{horange}{RGB}{255,127,0}  % orange
\definecolor{hpurple}{RGB}{111,45,168} % grape
\definecolor{hyellow}{RGB}{255,211,0}  % cyber yellow
\definecolor{hgray}{HTML}{323232}      % anthrazit gray

\begin{document}
\begin{tikzpicture}[>=Stealth]
\begin{axis}[
axis lines=none,
view={150}{10},
xmin=-1,xmax=6,
ymin=0,ymax=4,
zmin=-2,zmax=3.,
xlabel=$x$,
ylabel=$y$,
zlabel=$z$,
scale=1
]

% right lead 
% balls

\foreach \x in {-1,0}          % loop for balls 
  \foreach \y in {0,1,...,3}
    \foreach \z in {0,1,...,3}
       \addplot3 [only marks,mark=ball,mark size=2pt,ball color=hblue,line width=0.1pt] coordinates{(\x,\y,\z)};

% lines

% (axis cs:x,y,z)

\pgfplotsinvokeforeach{0,1,...,3} {
   \draw[color=hblue] (axis cs:-1,#1,0) -- (axis cs:-1,#1,3);
   \draw[color=hblue] (axis cs:-1,#1,0) -- (axis cs:0,#1,0);
   \draw[color=hblue] (axis cs:-1,#1,1) -- (axis cs:0,#1,1);
   \draw[color=hblue] (axis cs:-1,#1,2) -- (axis cs:0,#1,2);
   \draw[color=hblue] (axis cs:-1,#1,3) -- (axis cs:0,#1,3);
};

% lines

\pgfplotsinvokeforeach{0,1,...,3} {
   \draw[color=hblue] (axis cs:-1,0,#1) -- (axis cs:-1,3,#1);
};
\pgfplotsinvokeforeach{0,1,...,3} {
   \draw[color=hblue] (axis cs:0,#1,0) -- (axis cs:0,#1,3);
};
\pgfplotsinvokeforeach{0,1,...,3} {
   \draw[color=hblue] (axis cs:0,0,#1) -- (axis cs:0,3,#1);
};

% bottom
% \fill[color=hblue,opacity=0.2] (axis cs:1,0,0) -- (axis cs:0,0,0) -- (axis cs:0,3,0) -- (axis cs:1,3,0) -- cycle;
% back
% \fill[color=hblue,opacity=0.2] (axis cs:1,0,0) -- (axis cs:0,0,0) -- (axis cs:0,0,3) -- (axis cs:1,0,3) -- cycle;

% front
\fill[color=hblue,opacity=0.5] (axis cs:0,0,0) -- (axis cs:0,3,0) -- (axis cs:0,3,3) -- (axis cs:0,0,3) -- cycle;
% left side
\fill[color=hblue,opacity=0.5] (axis cs:0,3,0) -- (axis cs:-1,3,0) -- (axis cs:-1,3,3) -- (axis cs:0,3,3) -- cycle;
% top
\fill[color=hblue,opacity=0.5] (axis cs:0,3,3) -- (axis cs:-1,3,3) -- (axis cs:-1,0,3) -- (axis cs:0,0,3) -- cycle;

% interface right bath

\pgfplotsinvokeforeach{0,1,...,3} {
   \draw[color=horange] (axis cs:0,#1,0) -- (axis cs:1,#1,0);
   \draw[color=horange] (axis cs:0,#1,1) -- (axis cs:1,#1,1);
   \draw[color=horange] (axis cs:0,#1,2) -- (axis cs:1,#1,2);
   \draw[color=horange] (axis cs:0,#1,3) -- (axis cs:1,#1,3);
};

% ni-layer belonging to right bath

\fill[color=hred,opacity=0.5] (axis cs:1,0,0) -- (axis cs:1,3,0) -- (axis cs:1,3,3) -- (axis cs:1,0,3) -- cycle;

% lines
\pgfplotsinvokeforeach{0,1,...,3} {
   \draw[color=hred] (axis cs:1,#1,0) -- (axis cs:1,#1,3);
};
\pgfplotsinvokeforeach{0,1,...,3} {
   \draw[color=hred] (axis cs:1,0,#1) -- (axis cs:1,3,#1);
};

% balls
\foreach \y in {0,1,...,3}
  \foreach \z in {0,1,...,3}
     \addplot3 [only marks,mark=ball,mark size=2pt,ball color=hred,line width=0.1pt] coordinates{(1,\y,\z)};

% interface ni layer - Hubbard layer
\pgfplotsinvokeforeach{0,1,...,3} {
   \draw[color=black] (axis cs:1,#1,0) -- (axis cs:2,#1,0);
   \draw[color=black] (axis cs:1,#1,1) -- (axis cs:2,#1,1);
   \draw[color=black] (axis cs:1,#1,2) -- (axis cs:2,#1,2);
   \draw[color=black] (axis cs:1,#1,3) -- (axis cs:2,#1,3);
};

% central layer
\fill[color=hgreen,opacity=0.5] (axis cs:2,0,0) -- (axis cs:2,3,0) -- (axis cs:2,3,3) -- (axis cs:2,0,3) -- cycle;
% lines
\pgfplotsinvokeforeach{0,1,...,3} {
   \draw[color=hgreen] (axis cs:2,#1,0) -- (axis cs:2,#1,3);
};
\pgfplotsinvokeforeach{0,1,...,3} {
   \draw[color=hgreen] (axis cs:2,0,#1) -- (axis cs:2,3,#1);
};
% balls
\foreach \y in {0,1,...,3}
  \foreach \z in {0,1,...,3}
     \addplot3 [only marks,mark=ball,mark size=3pt,ball color=hgreen,line width=0.1pt] coordinates{(2,\y,\z)};

% interface ni layer - Hubbard layer
\pgfplotsinvokeforeach{0,1,...,3} {
   \draw[color=black] (axis cs:2,#1,0) -- (axis cs:3,#1,0);
   \draw[color=black] (axis cs:2,#1,1) -- (axis cs:3,#1,1);
   \draw[color=black] (axis cs:2,#1,2) -- (axis cs:3,#1,2);
   \draw[color=black] (axis cs:2,#1,3) -- (axis cs:3,#1,3);
};

% ni-layer belonging to left bath

\fill[color=hred,opacity=0.5] (axis cs:3,0,0) -- (axis cs:3,3,0) -- (axis cs:3,3,3) -- (axis cs:3,0,3) -- cycle;

% lines
\pgfplotsinvokeforeach{0,1,...,3} {
   \draw[color=hred] (axis cs:3,#1,0) -- (axis cs:3,#1,3);
};
\pgfplotsinvokeforeach{0,1,...,3} {
   \draw[color=hred] (axis cs:3,0,#1) -- (axis cs:3,3,#1);
};

% balls
\foreach \y in {0,1,...,3}
  \foreach \z in {0,1,...,3}
     \addplot3 [only marks,mark=ball,mark size=2pt,ball color=hred,line width=0.1pt] coordinates{(3,\y,\z)};

% interface left bath

\pgfplotsinvokeforeach{0,1,...,3} {
   \draw[color=horange] (axis cs:3,#1,0) -- (axis cs:4,#1,0);
   \draw[color=horange] (axis cs:3,#1,1) -- (axis cs:4,#1,1);
   \draw[color=horange] (axis cs:3,#1,2) -- (axis cs:4,#1,2);
   \draw[color=horange] (axis cs:3,#1,3) -- (axis cs:4,#1,3);
};

% left lead
% balls
\foreach \x in {4,5}
  \foreach \y in {0,1,...,3}
    \foreach \z in {0,1,...,3}
       \addplot3 [only marks,mark=ball,mark size=2pt,ball color=hblue,line width=0.1pt] coordinates{(\x,\y,\z)};

% lines
\pgfplotsinvokeforeach{0,1,...,3} {
   \draw[color=hblue] (axis cs:4,#1,0) -- (axis cs:4,#1,3);
   \draw[color=hblue] (axis cs:4,#1,0) -- (axis cs:5,#1,0);
   \draw[color=hblue] (axis cs:4,#1,1) -- (axis cs:5,#1,1);
   \draw[color=hblue] (axis cs:4,#1,2) -- (axis cs:5,#1,2);
   \draw[color=hblue] (axis cs:4,#1,3) -- (axis cs:5,#1,3);
};

\pgfplotsinvokeforeach{0,1,...,3} { % z-direction
   \draw[color=hblue] (axis cs:4,0,#1) -- (axis cs:4,3,#1);
};
\pgfplotsinvokeforeach{0,1,...,3} {
   \draw[color=hblue] (axis cs:5,#1,0) -- (axis cs:5,#1,3);
};
\pgfplotsinvokeforeach{0,1,...,3} {
   \draw[color=hblue] (axis cs:5,0,#1) -- (axis cs:5,3,#1);
};

% bottom
% \fill[color=hblue,opacity=0.5] (axis cs:4,0,0) -- (axis cs:3,0,0) -- (axis cs:3,3,0) -- (axis cs:4,3,0) -- cycle;
% back
% \fill[color=hblue,opacity=0.5] (axis cs:4,0,0) -- (axis cs:3,0,0) -- (axis cs:3,0,3) -- (axis cs:4,0,3) -- cycle;

% front
\fill[color=hblue,opacity=0.5] (axis cs:5,0,0) -- (axis cs:5,3,0) -- (axis cs:5,3,3) -- (axis cs:5,0,3) -- cycle;
% left side
\fill[color=hblue,opacity=0.5] (axis cs:5,3,0) -- (axis cs:4,3,0) -- (axis cs:4,3,3) -- (axis cs:5,3,3) -- cycle;
% top
\fill[color=hblue,opacity=0.5] (axis cs:5,3,3) -- (axis cs:4,3,3) -- (axis cs:4,0,3) -- (axis cs:5,0,3) -- cycle;

% coordinates for light

\coordinate (top1) at (axis cs:2,0.5,3);
\coordinate (top2) at (axis cs:2,1.5,3);
\coordinate (top3) at (axis cs:2,2.5,3);

% arrows for hoppings

\node at (axis cs:-0.1,3.5,-0.15) {\textcolor{hblue}{$\mu_r$}};
\node at (axis cs:5,3.5,-0.15) {\textcolor{hblue}{$\mu_l$}};
\node at (axis cs:2,2.8,-0.35) {\textcolor{hgreen}{$U,g$}};
\node at (axis cs:3.5,3,-0.25) {\textcolor{horange}{$\Gamma$}};
\node at (axis cs:1.3,3,-0.25) {\textcolor{black}{$v$}};

\end{axis}

% cw-light

\draw [->,>=Stealth,line width=2pt,decorate,decoration={snake,amplitude=0.2cm,segment length=0.4cm,pre length=0.4cm,post length=0.4cm},draw=hyellow] ($ (top1)+(120:2) $) -- (top1);
\draw [->,>=Stealth,line width=2pt,decorate,decoration={snake,amplitude=0.2cm,segment length=0.4cm,pre length=0.4cm,post length=0.4cm},draw=hyellow] ($ (top2)+(115:2) $) -- (top2);
\draw [->,>=Stealth,line width=2pt,decorate,decoration={snake,amplitude=0.2cm,segment length=0.4cm,pre length=0.4cm,post length=0.4cm},draw=hyellow] ($ (top3)+(110:2) $) -- (top3);
% \draw [->,>=Stealth,line width=2pt,decorate,decoration={snake,amplitude=0.2cm,segment length=0.8cm,pre length=0.4cm,post length=0.4cm},draw=hyellow] ($ (top4)+(105:3) $) -- (top4);

% pulsed light
% \begin{scope}[decoration={markings,
% mark=at position 0.0 with {{\arrowreversed[hyellow,xshift=-6]{Stealth}}}},
% domain=-1.6:1.5,samples=300,xshift=8.4cm,yshift=4.6cm,rotate=110]
% \draw[postaction={decorate},draw=hyellow,line width=2pt] plot (\x,{0.8*exp(-\x*\x/(2.*0.3))*sin(10.*\x r)});
% \end{scope}

\end{tikzpicture}
\end{document}

### 2022-07-21 figures_Paper1/spec_filling_mu1_v_0.4_0.8_E3_4_O_11.5_e.tex
First draft 21.07.2022

\documentclass[10pt]{standalone}
\usepackage[english]{babel} % language
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}

%%%%%%%%%%%%
% PGFPLOTS %
%%%%%%%%%%%%
\usepackage{pgfplots}    % pgfplots 
\usepackage{tikz-3dplot} % 3D coordinate frames
\usepackage{gnuplot-lua-tikz}
\usepgfplotslibrary{fillbetween}
\usepgfplotslibrary{colormaps}
\pgfplotsset{compat=1.17}
% \pgfplotsset{trig format plots=rad}

%%%%%%%%%%%%%%%%% 
% TikZ packages %
%%%%%%%%%%%%%%%%%
\usetikzlibrary{math}
\usetikzlibrary{calc}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{decorations.pathmorphing}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{positioning}
\usetikzlibrary{fit}
\usetikzlibrary{matrix}
\usetikzlibrary{intersections}
\usetikzlibrary{bending}
\usetikzlibrary{pgfplots.groupplots}

\usepackage{xcolor}
\usepackage{braket}

% alternative
%\definecolor{hturquoise}{RGB}{0,206,209}   %turquoise
%\definecolor{hred}{RGB}{255,0,0}             % red 
%\definecolor{hbrown}{RGB}{128,70,27}    % russet brown 
%\definecolor{hpurple}{RGB}{111,45,168} % grape
%\definecolor{hyellow}{RGB}{255,255,0}   % yellow
\definecolor{hgray}{HTML}{323232}      % anthrazit gray 
%\definecolor{hgreen}{RGB}{50,205,50}   % dark lime green 
%\definecolor{hmagenta}{RGB}{255,0,255}   % magenta

\definecolor{hcoral}{RGB}{255,127,80}     % coral
\definecolor{hblue}{RGB}{0,112,255}        % Brandeis blue
\definecolor{hred}{RGB}{199,44,72}         % raspberry red
\definecolor{hlime}{RGB}{0,255,0}            % lime green
\definecolor{hyellow}{RGB}{255,211,0}     % cyber yellow
\definecolor{hcyan}{RGB}{0,255,255}       % bright cyan

\DeclareMathAlphabet{\pazocal}{OMS}{zplm}{m}{n}
\newcommand{\capcali}{\pazocal{I}}
\newcommand{\capcalr}{\pazocal{R}}

\begin{document}

\begin{tikzpicture}[>=Stealth]

% foreground, background
\pgfdeclarelayer{background}
\pgfdeclarelayer{foreground}
\pgfdeclarelayer{main} 
\pgfsetlayers{background,main,foreground}

\begin{groupplot}[
group style={
group size=2 by 1,
xticklabels at=edge bottom,  
yticklabels at=edge left,
%vertical sep=10pt,
horizontal sep=20pt
}, 
minor tick num=1, 
width=0.6\textwidth,
height=0.6\textwidth    
]

% 1° figure

\nextgroupplot[
xmin=-15.,      
xmax=15., 
ymin=0.00, 
ymax=0.09,   
minor tick num=1, 
% grid=both,
xlabel={$\omega/t^{*}$},
ylabel={$A(\omega)/t^{*-1}$},
legend style={at={(axis cs:-9.3,0.017)},anchor=north,mark options={scale=0.85},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
legend cell align=left,
clip mode=individual,
clip marker paths=true, 
xtick={-15,-10,-5,0,5,10,15},
ytick={0.00,0.03,0.06,0.09},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012,\smash{\raisebox{-0.8\height}{5}}},
x tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd},
y tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill, 
    precision=0, 
    /tikz/.cd}
]

\addlegendimage{solid,color=hblue,scale={1.0},line width=1pt}
\addlegendentry{$v=0.4$};
\addlegendimage{solid,color=hred,scale={1.0},line width=1pt} 
\addlegendentry{$v=0.8$};

% % % % % % % %  PLOTS

% \draw (axis cs:4,0) -- (axis cs:10,0.01);

\addplot[solid,raw gnuplot,color=hblue,line width=1pt] gnuplot {
plot './Green_hyb0.4E3_O11.5.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.4E3_O11.5,solid,raw gnuplot,color=hblue,line width=1pt,opacity=0.0]gnuplot {
plot "./neq_distr_f_filling_hyb0.4E3_O11.5.dat" u 1:3 w l;
};

\addplot[solid,raw gnuplot,color=hred,line width=1pt] gnuplot {
plot './Green_hyb0.8E3_O11.5.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.8E3_O11.5,solid,raw gnuplot,color=hred,line width=1pt,opacity=0.0]gnuplot {
plot "./neq_distr_f_filling_hyb0.8E3_O11.5.dat" u 1:3 w l;
};

 \path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
 \addplot [fill=hblue,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4E3_O11.5 and xaxis,soft clip={domain=-15:15}]; 
 \addplot [fill=hred,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8E3_O11.5 and xaxis,soft clip={domain=-15:15}];

 \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(a)};
 \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$E_0=3$};

% 2° figure

\nextgroupplot[
xmin=-15.,     
xmax=15., 
ymin=0.00, 
ymax=0.09,   
minor tick num=1, 
% grid=both,
xlabel={$\omega/t^{*}$},
% ylabel={$A(\omega)/t^{*-1}$},
legend style={at={(axis cs:-9.3,0.017)},anchor=north,mark options={scale=0.85},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
legend cell align=left,
clip mode=individual,
clip marker paths=true, 
xtick={-15,-10,-5,0,5,10,15},
ytick={0.00,0.03,0.06,0.09},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012,\smash{\raisebox{-0.8\height}{5}}},
x tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd},
y tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd}
]

\addlegendimage{solid,color=hcoral,scale={1.0},line width=1pt}
\addlegendentry{$v=0.4$};
\addlegendimage{solid,color=hlime,scale={1.0},line width=1pt} 
\addlegendentry{$v=0.8$};

% % % % % % % %  PLOTS

% \draw (axis cs:4,0) -- (axis cs:10,0.01);

\addplot[solid,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
plot './Green_hyb0.4E4_O11.5.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.4E4_O11.5,solid,raw gnuplot,color=hcoral,line width=1pt,opacity=0.0]gnuplot {
plot "./neq_distr_f_filling_hyb0.4E4_O11.5.dat" u 1:3 w l;
};

\addplot[solid,raw gnuplot,color=hlime,line width=1pt] gnuplot {
plot './Green_hyb0.8E4_O11.5.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.8E4_O11.5,solid,raw gnuplot,color=hlime,line width=1pt,opacity=0.0]gnuplot {
plot "./neq_distr_f_filling_hyb0.8E4_O11.5.dat" u 1:3 w l;
};

 \path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
 \addplot [fill=hcoral,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4E4_O11.5 and xaxis,soft clip={domain=-15:15}]; 
 \addplot [fill=hlime,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8E4_O11.5 and xaxis,soft clip={domain=-15:15}];

 \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(b)};
 \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$E_0=4$};

\end{groupplot}

 \end{tikzpicture}

\end{document}

### 2022-07-21 figures_Paper1/spec_filling_mu1_v_0.4_0.8_O_11_eph.tex
First draft 21.07.2022

--- 2022-07-21 figures_Paper1/spec_filling_mu1_v_0.4_0.8_E3_4_O_11.5_e.tex
@@
 \addlegendimage{solid,color=hblue,scale={1.0},line width=1pt}
-\addlegendentry{$v=0.4$};
+\addlegendentry{$el$};
 \addlegendimage{solid,color=hred,scale={1.0},line width=1pt} 
-\addlegendentry{$v=0.8$};
+\addlegendentry{$el+ph$};
 
@@
 \addplot[solid,raw gnuplot,color=hblue,line width=1pt] gnuplot {
-plot './Green_hyb0.4E3_O11.5.dat' u 1:(-1/3.1415)*($3) w l;
+plot './Green_hyb0.4O11.dat' u 1:(-1/3.1415)*($3) w l;
 };
 
-\addplot[name path=neq_distr_f_filling_hyb0.4E3_O11.5,solid,raw gnuplot,color=hblue,line width=1pt,opacity=0.0]gnuplot {
-plot "./neq_distr_f_filling_hyb0.4E3_O11.5.dat" u 1:3 w l;
+\addplot[dashed,raw gnuplot,color=hblue,line width=1pt] gnuplot {
+plot './neq_distr_f_filling_hyb0.4O11.dat' u 1:3 w l;
 };
@@
 \addplot[solid,raw gnuplot,color=hred,line width=1pt] gnuplot {
-plot './Green_hyb0.8E3_O11.5.dat' u 1:(-1/3.1415)*($3) w l;
+plot './Green_hyb0.4O11ph.dat' u 1:(-1/3.1415)*($3) w l;
 };
 
-\addplot[name path=neq_distr_f_filling_hyb0.8E3_O11.5,solid,raw gnuplot,color=hred,line width=1pt,opacity=0.0]gnuplot {
-plot "./neq_distr_f_filling_hyb0.8E3_O11.5.dat" u 1:3 w l;
+\addplot[dashed,raw gnuplot,color=hred,line width=1pt] gnuplot {
+plot './neq_distr_f_filling_hyb0.4O11ph.dat' u 1:3 w l;
 };
 
- \path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
- \addplot [fill=hblue,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4E3_O11.5 and xaxis,soft clip={domain=-15:15}]; 
- \addplot [fill=hred,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8E3_O11.5 and xaxis,soft clip={domain=-15:15}];
-
  \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(a)};
- \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$E_0=3$};
+ \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$v=0.4$};
 
@@
 \addlegendimage{solid,color=hcoral,scale={1.0},line width=1pt}
-\addlegendentry{$v=0.4$};
+\addlegendentry{$el$};
 \addlegendimage{solid,color=hlime,scale={1.0},line width=1pt} 
-\addlegendentry{$v=0.8$};
+\addlegendentry{$el+ph$};
 
@@
 \addplot[solid,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
-plot './Green_hyb0.4E4_O11.5.dat' u 1:(-1/3.1415)*($3) w l;
+plot './Green_hyb0.8O11.dat' u 1:(-1/3.1415)*($3) w l;
 };
 
-\addplot[name path=neq_distr_f_filling_hyb0.4E4_O11.5,solid,raw gnuplot,color=hcoral,line width=1pt,opacity=0.0]gnuplot {
-plot "./neq_distr_f_filling_hyb0.4E4_O11.5.dat" u 1:3 w l;
+\addplot[dashed,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
+plot './neq_distr_f_filling_hyb0.8O11.dat' u 1:3 w l;
 };
@@
 \addplot[solid,raw gnuplot,color=hlime,line width=1pt] gnuplot {
-plot './Green_hyb0.8E4_O11.5.dat' u 1:(-1/3.1415)*($3) w l;
+plot './Green_hyb0.8O11ph.dat' u 1:(-1/3.1415)*($3) w l;
 };
 
-\addplot[name path=neq_distr_f_filling_hyb0.8E4_O11.5,solid,raw gnuplot,color=hlime,line width=1pt,opacity=0.0]gnuplot {
-plot "./neq_distr_f_filling_hyb0.8E4_O11.5.dat" u 1:3 w l;
+\addplot[dashed,raw gnuplot,color=hlime,line width=1pt] gnuplot {
+plot './neq_distr_f_filling_hyb0.8O11ph.dat' u 1:3 w l;
 };
 
- \path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
- \addplot [fill=hcoral,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4E4_O11.5 and xaxis,soft clip={domain=-15:15}]; 
- \addplot [fill=hlime,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8E4_O11.5 and xaxis,soft clip={domain=-15:15}];
-
  \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(b)};
- \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$E_0=4$};
+ \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$v=0.8$};
 

### 2022-07-21 figures_Paper1/spec_filling_mu1_v_0.4_0.8_O_5_11_e.tex
First draft 21.07.2022

--- 2022-07-21 figures_Paper1/spec_filling_mu1_v_0.4_0.8_O_11_eph.tex
@@
 minor tick num=1, 
-% grid=both,
+grid=both,
 xlabel={$\omega/t^{*}$},
 ylabel={$A(\omega)/t^{*-1}$},
-legend style={at={(axis cs:-9.3,0.017)},anchor=north,mark options={scale=0.85},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
+legend style={at={(axis cs:0,0.1)},anchor=north,mark options={scale=1.0},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
+legend cell align=left,
+clip mode=individual,
+clip marker paths=true, 
+xtick={-15,-10,-5,0,5,10,15},
+ytick={0.00,0.03,0.06,0.09},
+% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012},
+% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012,\smash{\raisebox{-0.8\height}{5}}},
+x tick label style={
+    /pgf/number format/.cd,
+    fixed,
+    fixed zerofill,
+    precision=0,
+    /tikz/.cd},
+y tick label style={
+    /pgf/number format/.cd,
+    fixed,
+    fixed zerofill,
+    precision=0, 
+    /tikz/.cd}
+]
+
+\addlegendimage{solid,color=hcoral,scale={1.0},line width=1pt}
+\addlegendentry{$v=0.4$};
+\addlegendimage{solid,color=hlime,scale={1.0},line width=1pt} 
+\addlegendentry{$v=0.8$};
+
+% \addplot +[dashed,very thin,color=hblue,mark=none] coordinates {(-2.55, 0.0) (-2.55, 0.035)};
+% \addplot +[dashed,very thin,color=hblue,mark=none] coordinates {(0.525, 0.0) (0.525, 0.035)};
+% \draw [stealth-stealth,thick,color=hblue](-2.55, 0.015) -- (0.525, 0.015);
+
+% \addplot +[dashed,very thin,color=hred,mark=none] coordinates {(2.55, 0.0) (2.55, 0.035)};
+% \addplot +[dashed,very thin,color=hred,mark=none] coordinates {(-0.525, 0.0) (-0.525, 0.035)};
+% \draw [stealth-stealth,thick,color=hred](2.55, 0.02) -- (-0.525, 0.02);
+
+% \draw [-stealth,thick,color=hgray](0.35, 0.0055) -- (0.45, 0.004);
+% \draw [-stealth,thick,color=hgray](-0.35, 0.0055) -- (-0.45, 0.004);
+
+% \draw [-stealth,thick,color=hgray](2.0, 0.0045) -- (2.2, 0.003);
+% \draw [-stealth,thick,color=hgray](-2.0, 0.0045) -- (-2.2, 0.003);
+
+% % % % % % % %  PLOTS
+
+% \draw (axis cs:4,0) -- (axis cs:10,0.01);
+
+\addplot[solid,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
+plot './Green_hyb0.4O5.dat' u 1:(-1/3.1415)*($3) w l;
+};
+
+\addplot[name path=neq_distr_f_filling_hyb0.4O5,solid,raw gnuplot,color=hcoral,line width=1pt,opacity=0.0] gnuplot {
+plot "neq_distr_f_filling_hyb0.4O5.dat" u 1:3 w l;
+};
+
+\addplot[solid,raw gnuplot,color=hlime,line width=1pt] gnuplot {
+plot './Green_hyb0.8O5.dat' u 1:(-1/3.1415)*($3) w l;
+};
+
+\addplot[name path=neq_distr_f_filling_hyb0.8O5,solid,raw gnuplot,color=hlime,line width=1pt,opacity=0.0] gnuplot {
+plot "neq_distr_f_filling_hyb0.8O5.dat" u 1:3 w l;
+};
+
+\path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
+\addplot [fill=hcoral,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O5 and xaxis,soft clip={domain=-15:15}];
+\addplot [fill=hlime,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O5 and xaxis,soft clip={domain=-15:15}];
+
+% \node[fill=none,color=hblue,scale={1.0}] at (axis cs:-1.20,0.017){$F$}; 
+% \node[fill=none,color=hred,scale={1.0}] at (axis cs:1.20,0.022){$F$};
+ \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(a)};
+ \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$\Omega=5$};
+
+% 2° figure
+
+\nextgroupplot[
+xmin=-15.,     
+xmax=15., 
+ymin=0.00, 
+ymax=0.09,   
+minor tick num=1, 
+grid=both,
+xlabel={$\omega/t^{*}$},
+% ylabel={$A(\omega)/t^{*-1}$},
+legend style={at={(axis cs:0,0.1)},anchor=north,mark options={scale=1.0},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
 legend cell align=left,
@@
 \addlegendimage{solid,color=hblue,scale={1.0},line width=1pt}
-\addlegendentry{$el$};
+\addlegendentry{$v=0.4$};
 \addlegendimage{solid,color=hred,scale={1.0},line width=1pt} 
-\addlegendentry{$el+ph$};
+\addlegendentry{$v=0.8$};
+
+% \addplot +[dashed,very thin,color=hblue,mark=none] coordinates {(-2.55, 0.0) (-2.55, 0.035)};
+% \addplot +[dashed,very thin,color=hblue,mark=none] coordinates {(0.525, 0.0) (0.525, 0.035)};
+% \draw [stealth-stealth,thick,color=hblue](-2.55, 0.015) -- (0.525, 0.015);
+
+% \addplot +[dashed,very thin,color=hred,mark=none] coordinates {(2.55, 0.0) (2.55, 0.035)};
+% \addplot +[dashed,very thin,color=hred,mark=none] coordinates {(-0.525, 0.0) (-0.525, 0.035)};
+% \draw [stealth-stealth,thick,color=hred](2.55, 0.02) -- (-0.525, 0.02);
+
+% \draw [-stealth,thick,color=hgray](0.35, 0.0055) -- (0.45, 0.004);
+% \draw [-stealth,thick,color=hgray](-0.35, 0.0055) -- (-0.45, 0.004);
+
+% \draw [-stealth,thick,color=hgray](2.0, 0.0045) -- (2.2, 0.003);
+% \draw [-stealth,thick,color=hgray](-2.0, 0.0045) -- (-2.2, 0.003);
 
@@
 
-\addplot[dashed,raw gnuplot,color=hblue,line width=1pt] gnuplot {
-plot './neq_distr_f_filling_hyb0.4O11.dat' u 1:3 w l;
+\addplot[name path=neq_distr_f_filling_hyb0.4O11,solid,raw gnuplot,color=hblue,line width=1pt,opacity=0.0] gnuplot {
+plot "neq_distr_f_filling_hyb0.4O11.dat" u 1:3 w l;
 };
@@
 \addplot[solid,raw gnuplot,color=hred,line width=1pt] gnuplot {
-plot './Green_hyb0.4O11ph.dat' u 1:(-1/3.1415)*($3) w l;
-};
-
-\addplot[dashed,raw gnuplot,color=hred,line width=1pt] gnuplot {
-plot './neq_distr_f_filling_hyb0.4O11ph.dat' u 1:3 w l;
-};
-
- \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(a)};
- \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$v=0.4$};
-
-% 2° figure
-
-\nextgroupplot[
-xmin=-15.,     
-xmax=15., 
-ymin=0.00, 
-ymax=0.09,   
-minor tick num=1, 
-% grid=both,
-xlabel={$\omega/t^{*}$},
-% ylabel={$A(\omega)/t^{*-1}$},
-legend style={at={(axis cs:-9.3,0.017)},anchor=north,mark options={scale=0.85},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
-legend cell align=left,
-clip mode=individual,
-clip marker paths=true, 
-xtick={-15,-10,-5,0,5,10,15},
-ytick={0.00,0.03,0.06,0.09},
-% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012},
-% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012,\smash{\raisebox{-0.8\height}{5}}},
-x tick label style={
-    /pgf/number format/.cd,
-    fixed,
-    fixed zerofill,
-    precision=0,
-    /tikz/.cd},
-y tick label style={
-    /pgf/number format/.cd,
-    fixed,
-    fixed zerofill,
-    precision=0,
-    /tikz/.cd}
-]
-
-\addlegendimage{solid,color=hcoral,scale={1.0},line width=1pt}
-\addlegendentry{$el$};
-\addlegendimage{solid,color=hlime,scale={1.0},line width=1pt} 
-\addlegendentry{$el+ph$};
-
-% % % % % % % %  PLOTS
-
-% \draw (axis cs:4,0) -- (axis cs:10,0.01);
-
-\addplot[solid,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
 plot './Green_hyb0.8O11.dat' u 1:(-1/3.1415)*($3) w l;
@@
 
-\addplot[dashed,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
-plot './neq_distr_f_filling_hyb0.8O11.dat' u 1:3 w l;
+\addplot[name path=neq_distr_f_filling_hyb0.8O11,solid,raw gnuplot,color=hred,line width=1pt,opacity=0.0] gnuplot {
+plot "neq_distr_f_filling_hyb0.8O11.dat" u 1:3 w l;
 };
 
-\addplot[solid,raw gnuplot,color=hlime,line width=1pt] gnuplot {
-plot './Green_hyb0.8O11ph.dat' u 1:(-1/3.1415)*($3) w l;
-};
+\path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
+\addplot [fill=hblue,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11 and xaxis,soft clip={domain=-15:15}];
+\addplot [fill=hred,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O11 and xaxis,soft clip={domain=-15:15}];
 
-\addplot[dashed,raw gnuplot,color=hlime,line width=1pt] gnuplot {
-plot './neq_distr_f_filling_hyb0.8O11ph.dat' u 1:3 w l;
-};
-
+% \node[fill=none,color=hblue,scale={1.0}] at (axis cs:-1.20,0.017){$F$};
+% \node[fill=none,color=hred,scale={1.0}] at (axis cs:1.20,0.022){$F$};
  \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(b)};
- \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$v=0.8$};
+ \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$\Omega=11$};
 

### 2022-07-21 compilation.sh

@@ -1,0 +1,10 @@
+file2='Paper1'
+
+rm $file2.aux
+rm $file2.bbl
+
+pdflatex $file2.tex
+bibtex $file2
+pdflatex $file2.tex
+pdflatex $file2.tex
+ 

### 2022-07-21 figures_Paper1/test_old/setup_PRB.97.115113.2018.tex
Added sources for figures

\documentclass{standalone}

\usepackage{amsmath}
\usepackage{pgfplots}
\pgfplotsset{compat=1.16}
\usepackage{tikz-3dplot}
\usetikzlibrary{calc}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{decorations.pathmorphing}

\usepackage{xcolor}
\usepackage{amsmath}

\definecolor{hblue}{RGB}{0,112,255}    % Brandeis blue
\definecolor{hred}{RGB}{199,44,72}     % raspberry red
\definecolor{hgreen}{RGB}{50,205,50}   % lime green
\definecolor{horange}{RGB}{255,127,0}  % orange
\definecolor{hpurple}{RGB}{111,45,168} % grape
\definecolor{hyellow}{RGB}{255,211,0}  % cyber yellow
\definecolor{hgray}{HTML}{323232}      % anthrazit gray

\begin{document}
\begin{tikzpicture}[>=Stealth]
\begin{axis}[
axis lines=none,
view={150}{10},
xmin=0,xmax=4,
ymin=0,ymax=3,
zmin=-2,zmax=3,
xlabel=$x$,
ylabel=$y$,
zlabel=$z$,
scale=1
]

% right lead
% balls
\foreach \x in {0,1}
  \foreach \y in {0,1,...,3}
    \foreach \z in {0,1,...,3}
       \addplot3 [only marks,mark=ball,mark size=2pt,ball color=hblue,line width=0.1pt] coordinates{(\x,\y,\z)};
% lines
\pgfplotsinvokeforeach{0,1,...,3} {
   \draw[color=hblue] (axis cs:0,#1,0) -- (axis cs:0,#1,3);
   \draw[color=hblue] (axis cs:0,#1,0) -- (axis cs:1,#1,0);
   \draw[color=hblue] (axis cs:0,#1,1) -- (axis cs:1,#1,1);
   \draw[color=hblue] (axis cs:0,#1,2) -- (axis cs:1,#1,2);
   \draw[color=hblue] (axis cs:0,#1,3) -- (axis cs:1,#1,3);
};
\pgfplotsinvokeforeach{0,1,...,3} {
   \draw[color=hblue] (axis cs:0,0,#1) -- (axis cs:0,3,#1);
};
\pgfplotsinvokeforeach{0,1,...,3} {
   \draw[color=hblue] (axis cs:1,#1,0) -- (axis cs:1,#1,3);
};
\pgfplotsinvokeforeach{0,1,...,3} {
   \draw[color=hblue] (axis cs:1,0,#1) -- (axis cs:1,3,#1);
};
% bottom
% \fill[color=hblue,opacity=0.2] (axis cs:1,0,0) -- (axis cs:0,0,0) -- (axis cs:0,3,0) -- (axis cs:1,3,0) -- cycle;
% back
% \fill[color=hblue,opacity=0.2] (axis cs:1,0,0) -- (axis cs:0,0,0) -- (axis cs:0,0,3) -- (axis cs:1,0,3) -- cycle;
% front
\fill[color=hblue,opacity=0.2] (axis cs:1,0,0) -- (axis cs:1,3,0) -- (axis cs:1,3,3) -- (axis cs:1,0,3) -- cycle;
% left side
\fill[color=hblue,opacity=0.2] (axis cs:1,3,0) -- (axis cs:0,3,0) -- (axis cs:0,3,3) -- (axis cs:1,3,3) -- cycle;
% top
\fill[color=hblue,opacity=0.2] (axis cs:1,3,3) -- (axis cs:0,3,3) -- (axis cs:0,0,3) -- (axis cs:1,0,3) -- cycle;

% interface right-center
\pgfplotsinvokeforeach{0,1,...,3} {
   \draw[color=hgreen] (axis cs:1,#1,0) -- (axis cs:2,#1,0);
   \draw[color=hgreen] (axis cs:1,#1,1) -- (axis cs:2,#1,1);
   \draw[color=hgreen] (axis cs:1,#1,2) -- (axis cs:2,#1,2);
   \draw[color=hgreen] (axis cs:1,#1,3) -- (axis cs:2,#1,3);
};

% central layer
\fill[color=hred,opacity=0.5] (axis cs:2,0,0) -- (axis cs:2,3,0) -- (axis cs:2,3,3) -- (axis cs:2,0,3) -- cycle;
% lines
\pgfplotsinvokeforeach{0,1,...,3} {
   \draw[color=hred] (axis cs:2,#1,0) -- (axis cs:2,#1,3);
};
\pgfplotsinvokeforeach{0,1,...,3} {
   \draw[color=hred] (axis cs:2,0,#1) -- (axis cs:2,3,#1);
};
% balls
\foreach \y in {0,1,...,3}
  \foreach \z in {0,1,...,3}
     \addplot3 [only marks,mark=ball,mark size=3pt,ball color=hred,line width=0.1pt] coordinates{(2,\y,\z)};

% interface center-left
\pgfplotsinvokeforeach{0,1,...,3} {
   \draw[color=hgreen] (axis cs:2,#1,0) -- (axis cs:3,#1,0);
   \draw[color=hgreen] (axis cs:2,#1,1) -- (axis cs:3,#1,1);
   \draw[color=hgreen] (axis cs:2,#1,2) -- (axis cs:3,#1,2);
   \draw[color=hgreen] (axis cs:2,#1,3) -- (axis cs:3,#1,3);
};

% left lead
% balls
\foreach \x in {3,4}
  \foreach \y in {0,1,...,3}
    \foreach \z in {0,1,...,3}
       \addplot3 [only marks,mark=ball,mark size=2pt,ball color=hblue,line width=0.1pt] coordinates{(\x,\y,\z)};
% lines
\pgfplotsinvokeforeach{0,1,...,3} {
   \draw[color=hblue] (axis cs:3,#1,0) -- (axis cs:3,#1,3);
   \draw[color=hblue] (axis cs:3,#1,0) -- (axis cs:4,#1,0);
   \draw[color=hblue] (axis cs:3,#1,1) -- (axis cs:4,#1,1);
   \draw[color=hblue] (axis cs:3,#1,2) -- (axis cs:4,#1,2);
   \draw[color=hblue] (axis cs:3,#1,3) -- (axis cs:4,#1,3);
};
\pgfplotsinvokeforeach{0,1,...,3} {
   \draw[color=hblue] (axis cs:3,0,#1) -- (axis cs:3,3,#1);
};
\pgfplotsinvokeforeach{0,1,...,3} {
   \draw[color=hblue] (axis cs:4,#1,0) -- (axis cs:4,#1,3);
};
\pgfplotsinvokeforeach{0,1,...,3} {
   \draw[color=hblue] (axis cs:4,0,#1) -- (axis cs:4,3,#1);
};
% bottom
% \fill[color=hblue,opacity=0.5] (axis cs:4,0,0) -- (axis cs:3,0,0) -- (axis cs:3,3,0) -- (axis cs:4,3,0) -- cycle;
% back
% \fill[color=hblue,opacity=0.5] (axis cs:4,0,0) -- (axis cs:3,0,0) -- (axis cs:3,0,3) -- (axis cs:4,0,3) -- cycle;
% front
\fill[color=hblue,opacity=0.5] (axis cs:4,0,0) -- (axis cs:4,3,0) -- (axis cs:4,3,3) -- (axis cs:4,0,3) -- cycle;
% left side
\fill[color=hblue,opacity=0.5] (axis cs:4,3,0) -- (axis cs:3,3,0) -- (axis cs:3,3,3) -- (axis cs:4,3,3) -- cycle;
% top
\fill[color=hblue,opacity=0.5] (axis cs:4,3,3) -- (axis cs:3,3,3) -- (axis cs:3,0,3) -- (axis cs:4,0,3) -- cycle;

% coordinates for light
\coordinate (top1) at (axis cs:2,1,3);
\coordinate (top2) at (axis cs:2,2,3);
\coordinate (top3) at (axis cs:2,3,3);

% volt-meter lines
\coordinate (leftlead) at (axis cs:4,1.5,0);
\coordinate (belowleftlead) at (axis cs:4,1.5,-1.5);
\coordinate (rightlead) at (axis cs:0,1.5,0);

\draw[line width=1pt] let 
      \p1=(leftlead),
      \p2=(belowleftlead),
      \p3=(rightlead)
in
      (leftlead) -- (belowleftlead) -- (\x3,\y2) -- (rightlead);

\end{axis}

% volt-meter display
\filldraw[draw=black,fill=white,line width=1pt] let 
      \p1=(belowleftlead),
      \p2=(rightlead)
in
      ($ (\x1/2.,\y1)+(\x2/2.,0) $) circle (0.5);
\draw[->] let 
      \p1=(belowleftlead),
      \p2=(rightlead)
in
      ($ (\x1/2.,\y1)+(\x2/2.,0) $) -- node[at start,below] {$V$} ($ (\x1/2.,\y1)+(\x2/2.,0)+(0.35355,0.35355) $);

% cw-light
\draw [->,>=Stealth,line width=2pt,decorate,decoration={snake,amplitude=0.3cm,segment length=0.8cm,pre length=0.4cm,post length=0.4cm},draw=hyellow] ($ (top1)+(120:3) $) -- (top1);
\draw [->,>=Stealth,line width=2pt,decorate,decoration={snake,amplitude=0.3cm,segment length=0.8cm,pre length=0.4cm,post length=0.4cm},draw=hyellow] ($ (top2)+(115:3) $) -- (top2);
\draw [->,>=Stealth,line width=2pt,decorate,decoration={snake,amplitude=0.3cm,segment length=0.8cm,pre length=0.4cm,post length=0.4cm},draw=hyellow] ($ (top3)+(110:3) $) -- (top3);

% pulsed light
% \begin{scope}[decoration={markings,
% mark=at position 0.0 with {{\arrowreversed[hyellow,xshift=-6]{Stealth}}}},
% domain=-1.6:1.5,samples=300,xshift=8.4cm,yshift=4.6cm,rotate=110]
% \draw[postaction={decorate},draw=hyellow,line width=2pt] plot (\x,{0.8*exp(-\x*\x/(2.*0.3))*sin(10.*\x r)});
% \end{scope}

\end{tikzpicture}
\end{document}

### 2022-07-21 figures_Paper1/test_old/spec_filling_mu1_v_0.4_0.8_E4_O_11.5_eph.tex
Added sources for figures

--- 2022-07-21 figures_Paper1/spec_filling_mu1_v_0.4_0.8_O_11_eph.tex
@@
 \addplot[solid,raw gnuplot,color=hblue,line width=1pt] gnuplot {
-plot './Green_hyb0.4O11.dat' u 1:(-1/3.1415)*($3) w l;
+plot './Green_hyb0.4E4_O11.5.dat' u 1:(-1/3.1415)*($3) w l;
 };
@@
 \addplot[dashed,raw gnuplot,color=hblue,line width=1pt] gnuplot {
-plot './neq_distr_f_filling_hyb0.4O11.dat' u 1:3 w l;
+plot './neq_distr_f_filling_hyb0.4E4_O11.5.dat' u 1:3 w l;
 };
@@
 \addplot[solid,raw gnuplot,color=hred,line width=1pt] gnuplot {
-plot './Green_hyb0.4O11ph.dat' u 1:(-1/3.1415)*($3) w l;
+plot './Green_hyb0.4phE4_O11.5.dat' u 1:(-1/3.1415)*($3) w l;
 };
@@
 \addplot[dashed,raw gnuplot,color=hred,line width=1pt] gnuplot {
-plot './neq_distr_f_filling_hyb0.4O11ph.dat' u 1:3 w l;
+plot './neq_distr_f_filling_hyb0.4phE4_O11.5.dat' u 1:3 w l;
 };
@@
 \addplot[solid,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
-plot './Green_hyb0.8O11.dat' u 1:(-1/3.1415)*($3) w l;
+plot './Green_hyb0.8E4_O11.5.dat' u 1:(-1/3.1415)*($3) w l;
 };
@@
 \addplot[dashed,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
-plot './neq_distr_f_filling_hyb0.8O11.dat' u 1:3 w l;
+plot './neq_distr_f_filling_hyb0.8E4_O11.5.dat' u 1:3 w l;
 };
@@
 \addplot[solid,raw gnuplot,color=hlime,line width=1pt] gnuplot {
-plot './Green_hyb0.8O11ph.dat' u 1:(-1/3.1415)*($3) w l;
+plot './Green_hyb0.8phE4_O11.5.dat' u 1:(-1/3.1415)*($3) w l;
 };
@@
 \addplot[dashed,raw gnuplot,color=hlime,line width=1pt] gnuplot {
-plot './neq_distr_f_filling_hyb0.8O11ph.dat' u 1:3 w l;
+plot './neq_distr_f_filling_hyb0.8phE4_O11.5.dat' u 1:3 w l;
 };

### 2022-07-21 figures_Paper1/test_old/spec_filling_mu1_v_0.4_0.8_O_5_11_e.tex
Added sources for figures

--- 2022-07-21 figures_Paper1/spec_filling_mu1_v_0.4_0.8_O_5_11_e.tex
@@
 group style={
-group size=2 by 1,
+group size=2 by 2,
 xticklabels at=edge bottom,  
@@
 
+%  3° figure
+
+\nextgroupplot[
+xmin=-15.,    
+xmax=15., 
+ymin=0.00, 
+ymax=0.09,   
+minor tick num=1, 
+grid=both,
+xlabel={$\omega/t^{*}$},
+ylabel={$A(\omega)/t^{*-1}$},
+legend style={at={(axis cs:0,0.1)},anchor=north,mark options={scale=1.0},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
+legend cell align=left,
+clip mode=individual,
+clip marker paths=true, 
+xtick={-15,-10,-5,0,5,10,15},
+ytick={0.00,0.03,0.06,0.09},
+% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012},
+% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012,\smash{\raisebox{-0.8\height}{5}}},
+x tick label style={
+    /pgf/number format/.cd,
+    fixed,
+    fixed zerofill,
+    precision=0,
+    /tikz/.cd},
+y tick label style={
+    /pgf/number format/.cd,
+    fixed,
+    fixed zerofill,
+    precision=0,
+    /tikz/.cd}
+]
+
+\addlegendimage{solid,color=hcoral,scale={1.0},line width=1pt}
+\addlegendentry{$\Omega=5$};
+\addlegendimage{solid,color=hblue,scale={1.0},line width=1pt}
+\addlegendentry{$\Omega=11$};
+
+% \addplot +[dashed,very thin,color=hblue,mark=none] coordinates {(-2.55, 0.0) (-2.55, 0.035)};
+% \addplot +[dashed,very thin,color=hblue,mark=none] coordinates {(0.525, 0.0) (0.525, 0.035)};
+% \draw [stealth-stealth,thick,color=hblue](-2.55, 0.015) -- (0.525, 0.015);
+
+% \addplot +[dashed,very thin,color=hred,mark=none] coordinates {(2.55, 0.0) (2.55, 0.035)};
+% \addplot +[dashed,very thin,color=hred,mark=none] coordinates {(-0.525, 0.0) (-0.525, 0.035)};
+% \draw [stealth-stealth,thick,color=hred](2.55, 0.02) -- (-0.525, 0.02);
+
+% \draw [-stealth,thick,color=hgray](0.35, 0.0055) -- (0.45, 0.004);
+% \draw [-stealth,thick,color=hgray](-0.35, 0.0055) -- (-0.45, 0.004);
+
+% \draw [-stealth,thick,color=hgray](2.0, 0.0045) -- (2.2, 0.003);
+% \draw [-stealth,thick,color=hgray](-2.0, 0.0045) -- (-2.2, 0.003);
+
+% % % % % % % %  PLOTS
+
+% \draw (axis cs:4,0) -- (axis cs:10,0.01);
+
+\addplot[solid,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
+plot './Green_hyb0.4O5.dat' u 1:(-1/3.1415)*($3) w l;
+};
+
+\addplot[name path=neq_distr_f_filling_hyb0.4O5,solid,raw gnuplot,color=hcoral,line width=1pt,opacity=0.0] gnuplot {
+plot "neq_distr_f_filling_hyb0.4O5.dat" u 1:3 w l;
+};
+
+\addplot[solid,raw gnuplot,color=hblue,line width=1pt] gnuplot {
+plot './Green_hyb0.4O11.dat' u 1:(-1/3.1415)*($3) w l;
+};
+
+\addplot[name path=neq_distr_f_filling_hyb0.4O11,solid,raw gnuplot,color=hblue,line width=1pt,opacity=0.0] gnuplot {
+plot "neq_distr_f_filling_hyb0.4O11.dat" u 1:3 w l;
+};
+
+\path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
+\addplot [fill=hcoral,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O5 and xaxis,soft clip={domain=-15:15}];
+\addplot [fill=hblue,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11 and xaxis,soft clip={domain=-15:15}];
+
+% \node[fill=none,color=hblue,scale={1.0}] at (axis cs:-1.20,0.017){$F$};
+% \node[fill=none,color=hred,scale={1.0}] at (axis cs:1.20,0.022){$F$};
+ \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(c)};
+ \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$v=0.4$};
+
+%  4° figure
+
+\nextgroupplot[
+xmin=-15.,    
+xmax=15., 
+ymin=0.00, 
+ymax=0.09,   
+minor tick num=1, 
+grid=both,
+xlabel={$\omega/t^{*}$},
+% ylabel={$A(\omega)/t^{*-1}$},
+legend style={at={(axis cs:0,0.1)},anchor=north,mark options={scale=1.0},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
+legend cell align=left,
+clip mode=individual,
+clip marker paths=true, 
+xtick={-15,-10,-5,0,5,10,15},
+ytick={0.00,0.03,0.06,0.09},
+% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012},
+% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012,\smash{\raisebox{-0.8\height}{5}}},
+x tick label style={
+    /pgf/number format/.cd,
+    fixed,
+    fixed zerofill,
+    precision=0,
+    /tikz/.cd},
+y tick label style={
+    /pgf/number format/.cd,
+    fixed,
+    fixed zerofill,
+    precision=0,
+    /tikz/.cd}
+]
+
+\addlegendimage{solid,color=hlime,scale={1.0},line width=1pt}
+\addlegendentry{$\Omega=5$};
+\addlegendimage{solid,color=hred,scale={1.0},line width=1pt}
+\addlegendentry{$\Omega=11$};
+
+% \addplot +[dashed,very thin,color=hblue,mark=none] coordinates {(-2.55, 0.0) (-2.55, 0.035)};
+% \addplot +[dashed,very thin,color=hblue,mark=none] coordinates {(0.525, 0.0) (0.525, 0.035)};
+% \draw [stealth-stealth,thick,color=hblue](-2.55, 0.015) -- (0.525, 0.015);
+
+% \addplot +[dashed,very thin,color=hred,mark=none] coordinates {(2.55, 0.0) (2.55, 0.035)};
+% \addplot +[dashed,very thin,color=hred,mark=none] coordinates {(-0.525, 0.0) (-0.525, 0.035)};
+% \draw [stealth-stealth,thick,color=hred](2.55, 0.02) -- (-0.525, 0.02);
+
+% \draw [-stealth,thick,color=hgray](0.35, 0.0055) -- (0.45, 0.004);
+% \draw [-stealth,thick,color=hgray](-0.35, 0.0055) -- (-0.45, 0.004);
+
+% \draw [-stealth,thick,color=hgray](2.0, 0.0045) -- (2.2, 0.003);
+% \draw [-stealth,thick,color=hgray](-2.0, 0.0045) -- (-2.2, 0.003);
+
+% % % % % % % %  PLOTS
+
+% \draw (axis cs:4,0) -- (axis cs:10,0.01);
+
+\addplot[solid,raw gnuplot,color=hlime,line width=1pt] gnuplot {
+plot './Green_hyb0.8O5.dat' u 1:(-1/3.1415)*($3) w l;
+};
+
+\addplot[name path=neq_distr_f_filling_hyb0.8O5,solid,raw gnuplot,color=hlime,line width=1pt,opacity=0.0] gnuplot {
+plot "neq_distr_f_filling_hyb0.8O5.dat" u 1:3 w l;
+};
+
+\addplot[solid,raw gnuplot,color=hred,line width=1pt] gnuplot {
+plot './Green_hyb0.8O11.dat' u 1:(-1/3.1415)*($3) w l;
+};
+
+\addplot[name path=neq_distr_f_filling_hyb0.8O11,solid,raw gnuplot,color=hred,line width=1pt,opacity=0.0] gnuplot {
+plot "neq_distr_f_filling_hyb0.8O11.dat" u 1:3 w l;
+};
+
+\path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
+\addplot [fill=hlime,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O5 and xaxis,soft clip={domain=-15:15}];
+\addplot [fill=hred,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O11 and xaxis,soft clip={domain=-15:15}];
+
+% \node[fill=none,color=hblue,scale={1.0}] at (axis cs:-1.20,0.017){$F$};
+% \node[fill=none,color=hred,scale={1.0}] at (axis cs:1.20,0.022){$F$};
+ \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(d)};
+ \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$v=0.8$};
+
 \end{groupplot}

### 2022-07-21 figures_Paper1/test_old/spec_filling_mu1_v_0.4_0.8_O_5_11_eph.tex
Added sources for figures

--- 2022-07-21 figures_Paper1/test_old/spec_filling_mu1_v_0.4_0.8_O_5_11_e.tex
@@
 minor tick num=1, 
-grid=both,
-xlabel={$\omega/t^{*}$},
+% grid=both,
+% xlabel={$\omega/t^{*}$},
 ylabel={$A(\omega)/t^{*-1}$},
@@
 
-\addlegendimage{solid,color=hcoral,scale={1.0},line width=1pt}
-\addlegendentry{$v=0.4$};
-\addlegendimage{solid,color=hlime,scale={1.0},line width=1pt} 
-\addlegendentry{$v=0.8$};
-
-% \addplot +[dashed,very thin,color=hblue,mark=none] coordinates {(-2.55, 0.0) (-2.55, 0.035)};
-% \addplot +[dashed,very thin,color=hblue,mark=none] coordinates {(0.525, 0.0) (0.525, 0.035)};
-% \draw [stealth-stealth,thick,color=hblue](-2.55, 0.015) -- (0.525, 0.015);
-
-% \addplot +[dashed,very thin,color=hred,mark=none] coordinates {(2.55, 0.0) (2.55, 0.035)};
-% \addplot +[dashed,very thin,color=hred,mark=none] coordinates {(-0.525, 0.0) (-0.525, 0.035)};
-% \draw [stealth-stealth,thick,color=hred](2.55, 0.02) -- (-0.525, 0.02);
-
-% \draw [-stealth,thick,color=hgray](0.35, 0.0055) -- (0.45, 0.004);
-% \draw [-stealth,thick,color=hgray](-0.35, 0.0055) -- (-0.45, 0.004);
-
-% \draw [-stealth,thick,color=hgray](2.0, 0.0045) -- (2.2, 0.003);
-% \draw [-stealth,thick,color=hgray](-2.0, 0.0045) -- (-2.2, 0.003);
+% \addlegendimage{solid,color=hblue,scale={1.0},line width=1pt}
+% \addlegendentry{$el$};
+% \addlegendimage{solid,color=hred,scale={1.0},line width=1pt} 
+% \addlegendentry{$el+ph$};
 
@@
 
-\addplot[solid,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
+\addplot[solid,raw gnuplot,color=hblue,line width=1pt] gnuplot {
 plot './Green_hyb0.4O5.dat' u 1:(-1/3.1415)*($3) w l;
@@
 
-\addplot[name path=neq_distr_f_filling_hyb0.4O5,solid,raw gnuplot,color=hcoral,line width=1pt,opacity=0.0] gnuplot {
-plot "neq_distr_f_filling_hyb0.4O5.dat" u 1:3 w l;
+\addplot[dashed,raw gnuplot,color=hblue,line width=1pt] gnuplot {
+plot './neq_distr_f_filling_hyb0.4O5.dat' u 1:3 w l;
 };
 
-\addplot[solid,raw gnuplot,color=hlime,line width=1pt] gnuplot {
-plot './Green_hyb0.8O5.dat' u 1:(-1/3.1415)*($3) w l;
+\addplot[solid,raw gnuplot,color=hred,line width=1pt] gnuplot {
+plot './Green_hyb0.4O5ph.dat' u 1:(-1/3.1415)*($3) w l;
 };
 
-\addplot[name path=neq_distr_f_filling_hyb0.8O5,solid,raw gnuplot,color=hlime,line width=1pt,opacity=0.0] gnuplot {
-plot "neq_distr_f_filling_hyb0.8O5.dat" u 1:3 w l;
+\addplot[dashed,raw gnuplot,color=hred,line width=1pt] gnuplot {
+plot './neq_distr_f_filling_hyb0.4O5ph.dat' u 1:3 w l;
 };
 
-\path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
-\addplot [fill=hcoral,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O5 and xaxis,soft clip={domain=-15:15}];
-\addplot [fill=hlime,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O5 and xaxis,soft clip={domain=-15:15}];
+% VERTICAL LINES + ARROWS MARKING THEIR DISTANCE
+
+\addplot +[dashed,semithick,color=hgray,mark=none] coordinates {(-2.5, 0.0) (-2.5, 0.09)};
+\addplot +[dashed,semithick,color=hgray,mark=none] coordinates {(2.5, 0.0) (2.5, 0.09)};
+% \draw [stealth-stealth,thick,color=gray](-2.5, 0.03) -- (2.5, 0.03);
 
@@
  \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(a)};
- \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$\Omega=5$};
+ \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$v=0.4$};
 
@@
 minor tick num=1, 
-grid=both,
-xlabel={$\omega/t^{*}$},
+% grid=both,
+% xlabel={$\omega/t^{*}$},
 % ylabel={$A(\omega)/t^{*-1}$},
@@
 
-\addlegendimage{solid,color=hblue,scale={1.0},line width=1pt}
-\addlegendentry{$v=0.4$};
-\addlegendimage{solid,color=hred,scale={1.0},line width=1pt} 
-\addlegendentry{$v=0.8$};
-
-% \addplot +[dashed,very thin,color=hblue,mark=none] coordinates {(-2.55, 0.0) (-2.55, 0.035)};
-% \addplot +[dashed,very thin,color=hblue,mark=none] coordinates {(0.525, 0.0) (0.525, 0.035)};
-% \draw [stealth-stealth,thick,color=hblue](-2.55, 0.015) -- (0.525, 0.015);
-
-% \addplot +[dashed,very thin,color=hred,mark=none] coordinates {(2.55, 0.0) (2.55, 0.035)};
-% \addplot +[dashed,very thin,color=hred,mark=none] coordinates {(-0.525, 0.0) (-0.525, 0.035)};
-% \draw [stealth-stealth,thick,color=hred](2.55, 0.02) -- (-0.525, 0.02);
-
-% \draw [-stealth,thick,color=hgray](0.35, 0.0055) -- (0.45, 0.004);
-% \draw [-stealth,thick,color=hgray](-0.35, 0.0055) -- (-0.45, 0.004);
-
-% \draw [-stealth,thick,color=hgray](2.0, 0.0045) -- (2.2, 0.003);
-% \draw [-stealth,thick,color=hgray](-2.0, 0.0045) -- (-2.2, 0.003);
+\addlegendimage{solid,color=hcoral,scale={1.0},line width=1pt}
+\addlegendentry{$el$};
+\addlegendimage{solid,color=hlime,scale={1.0},line width=1pt} 
+\addlegendentry{$el+ph$};
 
@@
 
-\addplot[solid,raw gnuplot,color=hblue,line width=1pt] gnuplot {
-plot './Green_hyb0.4O11.dat' u 1:(-1/3.1415)*($3) w l;
+\addplot[solid,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
+plot './Green_hyb0.8O5.dat' u 1:(-1/3.1415)*($3) w l;
 };
 
-\addplot[name path=neq_distr_f_filling_hyb0.4O11,solid,raw gnuplot,color=hblue,line width=1pt,opacity=0.0] gnuplot {
-plot "neq_distr_f_filling_hyb0.4O11.dat" u 1:3 w l;
+\addplot[dashed,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
+plot './neq_distr_f_filling_hyb0.8O5.dat' u 1:3 w l;
 };
 
-\addplot[solid,raw gnuplot,color=hred,line width=1pt] gnuplot {
-plot './Green_hyb0.8O11.dat' u 1:(-1/3.1415)*($3) w l;
+\addplot[solid,raw gnuplot,color=hlime,line width=1pt] gnuplot {
+plot './Green_hyb0.8O5ph.dat' u 1:(-1/3.1415)*($3) w l;
 };
 
-\addplot[name path=neq_distr_f_filling_hyb0.8O11,solid,raw gnuplot,color=hred,line width=1pt,opacity=0.0] gnuplot {
-plot "neq_distr_f_filling_hyb0.8O11.dat" u 1:3 w l;
+\addplot[dashed,raw gnuplot,color=hlime,line width=1pt] gnuplot {
+plot './neq_distr_f_filling_hyb0.8O5ph.dat' u 1:3 w l;
 };
 
-\path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
-\addplot [fill=hblue,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11 and xaxis,soft clip={domain=-15:15}];
-\addplot [fill=hred,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O11 and xaxis,soft clip={domain=-15:15}];
+% VERTICAL LINES + ARROWS MARKING THEIR DISTANCE
+
+\addplot +[dashed,semithick,color=hgray,mark=none] coordinates {(-2.5, 0.0) (-2.5, 0.09)};
+\addplot +[dashed,semithick,color=hgray,mark=none] coordinates {(2.5, 0.0) (2.5, 0.09)};
+% \draw [stealth-stealth,thick,color=gray](-2.5, 0.03) -- (2.5, 0.03);
 
@@
  \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(b)};
- \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$\Omega=11$};
+ \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$v=0.8$};
 
@@
 xmax=15., 
-ymin=0.00, 
-ymax=0.09,   
+ymin=-0.01, 
+ymax=0.01,   
 minor tick num=1, 
-grid=both,
+% grid=both, 
 xlabel={$\omega/t^{*}$},
-ylabel={$A(\omega)/t^{*-1}$},
-legend style={at={(axis cs:0,0.1)},anchor=north,mark options={scale=1.0},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
+ylabel={$j(\omega)$},
+legend style={at={(axis cs:0,0.011)},anchor=north,mark options={scale=1.0},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
 legend cell align=left,
@@
 xtick={-15,-10,-5,0,5,10,15},
-ytick={0.00,0.03,0.06,0.09},
+ytick={-0.01,0.00,0.01},
 % yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012},
@@
 
-\addlegendimage{solid,color=hcoral,scale={1.0},line width=1pt}
-\addlegendentry{$\Omega=5$};
 \addlegendimage{solid,color=hblue,scale={1.0},line width=1pt}
-\addlegendentry{$\Omega=11$};
-
-% \addplot +[dashed,very thin,color=hblue,mark=none] coordinates {(-2.55, 0.0) (-2.55, 0.035)};
-% \addplot +[dashed,very thin,color=hblue,mark=none] coordinates {(0.525, 0.0) (0.525, 0.035)};
-% \draw [stealth-stealth,thick,color=hblue](-2.55, 0.015) -- (0.525, 0.015);
-
-% \addplot +[dashed,very thin,color=hred,mark=none] coordinates {(2.55, 0.0) (2.55, 0.035)};
-% \addplot +[dashed,very thin,color=hred,mark=none] coordinates {(-0.525, 0.0) (-0.525, 0.035)};
-% \draw [stealth-stealth,thick,color=hred](2.55, 0.02) -- (-0.525, 0.02);
-
-% \draw [-stealth,thick,color=hgray](0.35, 0.0055) -- (0.45, 0.004);
-% \draw [-stealth,thick,color=hgray](-0.35, 0.0055) -- (-0.45, 0.004);
-
-% \draw [-stealth,thick,color=hgray](2.0, 0.0045) -- (2.2, 0.003);
-% \draw [-stealth,thick,color=hgray](-2.0, 0.0045) -- (-2.2, 0.003);
+\addlegendentry{$el$};
+\addlegendimage{solid,color=hred,scale={1.0},line width=1pt} 
+\addlegendentry{$el+ph$};
 
@@
 
-\addplot[solid,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
-plot './Green_hyb0.4O5.dat' u 1:(-1/3.1415)*($3) w l;
+\addplot[solid,raw gnuplot,color=hblue,line width=1pt] gnuplot {
+plot './J00_omega_hyb0.4O5.dat' u 1:2 w l;
 };
 
-\addplot[name path=neq_distr_f_filling_hyb0.4O5,solid,raw gnuplot,color=hcoral,line width=1pt,opacity=0.0] gnuplot {
-plot "neq_distr_f_filling_hyb0.4O5.dat" u 1:3 w l;
+\addplot[solid,raw gnuplot,color=hred,line width=1pt] gnuplot {
+plot './J00_omega_hyb0.4O5ph.dat' u 1:2 w l;
 };
 
-\addplot[solid,raw gnuplot,color=hblue,line width=1pt] gnuplot {
-plot './Green_hyb0.4O11.dat' u 1:(-1/3.1415)*($3) w l;
-};
+% VERTICAL LINES + ARROWS MARKING THEIR DISTANCE
 
-\addplot[name path=neq_distr_f_filling_hyb0.4O11,solid,raw gnuplot,color=hblue,line width=1pt,opacity=0.0] gnuplot {
-plot "neq_distr_f_filling_hyb0.4O11.dat" u 1:3 w l;
-};
-
-\path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
-\addplot [fill=hcoral,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O5 and xaxis,soft clip={domain=-15:15}];
-\addplot [fill=hblue,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11 and xaxis,soft clip={domain=-15:15}];
+\addplot +[dashed,semithick,color=hgray,mark=none] coordinates {(-2.5, 0.0) (-2.5, 0.01)};
+\addplot +[dashed,semithick,color=hgray,mark=none] coordinates {(2.5, 0.0) (2.5, 0.01)};
+\draw [stealth-stealth,thick,color=gray](-2.5, 0.005) -- (2.5, 0.005);
 
@@
 % \node[fill=none,color=hred,scale={1.0}] at (axis cs:1.20,0.022){$F$};
- \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(c)};
- \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$v=0.4$};
+ \node[fill=none,scale=1.0] at (axis cs:-13.5,0.008) {\bfseries(c)};
+ \node[fill=none,scale=1.0] at (axis cs:11.5,0.008) {$v=0.4$};
 

### 2022-07-21 figures_Paper1/test_old/spec_filling_mu1_v_0.4_0.8_O_5_eph.tex
Added sources for figures

--- 2022-07-21 figures_Paper1/test_old/spec_filling_mu1_v_0.4_0.8_O_5_11_eph.tex
@@
 group style={
-group size=2 by 2,
+group size=2 by 1,
 xticklabels at=edge bottom,  
@@
 % grid=both,
-% xlabel={$\omega/t^{*}$},
+xlabel={$\omega/t^{*}$},
 ylabel={$A(\omega)/t^{*-1}$},
-legend style={at={(axis cs:0,0.1)},anchor=north,mark options={scale=1.0},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
+legend style={at={(axis cs:-9.3,0.017)},anchor=north,mark options={scale=0.85},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
 legend cell align=left,
@@
 
-% \addlegendimage{solid,color=hblue,scale={1.0},line width=1pt}
-% \addlegendentry{$el$};
-% \addlegendimage{solid,color=hred,scale={1.0},line width=1pt} 
-% \addlegendentry{$el+ph$};
+\addlegendimage{solid,color=hblue,scale={1.0},line width=1pt}
+\addlegendentry{$el$};
+\addlegendimage{solid,color=hred,scale={1.0},line width=1pt} 
+\addlegendentry{$el+ph$};
 
@@
 
-% VERTICAL LINES + ARROWS MARKING THEIR DISTANCE
-
-\addplot +[dashed,semithick,color=hgray,mark=none] coordinates {(-2.5, 0.0) (-2.5, 0.09)};
-\addplot +[dashed,semithick,color=hgray,mark=none] coordinates {(2.5, 0.0) (2.5, 0.09)};
-% \draw [stealth-stealth,thick,color=gray](-2.5, 0.03) -- (2.5, 0.03);
-
-% \node[fill=none,color=hblue,scale={1.0}] at (axis cs:-1.20,0.017){$F$}; 
-% \node[fill=none,color=hred,scale={1.0}] at (axis cs:1.20,0.022){$F$};
  \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(a)};
@@
 % grid=both,
-% xlabel={$\omega/t^{*}$},
+xlabel={$\omega/t^{*}$},
 % ylabel={$A(\omega)/t^{*-1}$},
-legend style={at={(axis cs:0,0.1)},anchor=north,mark options={scale=1.0},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
+legend style={at={(axis cs:-9.3,0.017)},anchor=north,mark options={scale=0.85},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
 legend cell align=left,
@@
 
-% VERTICAL LINES + ARROWS MARKING THEIR DISTANCE
-
-\addplot +[dashed,semithick,color=hgray,mark=none] coordinates {(-2.5, 0.0) (-2.5, 0.09)};
-\addplot +[dashed,semithick,color=hgray,mark=none] coordinates {(2.5, 0.0) (2.5, 0.09)};
-% \draw [stealth-stealth,thick,color=gray](-2.5, 0.03) -- (2.5, 0.03);
-
-% \node[fill=none,color=hblue,scale={1.0}] at (axis cs:-1.20,0.017){$F$}; 
-% \node[fill=none,color=hred,scale={1.0}] at (axis cs:1.20,0.022){$F$};
  \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(b)};
- \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$v=0.8$};
-
-%  3° figure
-
-\nextgroupplot[
-xmin=-15.,    
-xmax=15., 
-ymin=-0.01, 
-ymax=0.01,   
-minor tick num=1, 
-% grid=both, 
-xlabel={$\omega/t^{*}$},
-ylabel={$j(\omega)$},
-legend style={at={(axis cs:0,0.011)},anchor=north,mark options={scale=1.0},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
-legend cell align=left,
-clip mode=individual,
-clip marker paths=true, 
-xtick={-15,-10,-5,0,5,10,15},
-ytick={-0.01,0.00,0.01},
-% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012},
-% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012,\smash{\raisebox{-0.8\height}{5}}},
-x tick label style={
-    /pgf/number format/.cd,
-    fixed,
-    fixed zerofill,
-    precision=0,
-    /tikz/.cd},
-y tick label style={
-    /pgf/number format/.cd,
-    fixed,
-    fixed zerofill,
-    precision=0,
-    /tikz/.cd}
-]
-
-\addlegendimage{solid,color=hblue,scale={1.0},line width=1pt}
-\addlegendentry{$el$};
-\addlegendimage{solid,color=hred,scale={1.0},line width=1pt} 
-\addlegendentry{$el+ph$};
-
-% % % % % % % %  PLOTS
-
-% \draw (axis cs:4,0) -- (axis cs:10,0.01);
-
-\addplot[solid,raw gnuplot,color=hblue,line width=1pt] gnuplot {
-plot './J00_omega_hyb0.4O5.dat' u 1:2 w l;
-};
-
-\addplot[solid,raw gnuplot,color=hred,line width=1pt] gnuplot {
-plot './J00_omega_hyb0.4O5ph.dat' u 1:2 w l;
-};
-
-% VERTICAL LINES + ARROWS MARKING THEIR DISTANCE
-
-\addplot +[dashed,semithick,color=hgray,mark=none] coordinates {(-2.5, 0.0) (-2.5, 0.01)};
-\addplot +[dashed,semithick,color=hgray,mark=none] coordinates {(2.5, 0.0) (2.5, 0.01)};
-\draw [stealth-stealth,thick,color=gray](-2.5, 0.005) -- (2.5, 0.005);
-
-% \node[fill=none,color=hblue,scale={1.0}] at (axis cs:-1.20,0.017){$F$}; 
-% \node[fill=none,color=hred,scale={1.0}] at (axis cs:1.20,0.022){$F$};
- \node[fill=none,scale=1.0] at (axis cs:-13.5,0.008) {\bfseries(c)};
- \node[fill=none,scale=1.0] at (axis cs:11.5,0.008) {$v=0.4$};
-
-%  4° figure
-
-\nextgroupplot[
-xmin=-15.,    
-xmax=15., 
-ymin=0.00, 
-ymax=0.09,   
-minor tick num=1, 
-grid=both,
-xlabel={$\omega/t^{*}$},
-% ylabel={$A(\omega)/t^{*-1}$},
-legend style={at={(axis cs:0,0.1)},anchor=north,mark options={scale=1.0},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
-legend cell align=left,
-clip mode=individual,
-clip marker paths=true, 
-xtick={-15,-10,-5,0,5,10,15},
-ytick={0.00,0.03,0.06,0.09},
-% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012},
-% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012,\smash{\raisebox{-0.8\height}{5}}},
-x tick label style={
-    /pgf/number format/.cd,
-    fixed,
-    fixed zerofill,
-    precision=0,
-    /tikz/.cd},
-y tick label style={
-    /pgf/number format/.cd,
-    fixed,
-    fixed zerofill,
-    precision=0,
-    /tikz/.cd}
-]
-
-\addlegendimage{solid,color=hlime,scale={1.0},line width=1pt}
-\addlegendentry{$\Omega=5$};
-\addlegendimage{solid,color=hred,scale={1.0},line width=1pt}
-\addlegendentry{$\Omega=11$};
-
-% \addplot +[dashed,very thin,color=hblue,mark=none] coordinates {(-2.55, 0.0) (-2.55, 0.035)};
-% \addplot +[dashed,very thin,color=hblue,mark=none] coordinates {(0.525, 0.0) (0.525, 0.035)};
-% \draw [stealth-stealth,thick,color=hblue](-2.55, 0.015) -- (0.525, 0.015);
-
-% \addplot +[dashed,very thin,color=hred,mark=none] coordinates {(2.55, 0.0) (2.55, 0.035)};
-% \addplot +[dashed,very thin,color=hred,mark=none] coordinates {(-0.525, 0.0) (-0.525, 0.035)};
-% \draw [stealth-stealth,thick,color=hred](2.55, 0.02) -- (-0.525, 0.02);
-
-% \draw [-stealth,thick,color=hgray](0.35, 0.0055) -- (0.45, 0.004);
-% \draw [-stealth,thick,color=hgray](-0.35, 0.0055) -- (-0.45, 0.004);
-
-% \draw [-stealth,thick,color=hgray](2.0, 0.0045) -- (2.2, 0.003);
-% \draw [-stealth,thick,color=hgray](-2.0, 0.0045) -- (-2.2, 0.003);
-
-% % % % % % % %  PLOTS
-
-% \draw (axis cs:4,0) -- (axis cs:10,0.01);
-
-\addplot[solid,raw gnuplot,color=hlime,line width=1pt] gnuplot {
-plot './Green_hyb0.8O5.dat' u 1:(-1/3.1415)*($3) w l;
-};
-
-\addplot[name path=neq_distr_f_filling_hyb0.8O5,solid,raw gnuplot,color=hlime,line width=1pt,opacity=0.0] gnuplot {
-plot "neq_distr_f_filling_hyb0.8O5.dat" u 1:3 w l;
-};
-
-\addplot[solid,raw gnuplot,color=hred,line width=1pt] gnuplot {
-plot './Green_hyb0.8O11.dat' u 1:(-1/3.1415)*($3) w l;
-};
-
-\addplot[name path=neq_distr_f_filling_hyb0.8O11,solid,raw gnuplot,color=hred,line width=1pt,opacity=0.0] gnuplot {
-plot "neq_distr_f_filling_hyb0.8O11.dat" u 1:3 w l;
-};
-
-\path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
-\addplot [fill=hlime,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O5 and xaxis,soft clip={domain=-15:15}];
-\addplot [fill=hred,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O11 and xaxis,soft clip={domain=-15:15}];
-
-% \node[fill=none,color=hblue,scale={1.0}] at (axis cs:-1.20,0.017){$F$};
-% \node[fill=none,color=hred,scale={1.0}] at (axis cs:1.20,0.022){$F$};
- \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(d)};
  \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$v=0.8$};

### 2022-08-23 Paper1.tex
Added sources for figures
Final version 23.08.2022

@@
 \usepackage{comment}
-\usepackage{placeins}%enables \FloatBarier
-\usepackage{hyperref}
+\usepackage{placeins}%enables \FloatBarrier
+\usepackage[colorlinks=true]{hyperref} %hidelinks=true
 
@@
 %% REFERENCE
-\newcommand{\fig}[1]{Fig.\thinspace{}\ref{#1}}
-\newcommand{\figs}[1]{Figs.\thinspace{}\ref{#1}} 
-\newcommand{\Fig}[1]{Figure \ref{#1}}
-\newcommand{\eq}[1]{Eq.\thinspace{}(\ref{#1})}
-\newcommand{\Eq}[1]{Eq.\thinspace{}(\ref{#1})}
-\newcommand{\eqs}[1]{Eqs.\thinspace{}(\ref{#1})}
-\newcommand{\Eqs}[1]{Eqs.\thinspace{}(\ref{#1})}
+\newcommand{\fig}[1]{Fig.~\ref{#1}}
+\newcommand{\figs}[1]{Figs.~\ref{#1}} 
+\newcommand{\Fig}[1]{Figure~\ref{#1}}
+\newcommand{\eq}[1]{Eq.~\eqref{#1}}
+\newcommand{\Eq}[1]{Eq.~\eqref{#1}}
+\newcommand{\eqs}[1]{Eqs.~\eqref{#1}}
+\newcommand{\Eqs}[1]{Eqs.~\eqref{#1}}
 \newcommand{\feqs}{eqs.\@\xspace}
@@
 \newcommand{\und}{\underline}
-\newcommand{\iim}{\Im{}\,}
+\DeclareMathOperator*{\rre}{Re}
+\DeclareMathOperator*{\iim}{Im}
+\DeclareMathOperator*{\Tr}{Tr}
 \newcommand{\li}{\mathcal L}
@@
 \newcommand{\vv}[1]{\boldsymbol{#1}}
-\newcommand{\Dph}{\underline{\Delta}_\mathrm{ph}(\omega)}
-\newcommand{\Daux}{\underline{\Delta}_\mathrm{aux}(\omega)}
-\newcommand{\DRph}{\Delta^R_\mathrm{ph}(\omega)}
-\newcommand{\DRaux}{\Delta^R_\mathrm{aux}(\omega)}
-\newcommand{\DKph}{\Delta^K_\mathrm{ph}(\omega)}
-\newcommand{\DKaux}{\Delta^K_\mathrm{aux}(\omega)}
+\newcommand{\Dph}{\underline{\Delta}\text{ph}(\omega)}
+\newcommand{\Daux}{\underline{\Delta}_\text{aux}(\omega)}
+\newcommand{\DRph}{\Delta^\text{R}_\text{ph}(\omega)}
+\newcommand{\DRaux}{\Delta^\text{R}_\text{aux}(\omega)}
+\newcommand{\DKph}{\Delta^\text{K}_\text{ph}(\omega)}
+\newcommand{\DKaux}{\Delta^\text{K}_\text{aux}(\omega)}
 
@@
 \newcommand{\phys}{} %my preference 
+\newcommand{\aamp}{\mathcal{A}}
 
@@
 \definecolor{brown}{RGB}{200,127,50}
+\definecolor{blue}{RGB}{0,0,255}
 
@@
 
+\newcommand{\jlcomm}[1]{{\color{orange} [JL COMMENT: #1]}}
+\newcommand{\jlch}[1]{{\color{orange} #1}}
+
+\newcommand{\tmcomm}[1]{{\color{blue} [TM COMMENT: #1]}}
+\newcommand{\tmch}[1]{{\color{blue} #1}}
+
 \begin{document}
 
-\title{Impact ionization processes in driven Mott insulating layer: influence of fermion baths and phonons}
+%EA
+\title{Impact ionization processes in a photodriven Mott insulator: influence of phononic dissipation}
 
@@
 
-We study a model for photovoltaic energy collection consisting of a Mott insulating layer coupled to local acoustic phonons between two wide-band fermion baths at different chemical potentials, driven to the non-equilibrium steady state by an external AC field.
-We treat electron correlations with non-equilibrium dynamical mean field theory (DMFT) using the so-called auxiliary master equation approach as impurity solver, incuding phonons via the Migdal approximation.
-
-We show that with a small coupling to fermion baths, the peak of the photocurrent is mainly due to impact ionization processes, while with higher coupling is due primarily to direct excitations.
-This occurs also for higher electric field amplitudes, that boost overall the photocurrent and the double occupation.
-Acoustic phonons slightly enhance the photocurrent for small driving frequencies and suppress it at higher values, in correspondence to the peak, disregarding the dominant electronic scattering process taking place.
-Their effect is independent of the bath-layer coupling value and the electric field amplitude.
+We study a model for photovoltaic energy collection consisting of a Mott insulating layer in presence of acoustic phonons, coupled to two wide-band fermion leads at different chemical potentials and driven by a periodic electric field.
+We treat electron correlations with nonequilibrium dynamical mean-field theory (DMFT) using the so-called auxiliary master equation approach as impurity solver and include dissipation by acoustic phonons via the Migdal approximation.
+For a small hybridization to the leads, we obtain a peak in the photocurrent as a function of the driving frequency which can be associated with impact ionization processes.
+For larger hybridizations the shallow peak suggests a suppression of impact ionization with respect to direct photovoltaic excitations.
+Acoustic phonons slightly enhance the photocurrent for small driving frequencies and suppress it at frequencies around the main peak.
+This effect occurs at all considered hybridization strengths.
 
@@
 
-\pgcomm{IS FERMION BATHS THE APPROPRIATE TERM?}
+The idea of designing photovoltaic devices exploiting the Mott gap to convert electromagnetic radiation into energy has become popular in recent years~\cite{mano.10,li.ch.13,gu.gu.13,co.ma.14,wa.li.15}.
+In particular, it has been suggested that in strongly correlated materials, highly excited charge carriers could use their extra energy to excite additional carriers across the Mott gap via impact ionization (II)~\cite{mano.10,co.ma.14}, thus
+potentially improving their efficiency beyond the Shockley-Queisser limit~\cite{sh.qu.61}.
+Although II is also present in conventional semiconductor devices, the time scales for electron-electron scattering are typically much longer than in correlated materials, so that highly excited electrons will mostly dissipate their energy to phonons.
 
-The idea of designing photovoltaic devices exploiting the Mott gap to convert electromagnetic radiation into energy has become popular in the recent years \cite{mano.10,li.ch.13,gu.gu.13,co.ma.14,wa.li.15}.
-In particular, it has been
-suggested that in strongly correlated materials, highly excited charge carriers could use their extra energy to excite additional carriers across the Mott gap via impact ionization \cite{mano.10,co.ma.14}, thus
-potentially improving their efficiency beyond the Shockley-Queisser limit \cite{sh.qu.61}.
-Although impact ionization is also present in conventional semiconductor devices, the time scales for electron-electron scattering are typically much longer than in correlated materials, so that highly excited electrons will mostly dissipate their energy to phonons.
+Experimentally, evidence for fast carrier multiplication processes has been detected via pump-probe experiments in VO$_2$~\cite{ho.bi.16}.
+Oxide heterostructures based on LaVO$_3$/SrTiO$_3$ have been identified as promising candidates, due to the ideal band gap and the strong polar field, able to separate the excited charge carriers~\cite{as.bl.13}.
+There are however some drawbacks, such as the low mobility of the carriers~\cite{wa.li.15,je.re.18}, which still put into question these materials’ applicability as efficient solar cells.
+Thus while a large-scale application of Mott-based solar cells may be difficult to achieve, employing them as photodetectors may be more promising on the long run, due to their high photoresponsivity.
+From the scientific point of view and for future applications it is thus worthwile to further investigate the properties of Mott-based photovoltaic materials and the mechanisms behind their inner workings, to explore whether alternative unexpected paths can be opened.
+In fact, a lot of theoretical work has been done to understand the II process (see, e.g.~\cite{co.ma.14,ec.we.11,ec.we.13,we.he.14,pe.be.19,so.do.18,ka.wo.20,ma.ev.22}).
 
-Experimentally, evidence for fast carrier multiplication processes has indeed been detected via pump-probe experiments in VO$_2$ \cite{ho.bi.16}.
-Oxide heterostructures based on LaVO$_3$/SrTiO$_3$ have been identified as promising candidates, due to the ideal band gap and the strong polar field, able to separate the excited charge carriers \cite{as.bl.13}.
-There are however some drawbacks, such as the low mobility of the carriers \cite{wa.li.15,je.re.18}, which still question these materials’ applicability as efficient solar cells.
-In this regard, it has to be mentioned that, while a large-scale application of Mott-based solar cells may be hard to achieve, the employment of such systems as photodetectors may be more promising on the long run, due to their high photoresponsivity.
+As a scattering process, II competes with electron-phonon (e-ph) scattering which is the dominant relaxation mechanism in conventional semiconductors.
+This may not be the case in Mott insulators, at least in certain cases ~\cite{co.ma.14}.
+Therefore, it is essential to understand the influence of e-ph scattering on the photocurrent and II in Mott photovoltaic devices, which is the issue we address in this paper.
 
-Therefore, the properties of the Mott-based photovoltaic mechanism deserve to be investigated further, from the scientific point of view and for future applications in order to explore, whether alternative unexpected paths could be opened.
-And in fact, a lot of theoretical work has been done, in order to understand the impact ionization process (see, e.g.
-\cite{co.ma.14,ec.we.11,ec.we.13,we.he.14,pe.be.19,so.do.18,ka.wo.20,ma.ev.22}).
+For this goal we consider the simplified model shown in Fig.~\ref{fig:setup}, consisting of a Hubbard layer located between two leads.
+The metallic leads have themselves a wide band, which is effectively narrowed due to the weak coupling to intermediate layers which we take as models for the contacts.
+Electrons on the Hubbard layer interact locally with acoustic phonons.
+An external periodic electric field induces a Floquet steady state with a current flowing from the lead with the lower to the higher chemical potential, thus transferring its energy.
+ We address this periodic problem
+ via nonequilibrium Floquet dynamical mean-field theory (F-DMFT).
 
-The effects of the coupling to metallic leads and of phonons dissipation are essential features to properly establish the occurrence of impact ionization in Mott-based photovoltaic setups.
-They haven't been taken into account up to now and in this article we address such issues.
-
-% First, because the effect of phonons on impact ionization is still to clarify completely and therefore there are still questions regarding the physical mechanisms to be answered.
-Once such questions are answered, a more detailed treatment of phonons, together with DFT may address more accurately the precise entity of the their effect.
-
-\begin{figure}[ht]
+\begin{figure}[b] 
 % \captionsetup{width=\textwidth} 
-\includegraphics[width=0.9\linewidth]{./figures_Paper1/setup.pdf}
-\caption{(Colour online) Schematic representation of the considered setup.
-A correlated layer with local Hubbard interaction $U$ and electron-phonon coupling $g$ (green) is sandwiched between two non-interacting layers (red) via the coupling $v$ (black).
-The latter are in turn coupled via $\Gamma$ (orange) to wide-band fermion reservoirs (blue) at different chemical potentials $\mu_{l/r}$.}
+\includegraphics[width=0.9\linewidth]{./figures_Paper1/setup_voltmeter.pdf}
+\caption{(Color online) Schematic representation of the setup.
+A central, correlated layer with local Hubbard interaction $U$ and e-ph coupling $g$ (green) is sandwiched between two non-interacting layers (red) via the hybridization $v$ (black).
+The latter are in turn coupled to wide-band fermion reservoirs (blue) with different chemical potentials $\mu_{\text{l}/\text{r}}$, which introduce a broadening $\Gamma=\Gamma_{\text{l}}=\Gamma_{\text{r}}$.}
 \label{fig:setup}
@@
 
-The setup used is depicted in Fig.\ref{fig:setup}: a Hubbard insulating layer with local acoustic phonons under AC driving is put between two intermediate non-interacting layers coupled to wide-band fermion reservoirs at different chemical potentials, acting as metallic leads.
-For sake of simplicity, we refer for the rest of the article to the non-interacting layers and fermion reservoirs together simply as fermion baths.
-We address the non-equilibrium steady state situation under an external AC field, treated via nonequilibrium Floquet dynamical mean-field theory (F-DMFT).
+Our goal is to investigate the occurrence of II in this photovoltaic setup and how it is affected by the presence of phonons. 
+Specifically we study the behavior of the photovoltaic current, the spectral properties as well as the double occupation as a function of the hybridization strength and the properties of the phonons.
+Our analysis can only provide qualitative results, while quantitative comparisons with experimental systems require a more realistic setup and are beyond the scope of this work.
 
-Our goal is to show for which values of the bath-layer coupling impact ionization clearly occurs and how is influenced by the effect of phonons.
+We find that a small hybridization to the leads is more favorable for II than a larger one.
+II therefore plays a crucial role in compensating the smaller charge injection, giving the same order of magnitude in the photocurrent as for the larger hybridization.
+In all cases, the interaction with phonons slightly enhances the photocurrent for small driving frequencies, while suppressing it in vicinity of the main peak.
 
-We limit our analysis to qualitative and semi-quantitative features of the influence of fermion baths and phonons on photocurrent, double occupation and spectral properties. 
-An accurate quantitative analysis of such effects and their relative signatures in possible experimental setups of Mott solar cells is outside the scope of this work.
-
-We find that a small coupling to fermion baths clearly enhances impact ionization respect to a bigger coupling, for which direct excitations are dominant.
-Impact ionization therefore plays a crucial role, compensating the smaller charge injection and giving the same magnitude in the photocurrent of the case with a bigger coupling.
-Such results remain the same considering higher values of electric field amplitude, although the current and double occupation are greatly increased.
-The phonons slightly enhance the photocurrent for small driving frequencies, while suppressing it at higher values, in corrispondence to the peak, disregarding the dominant electron scattering process taking place.
-Such influence of phonons on the photocurrent is substantially unaltered sweeping over different values of the bath-layer coupling and of electric field amplitude.
-
-The structure of the paper is the following: in Sec.\ref{sec:Model} we describe the model Hamiltonian.
-Methods, formalism and observables used are explained in Sec.\ref{sec:Method_formalism}.
-We discuss our results in Sec.\ref{sec:results}.
-We present our conclusions in Sec.\ref{sec:conclusions}.
+The structure of the paper is as follows: in Sec.~\ref{sec:Model} we describe the model Hamiltonian.
+Methods, formalism and observables are presented in Sec.~\ref{sec:Method_formalism}.
+We discuss our results in Sec.~\ref{sec:results} and present our conclusion in Sec.~\ref{sec:conclusions}.
 
@@
 
-Our setup (Fig.\ref{fig:setup}) consists of a central Hubbard layer at half filling with local phonon coupling, under an external AC driving,attached to fermionic baths:
-
+Our setup introduced in Sec.~\ref{sec:intro} and shown in Fig.~\ref{fig:setup} is described by the Hamiltonian
+%
 \begin{equation}
@@
 \begin{split} 
-\hat{H}(t)&=\varepsilon_c \sum_{i\sigma}\hat{n}_{i\sigma} -\sum_{\sigma}\sum_{(i,j)} t_{ij}(t) \hat{c}^{\dagger}_{i\sigma} \hat{c}_{j\sigma}
-\\ & + U \sum_{i} \hat{n}_{i\uparrow} \hat{n}_{i\downarrow}+\hat{H}_{e-ph} + \hat{H}_{ph}+\hat{H}_{bath}
+\hat{H}(t)&=\varepsilon_{\text{c}} \sum_{i\sigma}\hat{n}_{i\sigma} -\sum_{\sigma}\sum_{(i,j)} t_{ij}(t) \hat{c}^{\dagger}_{i\sigma} \hat{c}_{j\sigma}
+\\ & + U \sum_{i} \hat{n}_{i\uparrow} \hat{n}_{i\downarrow}+\hat{H}_{\text{e-ph}} + \hat{H}_{\text{ph}}+\hat{H}_{\text{lead}}.
 \end{split}
 \end{equation}
+% 
+The operator $\hat{c}^{\dagger}_{i\sigma}$ ($\hat{c}_{i\sigma}$) creates (annihilates) a particle with spin $\sigma= \lbrace \uparrow,\downarrow \rbrace$ on the $i$-th lattice site and $\hat{n}_{i\sigma}\equiv \hat{c}^{\dagger}_{i\sigma} \hat{c}_{i\sigma}$ is the particle number operator.
+We denote with $(i,j)$ the sum over nearest-neighbor sites and with $\varepsilon_{\text{c}} \equiv -U/2$ the on-site energy.
+The driving field consists of a time-periodic, homogeneous and monochromatic electric field with frequency $\Omega$.
+In the temporal gauge it enters via the Peierls substitution in the time-dependent hopping in Eq.~\eqref{eq:Hamiltonian}~\cite{peie.33}
 
-The operator $\hat{c}^{\dagger}_{i\sigma}$ ($\hat{c}_{i\sigma}$) creates (annihilates) an electron with spin $\sigma= \lbrace \uparrow,\downarrow \rbrace$ on the \emph{i-th} lattice site, with $\hat{n}_{i\sigma}\equiv \hat{c}^{\dagger}_{i\sigma} \hat{c}_{i\sigma}$.
-We denote with $(i,j)$ the sum over next neighbour sites and with $\varepsilon_c \equiv -U/2$ the electron onsite energy.
-The AC field consists of a time-periodic, homogeneous and monochromatic electric field with frequency $\Omega$.
-It enters via the Peierl's substitution in the time-dependent hopping in Eq.
-(\ref{eq:Hamiltonian}) \cite{peie.33}:
 \begin{equation}\label{eq:peierls} 
-t_{ij}(t) = t_{c} \ e^{-i \frac{q}{\hbar} \left( \vec{r}_j - \vec{r}_i \right) \cdot \vec{A}(t)}, 
+t_{ij}(t) = t_{\text{c}} \ e^{-\ii \frac{q}{\hbar} \left( \vec{r}_j - \vec{r}_i \right) \cdot \vec{A}(t)}, 
 \end{equation}
-where $t_{c}$ is the intra-lattice hopping, $\vec{A}$(t) is the time-dependent vector potential, $\hbar$ the Planck's constant and $q$ the charge of the electron.
-Here $\vec{A}(t)=\vec{e}_{0} A(t)$ is along the lattice body diagonal, i.e.
-$\vec{e}_{0}=(1,1,\dots,1)$.
-For the AC field, $A(t)=\frac{\hbar}{qa}A\sin\Omega t$, with $A=-\frac{qE_0a}{\hbar\Omega}$, being $E_0$ the electric field amplitude and $a$ the lattice spacing ~\cite{ts.ok.08}.
-Therefore in the temporal gauge $\vec{E}= -\partial_{t}\vec{A}(t) = \vec{e}_{0}E_0 \cos\Omega t$.
+% 
+where $t_{\text{c}}$ is the intra-layer hopping, $\vec{A}$(t) the time-dependent vector potential, $\hbar$ Planck's constant and $q$ the charge of the electrons.
+Following Refs.~\cite{ts.ok.08,mu.we.18}, we choose for simplicity
+ $\vec{A}(t)=\vec{e}_{0} A(t)$, which points along the 
+lattice body diagonal $\vec{e}_{0}=(1,1,\dots,1)$.
+$A(t)=\frac{\hbar}{qa}\aamp\sin(\Omega t)$ with $\aamp=-\frac{qE_0a}{\hbar\Omega}$,  $E_0$ is the  electric field amplitude, and $a$ the lattice spacing ~\cite{ts.ok.08}.
+In this temporal gauge the electric field is $\vec{E}= -\partial_{t}\vec{A}(t) = \vec{e}_{0}E_0 \cos(\Omega t)$.
 
-The local electron-phonon coupling is included as in Ref.\cite{ma.ga.22u}, considering an acoustic phonon branch attached to each lattice site via the Hamiltonian 
+The local e-ph coupling is included as in Ref.~\cite{ma.ga.22u} with an acoustic phonon branch attached to each lattice site via the Hamiltonian 
 \begin{equation}\label{eq:e-ph_ham} 
-\hat{H}_{e-ph} = g \sum_{i\sigma} \hat{n}_{i\sigma} \hat{x}_{i},  
+\hat{H}_{\text{e-ph}} = g \sum_{i\sigma} \hat{n}_{i\sigma} \hat{x}_{i},  
 \end{equation}
-with $g$ the electron-phonon coupling and $\hat{x}_{i} \equiv \frac{1}{\sqrt{2}} \left( \hat{b}^{\dagger}_{i} + \hat{b}_i \right)$, where $\hat{b}^{\dagger}_{i}$ ($\hat{b}_{i}$) creates (annihilates) a phonon of the acoustic branch at site $i$, with dispersion relation in $\hat{H}_{ph}$ \cite{ma.ga.22u}.
+with $g$ as e-ph coupling and $\hat{x}_{i} \equiv \frac{1}{\sqrt{2}} \left( \hat{b}^{\dagger}_{i} + \hat{b}_i \right)$, where $\hat{b}^{\dagger}_{i}$ ($\hat{b}_{i}$) creates (annihilates) a phonon of the acoustic branch at site $i$, with dispersion relation described by $\hat{H}_{\text{ph}}$~\cite{ma.ga.22u}.
+Details on the leads are provided in~\ref{sec:Dyson_equation}.
 
-Details on the baths are provided in \ref{sec:Dyson_equation}.
-
-In this paper we consider the correlated system as a $d$-dimensional layer in $d+1$ dimensions and we take the limit of infinite dimensions $d \rightarrow \infty$ by rescaling the hopping as $t_{c}=t^{*}/2\sqrt{d}$ \footnote{We tune $t^*$ such that we reproduce as best as possible the DOS of a 2D layer with $t_c$ = 1, following Ref.\cite{so.do.18}.}.
-With $a=1$, sums over crystal momentum ${\bf k}$ of a generic quantity $\chi$ read $\sum_{{\bf k}} \chi(\omega,{\bf k}) \rightarrow \int d\epsilon \int   d\overline{\epsilon} \ \rho(\epsilon,\overline{\epsilon}) \chi(\omega;\epsilon,\overline{\epsilon})$ with $\rho(\epsilon,\overline{\epsilon}) = (1/\pi t^{* 2}) \ exp(-( \epsilon^{2} + \overline{\epsilon}^{2})/t^{* 2})$ the joint density of states (JDOS) ~\cite{ts.ok.08}, with
+For mathematical simplicity~\cite{ge.ko.92,ao.ts.14}, 
+ we consider the correlated central region as a $d$-dimensional layer and consider the limit of infinite dimensions $d \rightarrow \infty$ by rescaling the hopping as $t_{\text{c}}=t^{\ast}/2\sqrt{d}$.
+Taking $a=1$, sums over the crystal momentum ${\bf k}$ of a generic quantity $\chi$ read $\sum_{{\bf k}} \chi(\omega,{\bf k}) \rightarrow \int d\epsilon \int   d\overline{\epsilon} \ \rho(\epsilon,\overline{\epsilon}) \chi(\omega;\epsilon,\overline{\epsilon})$ with $\rho(\epsilon,\overline{\epsilon}) = (1/\pi t^{\ast 2}) \exp[-( \epsilon^{2} + \overline{\epsilon}^{2})/t^{\ast 2}]$ as the joint density of states~\cite{ts.ok.08} and with
+% 
 \begin{align}\label{eq:d-dim_crystal_dep}
 \begin{split}  
-\epsilon & = -2t_{c} \sum_{i=1}^{d} cos(k_i a) \\  
-\overline{\epsilon}& = -2t_{c}\sum_{i=1}^{d} sin(k_i a). \\
+\epsilon & = -2t_{\text{c}} \sum_{i=1}^{d} \cos(k_i a), \\  
+\overline{\epsilon}& = -2t_{\text{c}}\sum_{i=1}^{d} \sin(k_i a). \\
 \end{split}  
 \end{align}
+%
 
-In this paper we set $\hbar = k_B = a = 1 = -q$, so that every physical quantity is in units of $t^{*}$.
+Within the remainder of this paper we set $\hbar = k_{\text{B}} = a = 1 = -q$, $t^{\ast}=2\sqrt{2}$ ~\footnote{With such choice for $t^{\ast}$ we reproduce the DOS of a 2D layer with $t_{\text{c}}=1$  in order to compare with Ref.~\cite{so.do.18}.} and $t_r \equiv \frac{t^{\ast}}{2\sqrt{2}}=1$ as unit of energy.
+
+% In Tommasos paper we also chose -q=1.
+Given the amplitude of the vector potential above, setting q=-1 allows us to take positive values of E_0 and Omega.
+same sign of j0 (see old draft).
+increasing the mu I have negative current meaning that particle/electric current is flowing in the opposite direction.
 
@@
 
-To correctly describe the nonequilibrium periodic steady-state (NESS), we use the Floquet generalization of non-equilibrium Green's function (NEGF) approach \cite{ts.ok.08}.
-Every function $G(t;t{'})$ satisfying the periodicity relation $G(t;t{'})=G(t+\tau;t{'}+\tau)$, with $\tau=2\pi/\Omega$ the period related to the external driving frequency $\Omega$, may be represented as \cite{ts.ok.08,sc.mo.02u,jo.fr.08}
+To correctly describe the nonequilibrium periodic steady state, we use the Floquet generalization of the nonequilibrium Green's function (NEGF) approach~\cite{ts.ok.08}.
+Every function $G(t,t^{\prime})$ satisfying the periodicity relation $G(t,t^{\prime})=G(t+\tau,t^{\prime}+\tau)$, with $\tau=2\pi/\Omega$ as the period related to the external driving frequency $\Omega$, may be represented as~\cite{ts.ok.08,sc.mo.02u,jo.fr.08}
 
@@
 \label{eq:FloquetGF} 
-\underline{G}_{mn}(\omega) =\int dt_{rel} \int_{-\tau/2}^{\tau/2} \frac{dt_{av}}{\tau} e^{i[\left(\omega+m\Omega\right) t -\left( \omega+n\Omega\right)t{'}]} \underline{G}(t,t'),
+\underline{G}_{mn}(\omega) =\int \dd t_{\text{rel}} \int_{-\tau/2}^{\tau/2} \frac{dt_{\text{av}}}{\tau} \ee^{\ii[\left(\omega+m\Omega\right) t -\left( \omega+n\Omega\right)t^{\prime}]} \underline{G}(t,t'),
 \end{equation}
 
-known as the the \emph{Keldysh-Floquet} GF, and
+known as the \emph{Keldysh-Floquet} GF.
+The integration variables $t_{\text{rel}} = t-t^{\prime}$ and $t_{\text{av}} = (t+t^{\prime})/2$ are the relative and average times.
+Within the rest of this work, we denote a Floquet-represented matrix either as $X_{mn}$ with explicit indices, or use a boldface letter $\bf{X}$.
+The underline indicates the overall \emph{Keldysh} structure
 
-\begin{equation}\label{eq:WignerGF}
-\underline{G}_{l}(\omega) =\int dt_{rel} \int_{-\tau/2}^{\tau/2} \frac{dt_{av}}{\tau} e^{i\omega t_{rel} + il\Omega t_{av}} \underline{G}(t,t'),
-\end{equation}
-
-the \emph{Wigner} GF ~\cite{ts.ok.08}.
-$t_{rel} = t-t{'}$ and $t_{av} = (t+t{'})/2$ are the relative and average-time variables.
-Eqs.
-(\ref{eq:FloquetGF}) and (\ref{eq:WignerGF}) are related via the relation
-
-\begin{equation}\label{eq:Wig2Fl}
-\underline{G}_{mn}(\omega)=\underline{G}_{m-n}\left(\omega+\frac{m+n}{2}\Omega \right),
-\end{equation}
-
-We denote in the rest of this work a Floquet-represented matrix as either $X_{mn}$, with the explicit indices, or using a boldface letter, $\bf{X}$.
-A single index as subscript, $X_{l}$, is reserved for the Wigner representation.
-The underline indicates the overall structure
 \begin{equation}\label{eq:Keld-structure}
@@
 \begin{pmatrix}
-{\bf G}^{R} & {\bf G}^{K}\\
-{\bf 0}         & {\bf G}^{A} \\
+{\bf G}^{\text{R}} & {\bf G}^{\text{K}}\\
+{\bf 0}         & {\bf G}^{\text{A}} \\
 \end{pmatrix},
@@
 which contains the \emph{retarded}, \emph{advanced} and \emph{Keldysh} components $\textbf{G}^{\text{R,A,K}}$, where $\textbf{G}^{\text{A}}=(\textbf{G}^{\text{R}})^{\dagger}$.
-The \emph{Keldysh} component is defined as $\textbf{G}^{K} \equiv \textbf{G}^{>} + \textbf{G}^{<}$, with $\textbf{G}^{\lessgtr}$ the \emph{lesser} and \emph{greater} components~\cite{schw.61,keld.65,ra.sm.86,ha.ja}
+The \emph{Keldysh} component is defined as $\textbf{G}^{\text{K}} \equiv \textbf{G}^{>} + \textbf{G}^{<}$, with $\textbf{G}^{\lessgtr}$ as \emph{lesser} and \emph{greater} components~\cite{schw.61,keld.65,ra.sm.86,ha.ja}.
 
@@
 \begin{equation}\label{eq:FullDysonEq}
-\underline{{\bf G}}^{-1}(\omega_n;\epsilon,\overline{\epsilon}) = \underline{{\bf G}}^{-1}_{0}(\omega_n;\epsilon,\overline{\epsilon}) - \underline{{\bf \Sigma}}(\omega_n;\epsilon,\overline{\epsilon}) - \underline{{\bf \Sigma}}_{e-ph}(\omega_n;\epsilon,\overline{\epsilon}),
+\underline{{\bf G}}^{-1}(\omega_n;\epsilon,\overline{\epsilon}) = \underline{{\bf G}}^{-1}_{0}(\omega_n;\epsilon,\overline{\epsilon}) - \underline{{\bf \Sigma}}(\omega_n;\epsilon,\overline{\epsilon}) - \underline{{\bf \Sigma}}_{\text{e-ph}}(\omega_n;\epsilon,\overline{\epsilon}).
 \end{equation}
 
-The lattice GF of the non-interacting part of the Hamiltonian, Eq. (\ref{eq:Hamiltonian}), is
+Therein, the lattice GF of the non-interacting part of the Hamiltonian in Eq.~\eqref{eq:Hamiltonian} is
 
 \begin{equation}\label{eq:non-int_InvGF} 
-\underline{G}^{-1}_{0,mn}(\omega_n;\epsilon,\overline{\epsilon}) =  \underline{g}^{-1}_{0,mn}(\omega_n;\epsilon,\overline{\epsilon}) - \sum_{\rho\in\{l,r\}}v^2_{\rho}\underline{g}_{b,\rho}(\omega_n;\epsilon)\delta_{mn},
+\underline{G}^{-1}_{0,mn}(\omega_n;\epsilon,\overline{\epsilon}) =  \underline{g}^{-1}_{0,mn}(\omega_n;\epsilon,\overline{\epsilon}) - \sum_{\rho\in\{\text{l},\text{r}\}}v^2_{\rho}\underline{g}_{\text{b},\rho}(\omega_n;\epsilon)\delta_{mn}
 \end{equation}
 
- with $v_{l/r}$ the bath-layer coupling, $\omega_n \equiv \omega + n\Omega$, $n\in\mathbbm{Z}$, and
+with $v_{\text{l}/\text{r}}$ as lead-layer hybridization, $\omega_n \equiv \omega + n\Omega$, $n\in\mathbbm{Z}$, and
 
- \begin{align}\label{eq:inv_non-int_lat_GF_comps}
+\begin{equation}\label{eq:inv_non-int_lat_GF_comps}
 \begin{split}
-\left[ g^{-1}_{0}(\omega_n;\epsilon,\overline{\epsilon})) \right]^{R}_{mn} & = \left( \omega_n + i0^{+} -\varepsilon_c \right)\delta_{mn} - \varepsilon_{mn}(\epsilon,\overline{\epsilon})) \\
-\left[ g^{-1}_{0}(\omega_n;\epsilon,\overline{\epsilon})) \right]^{K}_{mn} & = 0 \\
-\end{split}.
-\end{align}
+\left[ g^{-1}_{0}(\omega_n;\epsilon,\overline{\epsilon})) \right]^{\text{R}}_{mn} & = \left( \omega_n + i0^{+} -\varepsilon_{\text{c}} \right)\delta_{mn} - \varepsilon_{mn}(\epsilon,\overline{\epsilon}), \\
+\left[ g^{-1}_{0}(\omega_n;\epsilon,\overline{\epsilon})) \right]^{\text{K}}_{mn} & = 0
+\end{split}
+\end{equation}
 
-In the steady-state, the inverse Keldysh component is negligible \cite{so.do.18}. The Floquet dispersion relation, $\varepsilon_{mn}$, for the AC field in a hyper-cubic lattice is \cite{ts.ok.08}
+as the noninteracting Green's function of the isolated layer, whose inverse Keldysh component is negligible in the steady state.
+The Floquet dispersion relation $\varepsilon_{mn}$ for the periodic field in a hyper-cubic lattice is~\cite{ts.ok.08}
 
@@
 \label{eq:Floquet_disp}
-\varepsilon_{mn}(\epsilon,\overline{\epsilon}) = \left\{
-                \begin{array}{ll}
-                  \epsilon J_{m-n}(A) \quad m-n:\textrm{even} \\
-                  i\overline{\epsilon}J_{m-n}(A) \quad m-n:\textrm{odd}
-                \end{array}
-              \right  .
+\varepsilon_{mn}(\epsilon,\overline{\epsilon}) = \begin{cases}
+\epsilon J_{m-n}(\aamp) & m-n:\text{even}, \\
+\ii\overline{\epsilon}J_{m-n}(\aamp) & m-n:\text{odd},
+\end{cases}
+\end{equation} 
+% 
+where $J_n$ denotes the $n$-th order Bessel function of the first kind, with the argument $\aamp$ defined in Sec.~\ref{sec:Model}.
+The  GF $\underline{g}_{\text{b},\text{l}/\text{r}}$ on the $d$-dimensional boundary of the decoupled leads,  consisting of a single layer coupled to a semi-infinite reservoir in the wide-band limit with broadening $\Gamma_{\text{l}/\text{r}}$ (cf.
+Fig.~\ref{fig:setup}) is given by
+
+\begin{align}
+g^{\text{R}}_{\text{b},\text{l}/\text{r}}(\omega;\epsilon) &= \frac{1}{\omega-\varepsilon_{\text{l}/\text{r}}(\epsilon)+\ii\Gamma_{\text{l}/\text{r}}},\label{eq:retarded_bath_GF} \\
+g^{\text{K}}_{\text{b},\text{l}/\text{r}}(\omega;\epsilon) &= 2\ii \iim[g_{\text{b},\text{l}/\text{r}}^{\text{R}}(\omega;\epsilon)][1-2f(\omega,\mu_{\text{l}/\text{r}},\beta)], \label{eq:keldysh_bath_GF}
+\end{align}
+
+where $\varepsilon_{\text{l}/\text{r}}(\epsilon)=\varepsilon_{\text{l}/\text{r}} +\frac{t_{\text{l}/\text{r}}}{t^\ast}\epsilon$ is the dispersion, $f(\omega,\mu_{\text{l}/\text{r}},\beta)=1/[\ee^{\beta(\omega-\mu_{\text{l}/\text{r}})}+1]$ the Fermi-Dirac distribution function at inverse temperature $\beta \equiv 1/T$, $\varepsilon_{\text{l}/\text{r}}$ the onsite energy and $t_{\text{l}/\text{r}}$ the hopping within the $d$-dimensional layer of the lead.
+
+The electron self-energy (SE) $\underline{\bf{\Sigma}}$ is obtained from F-DMFT and therefore independent of the crystal momentum, i.e.
+$\underline{\bf{\Sigma}}(\omega;\epsilon,\overline{\epsilon}) \simeq \underline{\bf{\Sigma}}(\omega)$.
+Further details are given in Sec.~\ref{sec:FDMFT_implementation}.
+
+The e-ph SE is also included locally as $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega;\epsilon,\overline{\epsilon}) \simeq \underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$.
+In terms of the Keldysh contour time arguments $z$ and $z^\prime$, it has the form
+
+\begin{equation}\label{eq:backbone_e-ph_SE}
+\Sigma_{\text{e-ph}}(z,z^{\prime}) = \ii g^{2} G(z,z^{\prime}) D_{\text{ph}}(z,z^{\prime}).
 \end{equation}
 
-with $J_n$ denoting the $n$-th order Bessel function of the first kind, with argument $A$ defined in \se\ref{sec:Model}.
-$\underline{g}_{b,l/r}$ is the GF of the bath, composed by a $d$-dimensional layer, coupled to an infinite fermion reservoir via the hopping term $\Gamma$ (see Fig.\ref{fig:setup}).
-Its \emph{retarded} and \emph{Keldysh} components are
-
-\begin{equation}
-\label{eq:retarded_bath_GF}
-g^{R}_{b,l/r}(\omega;\epsilon) = \frac{1}{\omega-\varepsilon_{l/r}(\epsilon)+i\Gamma_{l/r}}
-\end{equation}
-
-\begin{equation}
-\label{eq:keldysh_bath_GF}
-g^{K}_{b,l/r}(\omega;\epsilon) = 2i \Im g_{b,l/r}^{R}(\omega;\epsilon)[1-2f(\omega,\mu_{l/r},\beta)]
-\end{equation}
-
-with dispersion $\varepsilon_{l/r}(\epsilon)=\varepsilon_{l/r} +\frac{t_{l/r}}{t^*}\epsilon$, where $f(\omega,\mu_{l/r},\beta)=1/(\ee^{\beta(\omega-\mu_{l/r})}+1)$ is the Fermi-Dirac distribution function at inverse temperature $\beta \equiv 1/T$, $\varepsilon_{l/r}$ is the onsite energy and $t_{l/r}$ is the hopping within the $d$-dimensional layer of the bath.
-
-The electron self-energy (SE) $\underline{\bf{\Sigma}}$ is obtained from F-DMFT and is therefore independent of the crystal momentum, i.e., $\underline{\bf{\Sigma}}(\omega;\epsilon,\overline{\epsilon}) \simeq \underline{\bf{\Sigma}}(\omega)$.
-Further details are given in Sec.
-\ref{sec:FDMFT_implementation}.
-
-The e-ph SE is also included locally, $\underline{\bf{\Sigma}}_{e-ph}(\omega;\epsilon,\overline{\epsilon}) \simeq \underline{\bf{\Sigma}}_{e-ph}(\omega)$.
-In terms of the contour time arguments $z,z^\prime$ it has the form
-
-\begin{equation}\label{eq:backbone_e-ph_SE}
-\Sigma_{\text{e-ph}}(z,z^{\prime}) = ig^{2} G(z,z^{\prime}) D_{\text{ph}}(z,z^{\prime}).
-\end{equation}
-
-The Keldysh components ~\cite{ao.ts.14} of the non-interacting phonon GF $\kel{D}_{\text{ph}}(t,t^{\prime})$ are given by
+The Keldysh components of the non-interacting phonon GF $\kel{D}_{\text{ph}}(t,t^{\prime})$ are given by~\cite{ao.ts.14}
 \begin{align}\label{eq:Ph_Prop_time}
 \begin{split} 
-D^{\text{R}}_{\text{ph}}(t,t^{\prime}) & = -i \theta(t-t^{\prime}) \int \dd\omega \ \ee^{-i\omega\left(t-t^{\prime}\right)} A_{\text{ph}}(\omega), \\
-D^{>}_{\text{ph}}(t,t^{\prime}) & = -i \int \dd\omega \ \ee^{-i\omega\left(t-t^{\prime}\right)} A_{\text{ph}}(\omega) \left( 1 + b(\omega) \right) \\
-D^{<}_{\text{ph}}(t,t^{\prime}) & = -i \int \dd\omega \ \ee^{-i\omega\left(t-t^{\prime}\right)} A_{\text{ph}}(\omega) \ b(\omega), \\
+D^{\text{R}}_{\text{ph}}(t,t^{\prime}) & = -\ii \theta(t-t^{\prime}) \int \dd\omega \ \ee^{-\ii\omega\left(t-t^{\prime}\right)} A_{\text{ph}}(\omega), \\
+D^{>}_{\text{ph}}(t,t^{\prime}) & = -\ii \int \dd\omega \ \ee^{-\ii\omega\left(t-t^{\prime}\right)} A_{\text{ph}}(\omega) \left[ 1 + b(\omega) \right] \\
+D^{<}_{\text{ph}}(t,t^{\prime}) & = -\ii \int \dd\omega \ \ee^{-\ii\omega\left(t-t^{\prime}\right)} A_{\text{ph}}(\omega) \ b(\omega), \\
 \end{split}, 
@@
 where $b(\omega)=1/(\ee^{\beta\omega}-1)$ is the Bose-Einstein distribution function at inverse temperature $\beta$.
-We focus on acoustic phonons, with $A_{\text{ph}}(\omega) = \omega/(\omega^{2}_{\text{ph}}) \ee^{-| \omega|/\omega_{\text{ph}}}$ the phonon spectral function and $\omega_{\text{ph}}$ a soft cutoff frequency \cite{pi.li.21}.
-The retarded and Keldysh components of Eq.~\eqref{eq:backbone_e-ph_SE} can be found in Ref.\cite{ma.ga.22u}.
+We focus on acoustic phonons, with spectral function $A_{\text{ph}}(\omega) = (\omega/\omega^{2}_{\text{ph}}) \ee^{-| \omega|/\omega_{\text{ph}}}$,  $\omega_{\text{ph}}$ being a soft cutoff frequency~\cite{pi.li.21}.
+The retarded and Keldysh components of the e-ph SE are easily extracted from  Eq.~\eqref{eq:backbone_e-ph_SE} and can be found in Ref.~\cite{ma.ga.22u}.
 
@@
 
-We compute the electron SE in the Dyson equation Eq.\eqref{eq:FullDysonEq} using DMFT approach~\cite{me.vo.89,ge.ko.92,ge.ko.96}, and in particular its nonequilibrium Floquet (F-DMFT) extension~\cite{ts.ok.08,sc.mo.02u,jo.fr.08}.
-\pgcomm{(I CAN CANCEL IT MAYBE, UNUSEFUL?) The DMFT approximation consists in neglecting the crystal momentum dependence of the electron SE, i.e.
+We compute the electron SE in the Dyson Equation~\eqref{eq:FullDysonEq} using DMFT~\cite{me.vo.89,ge.ko.92,ge.ko.96}, and in particular its nonequilibrium Floquet extension F-DMFT~\cite{ts.ok.08,sc.mo.02u,jo.fr.08}.
+In DMFT the crystal momentum dependence of the electron SE is neglected, i.e.
 $\kel{\mat{\Sigma}}(\omega,\epsilon,\overline{\epsilon}) \to \kel{\mat{\Sigma}}(\omega)$.
-This allows us to map the original problem into a single-site impurity model with a bath hybridization function, $\kel{\mat\Delta}(\omega)$ encoding the effect of all other lattice sites.} We briefly describe now the self-consistent F-DMFT scheme used.
-(i) We start from an initial guess for electron SE $\kel{\mat{\Sigma}}(\omega)$. (ii) We compute the local electron Green's function as
+This allows us to map the original lattice problem onto a single-site impurity model with a bath hybridization function $\kel{\mat\Delta}(\omega)$ encoding the effect of all other lattice sites.
+
+We briefly describe now the self-consistent F-DMFT scheme used.
+(i) We start from an initial guess for the electron SE $\kel{\mat{\Sigma}}(\omega)$ and set $\kel{\mat \Sigma}_{\text{e-ph}}(\omega)=0$. (ii) Then we compute the local electron GF as
 
@@
 \kel{\mat G}_{\text{loc}}(\omega) &= \int \dd\epsilon \int \dd\overline{\epsilon} \ \rho(\epsilon,\overline{\epsilon}) \times \\ 
-&\times \left[ \left( \kel{\mat G}^{-1}_{0}(\omega,\epsilon,\overline{\epsilon}) - \kel{\mat\Sigma}(\omega) - \kel{\mat \Sigma}_{\text{e-ph}}(\omega) \right)^{-1} \right].
+&\times \left[\kel{\mat G}^{-1}_{0}(\omega,\epsilon,\overline{\epsilon}) - \kel{\mat\Sigma}(\omega) - \kel{\mat \Sigma}_{\text{e-ph}}(\omega) \right]^{-1}.
 \end{split}
@@
 
-(iii) We compute $\kel{\mat{\Sigma}}_{\text{e-ph}}(\omega)$
-from Eq.\eqref{eq:backbone_e-ph_SE}.
-(iv) We map the problem into a in a single-site impurity one, with $\kel{\mat\Delta}(\omega)$ given by
+(iii) Using Eq.~\eqref{eq:backbone_e-ph_SE}, we obtain the phonon contribution to the SE $\kel{\mat{\Sigma}}_{\text{e-ph}}(\omega)$.
+(iv) The problem is mapped onto a single impurity plus bath, whose hybridization function
+is given by
 
 \begin{equation}\label{eq:imp_Dyson_eq}
-\kel{\mat{\Delta}}(\omega) = \kel{\mat{g}}^{-1}_{\text{0,site}}(\omega) - \kel{\mat{G}}^{-1}_{\text{loc}}(\omega) - \kel{\mat{\Sigma}}(\omega)
+\kel{\mat{\Delta}}(\omega) = \kel{\mat{g}}^{-1}_{0,\text{site}}(\omega) - \kel{\mat{G}}^{-1}_{\text{loc}}(\omega) - \kel{\mat{\Sigma}}(\omega),
 \end{equation}
 
-where $\kel{\mat{g}}^{-1}_{\text{0,site}}(\omega)$ is defined as in Eq.~(\ref{eq:inv_non-int_lat_GF_comps}) but without $\varepsilon_{mn}(\epsilon,\overline{\epsilon})$.
-(v) We map the impurity problem to an auxiliary one, we solve the many body problem and determine the new $\kel{\mat{\Sigma}}(\omega)$(see \ref{sec:amea}).
-(vi) We plug the obtained SEs in step (ii) and we iterate the steps (ii)-(vi) until convergence.
+where $\kel{\mat{g}}^{-1}_{0,\text{site}}(\omega)$ is defined as in Eq.~\eqref{eq:inv_non-int_lat_GF_comps} with $\varepsilon_{mn}(\epsilon,\overline{\epsilon})=0$.
+(v) The nonequilibrium many-body impurity problem is solved according to the procedure in Sec.~\ref{sec:amea}, leading to the new
+ $\kel{\mat{\Sigma}}(\omega)$. (vi) We insert the electron and e-ph SEs into step (ii) and iterate the steps (ii)-(vi) until convergence.
 
@@
 
-Eq.\eqref{eq:imp_Dyson_eq} gives a periodic time-dependent bath hybridization function $\kel{\mat\Delta}(\omega)$.
-We want to address photovoltaic effects, therefore following Ref.\cite{so.do.18}, we consider only the $(0,0)$-Floquet matrix element of Eq.\eqref{eq:imp_Dyson_eq} (corresponding to the time-average over a period $\tau$) and  we employ the Floquet-diagonal self-energy approximation (FDSA) for $\kel{\mat{\Sigma}}(\omega)$.
-We employ the FDSA in Eq.\eqref{eq:FullDysonEq} also for $\underline{\bf{\Sigma}}_{e-ph}(\omega)$, namely $\kel{\Sigma}_{mn,e-ph}(\omega_n) = \kel{\Sigma}_{00,e-ph}(\omega_n)\delta_{mn}$ \footnote{In the range in which FDSA is justified for $\kel{\Sigma}$, $\kel{\Sigma}_{00,e-ph}$ is orders of magnitude bigger than the other Floquet matrix elements $\kel{\Sigma}_{mn,e-ph}$.}.
-Therefore Eq.\eqref{eq:imp_Dyson_eq} reads
-
-\begin{equation}\label{eq:imp_Dyson_eq_av}
-\kel{\Delta}(\omega) = \kel{g}^{-1}_{\text{0,site}}(\omega) - \kel{G}^{-1}_{\text{loc}}(\omega) - \kel{\Sigma}(\omega)
-\end{equation}
-
-where all the quantities are time-averaged.
-Once we obtain the new $\kel{\Sigma}(\omega)$, we reconstruct the Floquet dependence of SEs via the translation property $\kel{\Sigma}_{mn}(\omega) = \kel{\Sigma}_{00}(\omega+m\Omega)\delta_{mn}$.
+From Eq.~\eqref{eq:imp_Dyson_eq}, we obtain the bath hybridization function $\kel{\mat\Delta}(\omega)$ whose periodic time-dependence is encoded in its Floquet structure.
+Being interested in photovoltaic effects, we follow Ref.~\cite{so.do.18} and use the Floquet-diagonal self-energy approximation (FDSA) for which Floquet off-diagonal terms in the electron SE $\kel{\mat{\Sigma}}(\omega)$ are neglected.
+In addition, we employ FDSA also for the phonon SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ \footnote{In the parameters range in which FDSA is justified for the electron SE $\kel{\mat{\Sigma}}(\omega)$ (Sec.~\ref{sec:results}), the diagonal terms of the phonon SE $\underline{\Sigma}_{mm,\text{e-ph}}(\omega)$ are orders of magnitude bigger than the off-diagonal ones}.
+Consequently, we only consider the
+ $(0,0)$-Floquet matrix element of Eq.~\eqref{eq:imp_Dyson_eq} in the impurity problem, which therefore becomes stationary.
+It is sufficient to restrict oneself to the $(0,0)$ component, since the other diagonal components can be reconstructed by using the property $\kel{\Sigma}_{mm}(\omega) = \kel{\Sigma}_{00}(\omega+m\Omega)$.
 
@@
 
-We briefly summarize the impurity solver used in step (v) of DMFT self-consistent loop (Sec.\ref{sec:FDMFT_implementation}).
+In the following, we briefly summarize the impurity solver used in step (v) of the DMFT self-consistent loop described in Sec.~\ref{sec:FDMFT_implementation}. In order to solve the many-body problem,
+ we use the auxiliary master equation approach (AMEA)~\cite{ar.kn.13,do.nu.14,do.ga.15,do.so.17}.
+Therein, we map the impurity problem onto an auxiliary open quantum system (AOQS) consisting of a finite number of bath sites $N_{\text{B}}$ attached to Markovian reservoirs described by the Lindblad equation.
+The  hybridization function $\kel{\Delta}_{\text{aux}}(\omega)$ of this AOQS is obtained by fitting the original DMFT one.
+The key point is that the many-body problem of this AOQS can be solved exactly
+using standard many-body-diagonalization methods, as long as  $N_{\text{B}}$ is small.
+The accuracy of this solution is set by the difference between
+ $\kel{\Delta}_{\text{aux}}$ and $\kel{\Delta}$, which  becomes exponentially  small with increasing $N_{\text{B}}$.
 
-We solve the many-body problem using the auxiliary master equation approach (AMEA)~\cite{ar.kn.13,do.nu.14,do.ga.15,do.so.17}.
-It maps the impurity problem in an open quantum system consisting of a finite number of bath sites $N_{\text{B}}$ attached to Markovian reservoirs described by the Lindblad equation.
-The corresponding hybridization function $\kel{\Delta}_{\text{aux}}(\omega)$ is obtained by fitting the original DMFT one.
-We reach convergence once $\kel{\Delta}_{\text{aux}}$ agrees with $\kel{\Delta}$ with a sufficient accuracy.
-With the parameters obtained from $\kel{\Delta}_{\text{aux}}$, we solve the auxiliary problem using standard many-body-diagonalization methods for open quantum systems, obtaining the new $\kel{\Sigma}(\omega)$.
-
-\subsection{Observables}
+\subsection{Physical quantities}
 \label{sec:observables}
 
-In this article, we consider time-averaged observables, defined as follows.
+To study direct excitation and II effects in this system,
+we consider the following time-averaged physical quantities.
 
-The photocurrent (or simply current, without any ambiguity) flowing from the left fermion bath to the right one, passing through the correlated layer is given by
+The photocurrent flowing from the left fermion lead to the right one, passing through the correlated layer is given by 
+% 
+\begin{align}
+j_{\text{l}\rightarrow\text{r}}&=v^2\int_{-\Omega/2}^{\Omega/2}\frac{\dd\omega}{2\pi} \int \dd\epsilon \int \dd\overline{\epsilon} \rho(\epsilon,\overline{\epsilon}) \rre\Tr(\boldsymbol{J})\label{eq: Current furmula_Omega}\\
+&= v^2\int_{-\infty}^{+\infty}\frac{\dd\omega}{2\pi} \int \dd\epsilon \int \dd\overline{\epsilon} \rho(\epsilon,\overline{\epsilon}) \rre(J_{00}),\label{eq: Current furmula_00}
+\end{align}
+% 
+where
+% 
+\begin{equation}
+  \boldsymbol{J}=\left[\boldsymbol{G}^{\text{R}}(\boldsymbol{g}_{\text{b},\text{l}}^{\text{K}}-\boldsymbol{g}_{\text{b},\text{r}}^{\text{K}})+\boldsymbol{G}^{\text{K}}(\boldsymbol{g}_{\text{b},\text{l}}^{\text{A}}-\boldsymbol{g}_{\text{b},\text{r}}^{\text{A}})\right]
+\end{equation}
+% 
+is taken from Ref.~\cite{so.do.18}. Of the two equivalent expressions, Eq.~\eqref{eq: Current furmula_00} is used in practice.
 
-\begin{align}
- j_{L\rightarrow R}&=v^2\int_{-\frac{\Omega}{2}}^{\frac{\Omega}{2}}\frac{d\omega}{2\pi} \int d\epsilon \int d\overline{\epsilon} \rho(\epsilon,\overline{\epsilon}) \text{Re Tr} \boldsymbol{J}\label{eq: Current furmula_Omega}\\
-  &= v^2\int_{-\infty}^{+\infty}\frac{d\omega}{2\pi} \int d\epsilon \int d\overline{\epsilon} \rho(\epsilon,\overline{\epsilon}) \text{Re} J_{00}\label{eq: Current furmula_00}
-  \end{align} 
-where $\boldsymbol{J}$ is given by the following expression
-\begin{equation}
-  \boldsymbol{J}=\left[\boldsymbol{G}^{\text{R}}(\boldsymbol{g}_{b,l}^{\text{K}}-\boldsymbol{g}_{b,r}^{\text{K}})+\boldsymbol{G}^{\text{K}}(\boldsymbol{g}_{b,l}^{\text{A}}-\boldsymbol{g}_{b,r}^{\text{A}})\right]
-\end{equation}
-
-obtained directly from Ref.\cite{so.do.18}.
-The two equivalent formulas Eq.\eqref{eq: Current furmula_Omega}-\eqref{eq: Current furmula_00} are used for consistency and they agree over all the chosen parameter space.
-
-The electronic spectral function (or density of states, DOS) reads
-
+The local electronic spectral function (DOS) reads
+%  
 \begin{equation}
 \label{eq:el_spectral_function}
- A(\omega)=-\frac{1}{\pi}\Im G_{loc,00}^{R}(\omega).
+ A(\omega)=-\frac{1}{\pi}\iim[G_{\text{loc},00}^{\text{R}}(\omega)],
 \end{equation}
-
-where $G^{\text{R}}_{\text{loc,00}}$ is the time-averaged retarded component of the GF given in Eq.~\eqref{eq:Lat_LocGF}. The non-equilibrium distribution function is defined via
-
+% 
+where $G^{\text{R}}_{\text{loc},00}$ is the time-averaged retarded component of the GF given in Eq.~\eqref{eq:Lat_LocGF}.
+Combining it with the time-averaged Keldysh component gives the occupation function
 \begin{equation}
-\label{eq:NEFD-dist}
-F_{\text{neq}}(\omega) = \frac{1}{2} \left\{1 - \frac{1}{2}\frac{\Im[G^{\text{K}}_{\text{loc}}(\omega)]}{\Im[G^{\text{R}}_{\text{loc}}(\omega)]} \right\}
-\end{equation}
-
-and the related occupation function is
-
-\begin{equation}
-\label{eq:Filling_func}
-N(\omega) \equiv A(\omega)F_{\text{neq}}(\omega).
+N(\omega) = \frac{1}{4\pi} [\iim(G^{\text{K}}_{\text{loc},00})-2\iim(G^{\text{R}}_{\text{loc},00})].
 \end{equation}
@@
 
-We want to study the occurrence of impact ionization in a Mott insulating layer.
-Therefore following \cite{so.do.18}, we choose $U=12$.
-We work with fermion baths and acoustic phonons at temperature $T=0.02$.
-We consider a particle-hole symmetric system with $\Gamma_l=\Gamma_r=0.37$, $t_l=t_r=1.7$ \footnote{The value of the hopping within the baths layers is consistent with the choice of metallic reservoirs, commonly used for photovoltaic applications.}\footnote{The values of the baths parameters are chosen such that they reproduce best the bandwidth of metallic leads at the same temperature $T$}, $\varepsilon_{l/r}=\mp 6$ and $v_l=v_r=v$.
+In order to study II in a Mott insulating layer, we set the bands to achieve the energy scheme shown in Fig.~\ref{fig:energy_setup}(a).
 
-To reproduce a realistic situation \footnote{ Real metallic leads usually have a wide bandwidth and are only partially filled}, we choose the baths bandwidth $W_b$ to be roughly the same of the correlated layer (see Fig.\ref{fig:energy_setup}(a)) as $W_b\approx8$ and we set the baths chemical potentials to $\mu_{l/r} =\mp 1$.
-The left/right bath band is centered at the same energy of the Lower Hubbard Band (LHB)/Upper Hubbard Band (UHB) (Fig.\ref{fig:energy_setup}(a)) and the effective gap is $\Delta_{\textrm{eff}} \approx 4$.
+ We follow Ref.~\cite{so.do.18} and choose $U=12$ and $E_0=2$.
+The fermion leads and acoustic phonons have temperature $T=0.02$.
+We consider a particle-hole symmetric system with $\Gamma_{\text{l}}=\Gamma_{\text{r}}=0.37$, $t_{\text{l}}=t_{\text{r}}=1.7$, $\varepsilon_{\text{l}/\text{r}}=\mp 6$ and $v_{\text{l}}=v_{\text{r}}=v$.
+The parameters $t_{\text{l/r}}$, $\varepsilon_{\text{l/r}}$, and  $\Gamma_{\text{l/r}}$ are chosen such that the leads' DOS approximately coincides with the Hubbard bands, i.e.
+they exhibit a \textquoteleft bandwidth\textquoteright~\footnote{Notice that the support of its spectrum is formally infinite.
+$W_{\text{b}}$ is the value at which the spectrum gets  suppressed.} $W_{\text{b}}\approx 8$ and are centered at the same position.
+The chemical potentials are set to $\mu_{\text{l}/\text{r}} =\mp 1$, so that a current from left to right is produced by energy taken from the driving.
 
-All the simulations are carried out with parameter $\alpha=t^{*}E_0/\Omega^{2}<0.5$, range in which FDSA is justified \cite{so.do.18}.
-We consider for the phonons parameters $g=0.8$ and $\omega_{ph}=0.1$.
+Due to the hybridization with the leads, the local DOS of the Hubbard layer only features a pseudogap
+ $\Delta_{\text{pg}} \approx 4$.
+All simulations are carried out with the dimensionless factor $\alpha\equiv t_{r}E_0/\Omega^{2}<0.5$ for which the FDSA is justified~\cite{so.do.18}\footnote{In Ref.~\cite{so.do.18} the factor is defined as $\alpha=t_{c}E_0/\Omega^{2}$ and $t_{\text{c}}=1$.
+Setting $t_{r}=1$, we define for consistency $\alpha$ as in the main text.} and first-order photon absorption processes are dominant.
+Whenever the electron-phonon interaction is switched on, we take $g=0.8$ and unless stated otherwise $\omega_{\text{ph}}=0.1$.
 
-With the help of preliminary considerations in Sec.\ref{sec:explicative_scheme}, we discuss the occurrence of impact ionization for $E_0=2$ at different $v$, considering only the fermion baths in Sec.\ref{sec:E0_2_only_electrons} and additionally the acoustic phonons in Sec.\ref{sec:E0_2_electrons_phonons}.
-In the same way, we consider the effect of higher electric field amplitudes in Sec.\ref{sec:higher_E0_only_electrons} and \ref{sec:higher_E0_electrons_phonons}.
+After some preliminary considerations in Sec.~\ref{sec:explicative_scheme}, we will discuss the occurrence of II at different $v$ first without (Sec.~\ref{sec:E0_2_only_electrons}) and then with coupling to acoustic phonons (Sec.~\ref{sec:E0_2_electrons_phonons}).
 
-\begin{figure}[ht]
-% \captionsetup{width=\textwidth} 
-\includegraphics[width=0.9\linewidth]{./figures_Paper1/energy_setup.pdf}
-\caption{(Colour online) Energy scheme and physical processes occuring in the considered setup.
-The baths bands are in red, the Hubbard bands in green and the vertical axis represents the energy.
-Panel (a) shows the quantities mentioned in Sec.\ref{sec:results}.
-Panel (b) illustrates a direct excitation process, in which an electron is excited  by a photon with energy $\Omega$ (yellow arrow) to the upper Hubbard band and escapes into the right bath (red arrow).
-Panel (c) displays an impact ionization process, where the photoexcited electron in the upper Hubbard band excites a second electron from the lower to the upper Hubbard band (black arrows) and they both escape into the right bath.}
+\begin{figure}[t]
+
+\includegraphics[width=0.85\linewidth]{./figures_Paper1/energy_setup.pdf}
+\caption{(Color online) Schematic representation of the processes occuring in the model considered.
+Red bands on the left and right describe the leads' DOS, where the dark color highlights occupied states and the light color empty states.
+Green bands are the LHB and UHB of the central layer.
+The vertical axis represents the energy.
+Panel (a) sketches the quantities introduced at the beginning of Sec.~\ref{sec:results}.
+Panel (b) illustrates a direct excitation process, in which an electron is excited by a photon with energy $\Omega$ (yellow arrow) to the UHB and escapes into the right lead (red arrow).
+Panel (c) displays an II process, where the photoexcited electron in the UHB excites a second electron from LHB to UHB (black arrows) and both escape into the right lead.
+In the nonequilibrium steady state considered here, only processes recovering the initial configuration are allowed.}
 \label{fig:energy_setup}
@@
 
-We propose here a scheme, based on energy considerations, to describe the occurrence of impact ionization (IO) in our setup.
-We partially follow Ref.\cite{so.do.18,ma.ev.22} for the \emph{only-electron} case, extending it to the case with electron-phonon interaction.
-It holds at non-equilibrium steady state (NESS), where energy and particles conservation have to be respected and therefore no charge accumulation in the correlated layer is allowed.
+To infer the conditions necessary for II, we consider the  scheme in Fig.~\ref{fig:energy_setup}.
+Thereby, we partially follow Ref.~\cite{so.do.18} for the electron-only (EO) case and extend the analysis to the case with e-ph interaction.
+Here, we also consider a more realistic structure of the leads.
+As in Ref.~\cite{so.do.18} we bypass transient behavior and consider directly the nonequilibrium Floquet steady state.
+In our analysis, we neglect higher-order processes such as multiparticle scattering II processes.
 
-We assume that only first-order photon absorption processes occur.
-This is in fact the case for the chosen $\alpha$-values (see above) \cite{so.do.18}.
-We neglect also higher-order processes as multi-scattering IO processes.
+In order to observe II, the bandwidth of the UHB has to be at least twice the pseudogap size $\Delta_{\text{pg}}$.
+Only in this case, the photoexcited electron can acquire enough energy to excite a second one across the pseudogap.
 
-The essential condition to meet to have IO is that the bandwidth of the UHB is twice the effective gap $\Delta_{\textrm{eff}}$ \cite{so.do.18}.
-Only in this case, the photoexcited electron has enough energy to excite a second one across the gap.
-
-\subsubsection{Only electrons}
+\subsubsection{EO system}
 \label{sec:scheme_only_electrons}
@@
 \begin{itemize}
-
-\item For $\Omega<\Delta_{\textrm{eff}}$, we don't have any current if the DOS of the correlated layer has a true gap \footnote{To overcome the effective gap with $\Omega<\Delta_{\textrm{eff}}$ multiple-photon absorption processes should take place, but as written in the main text, such effects are negligible in the studied parameter range.}.
-If $\Delta_{\textrm{eff}}$ is a partial gap, we have a clear suppression of the current.
-
-\item For $\Delta_{\textrm{eff}}<\Omega<\Delta_{\textrm{eff}}+2W_b$, an electron coming from the left bath into the LHB is photoexcited to the UHB and can escape directly into the right bath without additional scattering (Fig.\ref{fig:energy_setup}(b)).
-From now on, we refer to such processes as direct excitations (DE).
-
-\item For $2\Delta_{\textrm{eff}}<\Omega<\Delta_{\textrm{eff}}+2W_b$, a photoexcited electron in the UHB can excite via IO a second electron from LHB to the UHB, before being both dragged into the right bath (Fig.\ref{fig:energy_setup}(c)).
-
-\item For $\Omega>\Delta_{\textrm{eff}}+2W_b$, there are no final states available for a photoexcited electron and the transition shouldn't occur.
-
+\item For $\Omega<\Delta_{\text{pg}}$, we do not expect any current if the DOS of the correlated layer has a true gap~\footnote{To overcome a true gap with $\Omega<\Delta_{\text{pg}}$ multiple-photon absorption processes should take place, but as written in the main text, such effects are negligible in the studied parameters range.}.
+If $\Delta_{\text{pg}}$ is a partial gap, we expect a suppression of the current.
+\item For $\Delta_{\text{pg}}<\Omega<\Delta_{\text{pg}}+2W_{\text{b}}$ as shown in Fig.~\ref{fig:energy_setup}(b), an electron coming from the left lead into the LHB is photoexcited to the UHB and can escape directly into the right lead without additional scattering.
+We will refer to such processes as direct excitations (DEs).
+\item For $2\Delta_{\text{pg}}<\Omega<\Delta_{\text{pg}}+2W_{\text{b}}$ as shown in Fig.~\ref{fig:energy_setup}(c), a photoexcited electron in the UHB can excite via II a second electron from LHB to UHB, before both escape into the right lead.
+\item For $\Omega>\Delta_{\text{pg}}+2W_{\text{b}}$, there are no final states available for a photoexcited electron and we do not expect the transition to occur. 
 \end{itemize}
 
-From these considerations, we notice that in the energy window $\Delta_{\textrm{eff}}<\Omega<2\Delta_{\textrm{eff}}$ the only scattering processes taking place are DE, instead for $2\Delta_{\textrm{eff}}<\Omega<\Delta_{\textrm{eff}}+2W_b$ both DE and IO can occur.
+Notice that in the energy window $\Delta_{\text{pg}}<\Omega<2\Delta_{\text{pg}}$ the only scattering processes taking place are DEs, while for $2\Delta_{\text{pg}}<\Omega<\Delta_{\text{pg}}+2W_{\text{b}}$, both DE and II can occur.
+We want to stress however, that the boundaries of these energy ranges are not strict and that it is difficult to disentangle the effects of these physical processes.
 
-We point out that the boundaries of such energy ranges aren't strict and the separation of these physical processes can't be net, due to the influence of the various complicated mechanisms involved.
-
-\subsubsection{Electron and phonons}
+\subsubsection{Inclusion of e-ph interactions}
 \label{sec:scheme_electrons_phonons}
 
-With the inclusion of electron-phonon scattering, the outlined scheme remains valid except for the modification of the effective gap $\Delta_{\textrm{eff}}$.
-As shown in Sec.\ref{sec:E0_2_electrons_phonons}, the phonons broaden the DOS of the correlated layer and slightly close the gap.
-Therefore the effective gap is reduced by a small amount $\Delta_{\textrm{diss}}$ indicating the dissipation by phonons, i.e.
-$\Delta_{\textrm{eff,ph}}=\Delta_{\textrm{eff}}-\Delta_{\textrm{diss}}$.
+Upon inclusion of e-ph scattering, the outlined scheme remains valid except for a modification of the pseudogap $\Delta_{\text{pg}}$.
+As shown in Sec.~\ref{sec:E0_2_electrons_phonons}, the phonons broaden the DOS of the correlated layer and slightly fill the pseudogap.
+Therefore the pseudogap is reduced by a small amount indicating the dissipation by phonons.
 
-\subsection{$E_0=2$}
-\label{sec:E0_2}
-
-\begin{figure*}[ht]
-\includegraphics[width=\textwidth]{./figures_Paper1/j_vs_omega_mu1_v_0.4_0.8_eph.pdf}
+% \onecolumngrid
+\begin{figure*}[t]
+\includegraphics[width=0.7\textwidth]{./figures_Paper1/j_vs_omega_mu1_v_0.4_0.8_eph.pdf}
 % \captionsetup{width=\textwidth}
-\caption{(Colour online) $\Omega$-dependence of time-averaged steady-state current $j$ (in units of $j_0=\frac{qt^*}{\hbar a^2}$) (a), double occupancy $N_D$ (b) and time-averaged current $j$ rescaled by $v^2$ (c), for $v=0.4$ and $v=0.8$, when electron-phonon interaction is switched off and on.
-The electron-phonon coupling is set to $g=0.8$ and the phonon cutoff frequency to $\omega_{ph}=0.1$.
-Default parameters are specified at the beginning of section~\ref{sec:results}.}
+\caption{(Color online) 
+ (a) Time-averaged steady-state current $j$ and (b) double occupancy $N_{\text{D}}$ plotted as a function of the driving frequency $\Omega$.
+Results are shown for different values of the lead-layer hybridization $v$ as well as without and with e-ph interaction.
+ Default parameters are specified at the beginning of Sec.~\ref{sec:results}.} 
 \label{fig:j_vs_omega_mu1_v_0.4_0.8_eph}
 \end{figure*}
+% \twocolumngrid
 
-\subsubsection{Only electrons}
+\subsection{EO system}
 \label{sec:E0_2_only_electrons}
 
-\begin{figure}[ht] 
+We start with the EO case without e-ph interaction and investigate the dependence of the physical quantities on the lead-layer hybridization.
+
+In Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(a), the photocurrent $j$ increases as a function of the driving frequency $\Omega$ within the range $4\lesssim\Omega\lesssim8$ independent of the value of $v$.
+According to the discussion in Sec.~\ref{sec:scheme_only_electrons} (cf.
+Fig.~\ref{fig:energy_setup}), this $\Omega$-range is expected to allow only for DEs.
+The current in this range  increases with increasing $v$.
+Similarly, the double occupation shown in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(b) increases as a function of the driving frequency~\footnote{Notice that the increase of $N_{\text{D}}$ in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(b) as compared to Ref.~\cite{so.do.18} is not as steep and large in magnitude.
+This is due to our setup, where every photoexcited carrier can escape to the right lead.}.
+
+For $\Omega\gtrsim8$, the current increases further until it reaches its peak at $\Omega\approx 11$.
+In this range both DE and II can occur.
+The height of the peak is approximately the same for both $v$, despite the lead-layer hybridizations differing by a factor of two.
+The double occupation in this range shows a similar behavior as the current for $v=0.4$ with a peak around $\Omega\approx 11$, while it exhibits a plateau for $v=0.8$.
+For $v=0.4$ the current curve is characterized by a substantial change in slope around $\Omega \approx 8$, which is absent for $v=0.8$.
+ This, together with the comparable magnitude of the maxima at $\Omega\approx 11$ and the behavior of the double occupation strongly suggest that for $v=0.4$ a substantial number of II processes take place, while these are absent or negligible for $v=0.8$.
+Here,  the plateau in $N_{\text{D}}$ for $v=0.8$ suggests that photoexcited electrons arriving in the UHB quickly escape to the right fermionic lead and do not have time to induce II processes.
+
+The spectral and occupation function shown in Fig.~\ref{fig:spec_filling_mu1_v_0.4_0.8_O_5_11_e} corroborate this hypothesis.
+For $\Omega=5$ in the DE range, the occupation function in the UHB is almost the same for both $v$, while for $\Omega=11$ where the peak in the current occurs, the occupation of the UHB for $v=0.4$ is substantially larger,  in line with the behavior of $N_{\text{D}}$.
+
+\begin{figure}[b] 
 % \captionsetup{width=\textwidth}   
 \includegraphics[width=\linewidth]{./figures_Paper1/spec_filling_mu1_v_0.4_0.8_O_5_11_e.pdf}
-\caption{(Colour online) Spectral function $A(\omega)/t^{* -1}$ (solid) and occupation function $N(\omega)/t^{* -1}$ (shaded area), at $\Omega=5$ (a) and $\Omega=11$ (b) for $v=0.4,0.8$, when electron-phonon interaction is switched off.
-Default parameters are specified at the beginning of section~\ref{sec:results}.}
+\caption{(Color online) Spectral function $A(\omega)$ (solid line) and occupation function $N(\omega)$ (shaded area) at (a) $\Omega=5$ and (b) $\Omega=11$ for $v=0.4$ and $0.8$ for the EO system.
+Default parameters are specified at the beginning of Sec.~\ref{sec:results}.}
 \label{fig:spec_filling_mu1_v_0.4_0.8_O_5_11_e}
@@
 
-We start from the analysis of the results obtained considering the electron-phonon interaction switched off, to describe the behaviour of the observables in terms of the bath-layer coupling $v$ only.
+Finally, increasing $\Omega$ further, decreases the current and double occupation~\footnote{The current $j$ does not approach zero as expected for $\Omega>20$ because of the background current as discussed in Ref.~\cite{so.do.18}.}.
 
-In Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(a) the photocurrent $j$ as a function of the driving frequency $\Omega$ shows an increase for both $v$ in the region $4\lesssim\Omega\lesssim8$ due to DE creating an electron-holon pair.
-Such range corresponds in fact, with our choice of parameters (see Sec.\ref{sec:results} and \ref{sec:scheme_only_electrons}), to the $\Omega$-region in which only DE can occur.
-For the same $\Omega$, $j_{v=0.8}>j_{v=0.4}$, clearly due to bigger value of $v$.
-In this region, the double occupation (Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(b)) shows accordingly an increase for both $v$.
-
-For $\Omega\gtrsim8$, the current increases further reaching for both $v$ its peak, located at $\Omega\approx 11$ \footnote{The position of the current peak roughly correspond to the resonant driving frequency $\Omega=U$.}.
-The magnitude of the peak is approximately the same for both $v$, despite the bath-layer couplings are one the double of the other.
-The double occupation in this region shows a similar behaviour for $v=0.4$, with a peak around $\Omega\approx 11$, while exhibits for $v=0.8$ a plateau.
-
-This region corresponds (see \ref{sec:scheme_only_electrons}) to the one in which both DE and IO can occur.
-Therefore what described above strongly suggests that for $v=0.4$ the dominant process taking place is IO, while for $v=0.8$ the dominant one is DE.
-In fact, for $v=0.4$ there is a clear increase in $N_D$ \footnote{
-We point out that the increase of $N_D$ in Fig.\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}, in comparison with Ref.\cite{so.do.18} isn't so steep and big in magnitude because in our setup choice, every photoexcited carrier can escape in the right bath.}, well-known signature for IO \cite{so.do.18,ma.ev.22} and the magnitude of the current peak is comparable with $v=0.8$: given the current formula Eq.
-\eqref{eq: Current furmula_00}, the prefactor $v^2$ for $v=0.4$ is four time smaller than the one for $v=0.8$, therefore such result should imply a different electronic scattering, as IO, doubling the number of carriers for a single photon absorption.
-On the other hand, the plateau in $N_D$ for $v=0.8$ means that a double occupation of a site doesn't increase with $\Omega$, signalizing that photoexcited electrons simply arrive in UHB and escape.
-An additional strong confirmation to such picture comes from Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(c): the current $j$ rescaled by $v^2$ shows that the net contribution of the integral in $\eqref{eq: Current furmula_00}$ for $v=0.4$ is much bigger (roughly four times) than for $v=0.8$ and therefore the enhancement of the current has to come from a mutiplying-carriers electronic process.
-
-Such behaviour is extremely interesting: smaller $v$ means smaller probability amplitude of electrons entering in the LHB from the left bath and escaping from the UHB in the right bath.
-Despite that the magnitude of the photocurrent is roughly the same and IO process compensates almost completely this injection/drag deficency.
-
-The spectral features corroborate such hypotesis.
-In Fig.~\ref{fig:spec_filling_mu1_v_0.4_0.8_O_5_11_e}(a)-(b) the occupation function for $\Omega=5$, in the DE region, is almost the same for both $v$, while for $\Omega=11$ where the $j$-peak current occurs, the occupation of the UHB for $v=0.4$ is clearly bigger, in line with the peak of $N_D$.
-
-Finally, increasing further $\Omega$ the current and double occupation decrease until they approach their minimum for $\Omega\approx20$ \footnote{The current $j$ doesn't go to zero as it should for $\Omega>20$ because of a background current intrinsic in the AMEA approach in presence of a gap or a band edge \cite{so.do.18}.
-This background current depends on $v$, $\mu_{l/r}$ and $g$, therefore we have different offsets according to the chosen parameters.
-Since we are interested in the qualitative behavior of the current and not stricly on the magnitude, we don't show these background currents, which don't affect our analysis.}.
-
-\subsubsection{Electrons and phonons}   
+\subsection{Inclusion of e-ph interactions}
 \label{sec:E0_2_electrons_phonons}
 
-\begin{figure}[ht]
+We now discuss the effect of coupling to acoustic phonons on the results discussed above.
+
+The current $j$ in presence of phonons shown in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(a) is slighty larger than the EO one for $\Omega\lesssim7$.
+This effect is reduced with increasing $\Omega$ until a crossing occurs at $\Omega\approx7$ where the EO current overtakes.
+Between $7\lesssim\Omega\lesssim14$, the current in the presence of phonons exhibits the same qualitative behavior as the EO one, reaching its maximum at $\Omega\approx 11$.
+However the current magnitude is suppressed, especially around the peak.
+For $\Omega\gtrsim14$ the current with phonons goes down as for the EO case.
+
+The double occupation $N_{\text{D}}$  shown in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(b) is larger than and follows the behavior of its EO counterpart within the entire $\Omega$-range considered.
+The spectral and occupation function  shown in Fig.~\ref{fig:spec_filling_mu1_v_0.4_0.8_O_11_eph} display a redistribution of spectral weight from the peaks towards the edges of the bands, thus reducing the pseudogap.
+Consequently, the occupation of positive energy states is slightly shifted to the bottom of the UHB compared to the EO case, as the occupation function shows.
+ The spectral function in presence of phonons is  broadened and tends to fill the pseudogap $\Delta_{\text{pg}}$ as anticipated in Sec.~\ref{sec:scheme_electrons_phonons}.
+This reduction of the pseudogap explains why the current in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(a) is slightly larger in presence of phonons for $\Omega\lesssim7$. 
+With a smaller pseudogap and more states at its edges, more electrons can be directly excited with a given driving frequency thereby increasing the photocurrent.
+On the other hand, the suppression of the current by e-ph interaction in the range $7\lesssim\Omega\lesssim14$ is due to the reduction of spectral weight at frequencies $|\omega| \gtrsim 3.5$, cf.
+Fig.
+\ref{fig:spec_filling_mu1_v_0.4_0.8_O_11_eph}.
+
+\begin{figure}[t]
 % \captionsetup{width=\textwidth} 
 \includegraphics[width=\linewidth]{./figures_Paper1/spec_filling_mu1_v_0.4_0.8_O_11_eph.pdf}
-\caption{(Colour online) Spectral function $A(\omega)/t^{* -1}$ (solid line) and occupation function $N(\omega)/t^{* -1}$ (dashed line) at $\Omega=11$ when electron-phonon interaction is switched off and on, for $v=0.4$ (a) and $v=0.8$ (b).
-The electron-phonon coupling is set to $g=0.8$ and the phonon cutoff frequency to $\omega_{ph}=0.1$.
-Default parameters are specified at the beginning of section~\ref{sec:results}.}
+\caption{(Color online) Spectral function $A(\omega)$ (solid line) and occupation function $N(\omega)$ (shaded area) at $\Omega=11$ without and with e-ph interaction, for (a) $v=0.4$ and (b) $v=0.8$.
+Default parameters are specified at the beginning of Sec.~\ref{sec:results}.}
 \label{fig:spec_filling_mu1_v_0.4_0.8_O_11_eph}
@@
 
-We discuss now the effect of acoustic phonons on the results obtained in the previous section, switching on the electron-phonon coupling $g$.
+The increase of the double occupation $N_{\text{D}}$ seen in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(b) for the case with phonons can already be inferred from the occupation function $N(\omega)$ at positive frequencies depicted in Fig.~\ref{fig:spec_filling_mu1_v_0.4_0.8_O_11_eph}.
 
-The current $j$ in presence of phonons in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(a) is slighty bigger than the \emph{only-electron} one for both $v$ when $\Omega\lesssim7$.
-This difference decreases increasing $\Omega$, until $\Omega\approx7$,  where a crossing takes place and the \emph{only-electron} current becomes bigger.
-Between $7\lesssim\Omega\lesssim14$, the current in presence of phonons follows the same behaviour of the \emph{only-electron} one, reaching for both $v$ its maximum, also located at $\Omega\approx 11$, but it shows a clear suppression in magnitude, occuring especially around the peak at $\Omega\approx 11$.
-For $\Omega\gtrsim14$ the current with phonons for both $v$ goes down until the minimum for $\Omega\approx20$ as before.
+\begin{figure}[b] 
+% \captionsetup{width=\textwidth}  
+\includegraphics[width=\linewidth]{./figures_Paper1/j_vs_omega_mu1_v_0.4_0.8_E0_2_sweep_omegaph.pdf}
+\caption{(Color online) (a) Time-averaged steady-state current $j$ and (b) double occupancy $N_{\text{D}}$ as a function of $\Omega$, for $v=0.4, 0.8$, at phonon cutoff frequencies $\omega_{\text{ph}}=0.025, 0.05$.
+Default parameters are specified at the beginning of Sec.~\ref{sec:results}.}
+\label{fig:j_vs_omega_mu1_v_0.4_0.8_E0_2_sweep_omegaph}
+\end{figure}
 
-The double occupation $N_D$ with phonons (Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(b)) for both $v$ remains bigger and follows the behaviour of the corresponding \emph{only-electron} counterpart within all the $\Omega$-range considered.
+Summarizing, phonons enhance the current for almost all driving frequencies $\Omega\lesssim 7$ for which only DEs take place.
+They suppress the current in the range $7\lesssim\Omega\lesssim14$, where II is the dominant electronic scattering process for $v=0.4$ and DE for $v=0.8$.
 
-The spectral features including electron-phonon interaction shown in Fig.\ref{fig:spec_filling_mu1_v_0.4_0.8_O_11_eph} display a redistribution of the spectral weight towards the edges of the LHB and UHB, closing the gap and a suppression of the peaks of the bands.
-Consequently, the occupation of positive energy states is slightly shifted to the bottom of the UHB respect to the case without phonons, as the occupation function shows.
-The spectral function with phonons is then more broadened and tends to fill the effective gap $\Delta_{\textrm{eff}}$, as anticipated in Sec.\ref{sec:scheme_electrons_phonons}.
+%% By reducing the soft cutoff frequency, the spetral function of the phonons at low frequencies is increased.
+The idea is that this increases the influence of the phonons on the current thus increasing the current at low driving frequencies (DE) and reducing the current at driving frequencies around the peak (II).
+%
 
-Such feature explains why the current in presence of phonons in (Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(a)) is slighty bigger in magnitude respect to the \emph{only-electron} one for both $v$ for $\Omega\lesssim7$.
-Such driving frequencies can excite across the gap only electrons coming from the upper edge of the LHB and due to $\Delta_{\textrm{eff,ph}}<\Delta_{\textrm{eff}}$, for the same $\Omega$ more photoexcited electrons end up in the UHB respect to the \emph{only-electron} case, with a consequent increase of the photocurrent.
-For example, Fig.\ref{fig:spec_filling_mu1_v_0.4_0.8_O_11_eph}(a)-(b) shows that an electron excited with $\Omega=4-5$ from the upper edge of the LHB ends close to the lower edge of UHB where $A(\omega)$ with phonons is slightly bigger than the \emph{only-electron} one.
+This is confirmed by Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_E0_2_sweep_omegaph}, which shows that the impact of acoustic phonons on current and double occupation is slightly boosted when decreasing the soft cutoff frequency $\omega_{\text{ph}}$~\footnote{Reducing $\omega_{\text{ph}}$ has two effects.
+First, the spectral function $A_{\text{ph}}(\omega)$ exhibits more weight at low frequencies $\omega\approx\omega_{\text{ph}}$.
+Second, it restricts the maximal value of the reciprocal lattice vector $\vec{q}_{\text{max}}$ via $\omega_{\text{ph}}=\omega(\vec{q}_{\text{max}})$~\cite{ma.ga.22u}, meaning that short-wavelength phonons are neglected.}.
 
-We explain instead the suppression of the current with phonons respect to \emph{only-electron} one in the range $7\lesssim\Omega\lesssim14$, for both $v$, observing that for driving frequencies around the $j-$peak at $\Omega\approx 11$ the photoexcited electron in the UHB can come from three regions of LHB.
-Looking at Fig.
-\ref{fig:spec_filling_mu1_v_0.4_0.8_O_11_eph}(a)-(b), an electron can in fact be excited from the lower edge of LHB to lower edge of the UHB, from the middle of the LHB to the middle of UHB or from upper edge of LHB to the upper edge of the UHB.
-In the first and third case the electron comes and ends up in $\omega$-regions where the spectral function in presence of phonons has slightly more spectral weight than the \emph{only-electron} one, while in the second case the electron is excited between $\omega$-regions in which the \emph{only-electron} $A(\omega)$ is clearly bigger in magnitude than the one in presence of phonons.
-Overall, the dominant scattering process is the second one, yielding an higher current when only electrons are taken into account.
+The results above suggest that the influence of acoustic phonons on the electronic scattering processes is similar for all values of $v$, independent of how it affects DE or II.
+In other words, the effects of phonons is independent of the rate at which carriers are injected into and removed from the layer.
+ Fig.~\ref{fig:j_vs_omega_mu1_sweep_v_E0_2_eph} confirms this behavior for intermediate lead-layer hybridizations $v=0.5,0.6,0.7$, for which DE and II at $\Omega\gtrsim8$ are even stronger mixed and harder to separate.
+Also the location of the crossing in the current  between the EO and e-ph case is essentially independent of $v$, as can be seen in
+ Fig.~\ref{fig:j_vs_omega_mu1_sweep_v_E0_2_eph}(a).
+The increase of double occupation for the case with e-ph interaction 
+(cf. Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(b)-Fig.~\ref{fig:j_vs_omega_mu1_sweep_v_E0_2_eph}(b))
+coincides with the current suppression and is probably due to a stronger localization of photoexcited electrons in the UHB.
 
-\pgcomm{Maybe this explanation above related to tunneling current}
-
-Regarding the trend of double occupation $N_D$ with phonons for both $v$ in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(b), we notice from Fig.\ref{fig:spec_filling_mu1_v_0.4_0.8_O_11_eph} that, for positive energies,  the occupation function in presence of phonons is almost always bigger than the \emph{only-electron} one.
-
-We discuss now the effect of phonons on DE/IO processes, as outlined in Sec.\ref{sec:E0_2_only_electrons}.
-
-The presence of phonons enhances slightly the current in almost all the region in which only DE take place (until $\Omega\lesssim7$, while the DE region ends at $\Omega\approx8$).
-They suppress the current in the range $7\lesssim\Omega\lesssim14$, where IO is the dominant electronic scattering process for $v=0.4$ and DE for $v=0.8$.
-This is confirmed by Fig.\ref{fig:j_vs_omega_mu1_v_0.4_0.8_E0_2_sweep_omegaph}, that shows that the effect of acoustic phonons on the observables is slightly boosted decreasing the soft cutoff phonon frequency $\omega_{ph}$, as the comparison with Fig.\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph} highlights \footnote{Decreasing $\omega_{ph}$, the acoustic phonon modes linear dispersion is always more truncated and increased in magnitude.
-Therefore the maximal value of the reciprocal lattice vector $\vec{q}_{\text{max}}$ such that $\omega_{\text{ph}}=\omega(\vec{q}_{\text{max}})$ \cite{ma.ga.22u} is reduced and consequently the dissipation by acoustic phonons is more effective.}.
-
-The results above suggest that the effect of acoustic phonons on the electronic scattering processes is the same, independently from their DE or IO origin, in fact they don't change drastically the interaction between the electrons.
-
-Moreover, their effect is independent of $v$, therefore independent of "how many" carriers are injected/dragged into/from the layer.
-Fig.\ref{fig:j_vs_omega_mu1_sweep_v_E0_2_eph} confirms such behaviour for the intermediate bath-layer couplings $v=0.5,0.6,0.7$, for which DE and IO at $\Omega\gtrsim8$ are even more mixed and hard to identify, together with their features \footnote{We don't consider smaller $v$ and smaller $E_0$ because they give a really slow convergence of DMFT loop.
-Moreover, the observables' magnitude becomes comparable with numerical fluctuations caused by numerical precision issues.}.
-
-\pgcomm{Are there some confirmations in literature regarding the effects of the phonons I observed?}
-
-\begin{figure}[ht] 
+\begin{figure}[b] 
 % \captionsetup{width=\textwidth} 
 \includegraphics[width=\linewidth]{./figures_Paper1/j_vs_omega_mu1_sweep_v_E0_2_eph.pdf}
-\caption{(Colour online) $\Omega$-dependence of time-averaged steady-state current $j$ (in units of $j_0=\frac{qt^*}{\hbar a^2}$) (a) and double occupancy $N_D$ (b), for $v=0.5,0.6,0.7$, when electron-phonon interaction is switched off and on.
-The electron-phonon coupling is set to $g=0.8$ and the phonon cutoff frequency to $\omega_{ph}=0.1$.
-Default parameters are specified at the beginning of section~\ref{sec:results}.}
+\caption{(Color online) (a) Time-averaged steady-state current $j$ and (b) double occupancy $N_{\text{D}}$ as a function of $\Omega$, for $v=0.5,0.6,0.7$, without and with e-ph interaction.
+Default parameters are specified at the beginning of Sec.~\ref{sec:results}.}
 \label{fig:j_vs_omega_mu1_sweep_v_E0_2_eph}
@@
 
-\begin{figure}[ht] 
-% \captionsetup{width=\textwidth} 
-\includegraphics[width=\linewidth]{./figures_Paper1/j_vs_omega_mu1_v_0.4_0.8_E0_2_sweep_omegaph.pdf}
-\caption{(Colour online) $\Omega$-dependence of time-averaged steady-state current $j$ (in units of $j_0=\frac{qt^*}{\hbar a^2}$) (a) and double occupancy $N_D$ (b), for $v=0.4,0.8$, at  phonon cutoff frequencies $\omega_{ph}=0.025,0.05$.
-The electron-phonon coupling is set to $g=0.8$.
-Default parameters are specified at the beginning of section~\ref{sec:results}.}
-\label{fig:j_vs_omega_mu1_v_0.4_0.8_E0_2_sweep_omegaph}
-\end{figure}
-
-\newpage
-
-\subsection{Higher $E_0$}
-\label{sec:higher_E0}
-
-\begin{figure*}[ht] 
-\includegraphics[width=\textwidth]{./figures_Paper1/j_vs_omega_mu1_v_0.4_0.8_eph_E0_3_4.pdf}
-% \captionsetup{width=\textwidth}
-\caption{(Colour online) $\Omega$-dependence of time-averaged steady-state current $j$ (in units of $j_0=\frac{qt^*}{\hbar a^2}$) (a) and double occupancy $N_D$ (b), for $v=0.4,0.8$ at different electric field amplitudes $E_0=3,4$, when electron-phonon interaction is switched off and on.
-The electron-phonon coupling is set to $g=0.8$ and the phonon cutoff frequency to $\omega_{ph}=0.1$.
-Default parameters are specified at the beginning of section~\ref{sec:results}.}
-\label{fig:j_vs_omega_mu1_v_0.4_0.8_eph_E0_3_4}
-\end{figure*}
-
-\subsubsection{Only electrons}
-\label{sec:higher_E0_only_electrons}
-
-As for Sec.\ref{sec:E0_2_only_electrons}, we analyze first the results obtained without the electron-phonon interaction.
-
-The trend of the current as a function of $\Omega$ for the two different $v$ at increasing $E_0$ in Fig.\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph_E0_3_4}(a) follows the one outlined in Sec.
-\ref{sec:E0_2_only_electrons}.
-
-For both $E_0=3,4$ the current maximum, located around $\Omega\approx11.5$, is due mainly to IO for $v=0.4$ and mainly to DE for $v=0.8$, as the double occupation in Fig.\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph_E0_3_4}(b) clearly shows.
-These results are in accordance with Sec.\ref{sec:E0_2_only_electrons}.
-This is confirmed also by Fig.\ref{fig:spec_filling_mu1_v_0.4_0.8_E3_4_O_11.5_e}(a)-(b) in which is evident the bigger occupation of the UHB for $v=0.4$.
-
-There are however some features to be discussed more in detail.
-
-The magnitude of the current clearly increases with $E_0$ and there is a steeper increase of $j$ in the $\Omega$-region after $\Omega\approx8$ for both $v$ respect to $E_0=2$ (Fig.\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}).
-The current peak for $v=0.8$ becomes bigger than the corresponding one for $v=0.4$ increasing the electric field amplitude $E_0$.
-A small bump develops at $E_0=4$ for $v=0.4$ around $\Omega\approx6$.
-Its position, directly in the middle of DE region (Sec.\ref{sec:scheme_only_electrons}) suggests an origin due to DE \cite{so.do.18}.
-
-\pgcomm{The position of the current peaks seem to have a linear dependence on $E_0$. (see mail). Putting here the plots would have taken really long time and maybe we don't even insert this part.}
-
-Also the double occupation as a function of $\Omega$ for the two $v$ at increasing $E_0$ in Fig.\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph_E0_3_4}(b) follows the one outlined in Sec.
-\ref{sec:E0_2_only_electrons}.
-However, the magnitude of $N_D$ is enhanced clearly with $E_0$, especially the $N_D$ peaks for $v=0.4$, in comparison with the $E_0=2$ case in Fig.\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(b).
-Moreover, the difference in $N_D$ between the two $v$ at the same $E_0$ increases with $E_0$, as Fig.\ref{fig:spec_filling_mu1_v_0.4_0.8_E3_4_O_11.5_e} also shows.
-
-Therefore, increasing $E_0$, we have an overall enhancement of the photocurrent and of double occupation.
-The current for $v=0.8$ in which DE play a major role is enhanced respect to the one $v=0.4$ coming mainly from IO.
-However, the latter experiences an extreme increase in both the observables $j$ and $N_D$, confirmed by Fig.\ref{fig:spec_filling_mu1_v_0.4_0.8_E3_4_O_11.5_e}.
-
-\begin{figure}[ht]
-% \captionsetup{width=\textwidth} 
-\includegraphics[width=\linewidth]{./figures_Paper1/spec_filling_mu1_v_0.4_0.8_E3_4_O_11.5_e.pdf}
-\caption{(Colour online) Spectral function $A(\omega)/t^{* -1}$ (solid line) and occupation function $N(\omega)/t^{* -1}$ (shaded area) at $\Omega=11.5$ for $v=0.4,0.8$ when electron-phonon interaction is switched off, for $E_0=3$ (a) and $E_0=4$ (b).
-Default parameters are specified at the beginning of section~\ref{sec:results}.}
-\label{fig:spec_filling_mu1_v_0.4_0.8_E3_4_O_11.5_e}
-\end{figure}
-
-\subsubsection{Electrons and phonons}
-\label{sec:higher_E0_electrons_phonons}
-
-As in Sec.\ref{sec:E0_2_electrons_phonons}, we discuss now the results obtained including the acoustic phonons.
-
-The $\Omega$-dependence of the current with phonons respect to the \emph{only-electron} one follows for both $v$ and $E_0$ the behaviour outlined in Sec.\ref{sec:E0_2_electrons_phonons}, with two minor differences, namely the crossing between the currents with and without phonons, occurring in this case at $\Omega\approx8$ and the current peaks slighly shifted at $\Omega\approx11.5$.
-For the small bump at $E_0=4$, $v=0.4$ around $\Omega\approx6$ there is no difference whether the phonons are taken into account or not.
-
-The double occupation $N_D$ with phonons (Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph_E0_3_4}(b)) for both $v$ and $E_0$ is bigger and goes like the corresponding \emph{only-electron} one over all the $\Omega$-range, similarly to Sec.\ref{sec:E0_2_electrons_phonons}.
-
-However, for increasing $E_0$, the $N_D$-peak in presence of phonons for $v=0.4$, around $\Omega\approx11.5$, is clearly flattened on the relative \emph{only-electron} one.
-There is this tendency (even though really small) also for $v=0.8$.
-
-The spectral features with the electron-phonon interaction remain the same as described in Sec.\ref{sec:E0_2_electrons_phonons}(see Fig.\ref{fig:spec_filling_mu1_v_0.4_0.8_O_11_eph}).
-
-The effect of phonons on DE/IO processes as $E_0$ is increased is the same as discussed in Sec.\ref{sec:E0_2_electrons_phonons}.
-Overall, as Fig.\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph_E0_3_4}(a)-(b) show, their effect is independent of the electric field amplitude $E_0$, therefore independent of "how strong" electrons are driven from the external AC field.
-
-\section{Conclusions}
+\section{Conclusion}
 \label{sec:conclusions}
 
-We investigated the influence of fermion baths and phonons dissipation on electron transport and spectral properties of a Mott insulating layer driven to the non-equilibrium
-steady state by an external AC field.
-In order to reproduce a possible Mott-based photovoltaic setup between metallic leads, we considered partially filled wide-band fermion baths, addressing the issue regarding how acoustic phonons dissipate the energy carried by photoexcited electrons.
-We demonstrated the importance of the coupling to fermion baths on the electron scattering process occurring at different driving frequencies and observed how the dissipation by phonons influences the photocurrent and the double occupation.
-We found a strong evidence that the dominant electron scattering mechanism responsible for the photocurrent peak is impact ionization at small couplings to the fermion baths, almost absent at higher couplings.
-Higher electric field amplitudes substantially boost the photocurrent and the double occupation, without modifying the picture above.
-Acoustic phonons dissipation slightly boosts the photocurrent for small driving frequencies and suppresses it at higher ones, in correspondence to the peak, disregarding the dominant electron scattering process taking place.
-Phonons effect isn't influenced from the bath-layer coupling value and the electric field amplitude.
+We investigated the influence of fermion leads and phonon dissipation on electron transport and spectral properties of a Mott insulating layer driven to the nonequilibrium steady state by an external periodic field.
+In order to realize a Mott-based photovoltaic setup between metallic leads, we considered a correlated layer coupled to acoustic phonons, located between wide-band fermion leads.
+We demonstrated the importance of coupling to fermion leads for the electron scattering process occurring at different driving frequencies and observed how the dissipation by acoustic phonons influences the photocurrent and the double occupation.
+We found strong evidence that the dominant electron scattering mechanism responsible for the photocurrent peak at small hybridizations to the fermion leads is II, while DEs dominate at higher hybridizations.
+Dissipation via acoustic phonons slightly boosts the photocurrent for small driving frequencies and suppresses it at higher ones in the vicinity of the main peak.
+The effect of phonons is not affected by changes in the lead-layer hybridization.
 
-These results suggest that in correlated layers weakly coupled to single layers or quantum dots, in turn connected to metallic leads, impact ionization may occur significantly.
-From the experimental point of view, such realization is employed, for example, to bridge semiconductor quantum dots to reservoirs through small molecules \cite{wa.mc.13,wa.bo.17}, to extract hot photoexcited carriers \cite{ti.ke.10,ca.wa.16}.
+These results suggest that in systems where correlated layers are connected to metallic leads via weakly coupled single layers or molecules, II could contribute significantly to the photocurrent.
+From the experimental point of view, such setup is employed, for example, to bridge semiconductor quantum dots to reservoirs through small molecules~\cite{wa.mc.13,wa.bo.17} to extract hot photoexcited carriers~\cite{ti.ke.10,ca.wa.16}.
+Based on our results, moderate e-ph coupling does not suppress the photocurrent significantly and therefore in real materials, II could contribute to overcome the Schockley-Queisser limit~\cite{sh.qu.61}.
 
-A positive aspect towards the future research in this direction is that a moderate electron-phonon coupling doesn't seem to suppress drastically the current, as our results show, and therefore in real materials, impact ionization might contribute consistently to overcome the Schockley-Queisser limit \cite{sh.qu.61}.
-
-However, in order to address the occurrence of impact ionization in realistic setups, one should take into account the feedback of the electrons on the phonon dynamics with a self-consistent treatment and the effect of impurities scattering.
-Another step forward would be the extension to multiorbital systems \cite{pe.be.19} in a multilayer setup, to model oxide heterostructures \cite{as.bl.13,pe.be.19}, where the correlated region is made of multiple layers and photoexcited carriers are separated via an electric field gradient.
-
-%  For electric field amplitudes in the sunlight range the generated photocurrent, even though small, could yield an efficiency exploitable for some applications.
-On the the other side, for experimental setups or scientific-based devices, a strong AC electric field, realized with a more concentrated light source like laser, would give a much bigger photocurrent with a broader range of future applications.
-
-% In second instance, such model misses still some ingredients as impurities/defects scatterings, long-range Coulomb effects, a multilayer structure with an intrinsic electric field gradient separating the charges.
-All these additional elements are present in Mott materials as oxide heterostructures proposed as a prototype for Mott solar cells.
-At the present level there's no point in considering now such features towards a more realistic description, because all these additional ingredients would complicate and hide the basic mechanisms still to be clarified completely.
+Experimentally, the electric field amplitude considered in this paper is several orders of magnitude bigger than the sunlight one, however it is possible to achieve such amplitudes via THz pulses ~\cite{mu.we.18} ~\footnote{We do not consider smaller electric field amplitudes $E_0$ since DMFT only converges slowly for such a choice of parameters.
+Moreover, the observables' magnitude becomes comparable to our numerical precision.}.
+Moreover, in order to address the occurrence of II in realistic photovoltaic setups, one should extend such simplified model to multiorbital systems \cite{pe.be.19} in a multilayer setup, to model oxide heterostructures~\cite{as.bl.13,pe.be.19} where the correlated region consists of multiple layers and photoexcited carriers are separated via an electric field gradient.
+Another step forward would be to take into account the effect of impurity scattering and the feedback of the electrons onto the phonon dynamics with a self-consistent treatment.
 
 \section*{Acknowledgements}
+
+We thank A.
+Picano for fruitful discussions.
 This work was supported by the Austrian Science Fund (FWF) within Project P 33165-N, as well as NaWi Graz.
@@
 % references in Phys Rev style
-\bibliography{footnotes,references_database}
+\bibliography{references_database}
 

### 2022-08-23 figures_Paper1/energy_setup.tex
Final version 23.08.2022

@@
 \usepackage{pgfplots}
-\pgfplotsset{compat=1.13}
+\pgfplotsset{compat=1.18}
 \usetikzlibrary{math}
@@
 
+% compilation of figure raises warning: Dimension too large, since the axis environment
+% is clipped. This is warning can be ignored.
+\clip (-3.5,-12.3) -- (5.5,-12.3) -- (5.5,5.3) -- (-3.5,5.3) -- cycle;
+
 % Figure 1
+\begin{scope}
+% r-lead
+% \filldraw[draw=hred,fill=hred!20!white] (2.5,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;
+\fill[fill=hgreen!20!white] (0,3) -- (0,2) -- (0.2,1.99) arc [start angle=195, end angle=165,x radius=2cm, y radius=2cm] -- cycle;
+\draw[draw=hgreen] (0.2,1.99) arc [start angle=195, end angle=165,x radius=2cm, y radius=2cm];
+\draw[draw=hgreen] (0,2) -- (0,3);
+% UHB
+\fill[fill=hgreen!20!white] (0,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
+\draw[draw=hgreen] (0,5) arc [start angle=90, end angle=-84.7,x radius=2cm, y radius=1cm]; 
+\draw[draw=hgreen] (0,3) -- (0,5);
+% \draw (0,4) -- (5,4);
+% LHB
+\fill[fill=hgreen!20!white] (0,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
+\draw[draw=hgreen] (0,0) arc [start angle=-90, end angle=84.5,x radius=2cm, y radius=1cm];
+\draw[draw=hgreen] (0,0) -- (0,2);
+% \draw (-3,1) -- (3,1);
+% l-lead
+% \filldraw[draw=hred,fill=hred!20!white] (-2.5,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;
 
-% \path[>=stealth,<->,shorten >=0.15cm,shorten <=0.15cm,out=-30,in=-150,line width=2pt] (2.5,0.5) edge (5,0.5);
-
-% \filldraw[fill=hblue!50!white,draw=hblue,xshift=-2cm,rotate=-90] (-1,0) parabola[bend pos=0.5] bend +(0,2) +(3,0) -- cycle;
-
-\path[>=stealth,<->,shorten >=0.5cm,shorten <=0.5cm,line width=2pt] (4.7,2.5) edge (4.7,5.5);
-
-\filldraw[draw=hred,fill=hred!20!white] (2.5,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;
-
-\filldraw[draw=hgreen,fill=hgreen!20!white] (0,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
-
-\path[>=stealth,line width=1pt] (2.5,2.75) edge (4.5,2.75);
-
-\path[>=stealth,<->,shorten >=0.5cm,shorten <=0.5cm,line width=2pt] (0,1.5) edge (0,3.5);
-
-\path[>=stealth,line width=1pt] (-2.5,2.25) edge (-0.5,2.25);
-
-\filldraw[draw=hgreen,fill=hgreen!20!white] (0,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
-
-\filldraw[draw=hred,fill=hred!20!white] (-2.5,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;
-
-\path[>=stealth,<->,shorten >=0.5cm,shorten <=0.5cm,line width=2pt] (-2.7,-0.5) edge (-2.7,2.5);
+% r-lead width
+\path[>=stealth,<->,shorten >=0.5cm,shorten <=0.5cm,line width=2pt] (4.7,2.5) edge node[midway,right] {$W_{\text{b}}$} (4.7,5.5);
+% % chemical potential right
+% \draw[line width=1pt] (2.5,2.75) -- node[midway,below] {$\mu_{\text{r}}$} (4.5,2.75);
+%gap
+% \path[>=stealth,<->,shorten >=0.5cm,shorten <=0.5cm,line width=2pt] (0,1.5) edge node[midway,right] {$\Delta_{\text{eff}}$/$\Delta_{\text{eff},\text{ph}}$} (0,3.5);
+\path[>=stealth,<->,shorten >=0.5cm,shorten <=0.5cm,line width=2pt] (0.5,1.5) edge node[midway,right] {$\Delta_{\text{pg}}$} (0.5,3.5);
+% % chemical potential left
+% \draw[line width=1pt] (-2.5,2.25) -- node[midway,above] {$\mu_{\text{l}}$} (-0.5,2.25);
+% l-lead width
+\path[>=stealth,<->,shorten >=0.5cm,shorten <=0.5cm,line width=2pt] (-2.7,-0.5) edge node[midway,left] {$W_{\text{b}}$} (-2.7,2.5);
 
 % text
+\node at (3.5,4) [minimum size = 0.1 cm]{\textcolor{hred}{r-lead}}; 
+\node at (1,4) [minimum size = 0.1 cm]{\textcolor{hgreen}{UHB}};
+\node at (1,1) [minimum size = 0.1 cm]{\textcolor{hgreen}{LHB}};
+\node at (-1.8,1) [minimum size = 0.1 cm]{\textcolor{hred!20!white}{l-lead}};
 
-\node at (3.5,4) [minimum size = 0.1 cm]{\textcolor{hred}{r-bath}}; 
-\node at (1,4) [minimum size = 0.1 cm]{\textcolor{hgreen}{UH band}};
-\node at (1,1) [minimum size = 0.1 cm]{\textcolor{hgreen}{LH band}};
-\node at (-1.5,1) [minimum size = 0.1 cm]{\textcolor{hred}{l-bath}};
+\node at (-2.5,4.5) {\bfseries(a)};
+\end{scope}
 
-\node at (5.1,4) {\textcolor{black}{$W_{b}$}};
+% r-lead
+% (position of lead has to be set manually)
+\begin{axis}[%
+xmin=0,xmax=3.5,
+ymin=-5,ymax=5,
+xtick=\empty,
+ytick=\empty,
+axis line style={draw=none},
+scale=1,
+at={(2.5cm,1.15cm)}]
 
-\node at (3.5,2.6) {\textcolor{black}{$\mu_r$}};  
-\node at (-1.5,2.4) {\textcolor{black}{$\mu_l$}};
+\addplot[solid,domain=-5:2,hred,name path=spectrum,samples=200] ({1.*1.0^2/(x^2+1.0^2)},{x});
+\addplot[solid,domain=-5:2,hred,name path=occupation,samples=200] ({1.*1.0^2/(x^2+1.0^2)*1./(exp((x+2.2)/0.06)+1.)},{x});
+\path[name path=yaxis] (axis cs:0,-5) -- (axis cs:0,2);
 
-\node at (-3.1,1) {\textcolor{black}{$W_{b}$}};
+\addplot[fill=hred!20!white,domain=-5:2] fill between [of=spectrum and yaxis,soft clip={domain=-5:5}];
+\addplot[fill=hred!60!white,domain=-5:2] fill between [of=occupation and yaxis,soft clip={domain=-5:5}];
 
-\node at (1,2.5) {\textcolor{black}{$\Delta_{\textrm{eff}}$/$\Delta_{\textrm{eff,ph}}$}};
+\draw[line width=1pt] (axis cs:0,-2.2) -- node[midway,below] {$\mu_{\text{r}}$} (1,-2.2);
+\end{axis}
 
-\node at (-2.7,5) {\bfseries(a)};
+% l-lead
+% (position of lead has to be set manually)
+\begin{axis}[%
+ymin=-5,ymax=5,
+xmin=0,xmax=3.5,
+xtick=\empty,
+ytick=\empty,
+axis line style={draw=none},
+scale=1,
+clip mode=individual,
+at={(-2.5cm,-1.85cm)}]
+
+\addplot[solid,domain=-2:5,hred,name path=spectrum,samples=200] ({1.*1.0^2/(x^2+1.0^2)},{x});
+\addplot[solid,domain=-2:5,hred,name path=occupation,samples=200] ({1.*1.0^2/(x^2+1.0^2)*1./(exp((x-2.2)/0.06)+1.)},{x});
+\path[name path=yaxis] (axis cs:0,-2) -- (axis cs:0,5);
+
+\addplot[fill=hred!20!white] fill between [of=spectrum and yaxis,soft clip={domain=-2:5}];
+\addplot[fill=hred!60!white] fill between [of=occupation and yaxis,soft clip={domain=-2:5}];
+
+\draw[line width=1pt] (axis cs:0,2.2) -- node[midway,above] {$\mu_{\text{l}}$} (1,2.2);
+\end{axis}
 
 % Figure 2
-
-\filldraw[draw=hred,fill=hred!20!white] (2.5,-3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;
-
-\filldraw[draw=hgreen,fill=hgreen!20!white] (0,-3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
-
-\draw [->,>=Stealth,line width=1pt,decorate,decoration={snake,amplitude=0.2cm,segment length=0.4cm,pre length=0.4cm,post length=0.4cm},draw=hyellow] (-2.5,-2.5) -- (0,-3.5);
-
-\filldraw[draw=hgreen,fill=hgreen!20!white] (0,-6) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
-
-\filldraw[draw=hred,fill=hred!20!white] (-2.5,-6) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;
+\begin{scope}[yshift=-6cm]
+% % r-lead
+% \filldraw[draw=hred,fill=hred!20!white] (2.5,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  
+\fill[fill=hgreen!20!white] (0,3) -- (0,2) -- (0.2,1.99) arc [start angle=195, end angle=165,x radius=2cm, y radius=2cm] -- cycle;
+\draw[draw=hgreen] (0.2,1.99) arc [start angle=195, end angle=165,x radius=2cm, y radius=2cm];
+\draw[draw=hgreen] (0,2) -- (0,3);
+% UHB
+\fill[fill=hgreen!20!white] (0,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
+\draw[draw=hgreen] (0,5) arc [start angle=90, end angle=-84.7,x radius=2cm, y radius=1cm]; 
+\draw[draw=hgreen] (0,3) -- (0,5);
+% LHB
+\fill[fill=hgreen!20!white] (0,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
+\draw[draw=hgreen] (0,0) arc [start angle=-90, end angle=84.5,x radius=2cm, y radius=1cm];
+\draw[draw=hgreen] (0,0) -- (0,2);
+% % l-lead
+% \filldraw[draw=hred,fill=hred!20!white] (-2.5,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;
 
 % text
+\node at (3.5,4) [minimum size = 0.1 cm]{\textcolor{hred}{r-lead}}; 
+\node at (1,4) [minimum size = 0.1 cm]{\textcolor{hgreen}{UHB}};
+\node at (1,1) [minimum size = 0.1 cm]{\textcolor{hgreen}{LHB}};
+\node at (-1.8,1) [minimum size = 0.1 cm]{\textcolor{hred!20!white}{l-lead}};
 
-\node at (3.5,-2) [minimum size = 0.1 cm]{\textcolor{hred}{r-bath}}; 
-\node at (1,-2) [minimum size = 0.1 cm]{\textcolor{hgreen}{UH band}};
-\node at (1,-5) [minimum size = 0.1 cm]{\textcolor{hgreen}{LH band}};
-\node at (-1.5,-5) [minimum size = 0.1 cm]{\textcolor{hred}{l-bath}};
+\node at (-2.5,4.5) {\bfseries(b)};
 
-\node at (-1,-2.7) {\textcolor{hyellow}{$\Omega$}};
+% processes
 
-\node at (-2.7,-1) {\bfseries(b)};
+% particles
+\draw[dotted,color=black,fill=white] (0.5,1) circle[radius=3pt];
+\draw[color=black,fill=hgreen] (0.5,3.9) circle[radius=3pt];
+% driving
+\path[color=hyellow,>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=140,in=-140,line width=1pt] (0.5,1) edge (0.5,3.9);
+\draw [->,>=Stealth,line width=1pt,decorate,decoration={snake,amplitude=0.2cm,segment length=0.4cm,pre length=0.4cm,post length=0.4cm},draw=hyellow] (-2.0,3.5) -- (-0.3,2.5);
+\node at (-1,3.5) {\textcolor{hyellow}{$\Omega$}};
+% escape
+\path[color=hred,>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=-30,in=-150,line width=1pt] (0.5,3.9) edge (3.2,3.9);
 
-\draw[dotted,color=black,fill=white] (0.5,-5) circle[radius=3pt];
+\end{scope}
 
-\path[color=hyellow,>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=120,in=210,line width=1pt] (0.5,-5) edge (0.8,-2);
+% r-lead
+% (position of lead has to be set manually)
+\begin{axis}[%
+xmin=0,xmax=3.5,
+ymin=-5,ymax=5,
+xtick=\empty,
+ytick=\empty,
+axis line style={draw=none},
+scale=1,
+at={(2.5cm,-4.85cm)}]
 
-\draw[color=black,fill=hgreen] (0.8,-2.1) circle[radius=3pt];
+\addplot[solid,domain=-5:2,hred,name path=spectrum,samples=200] ({1.*1.0^2/(x^2+1.0^2)},{x});
+\addplot[solid,domain=-5:2,hred,name path=occupation,samples=200] ({1.*1.0^2/(x^2+1.0^2)*1./(exp((x+2.2)/0.06)+1.)},{x});
+\path[name path=yaxis] (axis cs:0,-5) -- (axis cs:0,2);
 
-\path[color=hred,>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=-30,in=-150,line width=1pt] (0.8,-2.2) edge (3.2,-2);
+\addplot[fill=hred!20!white,domain=-5:2] fill between [of=spectrum and yaxis,soft clip={domain=-5:5}];
+\addplot[fill=hred!60!white,domain=-5:2] fill between [of=occupation and yaxis,soft clip={domain=-5:5}];
+
+% \draw[line width=1pt] (axis cs:0,-2.2) -- node[midway,below] {$\mu_{\text{r}}$} (1,-2.2);
+\end{axis}
+
+% l-lead
+% (position of lead has to be set manually)
+\begin{axis}[%
+ymin=-5,ymax=5,
+xmin=0,xmax=3.5,
+xtick=\empty,
+ytick=\empty,
+axis line style={draw=none},
+scale=1,
+clip mode=individual,
+at={(-2.5cm,-7.85cm)}]
+
+\addplot[solid,domain=-2:5,hred,name path=spectrum,samples=200] ({1.*1.0^2/(x^2+1.0^2)},{x});
+\addplot[solid,domain=-2:5,hred,name path=occupation,samples=200] ({1.*1.0^2/(x^2+1.0^2)*1./(exp((x-2.2)/0.06)+1.)},{x});
+\path[name path=yaxis] (axis cs:0,-2) -- (axis cs:0,5);
+
+\addplot[fill=hred!20!white] fill between [of=spectrum and yaxis,soft clip={domain=-2:5}];
+\addplot[fill=hred!60!white] fill between [of=occupation and yaxis,soft clip={domain=-2:5}];
+
+% \draw[line width=1pt] (axis cs:0,2.2) -- node[midway,above] {$\mu_{\text{l}}$} (1,2.2);
+\end{axis}
 
 % Figure 3
-
-\filldraw[draw=hred,fill=hred!20!white] (2.5,-9) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;
-
-\filldraw[draw=hgreen,fill=hgreen!20!white] (0,-9) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
-
-\draw [->,>=Stealth,line width=1pt,decorate,decoration={snake,amplitude=0.2cm,segment length=0.4cm,pre length=0.4cm,post length=0.4cm},draw=hyellow] (-2.5,-8.5) -- (-0.2,-9.5);
-
-\filldraw[draw=hgreen,fill=hgreen!20!white] (0,-12) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
-
-\filldraw[draw=hred,fill=hred!20!white] (-2.5,-12) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;
+\begin{scope}[yshift=-12cm]
+% % r-lead
+% \filldraw[draw=hred,fill=hred!20!white] (2.5,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  
+\fill[fill=hgreen!20!white] (0,3) -- (0,2) -- (0.2,1.99) arc [start angle=195, end angle=165,x radius=2cm, y radius=2cm] -- cycle;
+\draw[draw=hgreen] (0.2,1.99) arc [start angle=195, end angle=165,x radius=2cm, y radius=2cm];
+\draw[draw=hgreen] (0,2) -- (0,3);
+% UHB
+\fill[fill=hgreen!20!white] (0,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
+\draw[draw=hgreen] (0,5) arc [start angle=90, end angle=-84.7,x radius=2cm, y radius=1cm]; 
+\draw[draw=hgreen] (0,3) -- (0,5);
+% LHB
+\fill[fill=hgreen!20!white] (0,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
+\draw[draw=hgreen] (0,0) arc [start angle=-90, end angle=84.5,x radius=2cm, y radius=1cm];
+\draw[draw=hgreen] (0,0) -- (0,2);
+% % l-lead
+% \filldraw[draw=hred,fill=hred!20!white] (-2.5,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;
 
 % text
+\node at (3.5,4) [minimum size = 0.1 cm]{\textcolor{hred}{r-lead}}; 
+\node at (1,4) [minimum size = 0.1 cm,xshift=0.2cm]{\textcolor{hgreen}{UHB}};
+\node at (1,1) [minimum size = 0.1 cm]{\textcolor{hgreen}{LHB}};
+\node at (-1.8,1) [minimum size = 0.1 cm]{\textcolor{hred!20!white}{l-lead}};
 
-\node at (3.5,-8) [minimum size = 0.1 cm]{\textcolor{hred}{r-bath}}; 
-\node at (1,-8) [minimum size = 0.1 cm]{\textcolor{hgreen}{UH band}};
-\node at (1,-11) [minimum size = 0.1 cm]{\textcolor{hgreen}{LH band}};
-\node at (-1.5,-11) [minimum size = 0.1 cm]{\textcolor{hred}{l-bath}};
+\node at (-2.5,4.5) {\bfseries(c)};
 
-\node at (-1,-8.7) {\textcolor{hyellow}{$\Omega$}};
+% processes
 
-\node at (-2.7,-7) {\bfseries(c)};
+% particles
+\draw[dotted,color=black,fill=white] (0.4,0.7) circle[radius=3pt];
+\draw[dotted,color=black,fill=white] (0.4,4.8) circle[radius=3pt];
+\draw[color=black,fill=hgreen] (0.4,3.25) circle[radius=3pt];
+\draw[dotted,color=black,fill=white] (0.9,1.7) circle[radius=3pt];
+\draw[color=black,fill=hgreen] (0.9,3.25) circle[radius=3pt];
+% driving
+\path[color=hyellow,>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=120,in=-120,line width=1pt] (0.4,0.7) edge (0.4,4.8);
+\draw [->,>=Stealth,line width=1pt,decorate,decoration={snake,amplitude=0.2cm,segment length=0.4cm,pre length=0.4cm,post length=0.4cm},draw=hyellow] (-2.0,3.5) -- (-0.3,2.5);
+\node at (-1,3.5) {\textcolor{hyellow}{$\Omega$}};
+% impact ionization
+\path[>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=-60,in=60,line width=1pt] (0.4,4.8) edge (0.4,3.25);
+\path[>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=120,in=-120,line width=1pt] (0.9,1.7) edge (0.9,3.25);
+% escape
+\path[color=hred,>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=30,in=150,line width=1pt] (0.4,3.25) edge (2.85,3.25);
+\path[color=hred,>=stealth,->,shorten >=0.15cm,shorten  <=0.15cm,out=-30,in=-150,line width=1pt] (0.9,3.25) edge (3.1,3.25);
 
-\draw[dotted,color=black,fill=white] (0.5,-11.3) circle[radius=3pt];
+\end{scope}
 
-\path[color=hyellow,>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=120,in=240,line width=1pt] (0.5,-11.3) edge (0.4,-7.2);
+% r-lead
+% (position of lead has to be set manually)
+\begin{axis}[%
+xmin=0,xmax=3.5,
+ymin=-5,ymax=5,
+xtick=\empty,
+ytick=\empty,
+axis line style={draw=none},
+scale=1,
+at={(2.5cm,-10.85cm)}]
 
-\draw[dotted,color=black,fill=white] (0.4,-7.3) circle[radius=3pt];
+\addplot[solid,domain=-5:2,hred,name path=spectrum,samples=200] ({1.*1.0^2/(x^2+1.0^2)},{x});
+\addplot[solid,domain=-5:2,hred,name path=occupation,samples=200] ({1.*1.0^2/(x^2+1.0^2)*1./(exp((x+2.2)/0.06)+1.)},{x});
+\path[name path=yaxis] (axis cs:0,-5) -- (axis cs:0,2);
 
-\path[>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=-60,in=-180,line width=1pt] (0.4,-7.3) edge (1.6,-8);
+\addplot[fill=hred!20!white,domain=-5:2] fill between [of=spectrum and yaxis,soft clip={domain=-5:5}];
+\addplot[fill=hred!60!white,domain=-5:2] fill between [of=occupation and yaxis,soft clip={domain=-5:5}];
 
-\draw[color=black,fill=hgreen] (1.6,-8) circle[radius=3pt];
+% \draw[line width=1pt] (axis cs:0,-2.2) -- node[midway,below] {$\mu_{\text{r}}$} (1,-2.2);
+\end{axis}
 
-\path[color=hred,>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=30,in=150,line width=1pt] (1.6,-8) edge (3.6,-8);
+% l-lead
+% (position of lead has to be set manually)
+\begin{axis}[%
+ymin=-5,ymax=5,
+xmin=0,xmax=3.5,
+xtick=\empty,
+ytick=\empty,
+axis line style={draw=none},
+scale=1,
+clip mode=individual,
+at={(-2.5cm,-13.85cm)}]
 
-\draw[dotted,color=black,fill=white] (0.9,-10.3) circle[radius=3pt];
+\addplot[solid,domain=-2:5,hred,name path=spectrum,samples=200] ({1.*1.0^2/(x^2+1.0^2)},{x});
+\addplot[solid,domain=-2:5,hred,name path=occupation,samples=200] ({1.*1.0^2/(x^2+1.0^2)*1./(exp((x-2.2)/0.06)+1.)},{x});
+\path[name path=yaxis] (axis cs:0,-2) -- (axis cs:0,5);
 
-\path[>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=120,in=-150,line width=1pt] (0.9,-10.3) edge (0.7,-8.8);
+\addplot[fill=hred!20!white] fill between [of=spectrum and yaxis,soft clip={domain=-2:5}];
+\addplot[fill=hred!60!white] fill between [of=occupation and yaxis,soft clip={domain=-2:5}];
 
-\draw[color=black,fill=hgreen] (0.67,-8.75) circle[radius=3pt];
-
-\path[color=hred,>=stealth,->,shorten >=0.15cm,shorten  <=0.15cm,out=-30,in=210,line width=1pt] (0.7,-8.7) edge (3.6,-8.4);
-
-% \path[>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=-30,in=-150,line width=1pt] (0.8,-2.2) edge (3.2,-2);
+% \draw[line width=1pt] (axis cs:0,2.2) -- node[midway,above] {$\mu_{\text{l}}$} (1,2.2);
+\end{axis}
 

### 2022-08-23 figures_Paper1/spec_filling_mu1_v_0.4_0.8_O_11_eph.tex
Final version 23.08.2022

@@
 minor tick num=1, 
-% grid=both,
-xlabel={$\omega/t^{*}$},
-ylabel={$A(\omega)/t^{*-1}$},
-legend style={at={(axis cs:-9.3,0.017)},anchor=north,mark options={scale=0.85},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
+grid=both,
+xlabel={$\omega$},
+ylabel={$A(\omega)$},
+legend style={at={(axis cs:-9.3,0.018)},anchor=north,mark options={scale=0.85},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
 legend cell align=left,
@@
 \addlegendimage{solid,color=hblue,scale={1.0},line width=1pt}
-\addlegendentry{$el$};
+\addlegendentry{el};
 \addlegendimage{solid,color=hred,scale={1.0},line width=1pt} 
-\addlegendentry{$el+ph$};
+\addlegendentry{el+ph};
 
@@
 
-\addplot[dashed,raw gnuplot,color=hblue,line width=1pt] gnuplot {
+\addplot[name path=neq_distr_f_filling_hyb0.4O11,solid,raw gnuplot,color=hblue,line width=1pt,opacity=0.0] gnuplot {
 plot './neq_distr_f_filling_hyb0.4O11.dat' u 1:3 w l;
@@
 
-\addplot[dashed,raw gnuplot,color=hred,line width=1pt] gnuplot {
+\addplot[name path=neq_distr_f_filling_hyb0.4O11ph,solid,raw gnuplot,color=hred,line width=1pt,opacity=0.0] gnuplot {
 plot './neq_distr_f_filling_hyb0.4O11ph.dat' u 1:3 w l;
 };
+
+\path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
+\addplot [fill=hblue,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11 and xaxis,soft clip={domain=-15:15}];
+\addplot [fill=hred,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11ph and xaxis,soft clip={domain=-15:15}];
 
@@
 minor tick num=1, 
-% grid=both,
-xlabel={$\omega/t^{*}$},
+grid=both,
+xlabel={$\omega$},
 % ylabel={$A(\omega)/t^{*-1}$},
-legend style={at={(axis cs:-9.3,0.017)},anchor=north,mark options={scale=0.85},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
+legend style={at={(axis cs:-9.3,0.018)},anchor=north,mark options={scale=0.85},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
 legend cell align=left,
@@
 \addlegendimage{solid,color=hcoral,scale={1.0},line width=1pt}
-\addlegendentry{$el$};
+\addlegendentry{el};
 \addlegendimage{solid,color=hlime,scale={1.0},line width=1pt} 
-\addlegendentry{$el+ph$};
+\addlegendentry{el+ph};
 
@@
 
-\addplot[dashed,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
+\addplot[name path=neq_distr_f_filling_hyb0.8O11,solid,raw gnuplot,color=hcoral,line width=1pt,opacity=0.0] gnuplot {
 plot './neq_distr_f_filling_hyb0.8O11.dat' u 1:3 w l;
@@
 
-\addplot[dashed,raw gnuplot,color=hlime,line width=1pt] gnuplot {
+\addplot[name path=neq_distr_f_filling_hyb0.8O11ph,solid,raw gnuplot,color=hlime,line width=1pt,opacity=0.0] gnuplot {
 plot './neq_distr_f_filling_hyb0.8O11ph.dat' u 1:3 w l;
 };
+
+\path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
+\addplot [fill=hcoral,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O11 and xaxis,soft clip={domain=-15:15}];
+\addplot [fill=hlime,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O11ph and xaxis,soft clip={domain=-15:15}];
 

### 2022-08-23 figures_Paper1/spec_filling_mu1_v_0.4_0.8_O_5_11_e.tex
Final version 23.08.2022

@@
 grid=both,
-xlabel={$\omega/t^{*}$},
-ylabel={$A(\omega)/t^{*-1}$},
-legend style={at={(axis cs:0,0.1)},anchor=north,mark options={scale=1.0},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
+xlabel={$\omega$},
+ylabel={$A(\omega)$},
+legend style={at={(axis cs:-8.8,0.017)},anchor=north,mark options={scale=1.0},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
 legend cell align=left,
@@
 grid=both,
-xlabel={$\omega/t^{*}$},
+xlabel={$\omega$},
 % ylabel={$A(\omega)/t^{*-1}$},
-legend style={at={(axis cs:0,0.1)},anchor=north,mark options={scale=1.0},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
+legend style={at={(axis cs:-8.8,0.017)},anchor=north,mark options={scale=1.0},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
 legend cell align=left,

### 2022-08-23 figures_Paper1/energy_setup_old.tex
Final version paper 23.08.2022

--- 2022-08-23 figures_Paper1/energy_setup.tex
@@
 \usepackage{pgfplots}
-\pgfplotsset{compat=1.18}
+\pgfplotsset{compat=1.13}
 \usetikzlibrary{math}
@@
 
-% compilation of figure raises warning: Dimension too large, since the axis environment
-% is clipped. This is warning can be ignored.
-\clip (-3.5,-12.3) -- (5.5,-12.3) -- (5.5,5.3) -- (-3.5,5.3) -- cycle;
-
 % Figure 1
@@
 % r-lead
-% \filldraw[draw=hred,fill=hred!20!white] (2.5,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;
-\fill[fill=hgreen!20!white] (0,3) -- (0,2) -- (0.2,1.99) arc [start angle=195, end angle=165,x radius=2cm, y radius=2cm] -- cycle;
-\draw[draw=hgreen] (0.2,1.99) arc [start angle=195, end angle=165,x radius=2cm, y radius=2cm];
-\draw[draw=hgreen] (0,2) -- (0,3);
+\filldraw[draw=hred,fill=hred!20!white] (2.5,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  
 % UHB
-\fill[fill=hgreen!20!white] (0,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
-\draw[draw=hgreen] (0,5) arc [start angle=90, end angle=-84.7,x radius=2cm, y radius=1cm]; 
-\draw[draw=hgreen] (0,3) -- (0,5);
-% \draw (0,4) -- (5,4);
+\filldraw[draw=hgreen,fill=hgreen!20!white] (0,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
 % LHB
-\fill[fill=hgreen!20!white] (0,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
-\draw[draw=hgreen] (0,0) arc [start angle=-90, end angle=84.5,x radius=2cm, y radius=1cm];
-\draw[draw=hgreen] (0,0) -- (0,2);
-% \draw (-3,1) -- (3,1);
+\filldraw[draw=hgreen,fill=hgreen!20!white] (0,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
 % l-lead
-% \filldraw[draw=hred,fill=hred!20!white] (-2.5,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;
+\filldraw[draw=hred,fill=hred!20!white] (-2.5,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;
 
@@
 \path[>=stealth,<->,shorten >=0.5cm,shorten <=0.5cm,line width=2pt] (4.7,2.5) edge node[midway,right] {$W_{\text{b}}$} (4.7,5.5);
-% % chemical potential right
-% \draw[line width=1pt] (2.5,2.75) -- node[midway,below] {$\mu_{\text{r}}$} (4.5,2.75);
+% chemical potential right
+\draw[line width=1pt] (2.5,2.75) -- node[midway,below] {$\mu_{\text{r}}$} (4.5,2.75);
 %gap
 % \path[>=stealth,<->,shorten >=0.5cm,shorten <=0.5cm,line width=2pt] (0,1.5) edge node[midway,right] {$\Delta_{\text{eff}}$/$\Delta_{\text{eff},\text{ph}}$} (0,3.5);
-\path[>=stealth,<->,shorten >=0.5cm,shorten <=0.5cm,line width=2pt] (0.5,1.5) edge node[midway,right] {$\Delta_{\text{pg}}$} (0.5,3.5);
-% % chemical potential left
-% \draw[line width=1pt] (-2.5,2.25) -- node[midway,above] {$\mu_{\text{l}}$} (-0.5,2.25);
+\path[>=stealth,<->,shorten >=0.5cm,shorten <=0.5cm,line width=2pt] (0,1.5) edge node[midway,right] {$\Delta_{\text{pg}}$} (0,3.5);
+% chemical potential left
+\draw[line width=1pt] (-2.5,2.25) -- node[midway,above] {$\mu_{\text{l}}$} (-0.5,2.25);
 % l-lead width
@@
 \node at (1,1) [minimum size = 0.1 cm]{\textcolor{hgreen}{LHB}};
-\node at (-1.8,1) [minimum size = 0.1 cm]{\textcolor{hred!20!white}{l-lead}};
+\node at (-1.5,1) [minimum size = 0.1 cm]{\textcolor{hred}{l-lead}};
 
-\node at (-2.5,4.5) {\bfseries(a)};
+\node at (-2.7,5) {\bfseries(a)};
 \end{scope}
-
-% r-lead
-% (position of lead has to be set manually)
-\begin{axis}[%
-xmin=0,xmax=3.5,
-ymin=-5,ymax=5,
-xtick=\empty,
-ytick=\empty,
-axis line style={draw=none},
-scale=1,
-at={(2.5cm,1.15cm)}]
-
-\addplot[solid,domain=-5:2,hred,name path=spectrum,samples=200] ({1.*1.0^2/(x^2+1.0^2)},{x});
-\addplot[solid,domain=-5:2,hred,name path=occupation,samples=200] ({1.*1.0^2/(x^2+1.0^2)*1./(exp((x+2.2)/0.06)+1.)},{x});
-\path[name path=yaxis] (axis cs:0,-5) -- (axis cs:0,2);
-
-\addplot[fill=hred!20!white,domain=-5:2] fill between [of=spectrum and yaxis,soft clip={domain=-5:5}];
-\addplot[fill=hred!60!white,domain=-5:2] fill between [of=occupation and yaxis,soft clip={domain=-5:5}];
-
-\draw[line width=1pt] (axis cs:0,-2.2) -- node[midway,below] {$\mu_{\text{r}}$} (1,-2.2);
-\end{axis}
-
-% l-lead
-% (position of lead has to be set manually)
-\begin{axis}[%
-ymin=-5,ymax=5,
-xmin=0,xmax=3.5,
-xtick=\empty,
-ytick=\empty,
-axis line style={draw=none},
-scale=1,
-clip mode=individual,
-at={(-2.5cm,-1.85cm)}]
-
-\addplot[solid,domain=-2:5,hred,name path=spectrum,samples=200] ({1.*1.0^2/(x^2+1.0^2)},{x});
-\addplot[solid,domain=-2:5,hred,name path=occupation,samples=200] ({1.*1.0^2/(x^2+1.0^2)*1./(exp((x-2.2)/0.06)+1.)},{x});
-\path[name path=yaxis] (axis cs:0,-2) -- (axis cs:0,5);
-
-\addplot[fill=hred!20!white] fill between [of=spectrum and yaxis,soft clip={domain=-2:5}];
-\addplot[fill=hred!60!white] fill between [of=occupation and yaxis,soft clip={domain=-2:5}];
-
-\draw[line width=1pt] (axis cs:0,2.2) -- node[midway,above] {$\mu_{\text{l}}$} (1,2.2);
-\end{axis}
 
@@
 \begin{scope}[yshift=-6cm]
-% % r-lead
-% \filldraw[draw=hred,fill=hred!20!white] (2.5,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  
-\fill[fill=hgreen!20!white] (0,3) -- (0,2) -- (0.2,1.99) arc [start angle=195, end angle=165,x radius=2cm, y radius=2cm] -- cycle;
-\draw[draw=hgreen] (0.2,1.99) arc [start angle=195, end angle=165,x radius=2cm, y radius=2cm];
-\draw[draw=hgreen] (0,2) -- (0,3);
+% r-lead
+\filldraw[draw=hred,fill=hred!20!white] (2.5,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  
 % UHB
-\fill[fill=hgreen!20!white] (0,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
-\draw[draw=hgreen] (0,5) arc [start angle=90, end angle=-84.7,x radius=2cm, y radius=1cm]; 
-\draw[draw=hgreen] (0,3) -- (0,5);
+\filldraw[draw=hgreen,fill=hgreen!20!white] (0,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
 % LHB
-\fill[fill=hgreen!20!white] (0,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
-\draw[draw=hgreen] (0,0) arc [start angle=-90, end angle=84.5,x radius=2cm, y radius=1cm];
-\draw[draw=hgreen] (0,0) -- (0,2);
-% % l-lead
-% \filldraw[draw=hred,fill=hred!20!white] (-2.5,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;
+\filldraw[draw=hgreen,fill=hgreen!20!white] (0,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
+% l-lead
+\filldraw[draw=hred,fill=hred!20!white] (-2.5,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;
 
@@
 \node at (1,1) [minimum size = 0.1 cm]{\textcolor{hgreen}{LHB}};
-\node at (-1.8,1) [minimum size = 0.1 cm]{\textcolor{hred!20!white}{l-lead}};
+\node at (-1.5,1) [minimum size = 0.1 cm]{\textcolor{hred}{l-lead}};
 
-\node at (-2.5,4.5) {\bfseries(b)};
+\node at (-2.7,5) {\bfseries(b)};
 
@@
 % driving
-\path[color=hyellow,>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=140,in=-140,line width=1pt] (0.5,1) edge (0.5,3.9);
-\draw [->,>=Stealth,line width=1pt,decorate,decoration={snake,amplitude=0.2cm,segment length=0.4cm,pre length=0.4cm,post length=0.4cm},draw=hyellow] (-2.0,3.5) -- (-0.3,2.5);
-\node at (-1,3.5) {\textcolor{hyellow}{$\Omega$}};
+\path[color=hyellow,>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=120,in=-120,line width=1pt] (0.5,1) edge (0.5,3.9);
+\draw [->,>=Stealth,line width=1pt,decorate,decoration={snake,amplitude=0.2cm,segment length=0.4cm,pre length=0.4cm,post length=0.4cm},draw=hyellow] (-2.5,3.5) -- (0,2.5);
+\node at (-1,3.3) {\textcolor{hyellow}{$\Omega$}};
 % escape
@@
 
-% r-lead
-% (position of lead has to be set manually)
-\begin{axis}[%
-xmin=0,xmax=3.5,
-ymin=-5,ymax=5,
-xtick=\empty,
-ytick=\empty,
-axis line style={draw=none},
-scale=1,
-at={(2.5cm,-4.85cm)}]
-
-\addplot[solid,domain=-5:2,hred,name path=spectrum,samples=200] ({1.*1.0^2/(x^2+1.0^2)},{x});
-\addplot[solid,domain=-5:2,hred,name path=occupation,samples=200] ({1.*1.0^2/(x^2+1.0^2)*1./(exp((x+2.2)/0.06)+1.)},{x});
-\path[name path=yaxis] (axis cs:0,-5) -- (axis cs:0,2);
-
-\addplot[fill=hred!20!white,domain=-5:2] fill between [of=spectrum and yaxis,soft clip={domain=-5:5}];
-\addplot[fill=hred!60!white,domain=-5:2] fill between [of=occupation and yaxis,soft clip={domain=-5:5}];
-
-% \draw[line width=1pt] (axis cs:0,-2.2) -- node[midway,below] {$\mu_{\text{r}}$} (1,-2.2);
-\end{axis}
-
-% l-lead
-% (position of lead has to be set manually)
-\begin{axis}[%
-ymin=-5,ymax=5,
-xmin=0,xmax=3.5,
-xtick=\empty,
-ytick=\empty,
-axis line style={draw=none},
-scale=1,
-clip mode=individual,
-at={(-2.5cm,-7.85cm)}]
-
-\addplot[solid,domain=-2:5,hred,name path=spectrum,samples=200] ({1.*1.0^2/(x^2+1.0^2)},{x});
-\addplot[solid,domain=-2:5,hred,name path=occupation,samples=200] ({1.*1.0^2/(x^2+1.0^2)*1./(exp((x-2.2)/0.06)+1.)},{x});
-\path[name path=yaxis] (axis cs:0,-2) -- (axis cs:0,5);
-
-\addplot[fill=hred!20!white] fill between [of=spectrum and yaxis,soft clip={domain=-2:5}];
-\addplot[fill=hred!60!white] fill between [of=occupation and yaxis,soft clip={domain=-2:5}];
-
-% \draw[line width=1pt] (axis cs:0,2.2) -- node[midway,above] {$\mu_{\text{l}}$} (1,2.2);
-\end{axis}
-
 % Figure 3
 \begin{scope}[yshift=-12cm]
-% % r-lead
-% \filldraw[draw=hred,fill=hred!20!white] (2.5,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  
-\fill[fill=hgreen!20!white] (0,3) -- (0,2) -- (0.2,1.99) arc [start angle=195, end angle=165,x radius=2cm, y radius=2cm] -- cycle;
-\draw[draw=hgreen] (0.2,1.99) arc [start angle=195, end angle=165,x radius=2cm, y radius=2cm];
-\draw[draw=hgreen] (0,2) -- (0,3);
+% r-lead
+\filldraw[draw=hred,fill=hred!20!white] (2.5,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  
 % UHB
-\fill[fill=hgreen!20!white] (0,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
-\draw[draw=hgreen] (0,5) arc [start angle=90, end angle=-84.7,x radius=2cm, y radius=1cm]; 
-\draw[draw=hgreen] (0,3) -- (0,5);
+\filldraw[draw=hgreen,fill=hgreen!20!white] (0,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
 % LHB
-\fill[fill=hgreen!20!white] (0,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
-\draw[draw=hgreen] (0,0) arc [start angle=-90, end angle=84.5,x radius=2cm, y radius=1cm];
-\draw[draw=hgreen] (0,0) -- (0,2);
-% % l-lead
-% \filldraw[draw=hred,fill=hred!20!white] (-2.5,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;
+\filldraw[draw=hgreen,fill=hgreen!20!white] (0,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
+% l-lead
+\filldraw[draw=hred,fill=hred!20!white] (-2.5,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;
 
@@
 \node at (1,1) [minimum size = 0.1 cm]{\textcolor{hgreen}{LHB}};
-\node at (-1.8,1) [minimum size = 0.1 cm]{\textcolor{hred!20!white}{l-lead}};
+\node at (-1.5,1) [minimum size = 0.1 cm]{\textcolor{hred}{l-lead}};
 
-\node at (-2.5,4.5) {\bfseries(c)};
+\node at (-2.7,5) {\bfseries(c)};
 
@@
 \path[color=hyellow,>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=120,in=-120,line width=1pt] (0.4,0.7) edge (0.4,4.8);
-\draw [->,>=Stealth,line width=1pt,decorate,decoration={snake,amplitude=0.2cm,segment length=0.4cm,pre length=0.4cm,post length=0.4cm},draw=hyellow] (-2.0,3.5) -- (-0.3,2.5);
-\node at (-1,3.5) {\textcolor{hyellow}{$\Omega$}};
+\draw [->,>=Stealth,line width=1pt,decorate,decoration={snake,amplitude=0.2cm,segment length=0.4cm,pre length=0.4cm,post length=0.4cm},draw=hyellow] (-2.5,3.5) -- (-0.3,2.5);
+\node at (-1,3.3) {\textcolor{hyellow}{$\Omega$}};
 % impact ionization
@@
 % escape
-\path[color=hred,>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=30,in=150,line width=1pt] (0.4,3.25) edge (2.85,3.25);
-\path[color=hred,>=stealth,->,shorten >=0.15cm,shorten  <=0.15cm,out=-30,in=-150,line width=1pt] (0.9,3.25) edge (3.1,3.25);
+\path[color=hred,>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=30,in=150,line width=1pt] (0.4,3.25) edge (2.9,3.25);
+\path[color=hred,>=stealth,->,shorten >=0.15cm,shorten  <=0.15cm,out=-30,in=-150,line width=1pt] (0.9,3.25) edge (3.4,3.25);
 
 \end{scope}
-
-% r-lead
-% (position of lead has to be set manually)
-\begin{axis}[%
-xmin=0,xmax=3.5,
-ymin=-5,ymax=5,
-xtick=\empty,
-ytick=\empty,
-axis line style={draw=none},
-scale=1,
-at={(2.5cm,-10.85cm)}]
-
-\addplot[solid,domain=-5:2,hred,name path=spectrum,samples=200] ({1.*1.0^2/(x^2+1.0^2)},{x});
-\addplot[solid,domain=-5:2,hred,name path=occupation,samples=200] ({1.*1.0^2/(x^2+1.0^2)*1./(exp((x+2.2)/0.06)+1.)},{x});
-\path[name path=yaxis] (axis cs:0,-5) -- (axis cs:0,2);
-
-\addplot[fill=hred!20!white,domain=-5:2] fill between [of=spectrum and yaxis,soft clip={domain=-5:5}];
-\addplot[fill=hred!60!white,domain=-5:2] fill between [of=occupation and yaxis,soft clip={domain=-5:5}];
-
-% \draw[line width=1pt] (axis cs:0,-2.2) -- node[midway,below] {$\mu_{\text{r}}$} (1,-2.2);
-\end{axis}
-
-% l-lead
-% (position of lead has to be set manually)
-\begin{axis}[%
-ymin=-5,ymax=5,
-xmin=0,xmax=3.5,
-xtick=\empty,
-ytick=\empty,
-axis line style={draw=none},
-scale=1,
-clip mode=individual,
-at={(-2.5cm,-13.85cm)}]
-
-\addplot[solid,domain=-2:5,hred,name path=spectrum,samples=200] ({1.*1.0^2/(x^2+1.0^2)},{x});
-\addplot[solid,domain=-2:5,hred,name path=occupation,samples=200] ({1.*1.0^2/(x^2+1.0^2)*1./(exp((x-2.2)/0.06)+1.)},{x});
-\path[name path=yaxis] (axis cs:0,-2) -- (axis cs:0,5);
-
-\addplot[fill=hred!20!white] fill between [of=spectrum and yaxis,soft clip={domain=-2:5}];
-\addplot[fill=hred!60!white] fill between [of=occupation and yaxis,soft clip={domain=-2:5}];
-
-% \draw[line width=1pt] (axis cs:0,2.2) -- node[midway,above] {$\mu_{\text{l}}$} (1,2.2);
-\end{axis}
 

### 2022-08-23 figures_Paper1/setup_association.tex
Final version paper 23.08.2022

--- 2022-07-21 figures_Paper1/setup.tex
@@
 \pgfplotsinvokeforeach{0,1,...,3} {
-   \draw[color=horange] (axis cs:0,#1,0) -- (axis cs:1,#1,0);
-   \draw[color=horange] (axis cs:0,#1,1) -- (axis cs:1,#1,1);
-   \draw[color=horange] (axis cs:0,#1,2) -- (axis cs:1,#1,2);
-   \draw[color=horange] (axis cs:0,#1,3) -- (axis cs:1,#1,3);
+   \draw[color=hblue] (axis cs:0,#1,0) -- (axis cs:1,#1,0);
+   \draw[color=hblue] (axis cs:0,#1,1) -- (axis cs:1,#1,1);
+   \draw[color=hblue] (axis cs:0,#1,2) -- (axis cs:1,#1,2);
+   \draw[color=hblue] (axis cs:0,#1,3) -- (axis cs:1,#1,3);
 };
@@
 \pgfplotsinvokeforeach{0,1,...,3} {
-   \draw[color=horange] (axis cs:3,#1,0) -- (axis cs:4,#1,0);
-   \draw[color=horange] (axis cs:3,#1,1) -- (axis cs:4,#1,1);
-   \draw[color=horange] (axis cs:3,#1,2) -- (axis cs:4,#1,2);
-   \draw[color=horange] (axis cs:3,#1,3) -- (axis cs:4,#1,3);
+   \draw[color=hblue] (axis cs:3,#1,0) -- (axis cs:4,#1,0);
+   \draw[color=hblue] (axis cs:3,#1,1) -- (axis cs:4,#1,1);
+   \draw[color=hblue] (axis cs:3,#1,2) -- (axis cs:4,#1,2);
+   \draw[color=hblue] (axis cs:3,#1,3) -- (axis cs:4,#1,3);
 };
@@
 % coordinates for light
-
 \coordinate (top1) at (axis cs:2,0.5,3);
@@
 % arrows for hoppings 
-
-\node at (axis cs:-0.1,3.5,-0.15) {\textcolor{hblue}{$\mu_r$}};
-\node at (axis cs:5,3.5,-0.15) {\textcolor{hblue}{$\mu_l$}};
+\node at (axis cs:-0.1,3.5,-0.15) {\textcolor{hblue}{$\mu_{\text{r}}$}};
+\node at (axis cs:5,3.5,-0.15) {\textcolor{hblue}{$\mu_{\text{l}}$}};
 \node at (axis cs:2,2.8,-0.35) {\textcolor{hgreen}{$U,g$}};
-\node at (axis cs:3.5,3,-0.25) {\textcolor{horange}{$\Gamma$}};
+\node at (axis cs:3,3,-0.25) {\textcolor{hred}{$\Gamma$}};
 \node at (axis cs:1.3,3,-0.25) {\textcolor{black}{$v$}};
@@
 % cw-light
-
 \draw [->,>=Stealth,line width=2pt,decorate,decoration={snake,amplitude=0.2cm,segment length=0.4cm,pre length=0.4cm,post length=0.4cm},draw=hyellow] ($ (top1)+(120:2) $) -- (top1);

### 2022-08-23 Paper1.tex
Final version paper 23.08.2022

@@
 \end{equation}
-
 known as the \emph{Keldysh-Floquet} GF.
@@
 The underline indicates the overall \emph{Keldysh} structure
-
+%
 \begin{equation}\label{eq:Keld-structure}
@@
 \end{equation}
-
+%
 which contains the \emph{retarded}, \emph{advanced} and \emph{Keldysh} components $\textbf{G}^{\text{R,A,K}}$, where $\textbf{G}^{\text{A}}=(\textbf{G}^{\text{R}})^{\dagger}$.
@@
 \end{equation}
-
 with $v_{\text{l}/\text{r}}$ as lead-layer hybridization, $\omega_n \equiv \omega + n\Omega$, $n\in\mathbbm{Z}$, and 
-
+%
 \begin{equation}\label{eq:inv_non-int_lat_GF_comps}
@@
 \end{equation}
-
+%
 as the noninteracting Green's function of the isolated layer, whose inverse Keldysh component is negligible in the steady state.
 The Floquet dispersion relation $\varepsilon_{mn}$ for the periodic field in a hyper-cubic lattice is~\cite{ts.ok.08}
-
+%
 \begin{equation}
@@
 Fig.~\ref{fig:setup}) is given by
-
+%  
 \begin{align}
@@
 \end{align} 
-
+%
 where $\varepsilon_{\text{l}/\text{r}}(\epsilon)=\varepsilon_{\text{l}/\text{r}} +\frac{t_{\text{l}/\text{r}}}{t^\ast}\epsilon$ is the dispersion, $f(\omega,\mu_{\text{l}/\text{r}},\beta)=1/[\ee^{\beta(\omega-\mu_{\text{l}/\text{r}})}+1]$ the Fermi-Dirac distribution function at inverse temperature $\beta \equiv 1/T$, $\varepsilon_{\text{l}/\text{r}}$ the onsite energy and $t_{\text{l}/\text{r}}$ the hopping within the $d$-dimensional layer of the lead.
@@
 The Keldysh components of the non-interacting phonon GF $\kel{D}_{\text{ph}}(t,t^{\prime})$ are given by~\cite{ao.ts.14}
+%
 \begin{align}\label{eq:Ph_Prop_time}
@@
 \end{align}
+%
 where $b(\omega)=1/(\ee^{\beta\omega}-1)$ is the Bose-Einstein distribution function at inverse temperature $\beta$.
@@
 (i) We start from an initial guess for the electron SE $\kel{\mat{\Sigma}}(\omega)$ and set $\kel{\mat \Sigma}_{\text{e-ph}}(\omega)=0$. (ii) Then we compute the local electron GF as 
-
+%  
 \begin{equation}\label{eq:Lat_LocGF}
@@
 \end{equation}
-
+% 
 (iii) Using Eq.~\eqref{eq:backbone_e-ph_SE}, we obtain the phonon contribution to the SE $\kel{\mat{\Sigma}}_{\text{e-ph}}(\omega)$.
@@
 is given by
-
+%
 \begin{equation}\label{eq:imp_Dyson_eq}
@@
 \end{equation}   
-
+%  
 where $\kel{\mat{g}}^{-1}_{0,\text{site}}(\omega)$ is defined as in Eq.~\eqref{eq:inv_non-int_lat_GF_comps} with $\varepsilon_{mn}(\epsilon,\overline{\epsilon})=0$.
@@
  $\Delta_{\text{pg}} \approx 4$.
-All simulations are carried out with the dimensionless factor $\alpha\equiv t_{r}E_0/\Omega^{2}<0.5$ for which the FDSA is justified~\cite{so.do.18}\footnote{In Ref.~\cite{so.do.18} the factor is defined as $\alpha=t_{c}E_0/\Omega^{2}$ and $t_{\text{c}}=1$.
+All simulations are carried out with the dimensionless factor $\alpha\equiv t_{r}E_0/\Omega^{2}<0.5$ for which the FDSA is justified~\footnote{In Ref.~\cite{so.do.18} the factor is defined as $\alpha=t_{c}E_0/\Omega^{2}$ and $t_{\text{c}}=1$.
 Setting $t_{r}=1$, we define for consistency $\alpha$ as in the main text.} and first-order photon absorption processes are dominant.
@@
 
+\begin{figure}[b] 
+% \captionsetup{width=\textwidth}   
+\includegraphics[width=\linewidth]{./figures_Paper1/spec_filling_mu1_v_0.4_0.8_O_5_11_e.pdf}
+\caption{(Color online) Spectral function $A(\omega)$ (solid line) and occupation function $N(\omega)$ (shaded area) at (a) $\Omega=5$ and (b) $\Omega=11$ for $v=0.4$ and $0.8$ for the EO system.
+Default parameters are specified at the beginning of Sec.~\ref{sec:results}.}
+\label{fig:spec_filling_mu1_v_0.4_0.8_O_5_11_e}
+\end{figure}
+
 For $\Omega\gtrsim8$, the current increases further until it reaches its peak at $\Omega\approx 11$.
@@
 For $\Omega=5$ in the DE range, the occupation function in the UHB is almost the same for both $v$, while for $\Omega=11$ where the peak in the current occurs, the occupation of the UHB for $v=0.4$ is substantially larger,  in line with the behavior of $N_{\text{D}}$.
-
-\begin{figure}[b] 
-% \captionsetup{width=\textwidth}   
-\includegraphics[width=\linewidth]{./figures_Paper1/spec_filling_mu1_v_0.4_0.8_O_5_11_e.pdf}
-\caption{(Color online) Spectral function $A(\omega)$ (solid line) and occupation function $N(\omega)$ (shaded area) at (a) $\Omega=5$ and (b) $\Omega=11$ for $v=0.4$ and $0.8$ for the EO system.
-Default parameters are specified at the beginning of Sec.~\ref{sec:results}.}
-\label{fig:spec_filling_mu1_v_0.4_0.8_O_5_11_e}
-\end{figure}
 
@@
 
-\begin{figure}[b] 
+\begin{figure}[t] 
 % \captionsetup{width=\textwidth} 
@@
 
-Experimentally, the electric field amplitude considered in this paper is several orders of magnitude bigger than the sunlight one, however it is possible to achieve such amplitudes via THz pulses ~\cite{mu.we.18} ~\footnote{We do not consider smaller electric field amplitudes $E_0$ since DMFT only converges slowly for such a choice of parameters.
-Moreover, the observables' magnitude becomes comparable to our numerical precision.}.
+Experimentally, the electric field amplitude considered in this paper~\footnote{We do not consider smaller electric field amplitudes $E_0$ since DMFT only converges slowly for such a choice of parameters.
+Moreover, the observables' magnitude becomes comparable to our numerical precision.} is several orders of magnitude larger than that of the sunlight, however it is possible to achieve such amplitudes via THz pulses ~\cite{mu.we.18}.
 Moreover, in order to address the occurrence of II in realistic photovoltaic setups, one should extend such simplified model to multiorbital systems \cite{pe.be.19} in a multilayer setup, to model oxide heterostructures~\cite{as.bl.13,pe.be.19} where the correlated region consists of multiple layers and photoexcited carriers are separated via an electric field gradient.

### 2022-08-24 Paper1.tex
changes Enrico 24.08.2022

@@
 For larger hybridizations the shallow peak suggests a suppression of impact ionization with respect to direct photovoltaic excitations.
-Acoustic phonons slightly enhance the photocurrent for small driving frequencies and suppress it at frequencies around the main peak.
-This effect occurs at all considered hybridization strengths.
+Acoustic phonons slightly enhance the photocurrent for small driving frequencies and suppress it at frequencies around the main peak
+% This effect occurs at all considered hybridization strengths.
+ at all considered hybridization strengths.
 
@@
 For this goal we consider the simplified model shown in Fig.~\ref{fig:setup}, consisting of a Hubbard layer located between two leads.
-The metallic leads have themselves a wide band, which is effectively narrowed due to the weak coupling to intermediate layers which we take as models for the contacts.
+The leads have themselves a wide band, as expected for good condutors, which are effectively narrowed due to the weak coupling to intermediate layers which we take as simplified models for the contacts.
 Electrons on the Hubbard layer interact locally with acoustic phonons.
@@
 Our analysis can only provide qualitative results, while quantitative comparisons with experimental systems require a more realistic setup and are beyond the scope of this work.
-
-We find that a small hybridization to the leads is more favorable for II than a larger one.
+Our calculations show that a small hybridization to the leads is more favorable for II than a larger one.
 II therefore plays a crucial role in compensating the smaller charge injection, giving the same order of magnitude in the photocurrent as for the larger hybridization.
@@
 
-The local e-ph coupling is included as in Ref.~\cite{ma.ga.22u} with an acoustic phonon branch attached to each lattice site via the Hamiltonian 
+Phonons are 
+%The local e-ph coupling is
+ included as in 
+%EACOMM check, put also previous references
+Ref.~\cite{ma.ga.22u} in the form of  acoustic  branches attached to each lattice site and coupled to the electrons via the Hamiltonian 
 \begin{equation}\label{eq:e-ph_ham} 
@@
 \end{equation}
-with $g$ as e-ph coupling and $\hat{x}_{i} \equiv \frac{1}{\sqrt{2}} \left( \hat{b}^{\dagger}_{i} + \hat{b}_i \right)$, where $\hat{b}^{\dagger}_{i}$ ($\hat{b}_{i}$) creates (annihilates) a phonon of the acoustic branch at site $i$, with dispersion relation described by $\hat{H}_{\text{ph}}$~\cite{ma.ga.22u}.
+with $g$ as e-ph coupling and $\hat{x}_{i} \equiv \frac{1}{\sqrt{2}} \left( \hat{b}^{\dagger}_{i} + \hat{b}_i \right)$, where $\hat{b}^{\dagger}_{i}$ ($\hat{b}_{i}$) creates (annihilates) a phonon of the acoustic branch at site $i$, with dispersion relation described by $\hat{H}_{\text{ph}}$~\cite{ma.ga.22u}, see below.
+In contrast to Holstein phonons these have a finite bandwidth which is more effective in energy dissipation.
 Details on the leads are provided in~\ref{sec:Dyson_equation}.
@@
 For mathematical simplicity~\cite{ge.ko.92,ao.ts.14}, 
- we consider the correlated central region as a $d$-dimensional layer and consider the limit of infinite dimensions $d \rightarrow \infty$ by rescaling the hopping as $t_{\text{c}}=t^{\ast}/2\sqrt{d}$.
+ we consider the correlated central region as a $d$-dimensional layer and consider the limit of infinite dimensions $d \rightarrow \infty$ by rescaling the hopping as 
+%EACOMM check parenthesis
+$t_{\text{c}}=t^{\ast}/(2\sqrt{d})$.
 Taking $a=1$, sums over the crystal momentum ${\bf k}$ of a generic quantity $\chi$ read $\sum_{{\bf k}} \chi(\omega,{\bf k}) \rightarrow \int d\epsilon \int   d\overline{\epsilon} \ \rho(\epsilon,\overline{\epsilon}) \chi(\omega;\epsilon,\overline{\epsilon})$ with $\rho(\epsilon,\overline{\epsilon}) = (1/\pi t^{\ast 2}) \exp[-( \epsilon^{2} + \overline{\epsilon}^{2})/t^{\ast 2}]$ as the joint density of states~\cite{ts.ok.08} and with
@@
 
-Within the remainder of this paper we set $\hbar = k_{\text{B}} = a = 1 = -q$, $t^{\ast}=2\sqrt{2}$ ~\footnote{With such choice for $t^{\ast}$ we reproduce the DOS of a 2D layer with $t_{\text{c}}=1$  in order to compare with Ref.~\cite{so.do.18}.} and $t_r \equiv \frac{t^{\ast}}{2\sqrt{2}}=1$ as unit of energy.
+Within the remainder of this paper we choose our units so that  $\hbar = k_{\text{B}} = a = 1 = -q$, $t^{\ast}=2\sqrt{2}$ ~\footnote{With such choice for $t^{\ast}$ we reproduce the DOS of a 2D layer with $t_{\text{c}}=1$  in order to compare with Ref.~\cite{so.do.18}.}, and $t_r \equiv \frac{t^{\ast}}{2\sqrt{2}}=1$ as unit of energy.
 
@@
 
-To correctly describe the nonequilibrium periodic steady state, we use the Floquet generalization of the nonequilibrium Green's function (NEGF) approach~\cite{ts.ok.08}.
+To correctly describe the nonequilibrium periodic steady state, we use the Floquet generalization of the nonequilibrium Green's function (NEGF) 
+approach~\cite{ts.ok.08,sc.mo.02u,jo.fr.08}.
 Every function $G(t,t^{\prime})$ satisfying the periodicity relation $G(t,t^{\prime})=G(t+\tau,t^{\prime}+\tau)$, with $\tau=2\pi/\Omega$ as the period related to the external driving frequency $\Omega$, may be represented as~\cite{ts.ok.08,sc.mo.02u,jo.fr.08}
@@
 The lattice Floquet GF of our setup obeys the Dyson equation 
-
 \begin{equation}\label{eq:FullDysonEq}
-\underline{{\bf G}}^{-1}(\omega_n;\epsilon,\overline{\epsilon}) = \underline{{\bf G}}^{-1}_{0}(\omega_n;\epsilon,\overline{\epsilon}) - \underline{{\bf \Sigma}}(\omega_n;\epsilon,\overline{\epsilon}) - \underline{{\bf \Sigma}}_{\text{e-ph}}(\omega_n;\epsilon,\overline{\epsilon}).
+\underline{{\bf G}}^{-1}(\omega_n;\epsilon,\overline{\epsilon}) = \underline{{\bf G}}^{-1}_{0}(\omega_n;\epsilon,\overline{\epsilon}) - \underline{{\bf \Sigma}}(\omega_n;\epsilon,\overline{\epsilon}) - \underline{{\bf \Sigma}}_{\text{e-ph}}(\omega_n;\epsilon,\overline{\epsilon}) \;,
 \end{equation}
+where in our approximation the electron-electron $ \underline{{\bf \Sigma}}(\omega_n;\epsilon,\overline{\epsilon})$ and electron-phonon $\underline{{\bf \Sigma}}_{\text{e-ph}}(\omega_n;\epsilon,\overline{\epsilon})$ self energies contribute independently to the total self energy~\footnote{In fact there is an indirect feedback via the DMFT self-consistency.}
 
@@
 
-The electron self-energy (SE) $\underline{\bf{\Sigma}}$ is obtained from F-DMFT and therefore independent of the crystal momentum, i.e.
+The electron self-energy (SE) $\underline{\bf{\Sigma}}$ is obtained from F-DMFT and therefore, in this approximation, independent of the crystal momentum, i.e.
 $\underline{\bf{\Sigma}}(\omega;\epsilon,\overline{\epsilon}) \simeq \underline{\bf{\Sigma}}(\omega)$.
 Further details are given in Sec.~\ref{sec:FDMFT_implementation}.
-
-The e-ph SE is also included locally as $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega;\epsilon,\overline{\epsilon}) \simeq \underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$.
+In the same spirit, the e-ph SE is included locally as $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega;\epsilon,\overline{\epsilon}) \simeq \underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$.
 In terms of the Keldysh contour time arguments $z$ and $z^\prime$, it has the form
@@
 where $b(\omega)=1/(\ee^{\beta\omega}-1)$ is the Bose-Einstein distribution function at inverse temperature $\beta$.
-We focus on acoustic phonons, with spectral function $A_{\text{ph}}(\omega) = (\omega/\omega^{2}_{\text{ph}}) \ee^{-| \omega|/\omega_{\text{ph}}}$,  $\omega_{\text{ph}}$ being a soft cutoff frequency~\cite{pi.li.21}.
+We consider acoustic phonons, with spectral function $A_{\text{ph}}(\omega) = (\omega/\omega^{2}_{\text{ph}}) \ee^{-| \omega|/\omega_{\text{ph}}}$,  $\omega_{\text{ph}}$ being a soft cutoff frequency~\cite{pi.li.21}.
 The retarded and Keldysh components of the e-ph SE are easily extracted from  Eq.~\eqref{eq:backbone_e-ph_SE} and can be found in Ref.~\cite{ma.ga.22u}.
@@
 
-We briefly describe now the self-consistent F-DMFT scheme used.
+For completeness, we now
+ briefly describe now the self-consistent F-DMFT scheme used.
 (i) We start from an initial guess for the electron SE $\kel{\mat{\Sigma}}(\omega)$ and set $\kel{\mat \Sigma}_{\text{e-ph}}(\omega)=0$. (ii) Then we compute the local electron GF as 
@@
 
-\subsubsection{Floquet-diagonal self-energy approximation}
-\label{sec:FDSA}
+%EACOMM I eliminated this and the next subsubsection, is this okay?  
+%\subsubsection{Floquet-diagonal self-energy approximation}
+%\label{sec:FDSA}
 
-From Eq.~\eqref{eq:imp_Dyson_eq}, we obtain the bath hybridization function $\kel{\mat\Delta}(\omega)$ whose periodic time-dependence is encoded in its Floquet structure.
-Being interested in photovoltaic effects, we follow Ref.~\cite{so.do.18} and use the Floquet-diagonal self-energy approximation (FDSA) for which Floquet off-diagonal terms in the electron SE $\kel{\mat{\Sigma}}(\omega)$ are neglected.
-In addition, we employ FDSA also for the phonon SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ \footnote{In the parameters range in which FDSA is justified for the electron SE $\kel{\mat{\Sigma}}(\omega)$ (Sec.~\ref{sec:results}), the diagonal terms of the phonon SE $\underline{\Sigma}_{mm,\text{e-ph}}(\omega)$ are orders of magnitude bigger than the off-diagonal ones}.
-Consequently, we only consider the
- $(0,0)$-Floquet matrix element of Eq.~\eqref{eq:imp_Dyson_eq} in the impurity problem, which therefore becomes stationary.
-It is sufficient to restrict oneself to the $(0,0)$ component, since the other diagonal components can be reconstructed by using the property $\kel{\Sigma}_{mm}(\omega) = \kel{\Sigma}_{00}(\omega+m\Omega)$.
+%EACOMM check this paragraph, which I changed a bit
+Eq.~\eqref{eq:imp_Dyson_eq} gives the bath hybridization function $\kel{\mat\Delta}(\omega)$ whose periodic time-dependence is encoded in its Floquet structure. 
+This means that, in principle, one would have to solve a time-periodic impurity problem leading to a non-diagonal self-energy in general. However, in 
+ Ref.~\cite{so.do.18} it was argued that for the electric field strengths considered, non-diagonal terms in the Floquet SE $\kel{\mat{\Sigma}}(\omega)$  can be safely neglected with respect to the diagonal ones.
+We follow this argument and adopt here
+this Floquet-diagonal self-energy approximation (FDSA) as well.
+ In addition, it turns out that also for the 
+ phonon SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ this approximation is justified\footnote{More specifically, we have verified that in the parameters range in which FDSA is justified for the electron SE $\kel{\mat{\Sigma}}(\omega)$ (Sec.~\ref{sec:results}), the off-diagonal terms of the phonon SE $\underline{\Sigma}_{mm,\text{e-ph}}(\omega)$ are orders of magnitude smaller than the diagonal ones}.
+Consequently, we  have to solve a nonequilibrium stationary impurity problem, by using only the  $(0,0)$-Floquet matrix elements of $\kel{\mat{\Sigma}}(\omega)$ and $\kel{\mat\Delta}(\omega)$, 
+%Eq.~\eqref{eq:imp_Dyson_eq}, 
+as the other diagonal components can be reconstructed by using the property $\kel{\Sigma}_{mm}(\omega) = \kel{\Sigma}_{00}(\omega+m\Omega)$.
 
-\subsubsection{Auxiliary master equation approach}
-\label{sec:amea}
+%\subsubsection{Auxiliary master equation approach}
+%\label{sec:amea}
 
-In the following, we briefly summarize the impurity solver used in step (v) of the DMFT self-consistent loop described in Sec.~\ref{sec:FDMFT_implementation}. In order to solve the many-body problem,
- we use the auxiliary master equation approach (AMEA)~\cite{ar.kn.13,do.nu.14,do.ga.15,do.so.17}.
+%We now
+% briefly summarize the impurity solver used in step (v) of the DMFT self-consistent loop %described in Sec.~\ref{sec:FDMFT_implementation}. 
+In order to solve the electron-electron many-body problem (step (v) of the DMFT self-consistent loop),
+ we use the auxiliary master equation approach (AMEA)~\cite{ar.kn.13,do.nu.14,do.ga.15,do.so.17}, which we now briefly summarize. 
 Therein, we map the impurity problem onto an auxiliary open quantum system (AOQS) consisting of a finite number of bath sites $N_{\text{B}}$ attached to Markovian reservoirs described by the Lindblad equation.
@@
 
-The photocurrent flowing from the left fermion lead to the right one, passing through the correlated layer is given by 
+The photocurrent flowing from the left fermion lead to the right one, passing through the correlated layer is given by two equivalent expressions, adapted from Ref.~\cite{so.do.18}
 % 
@@
 \begin{equation}
-  \boldsymbol{J}=\left[\boldsymbol{G}^{\text{R}}(\boldsymbol{g}_{\text{b},\text{l}}^{\text{K}}-\boldsymbol{g}_{\text{b},\text{r}}^{\text{K}})+\boldsymbol{G}^{\text{K}}(\boldsymbol{g}_{\text{b},\text{l}}^{\text{A}}-\boldsymbol{g}_{\text{b},\text{r}}^{\text{A}})\right]
+  \boldsymbol{J}=\left[\boldsymbol{G}^{\text{R}}(\boldsymbol{g}_{\text{b},\text{l}}^{\text{K}}-\boldsymbol{g}_{\text{b},\text{r}}^{\text{K}})+\boldsymbol{G}^{\text{K}}(\boldsymbol{g}_{\text{b},\text{l}}^{\text{A}}-\boldsymbol{g}_{\text{b},\text{r}}^{\text{A}})\right].
 \end{equation}
 % 
-is taken from Ref.~\cite{so.do.18}. Of the two equivalent expressions, Eq.~\eqref{eq: Current furmula_00} is used in practice.
+In our case, it is convenient to use 
+Eq.~\eqref{eq: Current furmula_00}.
 
@@
 \begin{equation}
-N(\omega) = \frac{1}{4\pi} [\iim(G^{\text{K}}_{\text{loc},00})-2\iim(G^{\text{R}}_{\text{loc},00})].
+N(\omega) = \frac{1}{4\pi} [\iim(G^{\text{K}}_{\text{loc},00}(\omega))-2\iim(G^{\text{R}}_{\text{loc},00}(\omega))].
 \end{equation}
@@
 
-In order to study II in a Mott insulating layer, we set the bands to achieve the energy scheme shown in Fig.~\ref{fig:energy_setup}(a).
-
- We follow Ref.~\cite{so.do.18} and choose $U=12$ and $E_0=2$.
+In order to study II in a Mott insulating layer, we adjust the bands to achieve the energy scheme shown in Fig.~\ref{fig:energy_setup}(a). 
+ We follow Ref.~\cite{so.do.18} and take $U=12$ and unless stated otherwise $E_0=2$.
 The fermion leads and acoustic phonons have temperature $T=0.02$.
 We consider a particle-hole symmetric system with $\Gamma_{\text{l}}=\Gamma_{\text{r}}=0.37$, $t_{\text{l}}=t_{\text{r}}=1.7$, $\varepsilon_{\text{l}/\text{r}}=\mp 6$ and $v_{\text{l}}=v_{\text{r}}=v$.
-The parameters $t_{\text{l/r}}$, $\varepsilon_{\text{l/r}}$, and  $\Gamma_{\text{l/r}}$ are chosen such that the leads' DOS approximately coincides with the Hubbard bands, i.e.
+The parameters $t_{\text{l/r}}$, $\varepsilon_{\text{l/r}}$, and  $\Gamma_{\text{l/r}}$ are chosen such that the leads' DOS approximately overlaps with the Hubbard bands, i.e.
 they exhibit a \textquoteleft bandwidth\textquoteright~\footnote{Notice that the support of its spectrum is formally infinite.
@@
 All simulations are carried out with the dimensionless factor $\alpha\equiv t_{r}E_0/\Omega^{2}<0.5$ for which the FDSA is justified~\footnote{In Ref.~\cite{so.do.18} the factor is defined as $\alpha=t_{c}E_0/\Omega^{2}$ and $t_{\text{c}}=1$.
-Setting $t_{r}=1$, we define for consistency $\alpha$ as in the main text.} and first-order photon absorption processes are dominant.
-Whenever the electron-phonon interaction is switched on, we take $g=0.8$ and unless stated otherwise $\omega_{\text{ph}}=0.1$.
+Setting $t_{r}=1$, we define for consistency $\alpha$ as in the main text.}.
+% and first-order photon absorption processes are dominant.
+ Whenever the electron-phonon interaction is included, we take $g=0.8$ and unless stated otherwise $\omega_{\text{ph}}=0.1$.
 
@@
 Green bands are the LHB and UHB of the central layer.
+Due to the hybridization with the metallic leads only a pseudogap $\Delta_{\text{pg}}$ is present between the bands.
  The vertical axis represents the energy.
@@
 
-\subsection{Energy considerations and physical processes}
+\subsection{Qualitative Energy considerations and physical processes}
 \label{sec:explicative_scheme}
@@
 Thereby, we partially follow Ref.~\cite{so.do.18} for the electron-only (EO) case and extend the analysis to the case with e-ph interaction.
-Here, we also consider a more realistic structure of the leads.
+In comparison with Ref.~\cite{so.do.18} here the wide-band leads more realistically described a metallic structure. This makes the identification of II processes more subtle, as discussed below.
 As in Ref.~\cite{so.do.18} we bypass transient behavior and consider directly the nonequilibrium Floquet steady state.
-In our analysis, we neglect higher-order processes such as multiparticle scattering II processes.
+In our analysis, we neglect higher-order processes such as multiparticle scattering processes.
 
-In order to observe II, the bandwidth of the UHB has to be at least twice the pseudogap size $\Delta_{\text{pg}}$.
-Only in this case, the photoexcited electron can acquire enough energy to excite a second one across the pseudogap.
+In order to observe II, the bandwidth of the UHB has to be at least twice the pseudogap~\footnote{Due to the hybridization with the metallic leads 
+only a pseudogap $\Delta_{\text{pg}}$ is present between the LHB and the UHB.} 
+size $\Delta_{\text{pg}}$. Only in this case, the photoexcited electron can acquire enough energy to excite a second one across the pseudogap.
 
@@
 \begin{itemize}
-\item For $\Omega<\Delta_{\text{pg}}$, we do not expect any current if the DOS of the correlated layer has a true gap~\footnote{To overcome a true gap with $\Omega<\Delta_{\text{pg}}$ multiple-photon absorption processes should take place, but as written in the main text, such effects are negligible in the studied parameters range.}.
-If $\Delta_{\text{pg}}$ is a partial gap, we expect a suppression of the current.
+\item For $\Omega<\Delta_{\text{pg}}$, 
+we expect a strong suppression of the current
+we do not expect any current if the DOS of the correlated layer has a true gap~\footnote{The remaining leak current can be either produced by multiple-photon absorption processes, which however, are strongly suppressed, or by the fact that there is no true gap}.
+%To overcome a true gap with $\Omega<\Delta_{\text{pg}}$  should take place, but as written in the main text, such effects are negligible in the studied parameters range.}.
+
+%~\footnote{To overcome a true gap with $\Omega<\Delta_{\text{pg}}$ multiple-photon absorption processes should take place, but as written in the main text, such effects are negligible in the studied parameters range.}.
+%If $\Delta_{\text{pg}}$ is a partial gap, we expect a suppression of the current.
 \item For $\Delta_{\text{pg}}<\Omega<\Delta_{\text{pg}}+2W_{\text{b}}$ as shown in Fig.~\ref{fig:energy_setup}(b), an electron coming from the left lead into the LHB is photoexcited to the UHB and can escape directly into the right lead without additional scattering.
-We will refer to such processes as direct excitations (DEs).
+Such processes are often referred to as direct excitations (DEs).
 \item For $2\Delta_{\text{pg}}<\Omega<\Delta_{\text{pg}}+2W_{\text{b}}$ as shown in Fig.~\ref{fig:energy_setup}(c), a photoexcited electron in the UHB can excite via II a second electron from LHB to UHB, before both escape into the right lead.
@@
 Notice that in the energy window $\Delta_{\text{pg}}<\Omega<2\Delta_{\text{pg}}$ the only scattering processes taking place are DEs, while for $2\Delta_{\text{pg}}<\Omega<\Delta_{\text{pg}}+2W_{\text{b}}$, both DE and II can occur.
-We want to stress however, that the boundaries of these energy ranges are not strict and that it is difficult to disentangle the effects of these physical processes.
+This is in contrast to the case of Ref.~\cite{so.do.18} in which the peculiar ad-hoc narrow lead bands only allowed for II current in a certain $\Omega$ regime.
+For this reason, and due to the fact that
+%We want to stress, that 
+the boundaries of these energy ranges are not strict, it is more tricky to disentangle  these physical processes in the present case.
 
@@
 
-Upon inclusion of e-ph scattering, the outlined scheme remains valid except for a modification of the pseudogap $\Delta_{\text{pg}}$.
-As shown in Sec.~\ref{sec:E0_2_electrons_phonons}, the phonons broaden the DOS of the correlated layer and slightly fill the pseudogap.
-Therefore the pseudogap is reduced by a small amount indicating the dissipation by phonons.
+Upon inclusion of e-ph scattering, the outlined scheme remains valid except for the fact that  the pseudogap $\Delta_{\text{pg}}$ is slightly modified.
+As shown in Sec.~\ref{sec:E0_2_electrons_phonons}, the phonons broaden the DOS of the correlated layer and slightly fill and shrink the pseudogap.
+%Therefore the pseudogap is reduced by a small amount indicating the dissipation by phonons.
 
@@
 
-\subsection{EO system}
+\subsection{Quantitative results}
+
+\subsubsection{EO system}
 \label{sec:E0_2_only_electrons}
 
-We start with the EO case without e-ph interaction and investigate the dependence of the physical quantities on the lead-layer hybridization.
+We start with the case without e-ph interaction and address the behavior 
+%investigate the dependence 
+of  physical quantities as a function of $\Omega$ for different strengths of the lead-layer hybridization.
 
@@
 
+\begin{figure}[b]  
+% \captionsetup{width=\textwidth} 
+\includegraphics[width=\linewidth]{./figures_Paper1/j_vs_omega_mu1_v_0.8_e_E0_3_4.pdf} 
+\caption{(Color online) (a) Time-averaged steady-state current $j$ and (b) double occupancy $N_{\text{D}}$ as a function of $\Omega$, at $v=0.8$ for $E_0=3,4$ for the EO system.
+Default parameters are specified at the beginning of Sec.~\ref{sec:results}.}
+\label{fig:j_vs_omega_mu1_v_0.8_e_E0_3_4}
+\end{figure}
+
+\begin{figure}[b]  
+% \captionsetup{width=\textwidth} 
+\includegraphics[width=\linewidth]{./figures_Paper1/j_vs_omega_mu1_v_0.4_0.8_e_E0_3_4.pdf}
+\caption{(Color online) (a) Time-averaged steady-state current $j$ and (b) double occupancy $N_{\text{D}}$ as a function of $\Omega$, for $v=0.4,0.8$ at electric field amplitudes $E_0=3,4$ for the EO system.
+Default parameters are specified at the beginning of Sec.~\ref{sec:results}.}
+\label{fig:j_vs_omega_mu1_v_0.4_0.8_e_E0_3_4} 
+\end{figure}
+
 For $\Omega\gtrsim8$, the current increases further until it reaches its peak at $\Omega\approx 11$.
-In this range both DE and II can occur.
+In this range both DE and II can occur in principle.
 The height of the peak is approximately the same for both $v$, despite the lead-layer hybridizations differing by a factor of two.
 The double occupation in this range shows a similar behavior as the current for $v=0.4$ with a peak around $\Omega\approx 11$, while it exhibits a plateau for $v=0.8$.
-For $v=0.4$ the current curve is characterized by a substantial change in slope around $\Omega \approx 8$, which is absent for $v=0.8$.
- This, together with the comparable magnitude of the maxima at $\Omega\approx 11$ and the behavior of the double occupation strongly suggest that for $v=0.4$ a substantial number of II processes take place, while these are absent or negligible for $v=0.8$.
+For $v=0.4$ the current curve is characterized by a substantial increase in slope around 
+%EACOMM i put 7, this is where it actually occur
+$\Omega \approx 7$, which cannot be observed for $v=0.8$.
+ This, together with the comparable magnitude of the maxima at $\Omega\approx 11$ and the behavior of the double occupation strongly suggest that for $v=0.4$ a substantial rate of II processes take place, while these are absent or negligible for $v=0.8$.
 Here,  the plateau in $N_{\text{D}}$ for $v=0.8$ suggests that photoexcited electrons arriving in the UHB quickly escape to the right fermionic lead and do not have time to induce II processes.
@@
 For $\Omega=5$ in the DE range, the occupation function in the UHB is almost the same for both $v$, while for $\Omega=11$ where the peak in the current occurs, the occupation of the UHB for $v=0.4$ is substantially larger,  in line with the behavior of $N_{\text{D}}$.
+Increasing $\Omega$ further produces excitations near the border of the UHB where the DOS is reduced, and, thus  current and double occupation decrease~\footnote{The current $j$ does not approach zero as expected for $\Omega>20$ because of the background current as discussed in Ref.~\cite{so.do.18}.}.
 
-Finally, increasing $\Omega$ further, decreases the current and double occupation~\footnote{The current $j$ does not approach zero as expected for $\Omega>20$ because of the background current as discussed in Ref.~\cite{so.do.18}.}.
+NEW PART: If the electric field amplitude $E_0$ is increased, as shown in Fig.~\ref{fig:j_vs_omega_mu1_v_0.8_e_E0_3_4}(a), the current curve develops an increase in slope around $\Omega\approx7$ and the double occupation (cf.
+Fig.~\ref{fig:j_vs_omega_mu1_v_0.8_e_E0_3_4}(b)) a peak around $\Omega\approx 11$ at the lead-hybridization value $v=0.8$.
+Such behavior suggests that at larger $E_0$ larger $v$ allows for II, although its contribution on the current is significantly suppressed than with smaller $v$ values.
 
-\subsection{Inclusion of e-ph interactions}
+WHICH FIGURE I PUT?
+Fig.~\ref{fig:j_vs_omega_mu1_v_0.8_e_E0_3_4} or Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_e_E0_3_4}?
+Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_e_E0_3_4} confirms findings of $E_0=2$ case and it's in line with the message of the article (For a small hybridization to the leads, we obtain a peak in the photocurrent as a function of the driving frequency which can be associated with impact ionization processes.
+For larger hybridizations the shallow peak suggests a suppression of impact ionization with respect to direct photovoltaic excitations.).
+In case we keep Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_e_E0_3_4} do I have to comment the curves for $v=0.4$?
+do we have to add something to the abstract/introduction about this new part?
+
+\subsubsection{Inclusion of e-ph interactions}
 \label{sec:E0_2_electrons_phonons}
 
-We now discuss the effect of coupling to acoustic phonons on the results discussed above.
+We now discuss the effect of coupling to acoustic phonons on these results.
 
@@
 With a smaller pseudogap and more states at its edges, more electrons can be directly excited with a given driving frequency thereby increasing the photocurrent.
-On the other hand, the suppression of the current by e-ph interaction in the range $7\lesssim\Omega\lesssim14$ is due to the reduction of spectral weight at frequencies $|\omega| \gtrsim 3.5$, cf.
+%%EACOMM, see other references for theese in gap states
+~\footnote{This effect is loosely related to enhancement of current due to the phonon-induced in-gap ladder states in~\cite{ha.ar.22u}.}
+ On the other hand, the suppression of the current by e-ph interaction in the range $7\lesssim\Omega\lesssim14$ is due to the dissipation-induced reduction of spectral weight at frequencies $|\omega| \gtrsim 3.5$, cf.
 Fig.
@@
 Summarizing, phonons enhance the current for almost all driving frequencies $\Omega\lesssim 7$ for which only DEs take place.
-They suppress the current in the range $7\lesssim\Omega\lesssim14$, where II is the dominant electronic scattering process for $v=0.4$ and DE for $v=0.8$.
-
+They suppress the current in the high-frequency range $7\lesssim\Omega\lesssim14$.
+%EACOMM I removed this sentence because there is no real causal relation since the current is suppressed in both cases.
+%where II is the dominant electronic scattering process for $v=0.4$ and DE for $v=0.8$.  
 %% By reducing the soft cutoff frequency, the spetral function of the phonons at low frequencies is increased.
@@
 
-This is confirmed by Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_E0_2_sweep_omegaph}, which shows that the impact of acoustic phonons on current and double occupation is slightly boosted when decreasing the soft cutoff frequency $\omega_{\text{ph}}$~\footnote{Reducing $\omega_{\text{ph}}$ has two effects.
-First, the spectral function $A_{\text{ph}}(\omega)$ exhibits more weight at low frequencies $\omega\approx\omega_{\text{ph}}$.
-Second, it restricts the maximal value of the reciprocal lattice vector $\vec{q}_{\text{max}}$ via $\omega_{\text{ph}}=\omega(\vec{q}_{\text{max}})$~\cite{ma.ga.22u}, meaning that short-wavelength phonons are neglected.}.
+%In order to verify the robustness of these results on the properties of the phonons, 
+%we have  
+This behavior is qualitatively valid for different values of 
+the soft cutoff phonon frequency
+ $\omega_{\text{ph}}$. This can be seen in
+%is confirmed by
+ Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_E0_2_sweep_omegaph}, which shows that the impact of acoustic phonons on 
+current and double occupation is slightly boosted when decreasing $\omega_{\text{ph}}$~\footnote{Reducing $\omega_{\text{ph}}$ has two effects.
+First, the phonon spectral function $A_{\text{ph}}(\omega)$ exhibits more weight at low frequencies $\omega\approx\omega_{\text{ph}}$.
+Second, it restricts the maximum value of the reciprocal lattice vector $\vec{q}_{\text{max}}$ via $\omega_{\text{ph}}=\omega(\vec{q}_{\text{max}})$~\cite{ma.ga.22u}, meaning that short-wavelength phonons are suppressed.}.
 
-The results above suggest that the influence of acoustic phonons on the electronic scattering processes is similar for all values of $v$, independent of how it affects DE or II.
-In other words, the effects of phonons is independent of the rate at which carriers are injected into and removed from the layer.
- Fig.~\ref{fig:j_vs_omega_mu1_sweep_v_E0_2_eph} confirms this behavior for intermediate lead-layer hybridizations $v=0.5,0.6,0.7$, for which DE and II at $\Omega\gtrsim8$ are even stronger mixed and harder to separate.
+The results above suggest that the influence of acoustic phonons on the electronic scattering processes does not depend significantly on $v$, i.e.
+on whether II processes are significant or not.
+In other words, the effects of phonons does not depend significantly
+on the rate at which carriers are injected into and removed from the layer.
+ Fig.~\ref{fig:j_vs_omega_mu1_sweep_v_E0_2_eph} confirms this behavior for intermediate lead-layer hybridizations $v=0.5,0.6,0.7$.
+%EACOMM I removed this sentence. It's not quite clear 
+%%for which DE and II at $\Omega\gtrsim8$ are even stronger mixed and harder to separate.
  Also the location of the crossing in the current  between the EO and e-ph case is essentially independent of $v$, as can be seen in 
@@
 (cf. Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(b)-Fig.~\ref{fig:j_vs_omega_mu1_sweep_v_E0_2_eph}(b))
-coincides with the current suppression and is probably due to a stronger localization of photoexcited electrons in the UHB.
+coincides with the current suppression and is probably due to a 
+suppression of the mobility 
+%stronger localization 
+of photoexcited electrons in the UHB.
 
@@
 In order to realize a Mott-based photovoltaic setup between metallic leads, we considered a correlated layer coupled to acoustic phonons, located between wide-band fermion leads.
-We demonstrated the importance of coupling to fermion leads for the electron scattering process occurring at different driving frequencies and observed how the dissipation by acoustic phonons influences the photocurrent and the double occupation.
-We found strong evidence that the dominant electron scattering mechanism responsible for the photocurrent peak at small hybridizations to the fermion leads is II, while DEs dominate at higher hybridizations.
-Dissipation via acoustic phonons slightly boosts the photocurrent for small driving frequencies and suppresses it at higher ones in the vicinity of the main peak.
+We studied the influence of the strength 
+of the coupling to the leads
+on 
+scattering process occurring at different driving frequencies and observed how the dissipation by acoustic phonons influences the photocurrent and the double occupation.
+We found evidence of a significant rate of II processes leading to a photocurrent peak
+%the dominant electron scattering mechanism responsible for the photocurrent peak 
+at small hybridizations, while these are suppressed  for larger hybridizations.
+Dissipation via acoustic phonons slightly boosts the photocurrent for small driving frequencies and suppresses it at larger ones in the vicinity of the main peak.
 The effect of phonons is not affected by changes in the lead-layer hybridization.
@@
 
-Experimentally, the electric field amplitude considered in this paper~\footnote{We do not consider smaller electric field amplitudes $E_0$ since DMFT only converges slowly for such a choice of parameters.
-Moreover, the observables' magnitude becomes comparable to our numerical precision.} is several orders of magnitude larger than that of the sunlight, however it is possible to achieve such amplitudes via THz pulses ~\cite{mu.we.18}.
-Moreover, in order to address the occurrence of II in realistic photovoltaic setups, one should extend such simplified model to multiorbital systems \cite{pe.be.19} in a multilayer setup, to model oxide heterostructures~\cite{as.bl.13,pe.be.19} where the correlated region consists of multiple layers and photoexcited carriers are separated via an electric field gradient.
+Experimentally, the electric field amplitude considered in this paper~\footnote{We do not consider smaller electric field amplitudes $E_0$ since DMFT only converges slowly for such a choice of parameters.} is several orders of magnitude larger than that of the sunlight, so that these results are rather relevant for photoexcitations produced by intense laser pulses (see also the discussion in ~\cite{mu.we.18} rather than true photovoltaic systems.
+On the other hand, one may try to estrapolate the idea of
+%%EACOMM IMPORTANT fill and relate to the discussion larger e fields
+in the other, namely to smaller electric fields for which a smaller hybridisation is necessary in order to support impact ionisation. For a more realistic system to model
+oxide heterostructures~\cite{as.bl.13,pe.be.19}
+the regime of small hybridisation should be replaced by a multilayer device in which photoexcited carrier, separated by an electric field gradient, have more time to induce impact ionisation processes.
+Also further effects should be taken into account, such as multiorbital correlated systems as well as impurity scattering.
+This will be the content of future studies.
+
+%Moreover, in order to address the occurrence of II in realistic photovoltaic setups, one should extend such simplified model to multiorbital systems \cite{pe.be.19} in a multilayer setup, to model  where the correlated region consists of multiple layers and photoexcited carriers are separated via an electric field gradient.
 Another step forward would be to take into account the effect of impurity scattering and the feedback of the electrons onto the phonon dynamics with a self-consistent treatment.

### 2022-08-26 Paper1.tex
Final version Paolo 26.08.2022

@@
 
-We study a model for photovoltaic energy collection consisting of a Mott insulating layer in presence of acoustic phonons, coupled to two wide-band fermion leads at different chemical potentials and driven by a periodic electric field.
+We study a model for photovoltaic energy collection consisting of a Mott insulating layer in presence of acoustic phonons, coupled to two wide-band fermion leads at different chemical potentials and driven %PGCH[
+into a nonequilibrium steady state
+%PGCH]
+by a periodic electric field.
 We treat electron correlations with nonequilibrium dynamical mean-field theory (DMFT) using the so-called auxiliary master equation approach as impurity solver and include dissipation by acoustic phonons via the Migdal approximation.
@@
 For larger hybridizations the shallow peak suggests a suppression of impact ionization with respect to direct photovoltaic excitations.
-Acoustic phonons slightly enhance the photocurrent for small driving frequencies and suppress it at frequencies around the main peak
-% This effect occurs at all considered hybridization strengths.
- at all considered hybridization strengths.
+Acoustic phonons slightly enhance the photocurrent for small driving frequencies and suppress it at frequencies around the main peak at all considered hybridization strengths.
 
@@
 From the scientific point of view and for future applications it is thus worthwile to further investigate the properties of Mott-based photovoltaic materials and the mechanisms behind their inner workings, to explore whether alternative unexpected paths can be opened.
-In fact, a lot of theoretical work has been done to understand the II process (see, e.g.~\cite{co.ma.14,ec.we.11,ec.we.13,we.he.14,pe.be.19,so.do.18,ka.wo.20,ma.ev.22}).
+In fact, a lot of theoretical work has been done to understand the II process (see, e.g.~\cite{co.ma.14,ec.we.11,ec.we.13,we.he.14,pe.be.19,so.do.18,ka.wo.20,mano.19,ma.ev.22}).
 
@@
 For this goal we consider the simplified model shown in Fig.~\ref{fig:setup}, consisting of a Hubbard layer located between two leads.
-The leads have themselves a wide band, as expected for good condutors, which are effectively narrowed due to the weak coupling to intermediate layers which we take as simplified models for the contacts.
+The leads have themselves a wide band, as expected for good conductors, which is effectively narrowed due to the weak coupling to intermediate layers which we take as simplified models for the contacts.
 Electrons on the Hubbard layer interact locally with acoustic phonons.
-An external periodic electric field induces a Floquet steady state with a current flowing from the lead with the lower to the higher chemical potential, thus transferring its energy.
- We address this periodic problem
- via nonequilibrium Floquet dynamical mean-field theory (F-DMFT).
+An external periodic electric field induces a Floquet steady state with a current flowing from the lead with the lower to the lead with the higher chemical potential, thus transferring its energy.
+ We address this periodic problem via nonequilibrium Floquet dynamical mean-field theory (F-DMFT).
 
@@
 Our goal is to investigate the occurrence of II in this photovoltaic setup and how it is affected by the presence of phonons.
-Specifically we study the behavior of the photovoltaic current, the spectral properties as well as the double occupation as a function of the hybridization strength and the properties of the phonons.
+Specifically, we study the behavior of the photovoltaic current, the spectral properties as well as the double occupation as a function of the hybridization strength and the properties of the phonons.
 Our analysis can only provide qualitative results, while quantitative comparisons with experimental systems require a more realistic setup and are beyond the scope of this work.
+
 Our calculations show that a small hybridization to the leads is more favorable for II than a larger one.
@@
 
-Phonons are 
-%The local e-ph coupling is
- included as in 
-%EACOMM check, put also previous references
-Ref.~\cite{ma.ga.22u} in the form of  acoustic  branches attached to each lattice site and coupled to the electrons via the Hamiltonian 
+As in Ref.~\cite{ma.ga.22u}, phonons are included in the form of acoustic  branches attached to each lattice site and coupled to the electrons via the Hamiltonian 
 \begin{equation}\label{eq:e-ph_ham} 
@@
 \end{equation}
-with $g$ as e-ph coupling and $\hat{x}_{i} \equiv \frac{1}{\sqrt{2}} \left( \hat{b}^{\dagger}_{i} + \hat{b}_i \right)$, where $\hat{b}^{\dagger}_{i}$ ($\hat{b}_{i}$) creates (annihilates) a phonon of the acoustic branch at site $i$, with dispersion relation described by $\hat{H}_{\text{ph}}$~\cite{ma.ga.22u}, see below.
-In contrast to Holstein phonons these have a finite bandwidth which is more effective in energy dissipation.
-Details on the leads are provided in~\ref{sec:Dyson_equation}.
+with $g$ as e-ph coupling and $\hat{x}_{i} \equiv \frac{1}{\sqrt{2}} \left( \hat{b}^{\dagger}_{i} + \hat{b}_i \right)$, where $\hat{b}^{\dagger}_{i}$ ($\hat{b}_{i}$) creates (annihilates) a phonon of the acoustic branch at site $i$, with dispersion relation described by $\hat{H}_{\text{ph}}$, discussed in Sec~\ref{sec:Dyson_equation}.
+In contrast to Holstein phonons, they have a finite bandwidth, which is more effective in energy dissipation.
+Details on the leads are provided in Sec.~\ref{sec:Dyson_equation}.
 
 For mathematical simplicity~\cite{ge.ko.92,ao.ts.14}, 
- we consider the correlated central region as a $d$-dimensional layer and consider the limit of infinite dimensions $d \rightarrow \infty$ by rescaling the hopping as 
-%EACOMM check parenthesis
-$t_{\text{c}}=t^{\ast}/(2\sqrt{d})$.
+ we consider the correlated central region as a $d$-dimensional layer and consider the limit of infinite dimensions $d \rightarrow \infty$ by rescaling the hopping as $t_{\text{c}}=t^{\ast}/(2\sqrt{d})$.
 Taking $a=1$, sums over the crystal momentum ${\bf k}$ of a generic quantity $\chi$ read $\sum_{{\bf k}} \chi(\omega,{\bf k}) \rightarrow \int d\epsilon \int   d\overline{\epsilon} \ \rho(\epsilon,\overline{\epsilon}) \chi(\omega;\epsilon,\overline{\epsilon})$ with $\rho(\epsilon,\overline{\epsilon}) = (1/\pi t^{\ast 2}) \exp[-( \epsilon^{2} + \overline{\epsilon}^{2})/t^{\ast 2}]$ as the joint density of states~\cite{ts.ok.08} and with
@@
 Within the remainder of this paper we choose our units so that  $\hbar = k_{\text{B}} = a = 1 = -q$, $t^{\ast}=2\sqrt{2}$ ~\footnote{With such choice for $t^{\ast}$ we reproduce the DOS of a 2D layer with $t_{\text{c}}=1$  in order to compare with Ref.~\cite{so.do.18}.}, and $t_r \equiv \frac{t^{\ast}}{2\sqrt{2}}=1$ as unit of energy.
-
-% In Tommasos paper we also chose -q=1.
-Given the amplitude of the vector potential above, setting q=-1 allows us to take positive values of E_0 and Omega.
-same sign of j0 (see old draft).
-increasing the mu I have negative current meaning that particle/electric current is flowing in the opposite direction.
 
@@
 \begin{equation}\label{eq:FullDysonEq}
-\underline{{\bf G}}^{-1}(\omega_n;\epsilon,\overline{\epsilon}) = \underline{{\bf G}}^{-1}_{0}(\omega_n;\epsilon,\overline{\epsilon}) - \underline{{\bf \Sigma}}(\omega_n;\epsilon,\overline{\epsilon}) - \underline{{\bf \Sigma}}_{\text{e-ph}}(\omega_n;\epsilon,\overline{\epsilon}) \;,
+\underline{{\bf G}}^{-1}(\omega_n;\epsilon,\overline{\epsilon}) = \underline{{\bf G}}^{-1}_{0}(\omega_n;\epsilon,\overline{\epsilon}) - \underline{{\bf \Sigma}}(\omega_n;\epsilon,\overline{\epsilon}) - \underline{{\bf \Sigma}}_{\text{e-ph}}(\omega_n;\epsilon,\overline{\epsilon}),
 \end{equation}
-where in our approximation the electron-electron $ \underline{{\bf \Sigma}}(\omega_n;\epsilon,\overline{\epsilon})$ and electron-phonon $\underline{{\bf \Sigma}}_{\text{e-ph}}(\omega_n;\epsilon,\overline{\epsilon})$ self energies contribute independently to the total self energy~\footnote{In fact there is an indirect feedback via the DMFT self-consistency.}
+where in our approximation the electron self-energy (SE) $ \underline{{\bf \Sigma}}$ and e-ph SE $\underline{{\bf \Sigma}}_{\text{e-ph}}$ contribute independently to the total SE~\footnote{In fact, there is an indirect feedback via the DMFT self-consistency.}.
 
@@
 
-The electron self-energy (SE) $\underline{\bf{\Sigma}}$ is obtained from F-DMFT and therefore, in this approximation, independent of the crystal momentum, i.e.
+The electron SE $\underline{\bf{\Sigma}}$ is obtained from F-DMFT and therefore, in this approximation, independent of the crystal momentum, i.e.
 $\underline{\bf{\Sigma}}(\omega;\epsilon,\overline{\epsilon}) \simeq \underline{\bf{\Sigma}}(\omega)$.
@@
 
-We compute the electron SE in the Dyson Equation~\eqref{eq:FullDysonEq} using DMFT~\cite{me.vo.89,ge.ko.92,ge.ko.96}, and in particular its nonequilibrium Floquet extension F-DMFT~\cite{ts.ok.08,sc.mo.02u,jo.fr.08}.
+We compute the electron SE in the Dyson equation~\eqref{eq:FullDysonEq} using DMFT~\cite{me.vo.89,ge.ko.92,ge.ko.96}, and in particular its nonequilibrium Floquet extension F-DMFT~\cite{ts.ok.08,sc.mo.02u,jo.fr.08}.
 In DMFT the crystal momentum dependence of the electron SE is neglected, i.e.
@@
 For completeness, we now
- briefly describe now the self-consistent F-DMFT scheme used.
+ briefly describe the self-consistent F-DMFT scheme used.
 (i) We start from an initial guess for the electron SE $\kel{\mat{\Sigma}}(\omega)$ and set $\kel{\mat \Sigma}_{\text{e-ph}}(\omega)=0$. (ii) Then we compute the local electron GF as 
@@
 where $\kel{\mat{g}}^{-1}_{0,\text{site}}(\omega)$ is defined as in Eq.~\eqref{eq:inv_non-int_lat_GF_comps} with $\varepsilon_{mn}(\epsilon,\overline{\epsilon})=0$.
-(v) The nonequilibrium many-body impurity problem is solved according to the procedure in Sec.~\ref{sec:amea}, leading to the new
- $\kel{\mat{\Sigma}}(\omega)$. (vi) We insert the electron and e-ph SEs into step (ii) and iterate the steps (ii)-(vi) until convergence.
+(v) The nonequilibrium many-body impurity problem is solved according to the procedure described below, leading to the new $\kel{\mat{\Sigma}}(\omega)$.
+(vi) We insert the electron and e-ph SEs into step (ii) and iterate the steps (ii)-(vi) until convergence.
 
-%EACOMM I eliminated this and the next subsubsection, is this okay?  
-%\subsubsection{Floquet-diagonal self-energy approximation}
-%\label{sec:FDSA}
+%PGCH[ I changed some words and rephrased the last sentence in this paragraph after Enrico modified it
 
-%EACOMM check this paragraph, which I changed a bit
-Eq.~\eqref{eq:imp_Dyson_eq} gives the bath hybridization function $\kel{\mat\Delta}(\omega)$ whose periodic time-dependence is encoded in its Floquet structure. 
-This means that, in principle, one would have to solve a time-periodic impurity problem leading to a non-diagonal self-energy in general. However, in 
- Ref.~\cite{so.do.18} it was argued that for the electric field strengths considered, non-diagonal terms in the Floquet SE $\kel{\mat{\Sigma}}(\omega)$  can be safely neglected with respect to the diagonal ones.
+Eq.~\eqref{eq:imp_Dyson_eq} gives a bath hybridization function $\kel{\mat\Delta}(\omega)$ whose periodic time-dependence is encoded in its Floquet structure. 
+This means that, in principle, one should solve a time-periodic impurity problem leading to a non-diagonal SE.
+However, in Ref.~\cite{so.do.18} it was argued and shown that for the considered electric field amplitudes, off-diagonal terms in the electron SE $\kel{\mat{\Sigma}}(\omega)$ can be safely neglected with respect to the diagonal ones.
 We follow this argument and adopt here
-this Floquet-diagonal self-energy approximation (FDSA) as well.
- In addition, it turns out that also for the 
- phonon SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ this approximation is justified\footnote{More specifically, we have verified that in the parameters range in which FDSA is justified for the electron SE $\kel{\mat{\Sigma}}(\omega)$ (Sec.~\ref{sec:results}), the off-diagonal terms of the phonon SE $\underline{\Sigma}_{mm,\text{e-ph}}(\omega)$ are orders of magnitude smaller than the diagonal ones}.
-Consequently, we  have to solve a nonequilibrium stationary impurity problem, by using only the  $(0,0)$-Floquet matrix elements of $\kel{\mat{\Sigma}}(\omega)$ and $\kel{\mat\Delta}(\omega)$, 
-%Eq.~\eqref{eq:imp_Dyson_eq}, 
-as the other diagonal components can be reconstructed by using the property $\kel{\Sigma}_{mm}(\omega) = \kel{\Sigma}_{00}(\omega+m\Omega)$.
+this Floquet-diagonal self-energy approximation (FDSA) as well. In addition, it turns out that also for the 
+ phonon SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ this approximation is justified~\footnote{More specifically, we verified that in the parameters range in which FDSA is justified for the electron SE $\kel{\mat{\Sigma}}(\omega)$ (Sec.~\ref{sec:results}), the off-diagonal terms of the phonon SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ are orders of magnitude smaller than the diagonal ones}.
+Consequently, we  solve a nonequilibrium stationary impurity problem, by considering only the $(0,0)$-Floquet matrix element of all the quantities in Eq.~\eqref{eq:imp_Dyson_eq}.
+The other diagonal components of the SEs are then reconstructed by using the property $\kel{\Sigma}_{mm}(\omega) = \kel{\Sigma}_{00}(\omega+m\Omega)$.
 
-%\subsubsection{Auxiliary master equation approach}
-%\label{sec:amea}
+%PGCH]
 
-%We now
-% briefly summarize the impurity solver used in step (v) of the DMFT self-consistent loop %described in Sec.~\ref{sec:FDMFT_implementation}. 
-In order to solve the electron-electron many-body problem (step (v) of the DMFT self-consistent loop),
- we use the auxiliary master equation approach (AMEA)~\cite{ar.kn.13,do.nu.14,do.ga.15,do.so.17}, which we now briefly summarize. 
+In order to solve the many-body problem in step (v) of the DMFT self-consistent loop, we use the auxiliary master equation approach (AMEA)~\cite{ar.kn.13,do.nu.14,do.ga.15,do.so.17}, which we now briefly summarize.
 Therein, we map the impurity problem onto an auxiliary open quantum system (AOQS) consisting of a finite number of bath sites $N_{\text{B}}$ attached to Markovian reservoirs described by the Lindblad equation.
 The  hybridization function $\kel{\Delta}_{\text{aux}}(\omega)$ of this AOQS is obtained by fitting the original DMFT one.
-The key point is that the many-body problem of this AOQS can be solved exactly
-using standard many-body-diagonalization methods, as long as  $N_{\text{B}}$ is small.
-The accuracy of this solution is set by the difference between
- $\kel{\Delta}_{\text{aux}}$ and $\kel{\Delta}$, which  becomes exponentially  small with increasing $N_{\text{B}}$.
+The key point is that the many-body problem of this AOQS can be solved exactly using standard many-body-diagonalization methods, as long as  $N_{\text{B}}$ is small.
+The accuracy of this solution is set by the difference between $\kel{\Delta}_{\text{aux}}$ and $\kel{\Delta}$, which  becomes exponentially  small with increasing $N_{\text{B}}$.
 
@@
  We follow Ref.~\cite{so.do.18} and take $U=12$ and unless stated otherwise $E_0=2$.
-The fermion leads and acoustic phonons have temperature $T=0.02$.
+The fermion leads and the acoustic phonons have temperature $T=0.02$.
 We consider a particle-hole symmetric system with $\Gamma_{\text{l}}=\Gamma_{\text{r}}=0.37$, $t_{\text{l}}=t_{\text{r}}=1.7$, $\varepsilon_{\text{l}/\text{r}}=\mp 6$ and $v_{\text{l}}=v_{\text{r}}=v$.
@@
 $W_{\text{b}}$ is the value at which the spectrum gets  suppressed.} $W_{\text{b}}\approx 8$ and are centered at the same position.
-The chemical potentials are set to $\mu_{\text{l}/\text{r}} =\mp 1$, so that a current from left to right is produced by energy taken from the driving.
+The chemical potentials are set to $\mu_{\text{l}/\text{r}} =\mp 1$, so that a current from left to right is produced by taking energy from the driving.
 
@@
 Setting $t_{r}=1$, we define for consistency $\alpha$ as in the main text.}.
-% and first-order photon absorption processes are dominant.
 Whenever the electron-phonon interaction is included, we take $g=0.8$ and unless stated otherwise $\omega_{\text{ph}}=0.1$.
 
-After some preliminary considerations in Sec.~\ref{sec:explicative_scheme}, we will discuss the occurrence of II at different $v$ first without (Sec.~\ref{sec:E0_2_only_electrons}) and then with coupling to acoustic phonons (Sec.~\ref{sec:E0_2_electrons_phonons}).
+After some preliminary considerations in Sec.~\ref{sec:explicative_scheme}, we discuss the occurrence of II at different $v$ first without (Sec.~\ref{sec:E0_2_only_electrons}) and then with coupling to acoustic phonons (Sec.~\ref{sec:E0_2_electrons_phonons}).
 
@@
 
-\includegraphics[width=0.85\linewidth]{./figures_Paper1/energy_setup.pdf}
+\includegraphics[width=0.8\linewidth]{./figures_Paper1/energy_setup.pdf}
 \caption{(Color online) Schematic representation of the processes occuring in the model considered.
@@
 Green bands are the LHB and UHB of the central layer.
-Due to the hybridization with the metallic leads only a pseudogap $\Delta_{\text{pg}}$ is present between the bands.
 The vertical axis represents the energy.
+Due to the hybridization with the metallic leads only a pseudogap $\Delta_{\text{pg}}$ is present between the Hubbard bands.
 Panel (a) sketches the quantities introduced at the beginning of Sec.~\ref{sec:results}.
@@
 
-\subsection{Qualitative Energy considerations and physical processes}
+\subsection{Qualitative energy considerations and physical processes}
 \label{sec:explicative_scheme}
@@
 Thereby, we partially follow Ref.~\cite{so.do.18} for the electron-only (EO) case and extend the analysis to the case with e-ph interaction.
-In comparison with Ref.~\cite{so.do.18} here the wide-band leads more realistically described a metallic structure. This makes the identification of II processes more subtle, as discussed below.
-As in Ref.~\cite{so.do.18} we bypass transient behavior and consider directly the nonequilibrium Floquet steady state.
-In our analysis, we neglect higher-order processes such as multiparticle scattering processes.
+In comparison with Ref.~\cite{so.do.18}, here the wide-band leads describe more realistically a metallic structure. This makes the identification of II processes more subtle, as discussed below.
+As in Ref.~\cite{so.do.18} we bypass transient behavior and consider directly the Floquet steady state. In our analysis, we neglect higher-order processes such as multiparticle scattering processes.
 
 In order to observe II, the bandwidth of the UHB has to be at least twice the pseudogap~\footnote{Due to the hybridization with the metallic leads 
-only a pseudogap $\Delta_{\text{pg}}$ is present between the LHB and the UHB.} 
-size $\Delta_{\text{pg}}$. Only in this case, the photoexcited electron can acquire enough energy to excite a second one across the pseudogap.
+only a pseudogap $\Delta_{\text{pg}}$ is present between the LHB and the UHB.} size $\Delta_{\text{pg}}$.
+Only in this case, the photoexcited electron can acquire enough energy to excite a second one across the pseudogap.
 
@@
 \item For $\Omega<\Delta_{\text{pg}}$, 
-we expect a strong suppression of the current
-we do not expect any current if the DOS of the correlated layer has a true gap~\footnote{The remaining leak current can be either produced by multiple-photon absorption processes, which however, are strongly suppressed, or by the fact that there is no true gap}.
-%To overcome a true gap with $\Omega<\Delta_{\text{pg}}$  should take place, but as written in the main text, such effects are negligible in the studied parameters range.}.
-
-%~\footnote{To overcome a true gap with $\Omega<\Delta_{\text{pg}}$ multiple-photon absorption processes should take place, but as written in the main text, such effects are negligible in the studied parameters range.}.
-%If $\Delta_{\text{pg}}$ is a partial gap, we expect a suppression of the current.
+we expect a strong suppression of the current~\footnote{The remaining leak current can be either produced by multiple-photon absorption processes, which however, are strongly suppressed, or by the fact that there is no true gap} and
+we do not expect any current if the DOS of the correlated layer has a true gap.
 \item For $\Delta_{\text{pg}}<\Omega<\Delta_{\text{pg}}+2W_{\text{b}}$ as shown in Fig.~\ref{fig:energy_setup}(b), an electron coming from the left lead into the LHB is photoexcited to the UHB and can escape directly into the right lead without additional scattering.
@@
 Notice that in the energy window $\Delta_{\text{pg}}<\Omega<2\Delta_{\text{pg}}$ the only scattering processes taking place are DEs, while for $2\Delta_{\text{pg}}<\Omega<\Delta_{\text{pg}}+2W_{\text{b}}$, both DE and II can occur.
-This is in contrast to the case of Ref.~\cite{so.do.18} in which the peculiar ad-hoc narrow lead bands only allowed for II current in a certain $\Omega$ regime.
-For this reason, and due to the fact that
-%We want to stress, that 
-the boundaries of these energy ranges are not strict, it is more tricky to disentangle  these physical processes in the present case.
+This is in contrast to the case of Ref.~\cite{so.do.18}, in which the peculiar ad-hoc narrow leads' bands only allow for II processes in a certain $\Omega$-range.
+For this reason, and due to the fact that the boundaries of these energy ranges are not strict, it is more tricky to disentangle these physical processes in the present case.
 
@@
 As shown in Sec.~\ref{sec:E0_2_electrons_phonons}, the phonons broaden the DOS of the correlated layer and slightly fill and shrink the pseudogap.
-%Therefore the pseudogap is reduced by a small amount indicating the dissipation by phonons.
 
@@
 
-\subsection{Quantitative results}
+%PGCH: I put this section as a subsection as before
 
-\subsubsection{EO system}
+\subsection{EO system}
 \label{sec:E0_2_only_electrons}
 
-We start with the case without e-ph interaction and address the behavior 
-%investigate the dependence 
-of  physical quantities as a function of $\Omega$ for different strengths of the lead-layer hybridization.
+We start with the case without e-ph interaction and address the behavior of the physical quantities as functions of $\Omega$ for different values of the lead-layer hybridization.
 
@@
 Similarly, the double occupation shown in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(b) increases as a function of the driving frequency~\footnote{Notice that the increase of $N_{\text{D}}$ in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(b) as compared to Ref.~\cite{so.do.18} is not as steep and large in magnitude.
-This is due to our setup, where every photoexcited carrier can escape to the right lead.}.
+This is due to our setup, where every photoexcited carrier can escape into the right lead.}.
 
@@
 
-\begin{figure}[b]  
-% \captionsetup{width=\textwidth} 
-\includegraphics[width=\linewidth]{./figures_Paper1/j_vs_omega_mu1_v_0.4_0.8_e_E0_3_4.pdf}
-\caption{(Color online) (a) Time-averaged steady-state current $j$ and (b) double occupancy $N_{\text{D}}$ as a function of $\Omega$, for $v=0.4,0.8$ at electric field amplitudes $E_0=3,4$ for the EO system.
-Default parameters are specified at the beginning of Sec.~\ref{sec:results}.}
-\label{fig:j_vs_omega_mu1_v_0.4_0.8_e_E0_3_4} 
-\end{figure}
-
 For $\Omega\gtrsim8$, the current increases further until it reaches its peak at $\Omega\approx 11$.
-In this range both DE and II can occur in principle.
-The height of the peak is approximately the same for both $v$, despite the lead-layer hybridizations differing by a factor of two.
+In this range both DE and II can occur in principle. The height of the peak is approximately the same for both $v$, despite
+%PGCH: REMOVED:the lead-layer hybridizations differing by a factor of two. ALTERNATIVE FORMULATION:
+%PGCH[
+they differ by a factor of two.
+%PGCH]
 The double occupation in this range shows a similar behavior as the current for $v=0.4$ with a peak around $\Omega\approx 11$, while it exhibits a plateau for $v=0.8$.
-For $v=0.4$ the current curve is characterized by a substantial increase in slope around 
-%EACOMM i put 7, this is where it actually occur
-$\Omega \approx 7$, which cannot be observed for $v=0.8$.
- This, together with the comparable magnitude of the maxima at $\Omega\approx 11$ and the behavior of the double occupation strongly suggest that for $v=0.4$ a substantial rate of II processes take place, while these are absent or negligible for $v=0.8$.
+For $v=0.4$ the current curve is characterized by a substantial increase in slope around $\Omega \approx 7$, which cannot be observed for $v=0.8$. This, together with the comparable magnitude of the
+%PGCH[
+current
+%PGCH]
+maxima at $\Omega\approx 11$ and the behavior of the double occupation strongly suggests that for $v=0.4$ a substantial rate of II processes take place, while these are absent or negligible for $v=0.8$.
 Here,  the plateau in $N_{\text{D}}$ for $v=0.8$ suggests that photoexcited electrons arriving in the UHB quickly escape to the right fermionic lead and do not have time to induce II processes.
 
-The spectral and occupation function shown in Fig.~\ref{fig:spec_filling_mu1_v_0.4_0.8_O_5_11_e} corroborate this hypothesis.
-For $\Omega=5$ in the DE range, the occupation function in the UHB is almost the same for both $v$, while for $\Omega=11$ where the peak in the current occurs, the occupation of the UHB for $v=0.4$ is substantially larger,  in line with the behavior of $N_{\text{D}}$.
-Increasing $\Omega$ further produces excitations near the border of the UHB where the DOS is reduced, and, thus  current and double occupation decrease~\footnote{The current $j$ does not approach zero as expected for $\Omega>20$ because of the background current as discussed in Ref.~\cite{so.do.18}.}.
+The spectral and occupation functions shown in Fig.~\ref{fig:spec_filling_mu1_v_0.4_0.8_O_5_11_e} corroborate this hypothesis.
+For $\Omega=5$, in the DE range, the occupation function in the UHB is almost the same for both $v$, while for $\Omega=11$ where the peak in the current occurs, the occupation of the UHB for $v=0.4$ is substantially larger,  in line with the behavior of $N_{\text{D}}$.
 
-NEW PART: If the electric field amplitude $E_0$ is increased, as shown in Fig.~\ref{fig:j_vs_omega_mu1_v_0.8_e_E0_3_4}(a), the current curve develops an increase in slope around $\Omega\approx7$ and the double occupation (cf.
-Fig.~\ref{fig:j_vs_omega_mu1_v_0.8_e_E0_3_4}(b)) a peak around $\Omega\approx 11$ at the lead-hybridization value $v=0.8$.
-Such behavior suggests that at larger $E_0$ larger $v$ allows for II, although its contribution on the current is significantly suppressed than with smaller $v$ values.
+Further increasing $\Omega$ produces excitations near the border of the UHB where the DOS is reduced and thus  current and double occupation decrease~\footnote{The current $j$ does not approach zero as expected for $\Omega>20$ because of the background current as discussed in Ref.~\cite{so.do.18}.}.
 
-WHICH FIGURE I PUT?
-Fig.~\ref{fig:j_vs_omega_mu1_v_0.8_e_E0_3_4} or Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_e_E0_3_4}?
-Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_e_E0_3_4} confirms findings of $E_0=2$ case and it's in line with the message of the article (For a small hybridization to the leads, we obtain a peak in the photocurrent as a function of the driving frequency which can be associated with impact ionization processes.
-For larger hybridizations the shallow peak suggests a suppression of impact ionization with respect to direct photovoltaic excitations.).
-In case we keep Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_e_E0_3_4} do I have to comment the curves for $v=0.4$?
-do we have to add something to the abstract/introduction about this new part?
+%PGCH[ Added Enrico's part. I changed some words.
 
-\subsubsection{Inclusion of e-ph interactions}
+This behavior is influenced by the  electric field amplitude $E_0$  as illustrated in Fig.~\ref{fig:j_vs_omega_mu1_v_0.8_e_E0_3_4}(a).
+For $E_0=4$ the current develops a sudden increase in slope around $\Omega\approx7$ as well as a pronounced peak around $\Omega\approx 11$ for the larger hybridization $v=0.8$.
+This feature starts developing already at $E_0=3$.
+This tendency, corroborated by the behavior of the double occupation displayed in Fig.~\ref{fig:j_vs_omega_mu1_v_0.8_e_E0_3_4}(b), suggests an  important role of II also for larger values of $v$, provided the field amplitude is strong enough.
+
+%PGCH]
+
+%PGCH: I put this section as a subsection as before
+
+\subsection{Inclusion of e-ph interactions}
 \label{sec:E0_2_electrons_phonons}
@@
 The double occupation $N_{\text{D}}$  shown in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(b) is larger than and follows the behavior of its EO counterpart within the entire $\Omega$-range considered.
-The spectral and occupation function  shown in Fig.~\ref{fig:spec_filling_mu1_v_0.4_0.8_O_11_eph} display a redistribution of spectral weight from the peaks towards the edges of the bands, thus reducing the pseudogap.
+The spectral and occupation functions  shown in Fig.~\ref{fig:spec_filling_mu1_v_0.4_0.8_O_11_eph} display a redistribution of spectral weight from the peaks towards the edges of the bands, thus reducing the pseudogap.
 Consequently, the occupation of positive energy states is slightly shifted to the bottom of the UHB compared to the EO case, as the occupation function shows.
@@
 This reduction of the pseudogap explains why the current in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(a) is slightly larger in presence of phonons for $\Omega\lesssim7$.
-With a smaller pseudogap and more states at its edges, more electrons can be directly excited with a given driving frequency thereby increasing the photocurrent.
-%%EACOMM, see other references for theese in gap states
-~\footnote{This effect is loosely related to enhancement of current due to the phonon-induced in-gap ladder states in~\cite{ha.ar.22u}.}
+%PGCH: removed reference to in gap phonon states
+With a smaller pseudogap and more states at its edges, more electrons can be directly excited with a given driving frequency $\Omega$ thereby increasing the photocurrent.
 On the other hand, the suppression of the current by e-ph interaction in the range $7\lesssim\Omega\lesssim14$ is due to the dissipation-induced reduction of spectral weight at frequencies $|\omega| \gtrsim 3.5$, cf.
@@
 
-\begin{figure}[t]
+\begin{figure}[b]
 % \captionsetup{width=\textwidth} 
@@
 
-\begin{figure}[b] 
+\begin{figure}[t] 
 % \captionsetup{width=\textwidth}  
@@
 
-Summarizing, phonons enhance the current for almost all driving frequencies $\Omega\lesssim 7$ for which only DEs take place.
-They suppress the current in the high-frequency range $7\lesssim\Omega\lesssim14$.
-%EACOMM I removed this sentence because there is no real causal relation since the current is suppressed in both cases.
-%where II is the dominant electronic scattering process for $v=0.4$ and DE for $v=0.8$.  
-%% By reducing the soft cutoff frequency, the spetral function of the phonons at low frequencies is increased.
-The idea is that this increases the influence of the phonons on the current thus increasing the current at low driving frequencies (DE) and reducing the current at driving frequencies around the peak (II).
-%
+Summarizing, phonons
+%PGCH[ 
+slightly
+%PGCH]
+enhance the current for almost all driving frequencies $\Omega\lesssim 7$ for which only DEs take place. They suppress the current in the high-frequency range $7\lesssim\Omega\lesssim14$.
 
-%In order to verify the robustness of these results on the properties of the phonons, 
-%we have  
-This behavior is qualitatively valid for different values of 
-the soft cutoff phonon frequency
- $\omega_{\text{ph}}$. This can be seen in
-%is confirmed by
- Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_E0_2_sweep_omegaph}, which shows that the impact of acoustic phonons on 
+This behavior is qualitatively valid for different values of the soft cutoff phonon frequency
+ $\omega_{\text{ph}}$. This can be seen in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_E0_2_sweep_omegaph}, which shows that the impact of acoustic phonons on 
 current and double occupation is slightly boosted when decreasing $\omega_{\text{ph}}$~\footnote{Reducing $\omega_{\text{ph}}$ has two effects.
@@
 Second, it restricts the maximum value of the reciprocal lattice vector $\vec{q}_{\text{max}}$ via $\omega_{\text{ph}}=\omega(\vec{q}_{\text{max}})$~\cite{ma.ga.22u}, meaning that short-wavelength phonons are suppressed.}.
-
-The results above suggest that the influence of acoustic phonons on the electronic scattering processes does not depend significantly on $v$, i.e.
-on whether II processes are significant or not.
-In other words, the effects of phonons does not depend significantly
-on the rate at which carriers are injected into and removed from the layer.
- Fig.~\ref{fig:j_vs_omega_mu1_sweep_v_E0_2_eph} confirms this behavior for intermediate lead-layer hybridizations $v=0.5,0.6,0.7$.
-%EACOMM I removed this sentence. It's not quite clear 
-%%for which DE and II at $\Omega\gtrsim8$ are even stronger mixed and harder to separate.
- Also the location of the crossing in the current  between the EO and e-ph case is essentially independent of $v$, as can be seen in 
- Fig.~\ref{fig:j_vs_omega_mu1_sweep_v_E0_2_eph}(a).
-The increase of double occupation for the case with e-ph interaction 
-(cf. Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(b)-Fig.~\ref{fig:j_vs_omega_mu1_sweep_v_E0_2_eph}(b))
-coincides with the current suppression and is probably due to a 
-suppression of the mobility 
-%stronger localization 
-of photoexcited electrons in the UHB.
 
@@
 
+The results above suggest that the influence of acoustic phonons on the electronic scattering processes does not depend significantly on $v$, i.e.
+on whether II processes are significant or not.
+In other words, the effect of phonons doesn't depend significantly on the rate at which carriers are injected into and removed from the layer.
+Fig.~\ref{fig:j_vs_omega_mu1_sweep_v_E0_2_eph} confirms this behavior for intermediate lead-layer hybridizations $v=0.5,0.6,0.7$.
+Also the location of the crossing in the current  between the EO and e-ph case is essentially independent of $v$, as can be seen in
+ Fig.~\ref{fig:j_vs_omega_mu1_sweep_v_E0_2_eph}(a).
+%PGCH: I find this sentence below not clearly motivated.
+In the e-ph case, the correlation between the increase of N_D and the current suppression is true, but it's also true that the double occupation is larger than the EO counterpart also when the current with phonons is enhanced in the low-frequency range.
+The increase of double occupation in the case with e-ph interaction 
+(cf. Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(b)-Fig.~\ref{fig:j_vs_omega_mu1_sweep_v_E0_2_eph}(b))
+coincides with the current suppression and is probably due to a suppression of the mobility of photoexcited electrons in the UHB.
+
 \section{Conclusion}   
@@
 
-We investigated the influence of fermion leads and phonon dissipation on electron transport and spectral properties of a Mott insulating layer driven to the nonequilibrium steady state by an external periodic field.
+We investigated the influence of fermion leads and phonon dissipation on electron transport and spectral properties of a Mott insulating layer driven to the nonequilibrium steady state by an external periodic electric field.
 In order to realize a Mott-based photovoltaic setup between metallic leads, we considered a correlated layer coupled to acoustic phonons, located between wide-band fermion leads.
 We studied the influence of the strength 
-of the coupling to the leads
-on 
-scattering process occurring at different driving frequencies and observed how the dissipation by acoustic phonons influences the photocurrent and the double occupation.
-We found evidence of a significant rate of II processes leading to a photocurrent peak
-%the dominant electron scattering mechanism responsible for the photocurrent peak 
-at small hybridizations, while these are suppressed  for larger hybridizations.
+of the coupling to the leads on the scattering process occurring at different driving frequencies and observed how the dissipation by acoustic phonons influences the photocurrent and the double occupation.
+We found evidence of a significant rate of II processes leading to a photocurrent peak at small hybridizations, while these are suppressed  for larger hybridizations.
 Dissipation via acoustic phonons slightly boosts the photocurrent for small driving frequencies and suppresses it at larger ones in the vicinity of the main peak.
-The effect of phonons is not affected by changes in the lead-layer hybridization.
+The effect of phonons is not affected significantly by changes in the lead-layer hybridization.
 
-These results suggest that in systems where correlated layers are connected to metallic leads via weakly coupled single layers or molecules, II could contribute significantly to the photocurrent.
-From the experimental point of view, such setup is employed, for example, to bridge semiconductor quantum dots to reservoirs through small molecules~\cite{wa.mc.13,wa.bo.17} to extract hot photoexcited carriers~\cite{ti.ke.10,ca.wa.16}.
-Based on our results, moderate e-ph coupling does not suppress the photocurrent significantly and therefore in real materials, II could contribute to overcome the Schockley-Queisser limit~\cite{sh.qu.61}.
+%PGCH: Removed the paragraph related to suggestions and possible experimental realization of our setup.
 
-Experimentally, the electric field amplitude considered in this paper~\footnote{We do not consider smaller electric field amplitudes $E_0$ since DMFT only converges slowly for such a choice of parameters.} is several orders of magnitude larger than that of the sunlight, so that these results are rather relevant for photoexcitations produced by intense laser pulses (see also the discussion in ~\cite{mu.we.18} rather than true photovoltaic systems.
-On the other hand, one may try to estrapolate the idea of
-%%EACOMM IMPORTANT fill and relate to the discussion larger e fields
-in the other, namely to smaller electric fields for which a smaller hybridisation is necessary in order to support impact ionisation. For a more realistic system to model
-oxide heterostructures~\cite{as.bl.13,pe.be.19}
-the regime of small hybridisation should be replaced by a multilayer device in which photoexcited carrier, separated by an electric field gradient, have more time to induce impact ionisation processes.
-Also further effects should be taken into account, such as multiorbital correlated systems as well as impurity scattering.
-This will be the content of future studies.
+%PGCH[ Added Enrico's part but I changed some words and rephrased
 
-%Moreover, in order to address the occurrence of II in realistic photovoltaic setups, one should extend such simplified model to multiorbital systems \cite{pe.be.19} in a multilayer setup, to model  where the correlated region consists of multiple layers and photoexcited carriers are separated via an electric field gradient.
-Another step forward would be to take into account the effect of impurity scattering and the feedback of the electrons onto the phonon dynamics with a self-consistent treatment.
+Experimentally, the electric field amplitude considered in this paper~\footnote{We don't consider smaller electric field amplitudes $E_0$ since DMFT only converges slowly for such a choice of parameters.} is several orders of magnitude larger than that of the sunlight, therefore these results are more relevant for photoexcitations produced by intense laser pulses (see also the discussion in ~\cite{mu.we.18}) rather than for true photovoltaic systems.
+On the other hand, one may try to qualitatively extrapolate the discussion at the end of Sec.~\ref{sec:E0_2_only_electrons} in the other direction,  namely to smaller electric field amplitudes, for which a smaller hybridization
+%PGCH: REMOVED: is. ALTERNATIVE FORMULATION:
+%PGCH[
+would be
+%PGCH]
+necessary in order to sustain II.
+In a more realistic setup modelling oxide heterostructures~\cite{as.bl.13,pe.be.19}, a regime of effectively small hybridization would be achieved by considering several layers in which photoexcited carriers, separated by an electric field gradient, have more time to induce II processes before escaping into the leads.
+In order to address the occurrence of II in such setups, also further extensions should be taken into account, such as the inclusion of multiorbital correlated systems as well as impurity scattering.
+Such topics would be interesting for future studies.
+
+%PGCH]
 

### 2022-08-26 Paper1.tex
Final version 26.08.2022

@@
 
-We study a model for photovoltaic energy collection consisting of a Mott insulating layer in presence of acoustic phonons, coupled to two wide-band fermion leads at different chemical potentials and driven %PGCH[
-into a nonequilibrium steady state
-%PGCH]
-by a periodic electric field.
+We study a model for photovoltaic energy collection consisting of a Mott insulating layer in presence of acoustic phonons, coupled to two wide-band fermion leads at different chemical potentials and driven
+into a nonequilibrium steady state by a periodic electric field.
 We treat electron correlations with nonequilibrium dynamical mean-field theory (DMFT) using the so-called auxiliary master equation approach as impurity solver and include dissipation by acoustic phonons via the Migdal approximation.
@@
 
-%PGCH[ I changed some words and rephrased the last sentence in this paragraph after Enrico modified it
-
 Eq.~\eqref{eq:imp_Dyson_eq} gives a bath hybridization function $\kel{\mat\Delta}(\omega)$ whose periodic time-dependence is encoded in its Floquet structure. 
@@
 The other diagonal components of the SEs are then reconstructed by using the property $\kel{\Sigma}_{mm}(\omega) = \kel{\Sigma}_{00}(\omega+m\Omega)$.
-
-%PGCH]
 
@@
 
-%PGCH: I put this section as a subsection as before
-
 \subsection{EO system}
@@
 For $\Omega\gtrsim8$, the current increases further until it reaches its peak at $\Omega\approx 11$.
-In this range both DE and II can occur in principle. The height of the peak is approximately the same for both $v$, despite
-%PGCH: REMOVED:the lead-layer hybridizations differing by a factor of two. ALTERNATIVE FORMULATION:
-%PGCH[
-they differ by a factor of two.
-%PGCH]
+In this range both DE and II can occur in principle.
+The height of the peak is approximately the same for both $v$, despite they differ by a factor of two.
 The double occupation in this range shows a similar behavior as the current for $v=0.4$ with a peak around $\Omega\approx 11$, while it exhibits a plateau for $v=0.8$.
-For $v=0.4$ the current curve is characterized by a substantial increase in slope around $\Omega \approx 7$, which cannot be observed for $v=0.8$. This, together with the comparable magnitude of the
-%PGCH[
-current
-%PGCH]
-maxima at $\Omega\approx 11$ and the behavior of the double occupation strongly suggests that for $v=0.4$ a substantial rate of II processes take place, while these are absent or negligible for $v=0.8$.
+For $v=0.4$ the current curve is characterized by a substantial increase in slope around $\Omega \approx 7$, which cannot be observed for $v=0.8$.
+This, together with the comparable magnitude of the current maxima at $\Omega\approx 11$ and the behavior of the double occupation strongly suggests that for $v=0.4$ a substantial rate of II processes take place, while these are absent or negligible for $v=0.8$.
 Here,  the plateau in $N_{\text{D}}$ for $v=0.8$ suggests that photoexcited electrons arriving in the UHB quickly escape to the right fermionic lead and do not have time to induce II processes.
@@
 
-%PGCH[ Added Enrico's part. I changed some words.
-
 This behavior is influenced by the  electric field amplitude $E_0$  as illustrated in Fig.~\ref{fig:j_vs_omega_mu1_v_0.8_e_E0_3_4}(a).
@@
 This tendency, corroborated by the behavior of the double occupation displayed in Fig.~\ref{fig:j_vs_omega_mu1_v_0.8_e_E0_3_4}(b), suggests an  important role of II also for larger values of $v$, provided the field amplitude is strong enough.
-
-%PGCH]
-
-%PGCH: I put this section as a subsection as before
 
@@
 This reduction of the pseudogap explains why the current in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(a) is slightly larger in presence of phonons for $\Omega\lesssim7$.
-%PGCH: removed reference to in gap phonon states
 With a smaller pseudogap and more states at its edges, more electrons can be directly excited with a given driving frequency $\Omega$ thereby increasing the photocurrent.
@@
 
-Summarizing, phonons
-%PGCH[ 
-slightly
-%PGCH]
-enhance the current for almost all driving frequencies $\Omega\lesssim 7$ for which only DEs take place. They suppress the current in the high-frequency range $7\lesssim\Omega\lesssim14$.
+Summarizing, phonons slightly enhance the current for almost all driving frequencies $\Omega\lesssim 7$ for which only DEs take place.
+They suppress the current in the high-frequency range $7\lesssim\Omega\lesssim14$.
 
@@
  Fig.~\ref{fig:j_vs_omega_mu1_sweep_v_E0_2_eph}(a).
-%PGCH: I find this sentence below not clearly motivated.
-In the e-ph case, the correlation between the increase of N_D and the current suppression is true, but it's also true that the double occupation is larger than the EO counterpart also when the current with phonons is enhanced in the low-frequency range.
-The increase of double occupation in the case with e-ph interaction 
-(cf. Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(b)-Fig.~\ref{fig:j_vs_omega_mu1_sweep_v_E0_2_eph}(b))
-coincides with the current suppression and is probably due to a suppression of the mobility of photoexcited electrons in the UHB.
 
@@
 
-%PGCH: Removed the paragraph related to suggestions and possible experimental realization of our setup.
-
-%PGCH[ Added Enrico's part but I changed some words and rephrased
-
 Experimentally, the electric field amplitude considered in this paper~\footnote{We don't consider smaller electric field amplitudes $E_0$ since DMFT only converges slowly for such a choice of parameters.} is several orders of magnitude larger than that of the sunlight, therefore these results are more relevant for photoexcitations produced by intense laser pulses (see also the discussion in ~\cite{mu.we.18}) rather than for true photovoltaic systems.
-On the other hand, one may try to qualitatively extrapolate the discussion at the end of Sec.~\ref{sec:E0_2_only_electrons} in the other direction,  namely to smaller electric field amplitudes, for which a smaller hybridization
-%PGCH: REMOVED: is. ALTERNATIVE FORMULATION:
-%PGCH[
-would be
-%PGCH]
-necessary in order to sustain II.
+On the other hand, one may try to qualitatively extrapolate the discussion at the end of Sec.~\ref{sec:E0_2_only_electrons} in the other direction,  namely to smaller electric field amplitudes, for which a smaller hybridization would be necessary in order to sustain II.
 In a more realistic setup modelling oxide heterostructures~\cite{as.bl.13,pe.be.19}, a regime of effectively small hybridization would be achieved by considering several layers in which photoexcited carriers, separated by an electric field gradient, have more time to induce II processes before escaping into the leads.
-In order to address the occurrence of II in such setups, also further extensions should be taken into account, such as the inclusion of multiorbital correlated systems as well as impurity scattering.
+In order to address the occurrence of II in such setup, also further extensions should be taken into account, such as the inclusion of multiorbital correlated systems as well as impurity scattering.
 Such topics would be interesting for future studies.
-
-%PGCH]
 

### 2022-08-30 Paper1.tex
Last version paper 30.08.2022
Smoothened formulations in text and footnotes. Moved fig. 8 to bottom of page. Altered fig. 1 slightly to contain Gamma_l and Gamma_r, not Gamma. Renamed energy scale to t_{resc}.

@@
 
-\newcommand{\mscomm}[1]{{\color{blue} MS Comment: #1}}
-%\newcommand{\kh}[1] {\textcolor{green}{KH comment: #1}}
-
 \definecolor{orange}{RGB}{252,77,6}
@@
 
-%EA
 \title{Impact ionization processes in a photodriven Mott insulator: influence of phononic dissipation}
@@
 As a scattering process, II competes with electron-phonon (e-ph) scattering which is the dominant relaxation mechanism in conventional semiconductors.
-This may not be the case in Mott insulators, at least in certain cases ~\cite{co.ma.14}.
+This may not be the case in Mott insulators, at least in certain cases~\cite{co.ma.14}.
 Therefore, it is essential to understand the influence of e-ph scattering on the photocurrent and II in Mott photovoltaic devices, which is the issue we address in this paper.
@@
 \begin{figure}[b] 
-% \captionsetup{width=\textwidth} 
 \includegraphics[width=0.9\linewidth]{./figures_Paper1/setup_voltmeter.pdf}
@@
 A central, correlated layer with local Hubbard interaction $U$ and e-ph coupling $g$ (green) is sandwiched between two non-interacting layers (red) via the hybridization $v$ (black).
-The latter are in turn coupled to wide-band fermion reservoirs (blue) with different chemical potentials $\mu_{\text{l}/\text{r}}$, which introduce a broadening $\Gamma=\Gamma_{\text{l}}=\Gamma_{\text{r}}$.}
+The latter are in turn coupled to wide-band fermion reservoirs (blue) with different chemical potentials $\mu_{\text{l}/\text{r}}$, which introduce broadenings $\Gamma_{\text{l}/\text{r}}$.}
 \label{fig:setup}
@@
 % 
-The operator $\hat{c}^{\dagger}_{i\sigma}$ ($\hat{c}_{i\sigma}$) creates (annihilates) a particle with spin $\sigma= \lbrace \uparrow,\downarrow \rbrace$ on the $i$-th lattice site and $\hat{n}_{i\sigma}\equiv \hat{c}^{\dagger}_{i\sigma} \hat{c}_{i\sigma}$ is the particle number operator.
+The operator $\hat{c}^{\dagger}_{i\sigma}$ ($\hat{c}_{i\sigma}$) creates (annihilates) an electron with spin $\sigma= \lbrace \uparrow,\downarrow \rbrace$ on the $i$-th lattice site and $\hat{n}_{i\sigma}\equiv \hat{c}^{\dagger}_{i\sigma} \hat{c}_{i\sigma}$ is the particle number operator.
 We denote with $(i,j)$ the sum over nearest-neighbor sites and with $\varepsilon_{\text{c}} \equiv -U/2$ the on-site energy.
@@
 lattice body diagonal $\vec{e}_{0}=(1,1,\dots,1)$.
-$A(t)=\frac{\hbar}{qa}\aamp\sin(\Omega t)$ with $\aamp=-\frac{qE_0a}{\hbar\Omega}$,  $E_0$ is the  electric field amplitude, and $a$ the lattice spacing ~\cite{ts.ok.08}.
+Therein $A(t)=\frac{\hbar}{qa}\aamp\sin(\Omega t)$ with $\aamp=-\frac{qE_0a}{\hbar\Omega}$, $E_0$ is the electric field amplitude, and $a$ the lattice spacing~\cite{ts.ok.08}.
 In this temporal gauge the electric field is $\vec{E}= -\partial_{t}\vec{A}(t) = \vec{e}_{0}E_0 \cos(\Omega t)$.
@@
 
-Within the remainder of this paper we choose our units so that  $\hbar = k_{\text{B}} = a = 1 = -q$, $t^{\ast}=2\sqrt{2}$ ~\footnote{With such choice for $t^{\ast}$ we reproduce the DOS of a 2D layer with $t_{\text{c}}=1$  in order to compare with Ref.~\cite{so.do.18}.}, and $t_r \equiv \frac{t^{\ast}}{2\sqrt{2}}=1$ as unit of energy.
+Within the remainder of this paper we choose our units so that  $\hbar = k_{\text{B}} = a = 1 = -q$, $t^{\ast}=2\sqrt{2}$~\footnote{With such choice for $t^{\ast}$ we reproduce the DOS of a 2D layer with $t_{\text{c}}=1$  in order to compare with Ref.~\cite{so.do.18}.}, and $t_{\text{resc}} \equiv \frac{t^{\ast}}{2\sqrt{2}}=1$ as unit of energy.
 
@@
 
-For completeness, we now
- briefly describe the self-consistent F-DMFT scheme used.
+For completeness, we now briefly describe the self-consistency F-DMFT scheme used.
 (i) We start from an initial guess for the electron SE $\kel{\mat{\Sigma}}(\omega)$ and set $\kel{\mat \Sigma}_{\text{e-ph}}(\omega)=0$. (ii) Then we compute the local electron GF as 
@@
 this Floquet-diagonal self-energy approximation (FDSA) as well. In addition, it turns out that also for the 
- phonon SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ this approximation is justified~\footnote{More specifically, we verified that in the parameters range in which FDSA is justified for the electron SE $\kel{\mat{\Sigma}}(\omega)$ (Sec.~\ref{sec:results}), the off-diagonal terms of the phonon SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ are orders of magnitude smaller than the diagonal ones}.
+ phonon SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ this approximation is justified~\footnote{More specifically, we verified that in the parameter range in which FDSA is justified for the electron SE $\kel{\mat{\Sigma}}(\omega)$ (Sec.~\ref{sec:results}), the off-diagonal terms of the phonon SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ are at least two orders of magnitude smaller than the diagonal ones}.
 Consequently, we  solve a nonequilibrium stationary impurity problem, by considering only the $(0,0)$-Floquet matrix element of all the quantities in Eq.~\eqref{eq:imp_Dyson_eq}.
@@
 The parameters $t_{\text{l/r}}$, $\varepsilon_{\text{l/r}}$, and  $\Gamma_{\text{l/r}}$ are chosen such that the leads' DOS approximately overlaps with the Hubbard bands, i.e.
-they exhibit a \textquoteleft bandwidth\textquoteright~\footnote{Notice that the support of its spectrum is formally infinite.
+they exhibit a \textquoteleft bandwidth\textquoteright~\footnote{Notice that the support of the leads' spectra are formally infinite.
 $W_{\text{b}}$ is the value at which the spectrum gets  suppressed.} $W_{\text{b}}\approx 8$ and are centered at the same position.
@@
  $\Delta_{\text{pg}} \approx 4$.
-All simulations are carried out with the dimensionless factor $\alpha\equiv t_{r}E_0/\Omega^{2}<0.5$ for which the FDSA is justified~\footnote{In Ref.~\cite{so.do.18} the factor is defined as $\alpha=t_{c}E_0/\Omega^{2}$ and $t_{\text{c}}=1$.
-Setting $t_{r}=1$, we define for consistency $\alpha$ as in the main text.}.
+All simulations are carried out with the dimensionless factor $\alpha\equiv t_{\text{resc}}E_0/\Omega^{2}<0.5$ for which the FDSA is justified~\footnote{In Ref.~\cite{so.do.18} the factor is defined as $\alpha=t_{c}E_0/\Omega^{2}$ and $t_{\text{c}}=1$.
+Setting $t_{\text{resc}}=1$, we define for consistency $\alpha$ as in the main text.}.
 Whenever the electron-phonon interaction is included, we take $g=0.8$ and unless stated otherwise $\omega_{\text{ph}}=0.1$.
@@
 \item For $\Omega<\Delta_{\text{pg}}$, 
-we expect a strong suppression of the current~\footnote{The remaining leak current can be either produced by multiple-photon absorption processes, which however, are strongly suppressed, or by the fact that there is no true gap} and
+we expect a strong suppression of the current~\footnote{The remaining leak current originates either from multiple-photon absorption processes
+which are strongly suppressed, or from the absence of a true gap.} and
 we do not expect any current if the DOS of the correlated layer has a true gap.
@@
 Notice that in the energy window $\Delta_{\text{pg}}<\Omega<2\Delta_{\text{pg}}$ the only scattering processes taking place are DEs, while for $2\Delta_{\text{pg}}<\Omega<\Delta_{\text{pg}}+2W_{\text{b}}$, both DE and II can occur.
-This is in contrast to the case of Ref.~\cite{so.do.18}, in which the peculiar ad-hoc narrow leads' bands only allow for II processes in a certain $\Omega$-range.
-For this reason, and due to the fact that the boundaries of these energy ranges are not strict, it is more tricky to disentangle these physical processes in the present case.
+This is in contrast to the case of Ref.~\cite{so.do.18}, in which the ad-hoc narrow leads' bands only allow for II processes in a certain $\Omega$-range.
+For this reason, and due to the fact that the boundaries of these energy ranges are not strict, it is more difficult to disentangle these physical processes in the present case.
 
@@
 Upon inclusion of e-ph scattering, the outlined scheme remains valid except for the fact that  the pseudogap $\Delta_{\text{pg}}$ is slightly modified.
-As shown in Sec.~\ref{sec:E0_2_electrons_phonons}, the phonons broaden the DOS of the correlated layer and slightly fill and shrink the pseudogap.
+As shown in Sec.~\ref{sec:E0_2_electrons_phonons}, the phonons broaden the DOS of the correlated layer, which slightly fills and shrinks the pseudogap.
 
-% \onecolumngrid
 \begin{figure*}[t]
 \includegraphics[width=0.7\textwidth]{./figures_Paper1/j_vs_omega_mu1_v_0.4_0.8_eph.pdf}
-% \captionsetup{width=\textwidth}
 \caption{(Color online) 
- (a) Time-averaged steady-state current $j$ and (b) double occupancy $N_{\text{D}}$ plotted as a function of the driving frequency $\Omega$.
+ (a) Time-averaged steady state current $j$ and (b) double occupancy $N_{\text{D}}$ plotted as a function of the driving frequency $\Omega$.
 Results are shown for different values of the lead-layer hybridization $v$ as well as without and with e-ph interaction.
@@
 \end{figure*}
-% \twocolumngrid
 
@@
 \begin{figure}[b] 
-% \captionsetup{width=\textwidth}   
 \includegraphics[width=\linewidth]{./figures_Paper1/spec_filling_mu1_v_0.4_0.8_O_5_11_e.pdf}
@@
 \begin{figure}[b]  
-% \captionsetup{width=\textwidth} 
 \includegraphics[width=\linewidth]{./figures_Paper1/j_vs_omega_mu1_v_0.8_e_E0_3_4.pdf} 
-\caption{(Color online) (a) Time-averaged steady-state current $j$ and (b) double occupancy $N_{\text{D}}$ as a function of $\Omega$, at $v=0.8$ for $E_0=3,4$ for the EO system.
+\caption{(Color online) (a) Time-averaged steady state current $j$ and (b) double occupancy $N_{\text{D}}$ as a function of $\Omega$, at $v=0.8$ for $E_0=3,4$ for the EO system.
 Default parameters are specified at the beginning of Sec.~\ref{sec:results}.}
@@
 In this range both DE and II can occur in principle.
-The height of the peak is approximately the same for both $v$, despite they differ by a factor of two.
+The height of the peak is approximately the same for both $v$, despite both hybridizations differing by a factor of two.
 The double occupation in this range shows a similar behavior as the current for $v=0.4$ with a peak around $\Omega\approx 11$, while it exhibits a plateau for $v=0.8$.
 For $v=0.4$ the current curve is characterized by a substantial increase in slope around $\Omega \approx 7$, which cannot be observed for $v=0.8$.
-This, together with the comparable magnitude of the current maxima at $\Omega\approx 11$ and the behavior of the double occupation strongly suggests that for $v=0.4$ a substantial rate of II processes take place, while these are absent or negligible for $v=0.8$.
+This, together with the comparable magnitude of the current maxima at $\Omega\approx 11$ and the behavior of the double occupation strongly suggests that for $v=0.4$ a substantial amount of II processes take place, while these are absent or negligible for $v=0.8$.
 Here,  the plateau in $N_{\text{D}}$ for $v=0.8$ suggests that photoexcited electrons arriving in the UHB quickly escape to the right fermionic lead and do not have time to induce II processes.
@@
 
-This behavior is influenced by the  electric field amplitude $E_0$  as illustrated in Fig.~\ref{fig:j_vs_omega_mu1_v_0.8_e_E0_3_4}(a).
-For $E_0=4$ the current develops a sudden increase in slope around $\Omega\approx7$ as well as a pronounced peak around $\Omega\approx 11$ for the larger hybridization $v=0.8$.
-This feature starts developing already at $E_0=3$.
+This behavior is affected by the electric field amplitude $E_0$ as illustrated in Fig.~\ref{fig:j_vs_omega_mu1_v_0.8_e_E0_3_4}(a).
+For $E_0=4$ the current develops a sudden increase in slope around $\Omega\approx7$, as well as a pronounced peak around $\Omega\approx 11$ for the larger hybridization $v=0.8$.
+Both features start developing already at $E_0=3$.
 This tendency, corroborated by the behavior of the double occupation displayed in Fig.~\ref{fig:j_vs_omega_mu1_v_0.8_e_E0_3_4}(b), suggests an  important role of II also for larger values of $v$, provided the field amplitude is strong enough.
@@
 With a smaller pseudogap and more states at its edges, more electrons can be directly excited with a given driving frequency $\Omega$ thereby increasing the photocurrent.
-On the other hand, the suppression of the current by e-ph interaction in the range $7\lesssim\Omega\lesssim14$ is due to the dissipation-induced reduction of spectral weight at frequencies $|\omega| \gtrsim 3.5$, cf.
-Fig.
+On the other hand, the suppression of the current by e-ph interaction in the range $7\lesssim\Omega\lesssim14$ is due to the dissipation-induced reduction of spectral weight at frequencies $|\omega| \gtrsim 3.5$, see Fig.
 \ref{fig:spec_filling_mu1_v_0.4_0.8_O_11_eph}.
@@
 \begin{figure}[b]
-% \captionsetup{width=\textwidth} 
 \includegraphics[width=\linewidth]{./figures_Paper1/spec_filling_mu1_v_0.4_0.8_O_11_eph.pdf}
@@
 \begin{figure}[t] 
-% \captionsetup{width=\textwidth}  
 \includegraphics[width=\linewidth]{./figures_Paper1/j_vs_omega_mu1_v_0.4_0.8_E0_2_sweep_omegaph.pdf}
-\caption{(Color online) (a) Time-averaged steady-state current $j$ and (b) double occupancy $N_{\text{D}}$ as a function of $\Omega$, for $v=0.4, 0.8$, at phonon cutoff frequencies $\omega_{\text{ph}}=0.025, 0.05$.
+\caption{(Color online) (a) Time-averaged steady state current $j$ and (b) double occupancy $N_{\text{D}}$ as a function of $\Omega$, for $v=0.4, 0.8$, at phonon cutoff frequencies $\omega_{\text{ph}}=0.025, 0.05$.
 Default parameters are specified at the beginning of Sec.~\ref{sec:results}.}
@@
 This behavior is qualitatively valid for different values of the soft cutoff phonon frequency
- $\omega_{\text{ph}}$. This can be seen in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_E0_2_sweep_omegaph}, which shows that the impact of acoustic phonons on 
+ $\omega_{\text{ph}}$. It can be seen in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_E0_2_sweep_omegaph}, which shows that the impact of acoustic phonons on 
 current and double occupation is slightly boosted when decreasing $\omega_{\text{ph}}$~\footnote{Reducing $\omega_{\text{ph}}$ has two effects.
-First, the phonon spectral function $A_{\text{ph}}(\omega)$ exhibits more weight at low frequencies $\omega\approx\omega_{\text{ph}}$.
+First, the phonon spectral function $A_{\text{ph}}(\omega)$ exhibits more weight at low frequencies around $\omega\approx\omega_{\text{ph}}$.
 Second, it restricts the maximum value of the reciprocal lattice vector $\vec{q}_{\text{max}}$ via $\omega_{\text{ph}}=\omega(\vec{q}_{\text{max}})$~\cite{ma.ga.22u}, meaning that short-wavelength phonons are suppressed.}.
 
-\begin{figure}[t] 
-% \captionsetup{width=\textwidth} 
+\begin{figure}[b] 
 \includegraphics[width=\linewidth]{./figures_Paper1/j_vs_omega_mu1_sweep_v_E0_2_eph.pdf}
-\caption{(Color online) (a) Time-averaged steady-state current $j$ and (b) double occupancy $N_{\text{D}}$ as a function of $\Omega$, for $v=0.5,0.6,0.7$, without and with e-ph interaction.
+\caption{(Color online) (a) Time-averaged steady state current $j$ and (b) double occupancy $N_{\text{D}}$ as a function of $\Omega$, for $v=0.5,0.6,0.7$, without and with e-ph interaction.
 Default parameters are specified at the beginning of Sec.~\ref{sec:results}.}
@@
 
-The results above suggest that the influence of acoustic phonons on the electronic scattering processes does not depend significantly on $v$, i.e.
-on whether II processes are significant or not.
-In other words, the effect of phonons doesn't depend significantly on the rate at which carriers are injected into and removed from the layer.
+The results above suggest that the influence of acoustic phonons on the electronic scattering processes does not depend significantly on $v$.
+In other words, the effect of phonons does not depend significantly on the rate at which carriers are injected into and removed from the layer.
 Fig.~\ref{fig:j_vs_omega_mu1_sweep_v_E0_2_eph} confirms this behavior for intermediate lead-layer hybridizations $v=0.5,0.6,0.7$.
@@
 of the coupling to the leads on the scattering process occurring at different driving frequencies and observed how the dissipation by acoustic phonons influences the photocurrent and the double occupation.
-We found evidence of a significant rate of II processes leading to a photocurrent peak at small hybridizations, while these are suppressed  for larger hybridizations.
+We found evidence of a significant amount of II processes leading to a photocurrent peak at small hybridizations, while these are suppressed  for larger hybridizations.
 Dissipation via acoustic phonons slightly boosts the photocurrent for small driving frequencies and suppresses it at larger ones in the vicinity of the main peak.
@@
 
-Experimentally, the electric field amplitude considered in this paper~\footnote{We don't consider smaller electric field amplitudes $E_0$ since DMFT only converges slowly for such a choice of parameters.} is several orders of magnitude larger than that of the sunlight, therefore these results are more relevant for photoexcitations produced by intense laser pulses (see also the discussion in ~\cite{mu.we.18}) rather than for true photovoltaic systems.
-On the other hand, one may try to qualitatively extrapolate the discussion at the end of Sec.~\ref{sec:E0_2_only_electrons} in the other direction,  namely to smaller electric field amplitudes, for which a smaller hybridization would be necessary in order to sustain II.
+Experimentally, the electric field amplitude considered in this paper~\footnote{We don't consider smaller electric field amplitudes $E_0$ since DMFT only converges slowly for such a choice of parameters.} is several orders of magnitude larger than that of the sunlight, therefore our results are more relevant for photoexcitations produced by intense laser pulses (see also the discussion in~\cite{mu.we.18}) rather than for true photovoltaic systems.
+On the other hand, one may try to qualitatively extrapolate the discussion at the end of Sec.~\ref{sec:E0_2_only_electrons} in the other direction to smaller electric field amplitudes, for which a smaller hybridization would be necessary in order to sustain II.
 In a more realistic setup modelling oxide heterostructures~\cite{as.bl.13,pe.be.19}, a regime of effectively small hybridization would be achieved by considering several layers in which photoexcited carriers, separated by an electric field gradient, have more time to induce II processes before escaping into the leads.
-In order to address the occurrence of II in such setup, also further extensions should be taken into account, such as the inclusion of multiorbital correlated systems as well as impurity scattering.
-Such topics would be interesting for future studies.
+To address the occurrence of II in such a setup, further extensions such as considering multiple orbitals and impurity scattering should be taken into account.
+These would be interesting for future studies.
 
@@
 
-\bibliographystyle{prsty}   
-% references in Phys Rev style
+\bibliographystyle{prsty}   % references in Phys Rev style
 \bibliography{references_database}
 
-% \bibliographystyle{/afs/itp.tugraz.at/user/arrigoni/noneq-group/bibtex/prsty} 
-%\bibliography{New_References,/afs/itp.tugraz.at/user/arrigoni/noneq-group/bibtex/references_database.bib}
-% \bibliography{Additional_Refs.bib,references_database.bib}
-%\bibliography{New_References,references_database.bib}
-
 \end{document}

### 2022-08-30 Paper1.tex
Changed figures and quick typos fixing

@@
 this Floquet-diagonal self-energy approximation (FDSA) as well. In addition, it turns out that also for the 
- phonon SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ this approximation is justified~\footnote{More specifically, we verified that in the parameter range in which FDSA is justified for the electron SE $\kel{\mat{\Sigma}}(\omega)$ (Sec.~\ref{sec:results}), the off-diagonal terms of the phonon SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ are at least two orders of magnitude smaller than the diagonal ones}.
+ phonon SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ this approximation is justified~\footnote{More specifically, we verified that in the parameter range in which FDSA is justified for the electron SE $\kel{\mat{\Sigma}}(\omega)$ (Sec.~\ref{sec:results}), the off-diagonal terms of the phonon SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ are sufficiently suppressed with respect to the diagonal ones}.
 Consequently, we  solve a nonequilibrium stationary impurity problem, by considering only the $(0,0)$-Floquet matrix element of all the quantities in Eq.~\eqref{eq:imp_Dyson_eq}.
@@
 
-We start with the case without e-ph interaction and address the behavior of the physical quantities as functions of $\Omega$ for different values of the lead-layer hybridization.
+We set off by analyzing the case without e-ph interaction and address the behavior of the physical quantities as functions of $\Omega$ for different values of the lead-layer hybridization.
 
@@
 In this range both DE and II can occur in principle.
-The height of the peak is approximately the same for both $v$, despite both hybridizations differing by a factor of two.
+The height of the peak is approximately the same for both $v$, despite the hybridizations differ by a factor of two.
 The double occupation in this range shows a similar behavior as the current for $v=0.4$ with a peak around $\Omega\approx 11$, while it exhibits a plateau for $v=0.8$.
@@
 
-We now discuss the effect of coupling to acoustic phonons on these results.
+We now discuss the effect of coupling to acoustic phonons on the results presented thus far.
 
@@
 However the current magnitude is suppressed, especially around the peak.
-For $\Omega\gtrsim14$ the current with phonons goes down as for the EO case.
+For $\Omega\gtrsim14$ the current in presence of phonons drops as for the EO case.
 
@@
 The spectral and occupation functions  shown in Fig.~\ref{fig:spec_filling_mu1_v_0.4_0.8_O_11_eph} display a redistribution of spectral weight from the peaks towards the edges of the bands, thus reducing the pseudogap.
-Consequently, the occupation of positive energy states is slightly shifted to the bottom of the UHB compared to the EO case, as the occupation function shows.
+Consequently, the occupation of positive energy states is slightly shifted to the bottom of the UHB compared to the EO case, as evidenced by the occupation function.
  The spectral function in presence of phonons is  broadened and tends to fill the pseudogap $\Delta_{\text{pg}}$ as anticipated in Sec.~\ref{sec:scheme_electrons_phonons}.
@@
 
-\section*{Acknowledgements}
+\acknowledgments
 

### 2022-08-30 figures_Paper1/spec_filling_mu1_v_0.4_0.8_O_11_eph.tex
Last version paper 30.08.2022
Changed figures and quick typos fixing

@@
 \usepackage{tikz-3dplot} % 3D coordinate frames
-\usepackage{gnuplot-lua-tikz}
+%\usepackage{gnuplot-lua-tikz}                                % macOS does not like it -> restore if commenting it out gives you troubles
 \usepgfplotslibrary{fillbetween}
@@
 \pgfsetlayers{background,main,foreground}
+\pgfplotsset{tick scale binop=\times}
 
@@
 ytick={0.00,0.03,0.06,0.09},
-% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012},
-% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012,\smash{\raisebox{-0.8\height}{5}}},
+yticklabels={\smash{\raisebox{0.1\height}{0}},3,6,\smash{\raisebox{-0.8\height}{9}}},
 x tick label style={
@@
 
-\addlegendimage{solid,color=hblue,scale={1.0},line width=1pt}
-\addlegendentry{el};
-\addlegendimage{solid,color=hred,scale={1.0},line width=1pt} 
-\addlegendentry{el+ph};
+%\addlegendimage{solid,color=hblue,scale={1.0},line width=1pt}
+%\addlegendentry{el};
+%\addlegendimage{solid,color=hred,scale={1.0},line width=1pt} 
+%\addlegendentry{el+ph};
 
@@
 
-\addplot[solid,raw gnuplot,color=hblue,line width=1pt] gnuplot {
+\addplot[solid,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
 plot './Green_hyb0.4O11.dat' u 1:(-1/3.1415)*($3) w l;
@@
 
-\addplot[name path=neq_distr_f_filling_hyb0.4O11,solid,raw gnuplot,color=hblue,line width=1pt,opacity=0.0] gnuplot {
+\addplot[name path=neq_distr_f_filling_hyb0.4O11,solid,raw gnuplot,color=hcoral,line width=1pt,opacity=0.0] gnuplot {
 plot './neq_distr_f_filling_hyb0.4O11.dat' u 1:3 w l;
@@
 
-\addplot[solid,raw gnuplot,color=hred,line width=1pt] gnuplot {
+\addplot[solid,raw gnuplot,color=hlime,line width=1pt] gnuplot {
 plot './Green_hyb0.4O11ph.dat' u 1:(-1/3.1415)*($3) w l;
@@
 
-\addplot[name path=neq_distr_f_filling_hyb0.4O11ph,solid,raw gnuplot,color=hred,line width=1pt,opacity=0.0] gnuplot {
+\addplot[name path=neq_distr_f_filling_hyb0.4O11ph,solid,raw gnuplot,color=hlime,line width=1pt,opacity=0.0] gnuplot {
 plot './neq_distr_f_filling_hyb0.4O11ph.dat' u 1:3 w l;
@@
 \path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
-\addplot [fill=hblue,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11 and xaxis,soft clip={domain=-15:15}];
-\addplot [fill=hred,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11ph and xaxis,soft clip={domain=-15:15}];
+\addplot [fill=hcoral,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11 and xaxis,soft clip={domain=-15:15}];
+\addplot [fill=hlime,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11ph and xaxis,soft clip={domain=-15:15}];
 
  \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(a)};
- \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$v=0.4$};
+ \node[draw,fill=white,scale=1.0] at (axis cs:11.25,0.085) {$v=0.4$};
 
@@
 % ylabel={$A(\omega)/t^{*-1}$},
-legend style={at={(axis cs:-9.3,0.018)},anchor=north,mark options={scale=0.85},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
+legend style={at={(axis cs:-16.0,0.06)},anchor=north,mark options={scale=0.85},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
 legend cell align=left,
@@
  \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(b)};
- \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$v=0.8$};
+ \node[draw,fill=white,scale=1.0] at (axis cs:11.25,0.085) {$v=0.8$};
 

### 2022-08-30 figures_Paper1/spec_filling_mu1_v_0.4_0.8_O_5_11_e.tex
Last version paper 30.08.2022
Changed figures and quick typos fixing

@@
 \usepackage{tikz-3dplot} % 3D coordinate frames
-\usepackage{gnuplot-lua-tikz}
+%\usepackage{gnuplot-lua-tikz}                     % macOS does not like it -> restore if you need it
 \usepgfplotslibrary{fillbetween}
@@
 legend style={at={(axis cs:-8.8,0.017)},anchor=north,mark options={scale=1.0},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
+legend cell align=left,
+clip mode=individual,
+clip marker paths=true, 
+xtick={-15,-10,-5,0,5,10,15},
+ytick={0.00,0.03,0.06,0.09},
+ yticklabels={\smash{\raisebox{0.1\height}{0}},3,6,\smash{\raisebox{-0.8\height}{9}}},
+x tick label style={
+    /pgf/number format/.cd,
+    fixed,
+    fixed zerofill,
+    precision=0,
+    /tikz/.cd},
+y tick label style={
+    /pgf/number format/.cd,
+    fixed,
+    fixed zerofill,
+    precision=0, 
+    /tikz/.cd}
+]
+
+%\addlegendimage{solid,color=hcoral,scale={1.0},line width=1pt}
+%\addlegendentry{$v=0.4$};
+%\addlegendimage{solid,color=hlime,scale={1.0},line width=1pt} 
+%\addlegendentry{$v=0.8$};
+
+% \addplot +[dashed,very thin,color=hblue,mark=none] coordinates {(-2.55, 0.0) (-2.55, 0.035)};
+% \addplot +[dashed,very thin,color=hblue,mark=none] coordinates {(0.525, 0.0) (0.525, 0.035)};
+% \draw [stealth-stealth,thick,color=hblue](-2.55, 0.015) -- (0.525, 0.015);
+
+% \addplot +[dashed,very thin,color=hred,mark=none] coordinates {(2.55, 0.0) (2.55, 0.035)};
+% \addplot +[dashed,very thin,color=hred,mark=none] coordinates {(-0.525, 0.0) (-0.525, 0.035)};
+% \draw [stealth-stealth,thick,color=hred](2.55, 0.02) -- (-0.525, 0.02);
+
+% \draw [-stealth,thick,color=hgray](0.35, 0.0055) -- (0.45, 0.004);
+% \draw [-stealth,thick,color=hgray](-0.35, 0.0055) -- (-0.45, 0.004);
+
+% \draw [-stealth,thick,color=hgray](2.0, 0.0045) -- (2.2, 0.003);
+% \draw [-stealth,thick,color=hgray](-2.0, 0.0045) -- (-2.2, 0.003);
+
+% % % % % % % %  PLOTS
+
+% \draw (axis cs:4,0) -- (axis cs:10,0.01);
+
+\addplot[solid,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
+plot './Green_hyb0.4O5.dat' u 1:(-1/3.1415)*($3) w l;
+};
+
+\addplot[name path=neq_distr_f_filling_hyb0.4O5,solid,raw gnuplot,color=hcoral,line width=1pt,opacity=0.0] gnuplot {
+plot "neq_distr_f_filling_hyb0.4O5.dat" u 1:3 w l;
+};
+
+\addplot[solid,raw gnuplot,color=hlime,line width=1pt] gnuplot {
+plot './Green_hyb0.8O5.dat' u 1:(-1/3.1415)*($3) w l;
+};
+
+\addplot[name path=neq_distr_f_filling_hyb0.8O5,solid,raw gnuplot,color=hlime,line width=1pt,opacity=0.0] gnuplot {
+plot "neq_distr_f_filling_hyb0.8O5.dat" u 1:3 w l;
+};
+
+\path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
+\addplot [fill=hcoral,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O5 and xaxis,soft clip={domain=-15:15}];
+\addplot [fill=hlime,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O5 and xaxis,soft clip={domain=-15:15}];
+
+% \node[fill=none,color=hblue,scale={1.0}] at (axis cs:-1.20,0.017){$F$}; 
+% \node[fill=none,color=hred,scale={1.0}] at (axis cs:1.20,0.022){$F$};
+ \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(a)};
+ \node[draw,fill=white,scale=1.0] at (axis cs:11.25,0.085) {$\Omega=5$};
+
+% 2° figure
+
+\nextgroupplot[
+xmin=-15.,     
+xmax=15., 
+ymin=0.00, 
+ymax=0.09,   
+minor tick num=1, 
+grid=both,
+xlabel={$\omega$},
+% ylabel={$A(\omega)/t^{*-1}$},
+legend style={at={(axis cs:-22.0,0.034)},anchor=west,mark options={scale=1.0},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
 legend cell align=left,
@@
 \addplot[solid,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
-plot './Green_hyb0.4O5.dat' u 1:(-1/3.1415)*($3) w l;
+plot './Green_hyb0.4O11.dat' u 1:(-1/3.1415)*($3) w l;
 };
 
-\addplot[name path=neq_distr_f_filling_hyb0.4O5,solid,raw gnuplot,color=hcoral,line width=1pt,opacity=0.0] gnuplot {
-plot "neq_distr_f_filling_hyb0.4O5.dat" u 1:3 w l;
+\addplot[name path=neq_distr_f_filling_hyb0.4O11,solid,raw gnuplot,color=hcoral,line width=1pt,opacity=0.0] gnuplot {
+plot "neq_distr_f_filling_hyb0.4O11.dat" u 1:3 w l;
 };
@@
 \addplot[solid,raw gnuplot,color=hlime,line width=1pt] gnuplot {
-plot './Green_hyb0.8O5.dat' u 1:(-1/3.1415)*($3) w l;
-};
-
-\addplot[name path=neq_distr_f_filling_hyb0.8O5,solid,raw gnuplot,color=hlime,line width=1pt,opacity=0.0] gnuplot {
-plot "neq_distr_f_filling_hyb0.8O5.dat" u 1:3 w l;
-};
-
-\path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
-\addplot [fill=hcoral,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O5 and xaxis,soft clip={domain=-15:15}];
-\addplot [fill=hlime,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O5 and xaxis,soft clip={domain=-15:15}];
-
-% \node[fill=none,color=hblue,scale={1.0}] at (axis cs:-1.20,0.017){$F$}; 
-% \node[fill=none,color=hred,scale={1.0}] at (axis cs:1.20,0.022){$F$};
- \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(a)};
- \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$\Omega=5$};
-
-% 2° figure
-
-\nextgroupplot[
-xmin=-15.,     
-xmax=15., 
-ymin=0.00, 
-ymax=0.09,   
-minor tick num=1, 
-grid=both,
-xlabel={$\omega$},
-% ylabel={$A(\omega)/t^{*-1}$},
-legend style={at={(axis cs:-8.8,0.017)},anchor=north,mark options={scale=1.0},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
-legend cell align=left,
-clip mode=individual,
-clip marker paths=true, 
-xtick={-15,-10,-5,0,5,10,15},
-ytick={0.00,0.03,0.06,0.09},
-% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012},
-% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012,\smash{\raisebox{-0.8\height}{5}}},
-x tick label style={
-    /pgf/number format/.cd,
-    fixed,
-    fixed zerofill,
-    precision=0,
-    /tikz/.cd},
-y tick label style={
-    /pgf/number format/.cd,
-    fixed,
-    fixed zerofill,
-    precision=0,
-    /tikz/.cd}
-]
-
-\addlegendimage{solid,color=hblue,scale={1.0},line width=1pt}
-\addlegendentry{$v=0.4$};
-\addlegendimage{solid,color=hred,scale={1.0},line width=1pt} 
-\addlegendentry{$v=0.8$};
-
-% \addplot +[dashed,very thin,color=hblue,mark=none] coordinates {(-2.55, 0.0) (-2.55, 0.035)};
-% \addplot +[dashed,very thin,color=hblue,mark=none] coordinates {(0.525, 0.0) (0.525, 0.035)};
-% \draw [stealth-stealth,thick,color=hblue](-2.55, 0.015) -- (0.525, 0.015);
-
-% \addplot +[dashed,very thin,color=hred,mark=none] coordinates {(2.55, 0.0) (2.55, 0.035)};
-% \addplot +[dashed,very thin,color=hred,mark=none] coordinates {(-0.525, 0.0) (-0.525, 0.035)};
-% \draw [stealth-stealth,thick,color=hred](2.55, 0.02) -- (-0.525, 0.02);
-
-% \draw [-stealth,thick,color=hgray](0.35, 0.0055) -- (0.45, 0.004);
-% \draw [-stealth,thick,color=hgray](-0.35, 0.0055) -- (-0.45, 0.004);
-
-% \draw [-stealth,thick,color=hgray](2.0, 0.0045) -- (2.2, 0.003);
-% \draw [-stealth,thick,color=hgray](-2.0, 0.0045) -- (-2.2, 0.003);
-
-% % % % % % % %  PLOTS
-
-% \draw (axis cs:4,0) -- (axis cs:10,0.01);
-
-\addplot[solid,raw gnuplot,color=hblue,line width=1pt] gnuplot {
-plot './Green_hyb0.4O11.dat' u 1:(-1/3.1415)*($3) w l;
-};
-
-\addplot[name path=neq_distr_f_filling_hyb0.4O11,solid,raw gnuplot,color=hblue,line width=1pt,opacity=0.0] gnuplot {
-plot "neq_distr_f_filling_hyb0.4O11.dat" u 1:3 w l;
-};
-
-\addplot[solid,raw gnuplot,color=hred,line width=1pt] gnuplot {
 plot './Green_hyb0.8O11.dat' u 1:(-1/3.1415)*($3) w l;
@@
 
-\addplot[name path=neq_distr_f_filling_hyb0.8O11,solid,raw gnuplot,color=hred,line width=1pt,opacity=0.0] gnuplot {
+\addplot[name path=neq_distr_f_filling_hyb0.8O11,solid,raw gnuplot,color=hlime,line width=1pt,opacity=0.0] gnuplot {
 plot "neq_distr_f_filling_hyb0.8O11.dat" u 1:3 w l;
@@
 \path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
-\addplot [fill=hblue,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11 and xaxis,soft clip={domain=-15:15}];
-\addplot [fill=hred,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O11 and xaxis,soft clip={domain=-15:15}];
+\addplot [fill=hcoral,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11 and xaxis,soft clip={domain=-15:15}];
+\addplot [fill=hlime,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O11 and xaxis,soft clip={domain=-15:15}];
 
@@
  \node[fill=none,scale=1.0] at (axis cs:-13.5,0.085) {\bfseries(b)};
- \node[fill=none,scale=1.0] at (axis cs:11.5,0.085) {$\Omega=11$};
+ \node[draw,fill=white,scale=1.0] at (axis cs:11.25,0.085) {$\Omega=11$};
 

### 2022-08-31 Paper1.tex
Final version paper 31.08.2022

@@
 % 
-(iii) Using Eq.~\eqref{eq:backbone_e-ph_SE}, we obtain the phonon contribution to the SE $\kel{\mat{\Sigma}}_{\text{e-ph}}(\omega)$.
+(iii) Using Eq.~\eqref{eq:backbone_e-ph_SE}, we obtain the phonon contribution to the e-ph SE $\kel{\mat{\Sigma}}_{\text{e-ph}}(\omega)$.
 (iv) The problem is mapped onto a single impurity plus bath, whose hybridization function
@@
 We follow this argument and adopt here
-this Floquet-diagonal self-energy approximation (FDSA) as well. In addition, it turns out that also for the 
- phonon SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ this approximation is justified~\footnote{More specifically, we verified that in the parameter range in which FDSA is justified for the electron SE $\kel{\mat{\Sigma}}(\omega)$ (Sec.~\ref{sec:results}), the off-diagonal terms of the phonon SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ are sufficiently suppressed with respect to the diagonal ones}.
+this Floquet-diagonal self-energy approximation (FDSA) as well.
+In addition, it turns out that also for the e-ph SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ this approximation is justified~\footnote{More specifically, we verified that in the parameter range in which FDSA is justified for the electron SE $\kel{\mat{\Sigma}}(\omega)$ (Sec.~\ref{sec:results}), the off-diagonal terms of the e-ph SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ are sufficiently suppressed}.
 Consequently, we  solve a nonequilibrium stationary impurity problem, by considering only the $(0,0)$-Floquet matrix element of all the quantities in Eq.~\eqref{eq:imp_Dyson_eq}.
@@
 
-We set off by analyzing the case without e-ph interaction and address the behavior of the physical quantities as functions of $\Omega$ for different values of the lead-layer hybridization.
+We start by analyzing the case without e-ph interaction and address the behavior of the physical quantities as functions of $\Omega$ for different values of the lead-layer hybridization.
 
-In Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(a), the photocurrent $j$ increases as a function of the driving frequency $\Omega$ within the range $4\lesssim\Omega\lesssim8$ independent of the value of $v$.
+In Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(a), the photocurrent $j$ increases as a function of the driving frequency $\Omega$ within the range $4\lesssim\Omega\lesssim8$.
 According to the discussion in Sec.~\ref{sec:scheme_only_electrons} (cf.

### 2022-08-31 figures_Paper1/spec_filling_mu1_v_0.4_0.8_O_11_eph.tex
Final version paper 31.08.2022

@@
 
-\addplot[solid,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
+\addplot[solid,raw gnuplot,color=hblue,line width=1pt] gnuplot {
 plot './Green_hyb0.4O11.dat' u 1:(-1/3.1415)*($3) w l;
@@
 
-\addplot[name path=neq_distr_f_filling_hyb0.4O11,solid,raw gnuplot,color=hcoral,line width=1pt,opacity=0.0] gnuplot {
+\addplot[name path=neq_distr_f_filling_hyb0.4O11,solid,raw gnuplot,color=hblue,line width=1pt,opacity=0.0] gnuplot {
 plot './neq_distr_f_filling_hyb0.4O11.dat' u 1:3 w l;
@@
 
-\addplot[solid,raw gnuplot,color=hlime,line width=1pt] gnuplot {
+\addplot[solid,raw gnuplot,color=hred,line width=1pt] gnuplot {
 plot './Green_hyb0.4O11ph.dat' u 1:(-1/3.1415)*($3) w l;
@@
 
-\addplot[name path=neq_distr_f_filling_hyb0.4O11ph,solid,raw gnuplot,color=hlime,line width=1pt,opacity=0.0] gnuplot {
+\addplot[name path=neq_distr_f_filling_hyb0.4O11ph,solid,raw gnuplot,color=hred,line width=1pt,opacity=0.0] gnuplot {
 plot './neq_distr_f_filling_hyb0.4O11ph.dat' u 1:3 w l;
@@
 \path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
-\addplot [fill=hcoral,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11 and xaxis,soft clip={domain=-15:15}];
-\addplot [fill=hlime,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11ph and xaxis,soft clip={domain=-15:15}];
+\addplot [fill=hblue,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11 and xaxis,soft clip={domain=-15:15}];
+\addplot [fill=hred,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11ph and xaxis,soft clip={domain=-15:15}];
 
@@
 
-\addlegendimage{solid,color=hcoral,scale={1.0},line width=1pt}
+\addlegendimage{solid,color=hblue,scale={1.0},line width=1pt}
 \addlegendentry{el};
-\addlegendimage{solid,color=hlime,scale={1.0},line width=1pt} 
+\addlegendimage{solid,color=hred,scale={1.0},line width=1pt} 
 \addlegendentry{el+ph};
@@
 
-\addplot[solid,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
+\addplot[solid,raw gnuplot,color=hblue,line width=1pt] gnuplot {
 plot './Green_hyb0.8O11.dat' u 1:(-1/3.1415)*($3) w l;
@@
 
-\addplot[name path=neq_distr_f_filling_hyb0.8O11,solid,raw gnuplot,color=hcoral,line width=1pt,opacity=0.0] gnuplot {
+\addplot[name path=neq_distr_f_filling_hyb0.8O11,solid,raw gnuplot,color=hblue,line width=1pt,opacity=0.0] gnuplot {
 plot './neq_distr_f_filling_hyb0.8O11.dat' u 1:3 w l;
@@
 
-\addplot[solid,raw gnuplot,color=hlime,line width=1pt] gnuplot {
+\addplot[solid,raw gnuplot,color=hred,line width=1pt] gnuplot {
 plot './Green_hyb0.8O11ph.dat' u 1:(-1/3.1415)*($3) w l;
@@
 
-\addplot[name path=neq_distr_f_filling_hyb0.8O11ph,solid,raw gnuplot,color=hlime,line width=1pt,opacity=0.0] gnuplot {
+\addplot[name path=neq_distr_f_filling_hyb0.8O11ph,solid,raw gnuplot,color=hred,line width=1pt,opacity=0.0] gnuplot {
 plot './neq_distr_f_filling_hyb0.8O11ph.dat' u 1:3 w l;
@@
 \path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
-\addplot [fill=hcoral,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O11 and xaxis,soft clip={domain=-15:15}];
-\addplot [fill=hlime,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O11ph and xaxis,soft clip={domain=-15:15}];
+\addplot [fill=hblue,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O11 and xaxis,soft clip={domain=-15:15}];
+\addplot [fill=hred,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O11ph and xaxis,soft clip={domain=-15:15}];
 

### 2022-08-31 figures_Paper1/spec_filling_mu1_v_0.4_0.8_O_5_11_e.tex
Final version paper 31.08.2022

@@
 
-%\addlegendimage{solid,color=hcoral,scale={1.0},line width=1pt}
+%\addlegendimage{solid,color=hblue,scale={1.0},line width=1pt}
 %\addlegendentry{$v=0.4$};
-%\addlegendimage{solid,color=hlime,scale={1.0},line width=1pt} 
+%\addlegendimage{solid,color=hred,scale={1.0},line width=1pt} 
 %\addlegendentry{$v=0.8$};
@@
 
-\addplot[name path=neq_distr_f_filling_hyb0.4O5,solid,raw gnuplot,color=hcoral,line width=1pt,opacity=0.0] gnuplot {
+\addplot[name path=neq_distr_f_filling_hyb0.4O5,solid,raw gnuplot,color=hblue,line width=1pt,opacity=0.0] gnuplot {
 plot "neq_distr_f_filling_hyb0.4O5.dat" u 1:3 w l;
@@
 
-\addplot[solid,raw gnuplot,color=hlime,line width=1pt] gnuplot {
+\addplot[solid,raw gnuplot,color=hred,line width=1pt] gnuplot {
 plot './Green_hyb0.8O5.dat' u 1:(-1/3.1415)*($3) w l;
@@
 
-\addplot[name path=neq_distr_f_filling_hyb0.8O5,solid,raw gnuplot,color=hlime,line width=1pt,opacity=0.0] gnuplot {
+\addplot[name path=neq_distr_f_filling_hyb0.8O5,solid,raw gnuplot,color=hred,line width=1pt,opacity=0.0] gnuplot {
 plot "neq_distr_f_filling_hyb0.8O5.dat" u 1:3 w l;
@@
 \path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
-\addplot [fill=hcoral,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O5 and xaxis,soft clip={domain=-15:15}];
-\addplot [fill=hlime,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O5 and xaxis,soft clip={domain=-15:15}];
+\addplot [fill=hblue,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O5 and xaxis,soft clip={domain=-15:15}];
+\addplot [fill=hred,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O5 and xaxis,soft clip={domain=-15:15}];
 
@@
 
-\addlegendimage{solid,color=hcoral,scale={1.0},line width=1pt}
+\addlegendimage{solid,color=hblue,scale={1.0},line width=1pt}
 \addlegendentry{$v=0.4$};
-\addlegendimage{solid,color=hlime,scale={1.0},line width=1pt} 
+\addlegendimage{solid,color=hred,scale={1.0},line width=1pt} 
 \addlegendentry{$v=0.8$};
@@
 
-\addplot[name path=neq_distr_f_filling_hyb0.4O11,solid,raw gnuplot,color=hcoral,line width=1pt,opacity=0.0] gnuplot {
+\addplot[name path=neq_distr_f_filling_hyb0.4O11,solid,raw gnuplot,color=hblue,line width=1pt,opacity=0.0] gnuplot {
 plot "neq_distr_f_filling_hyb0.4O11.dat" u 1:3 w l;
@@
 
-\addplot[solid,raw gnuplot,color=hlime,line width=1pt] gnuplot {
+\addplot[solid,raw gnuplot,color=hred,line width=1pt] gnuplot {
 plot './Green_hyb0.8O11.dat' u 1:(-1/3.1415)*($3) w l;
@@
 
-\addplot[name path=neq_distr_f_filling_hyb0.8O11,solid,raw gnuplot,color=hlime,line width=1pt,opacity=0.0] gnuplot {
+\addplot[name path=neq_distr_f_filling_hyb0.8O11,solid,raw gnuplot,color=hred,line width=1pt,opacity=0.0] gnuplot {
 plot "neq_distr_f_filling_hyb0.8O11.dat" u 1:3 w l;
@@
 \path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
-\addplot [fill=hcoral,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11 and xaxis,soft clip={domain=-15:15}];
-\addplot [fill=hlime,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O11 and xaxis,soft clip={domain=-15:15}];
+\addplot [fill=hblue,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11 and xaxis,soft clip={domain=-15:15}];
+\addplot [fill=hred,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O11 and xaxis,soft clip={domain=-15:15}];
 

### 2022-08-31 sub_arXiv/Paper1.tex
Added arXiv submission

--- 2022-08-31 Paper1.tex
@@
 \begin{figure}[b] 
-\includegraphics[width=0.9\linewidth]{./figures_Paper1/setup_voltmeter.pdf}
+\includegraphics[width=0.9\linewidth]{setup_voltmeter.pdf}
 \caption{(Color online) Schematic representation of the setup.
@@
 
-\includegraphics[width=0.8\linewidth]{./figures_Paper1/energy_setup.pdf}
+\includegraphics[width=0.8\linewidth]{energy_setup.pdf}
 \caption{(Color online) Schematic representation of the processes occuring in the model considered.
@@
 \begin{figure*}[t]
-\includegraphics[width=0.7\textwidth]{./figures_Paper1/j_vs_omega_mu1_v_0.4_0.8_eph.pdf}
+\includegraphics[width=0.7\textwidth]{j_vs_omega_mu1_v_0.4_0.8_eph.pdf}
 \caption{(Color online) 
@@
 \begin{figure}[b] 
-\includegraphics[width=\linewidth]{./figures_Paper1/spec_filling_mu1_v_0.4_0.8_O_5_11_e.pdf}
+\includegraphics[width=\linewidth]{spec_filling_mu1_v_0.4_0.8_O_5_11_e.pdf}
 \caption{(Color online) Spectral function $A(\omega)$ (solid line) and occupation function $N(\omega)$ (shaded area) at (a) $\Omega=5$ and (b) $\Omega=11$ for $v=0.4$ and $0.8$ for the EO system.
@@
 \begin{figure}[b]  
-\includegraphics[width=\linewidth]{./figures_Paper1/j_vs_omega_mu1_v_0.8_e_E0_3_4.pdf} 
+\includegraphics[width=\linewidth]{j_vs_omega_mu1_v_0.8_e_E0_3_4.pdf} 
 \caption{(Color online) (a) Time-averaged steady state current $j$ and (b) double occupancy $N_{\text{D}}$ as a function of $\Omega$, at $v=0.8$ for $E_0=3,4$ for the EO system.
@@
 \begin{figure}[b]
-\includegraphics[width=\linewidth]{./figures_Paper1/spec_filling_mu1_v_0.4_0.8_O_11_eph.pdf}
+\includegraphics[width=\linewidth]{spec_filling_mu1_v_0.4_0.8_O_11_eph.pdf}
 \caption{(Color online) Spectral function $A(\omega)$ (solid line) and occupation function $N(\omega)$ (shaded area) at $\Omega=11$ without and with e-ph interaction, for (a) $v=0.4$ and (b) $v=0.8$.
@@
 \begin{figure}[t] 
-\includegraphics[width=\linewidth]{./figures_Paper1/j_vs_omega_mu1_v_0.4_0.8_E0_2_sweep_omegaph.pdf}
+\includegraphics[width=\linewidth]{j_vs_omega_mu1_v_0.4_0.8_E0_2_sweep_omegaph.pdf}
 \caption{(Color online) (a) Time-averaged steady state current $j$ and (b) double occupancy $N_{\text{D}}$ as a function of $\Omega$, for $v=0.4, 0.8$, at phonon cutoff frequencies $\omega_{\text{ph}}=0.025, 0.05$.
@@
 \begin{figure}[b] 
-\includegraphics[width=\linewidth]{./figures_Paper1/j_vs_omega_mu1_sweep_v_E0_2_eph.pdf}
+\includegraphics[width=\linewidth]{j_vs_omega_mu1_sweep_v_E0_2_eph.pdf}
 \caption{(Color online) (a) Time-averaged steady state current $j$ and (b) double occupancy $N_{\text{D}}$ as a function of $\Omega$, for $v=0.5,0.6,0.7$, without and with e-ph interaction.

### 2022-09-07 sub_PRB/Paper1.tex
submission PRB

--- 2022-08-31 sub_arXiv/Paper1.tex
@@
 \begin{figure}[b] 
-\includegraphics[width=0.9\linewidth]{setup_voltmeter.pdf}
+\includegraphics[width=0.9\linewidth]{Fig1.pdf}
 \caption{(Color online) Schematic representation of the setup.
@@
 
-\includegraphics[width=0.8\linewidth]{energy_setup.pdf}
+\includegraphics[width=0.8\linewidth]{Fig2.pdf}
 \caption{(Color online) Schematic representation of the processes occuring in the model considered.
@@
 \begin{figure*}[t]
-\includegraphics[width=0.7\textwidth]{j_vs_omega_mu1_v_0.4_0.8_eph.pdf}
+\includegraphics[width=0.7\textwidth]{Fig3.pdf}
 \caption{(Color online) 
@@
 \begin{figure}[b] 
-\includegraphics[width=\linewidth]{spec_filling_mu1_v_0.4_0.8_O_5_11_e.pdf}
+\includegraphics[width=\linewidth]{Fig4.pdf}
 \caption{(Color online) Spectral function $A(\omega)$ (solid line) and occupation function $N(\omega)$ (shaded area) at (a) $\Omega=5$ and (b) $\Omega=11$ for $v=0.4$ and $0.8$ for the EO system.
@@
 \begin{figure}[b]  
-\includegraphics[width=\linewidth]{j_vs_omega_mu1_v_0.8_e_E0_3_4.pdf} 
+\includegraphics[width=\linewidth]{Fig5.pdf} 
 \caption{(Color online) (a) Time-averaged steady state current $j$ and (b) double occupancy $N_{\text{D}}$ as a function of $\Omega$, at $v=0.8$ for $E_0=3,4$ for the EO system.
@@
 \begin{figure}[b]
-\includegraphics[width=\linewidth]{spec_filling_mu1_v_0.4_0.8_O_11_eph.pdf}
+\includegraphics[width=\linewidth]{Fig6.pdf}
 \caption{(Color online) Spectral function $A(\omega)$ (solid line) and occupation function $N(\omega)$ (shaded area) at $\Omega=11$ without and with e-ph interaction, for (a) $v=0.4$ and (b) $v=0.8$.
@@
 \begin{figure}[t] 
-\includegraphics[width=\linewidth]{j_vs_omega_mu1_v_0.4_0.8_E0_2_sweep_omegaph.pdf}
+\includegraphics[width=\linewidth]{Fig7.pdf}
 \caption{(Color online) (a) Time-averaged steady state current $j$ and (b) double occupancy $N_{\text{D}}$ as a function of $\Omega$, for $v=0.4, 0.8$, at phonon cutoff frequencies $\omega_{\text{ph}}=0.025, 0.05$.
@@
 \begin{figure}[b] 
-\includegraphics[width=\linewidth]{j_vs_omega_mu1_sweep_v_E0_2_eph.pdf}
+\includegraphics[width=\linewidth]{Fig8.pdf}
 \caption{(Color online) (a) Time-averaged steady state current $j$ and (b) double occupancy $N_{\text{D}}$ as a function of $\Omega$, for $v=0.5,0.6,0.7$, without and with e-ph interaction.

### 2022-10-31 resub_PRB/letters/reply_to_referees.txt
added resub_PRB folder

Dear Dr. Kancharla,

Thank you very much for your e-mail from October 24th with the reply of the Referees on our paper. The first Referee recommends publication without hesitation. The second Referee believes that the paper has to be published in Physical Review B, discussing the points he raised.

In the new version of our paper we have taken into account in detail all comments. A detailed reply is also included to this letter.

We hope that our paper is now suitable for publication in Phys. Rev. B.

Yours sincerely,
Paolo Gazzaneo, Tommaso Maria Mazzocchi, Jan Lotze and Enrico Arrigoni

--------------------------------------------------
          First Referee                          
--------------------------------------------------

1. As the authors pointed out the electric field amplitude considered
in this paper is several orders of magnitude larger than that of the
sunlight, therefore, strictly speaking the results presented in the
present paper are more applicable to intense laser-light
photoexcitations

2. The authors have made an effort to extrapolate in the regime of
smaller electric field amplitude and smaller hybridization strength.
They note that in order to achieve the latter one would need to
several layers where photexcited carriers separated by an electric
field gradient would have more time to induce impact ionization before
escaping into the leads.

3. The authors plan in future investigation to address the previously
mentioned issue.

A1-A2-A3: We thank a lot the Referee for his remarks and acknowledgements about our article.

4. I would like to suggest that, perhaps, the authors, in their future
investigations, could include the role of “bad” metallic contacts,
maybe represented by narrow-band leads or possibly with a small-width
insulating barrier between the leads and the material as abstracted by
the Hubbard-like model studied. If the insulating barrier is
microscopically small the carriers would still be able to tunnel, but
perhaps would remain longer in the region of the material which might
allow II to occur.

A4: In our future investigation, we will keep this suggestion in mind.

----------------------------------------------------
        Second Referee                              
----------------------------------------------------

************************************************************************
*** To highlight the changes in the main text we marked them in BLUE ***
************************************************************************

1. It is really important to discuss why DMFT approximation is
expected to be meaningful in quasi-2D case (1-layer Hubbard model
coupled to leads).

A1: The Referee is right, we acknowledge that a discussion on the meaninfulness of DMFT approximation for quasi-2D cases is missing.

In the quasi-2D case we are addressing, the use of DMFT and therefore neglecting the momentum dependence of the electron self-energy leads to meaningful results for two main reasons. 
First: The considered system is not "strictly" two dimensional, meaning that there is still some dispersion in the third dimension, even though weak. This is exactly the case of our setup.
Second: We are not including in our treatment long-range magnetic fluctuations or, more generally, spin-fluctuations. The inclusion of such physics gives truly nonlocal effects and therefore nonlocal contributions in the self-energy, whose momentum-dependence has to be clearly taken into account in this case. In lower dimensional systems, as the one we are considering, these effects are usually not negligible, but this depends on the physics one is interested in: to clearly address the influence of the leads and acoustic phonons on impact ionization processes, spatially nonlocal correlations would complicate the overall picture and understanding.
Regarding this point, we are also limited in considering only single orbitals in the current version of our nonequilibrium many-body impurity solver.

As asked, we added in Sec.I a discussion on this point, with a reference to a comprehensive review of nonlocal correlations beyond DMFT (Rev. Mod. Phys. 90, 025003
(2018)).

2. It seems that chosen temperature is pretty high. Please discuss why
optical phonons are neglected.

A2:

We thank the Referee for raising this point, giving us the opportunity to clarify it better.

The value of the temperature of T=0.02, is not high in comparison with the other characteristic energy scales of the system, as e.g. the soft cutoff acoustic phonon frequency and the Hubbard interaction. It is actually the smallest chosen energy scale. Usually, the optical phonons modes energy is at least twice the acoustic phonons one, therefore the choice of a small value for the temperature justifies in our view taking into account acoustic phonons and neglecting optical phonons.
Just as a remark, we are interested in the effects of phononic dissipation and, to address such issue, the acoustic phonons with a finite bandwidth, in contrast to optical phonons, are more effective in energy dissipation, as already been written in Sec.II.

As the Referee suggests, we inserted a footnote in Sec.IV, addressing explicitly this point.

3. It is naturally expected that phonons reduce the bandgap (here,
pseudogap), as in standard semiconductors, where the phonons give
10-100meV reduction of the gap and the effect increases with
temperature. Strictly speaking, to obtain the change of the
bandstructure due to phonons one needs to calculate the Fan and DW
terms of the , generally speaking, momentum-dependent electron
self-energy. In this sense, again, how important are momentum
dependencies of electron Sigma in 2D case?

A3: We thank the Referee to have pointed out a similar effect of reduction of the pseudogap in semiconductors and for the clarification about the phonon renormalization of the band structure due to momentum-dependent self energy. This is an important point and we address the issue below.

The importance of momentum dependencies of the electron self-energy in the 2D case depends on the level of sophistication one would like to achieve in considering acoustic phonons and therefore if one is more interested in quantitative results or not. As explicitly stated in Sec.I, "...our analysis can only provide qualitative results, while quantitative comparisons with experimental systems require a more realistic setup and are beyond the scope of this work."
At this level, having used DMFT approximation and therefore considered momentum-independent self-energies, we can't quantify the importance of momentum dependencies in the electron self-energy.
However, as pointed out in the review Rev. Mod. Phys. 89, 015003, the Fan term is also "...traditionally referred to as the self-energy in the Migdal approximation". This is exactly the term we included, without momentum dependence, in the Dyson equation to take into account the effect of the acoustic phonons on electrons. In the same review, it's stated that "The Debye-Waller contribution to the electron self-energy is almost invariably ignored in the literature on metals and superconductors...". In a wider view, systems displaying strong correlations, as we one taken into account, fall into this category, therefore we are confident that such term can be safely neglected for a qualitative description of the effects of acoustic phonons.

We included a footnote in Sec.IIIB addressing such issue, together with a reference to the review mentioned above (Rev. Mod. Phys. 89, 015003).

4. It is not clear from Conclusions (at least for me) what stopped the
authors to consider more realistic weaker fields and hybridizations.

A4:

We thank the Referee for having brought up this important point.

We didn't consider weaker electric field amplitudes since DMFT only converges slowly for such a choice of parameters. We have already discussed this point in the footnote [47]. The same reasoning applies for smaller hybridizations, slowing down in a considerable way the convergence of the DMFT cycle.

We followed the suggestion of the Referee, putting in the main text in Sec.V the footnote [47], extending it to mention smaller hybridizations.

List of changes:

**********************************************************************************************
*** To highlight the changes we marked them in BLUE (in source code denoted by '\resub{}') ***
**********************************************************************************************

Motivated by questions/observations from Second Referee:

Modified Sec.I  
Added reference in Sec.I
Added footnote in Sec.IIIB
Added reference in Sec.IIIB
Added footnote in Sec.IV
Modified Sec.V

### 2022-10-31 resub_PRB/Paper1.tex
added resub_PRB folder

--- 2022-09-07 sub_PRB/Paper1.tex
@@
 
+\definecolor{hblue}{RGB}{0,0,255}
+\newcommand{\resub}[1]{{\color{hblue} #1}}
+
 \begin{document}
@@
 An external periodic electric field induces a Floquet steady state with a current flowing from the lead with the lower to the lead with the higher chemical potential, thus transferring its energy.
- We address this periodic problem via nonequilibrium Floquet dynamical mean-field theory (F-DMFT).
+ We address this periodic problem via nonequilibrium Floquet dynamical mean-field theory (F-DMFT) \resub{, which has been proven to give meaningful results in similar setups (see, e.g.~\cite{so.do.18}) and when spatially non-local correlations as long-range magnetic fluctuations are explicitly not taken into account~\cite{ro.ha.18}.}
 
@@
 
-As in Ref.~\cite{ma.ga.22u}, phonons are included in the form of acoustic  branches attached to each lattice site and coupled to the electrons via the Hamiltonian 
+As in Ref.~\cite{ma.ga.22}, phonons are included in the form of acoustic  branches attached to each lattice site and coupled to the electrons via the Hamiltonian 
 \begin{equation}\label{eq:e-ph_ham} 
@@
 Further details are given in Sec.~\ref{sec:FDMFT_implementation}.
-In the same spirit, the e-ph SE is included locally as $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega;\epsilon,\overline{\epsilon}) \simeq \underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$.
+In the same spirit, the e-ph SE is included locally as $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega;\epsilon,\overline{\epsilon}) \simeq \underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ ~\footnote{\resub{As explicitly stated in Sec.~\ref{sec:intro}, our analysis provides only qualitative results.
+A more accurate treatment that aims to provide quantitative predictions, should take into account the crystal momentum dependence of $\underline{\bf{\Sigma}}_{\text{e-ph}}$.
+We refer to the review~\cite{gius.17} for a detailed and comprehensive explanation.}}.
 In terms of the Keldysh contour time arguments $z$ and $z^\prime$, it has the form
@@
 We consider acoustic phonons, with spectral function $A_{\text{ph}}(\omega) = (\omega/\omega^{2}_{\text{ph}}) \ee^{-| \omega|/\omega_{\text{ph}}}$,  $\omega_{\text{ph}}$ being a soft cutoff frequency~\cite{pi.li.21}.
-The retarded and Keldysh components of the e-ph SE are easily extracted from  Eq.~\eqref{eq:backbone_e-ph_SE} and can be found in Ref.~\cite{ma.ga.22u}.
+The retarded and Keldysh components of the e-ph SE are easily extracted from  Eq.~\eqref{eq:backbone_e-ph_SE} and can be found in Ref.~\cite{ma.ga.22}.
 
@@
  We follow Ref.~\cite{so.do.18} and take $U=12$ and unless stated otherwise $E_0=2$.
-The fermion leads and the acoustic phonons have temperature $T=0.02$.
+The fermion leads and the acoustic phonons have temperature $T=0.02$~\footnote{\resub{The chosen value of the temperature is, in comparison with the other paramaters of the system, as e.g.
+$\omega_{\text{ph}}$ and $U$, the smallest energy scale.
+For this reason, we can neglect optical phonons in our qualitative treatment.}}.
 We consider a particle-hole symmetric system with $\Gamma_{\text{l}}=\Gamma_{\text{r}}=0.37$, $t_{\text{l}}=t_{\text{r}}=1.7$, $\varepsilon_{\text{l}/\text{r}}=\mp 6$ and $v_{\text{l}}=v_{\text{r}}=v$.
@@
 First, the phonon spectral function $A_{\text{ph}}(\omega)$ exhibits more weight at low frequencies around $\omega\approx\omega_{\text{ph}}$.
-Second, it restricts the maximum value of the reciprocal lattice vector $\vec{q}_{\text{max}}$ via $\omega_{\text{ph}}=\omega(\vec{q}_{\text{max}})$~\cite{ma.ga.22u}, meaning that short-wavelength phonons are suppressed.}.
+Second, it restricts the maximum value of the reciprocal lattice vector $\vec{q}_{\text{max}}$ via $\omega_{\text{ph}}=\omega(\vec{q}_{\text{max}})$~\cite{ma.ga.22}, meaning that short-wavelength phonons are suppressed.}.
 
@@
 
-Experimentally, the electric field amplitude considered in this paper~\footnote{We don't consider smaller electric field amplitudes $E_0$ since DMFT only converges slowly for such a choice of parameters.} is several orders of magnitude larger than that of the sunlight, therefore our results are more relevant for photoexcitations produced by intense laser pulses (see also the discussion in~\cite{mu.we.18}) rather than for true photovoltaic systems.
+Experimentally, the electric field amplitude considered in this paper is several orders of magnitude larger than that of the sunlight, therefore our results are more relevant for photoexcitations produced by intense laser pulses (see also the discussion in~\cite{mu.we.18}) rather than for true photovoltaic systems.
+\resub{We didn't consider smaller electric field amplitudes, because of the slow F-DMFT convergence for such a choice of parameters, that occurs also with weaker hybridization strengths.}
+
 On the other hand, one may try to qualitatively extrapolate the discussion at the end of Sec.~\ref{sec:E0_2_only_electrons} in the other direction to smaller electric field amplitudes, for which a smaller hybridization would be necessary in order to sustain II.
@@
 \bibliographystyle{prsty}   % references in Phys Rev style
-\bibliography{references_database}
+\bibliography{footnotes,references_database}
 

### 2022-11-02 resub_PRB/letters/reply_to_referees_jan.txt
Modified Paolos addenda in the paper and the replies to the referees.

Dear Dr. Kancharla,

Thank you very much for your e-mail from October 24th with the reply of the Referees on our paper. The first Referee recommends publication without hesitation. The second Referee believes that the paper has to be published in Physical Review B, discussing the points he raised.

In the new version of our paper we have taken into account in detail all comments. A detailed reply is also included to this letter.

We hope that our paper is now suitable for publication in Phys. Rev. B.

Yours sincerely,
Paolo Gazzaneo, Tommaso Maria Mazzocchi, Jan Lotze and Enrico Arrigoni

--------------------------------------------------
          First Referee                          
--------------------------------------------------

1. As the authors pointed out the electric field amplitude considered
in this paper is several orders of magnitude larger than that of the
sunlight, therefore, strictly speaking the results presented in the
present paper are more applicable to intense laser-light
photoexcitations

2. The authors have made an effort to extrapolate in the regime of
smaller electric field amplitude and smaller hybridization strength.
They note that in order to achieve the latter one would need to
several layers where photexcited carriers separated by an electric
field gradient would have more time to induce impact ionization before
escaping into the leads.

3. The authors plan in future investigation to address the previously
mentioned issue.

A1-A2-A3: We thank the Referee a lot for his remarks on and acknowledgement of our article.

4. I would like to suggest that, perhaps, the authors, in their future
investigations, could include the role of "bad" metallic contacts,
maybe represented by narrow-band leads or possibly with a small-width
insulating barrier between the leads and the material as abstracted by
the Hubbard-like model studied. If the insulating barrier is
microscopically small the carriers would still be able to tunnel, but
perhaps would remain longer in the region of the material which might
allow II to occur.

A4: We will keep this suggestion in mind for our future investigations.

----------------------------------------------------
        Second Referee                              
----------------------------------------------------

************************************************************************
*** To highlight the changes in the main text we marked them in BLUE ***
************************************************************************

1. It is really important to discuss why DMFT approximation is
expected to be meaningful in quasi-2D case (1-layer Hubbard model
coupled to leads).

A1: The Referee is right, we acknowledge that a discussion on the meaningfulness of the DMFT approximation for the quasi-2D case is missing.

In the quasi-2D case we address, the use of DMFT which neglects the momentum dependence of the electron self-energy leads to meaningful results for two main reasons.

First: The physical system we want to model with our setup is not "strictly" two dimensional, meaning that there is still some dispersion in the third dimension, even though it may be weak. For such quasi-2D systems DMFT can yield useful results (Phys. Rev. B 97, 115113 (2018)).

Second: In our treatment we do not include nonlocal correlations which give rise to long-ranged collective excitations such as magnons. Including nonlocal correlations leads to truly nonlocal effects and therefore nonlocal contributions in the self-energy, whose momentum-dependence then clearly has to be taken into account. In low dimensional systems, like the one we are considering, these effects are usually not negligible. Yet their inclusion is also a matter of choice, depending on the physics one is interested in: to clearly address the influence of the leads and acoustic phonons on impact ionization processes, spatially nonlocal correlations would complicate the overall picture and understanding.

As asked, we added in Sec. I a discussion on this point, with a reference to a comprehensive review of nonlocal correlations beyond DMFT [Rev. Mod. Phys. 90, 025003 (2018)].

2. It seems that chosen temperature is pretty high. Please discuss why
optical phonons are neglected.

A2:

We thank the Referee for raising this point, giving us the opportunity for further clarification.

The value of the temperature of T=0.02 is not high compared with the other characteristic energy scales of the system, e.g. the soft cutoff of the acoustic phonon frequency w_ph=0.1 and the Hubbard interaction U=12. It is actually the smallest chosen energy scale. Usually, the optical phonon modes energy is at least twice that of the acoustic phonons one [see Figs. 4 and 5 in Phys. Rev. B 102, 245104 (2020)]. Therefore the choice of a small value for the temperature justifies in our view taking into account only acoustic phonons and neglecting optical phonons.

Just as a remark, we are interested in the effects of phonon-mediated dissipation and for this purpose the acoustic phonons with a finite bandwidth, in contrast to optical phonons, are more effective in energy dissipation, as is already mentioned in Sec. II (there optical phonons are denoted Holstein phonons).

As the Referee suggests, we inserted a footnote in Sec. IV, addressing this point explicitly.

3. It is naturally expected that phonons reduce the bandgap (here,
pseudogap), as in standard semiconductors, where the phonons give
10-100meV reduction of the gap and the effect increases with
temperature. Strictly speaking, to obtain the change of the
bandstructure due to phonons one needs to calculate the Fan and DW
terms of the, generally speaking, momentum-dependent electron
self-energy. In this sense, again, how important are momentum
dependencies of electron Sigma in 2D case?

A3: We thank the Referee for pointing out a similar effect of reduced pseudogaps in semiconductors and for the clarification about the phonon renormalization of the band structure due to a momentum-dependent self-energy. This is an important point and we address it below.

The importance of the momentum dependence of the electron self-energy in the 2D case depends on the level of sophistication one wants to achieve in considering acoustic phonons and therefore whether one wants quantitative results or is content with qualitative results. As explicitly stated in Sec. I, "...our analysis can only provide qualitative results, while quantitative comparisons with experimental systems require a more realistic setup and are beyond the scope of this work."
At this level, having used the DMFT approximation and therefore considered momentum-independent self-energies, we cannot quantify the importance of momentum dependencies in the electron self-energy.
However, as pointed out in the review Rev. Mod. Phys. 89, 015003 (2017), the Fan term is also "...traditionally referred to as the self-energy in the Migdal approximation". This is exactly the term we included, albeit without momentum dependence, to take into account the effect of the acoustic phonons on electrons. In the same review it is noted that the Debye-Waller term is static, i.e. independent of frequency. Hence within DMFT, it would correspond to a change in the chemical potential. Since we consider the particle-hole symmetric case, the Debye-Waller term does not contribute.

We included a footnote in Sec. III.B addressing the momentum-dependence, together with a reference to the review mentioned above [Rev. Mod. Phys. 89, 015003 (2017)].

4. It is not clear from Conclusions (at least for me) what stopped the
authors to consider more realistic weaker fields and hybridizations.

A4:

We thank the Referee for having brought up this important point.

We did not consider weaker electric field amplitudes since DMFT only converges slowly for such a choice of parameters. We have already discussed this point in the footnote [47]. The same reasoning applies for smaller hybridization strength which slows down the convergence of the DMFT cycle considerably.

We followed the suggestion of the Referee, moving the footnote [47] into the main text in Sec. V and extending it to mention smaller hybridizations.

List of changes:

**********************************************************************************************
*** To highlight the changes we marked them in BLUE (in source code denoted by '\resub{}') ***
**********************************************************************************************

Motivated by questions/observations from Second Referee:

Modified Sec. I  
Added reference in Sec. I
Added footnote in Sec. IIIB
Added reference in Sec. IIIB
Added footnote in Sec. IV
Modified Sec. V

### 2022-11-02 resub_PRB/Paper1.tex
Modified Paolos addenda in the paper and the replies to the referees.

@@
 The idea of designing photovoltaic devices exploiting the Mott gap to convert electromagnetic radiation into energy has become popular in recent years~\cite{mano.10,li.ch.13,gu.gu.13,co.ma.14,wa.li.15}.
-In particular, it has been suggested that in strongly correlated materials, highly excited charge carriers could use their extra energy to excite additional carriers across the Mott gap via impact ionization (II)~\cite{mano.10,co.ma.14}, thus
-potentially improving their efficiency beyond the Shockley-Queisser limit~\cite{sh.qu.61}.
+In particular, it has been suggested that in strongly correlated materials, highly excited charge carriers could use their extra energy to excite additional carriers across the Mott gap via impact ionization (II)~\cite{mano.10,co.ma.14}, thus potentially improving their efficiency beyond the Shockley-Queisser limit~\cite{sh.qu.61}.
 Although II is also present in conventional semiconductor devices, the time scales for electron-electron scattering are typically much longer than in correlated materials, so that highly excited electrons will mostly dissipate their energy to phonons.
@@
 An external periodic electric field induces a Floquet steady state with a current flowing from the lead with the lower to the lead with the higher chemical potential, thus transferring its energy.
- We address this periodic problem via nonequilibrium Floquet dynamical mean-field theory (F-DMFT) \resub{, which has been proven to give meaningful results in similar setups (see, e.g.~\cite{so.do.18}) and when spatially non-local correlations as long-range magnetic fluctuations are explicitly not taken into account~\cite{ro.ha.18}.}
+We address this periodic problem via nonequilibrium Floquet dynamical mean-field theory (F-DMFT)\resub{, which has been shown to give meaningful results in similar setups (see, e.g.~\cite{so.do.18}).
+Since we are not interested in capturing long-ranged collective excitations, non-local correlations~\cite{ro.ha.18} are not taken into account.}
 
@@
 In the temporal gauge it enters via the Peierls substitution in the time-dependent hopping in Eq.~\eqref{eq:Hamiltonian}~\cite{peie.33}
-
+% 
 \begin{equation}\label{eq:peierls} 
@@
 where $t_{\text{c}}$ is the intra-layer hopping, $\vec{A}$(t) the time-dependent vector potential, $\hbar$ Planck's constant and $q$ the charge of the electrons.
-Following Refs.~\cite{ts.ok.08,mu.we.18}, we choose for simplicity
- $\vec{A}(t)=\vec{e}_{0} A(t)$, which points along the 
-lattice body diagonal $\vec{e}_{0}=(1,1,\dots,1)$.
+Following Refs.~\cite{ts.ok.08,mu.we.18}, we choose for simplicity $\vec{A}(t)=\vec{e}_{0} A(t)$, which points along the lattice body diagonal $\vec{e}_{0}=(1,1,\dots,1)$.
 Therein $A(t)=\frac{\hbar}{qa}\aamp\sin(\Omega t)$ with $\aamp=-\frac{qE_0a}{\hbar\Omega}$, $E_0$ is the electric field amplitude, and $a$ the lattice spacing~\cite{ts.ok.08}.
@@
 As in Ref.~\cite{ma.ga.22}, phonons are included in the form of acoustic  branches attached to each lattice site and coupled to the electrons via the Hamiltonian 
+% 
 \begin{equation}\label{eq:e-ph_ham} 
@@
 \end{equation}
+% 
 with $g$ as e-ph coupling and $\hat{x}_{i} \equiv \frac{1}{\sqrt{2}} \left( \hat{b}^{\dagger}_{i} + \hat{b}_i \right)$, where $\hat{b}^{\dagger}_{i}$ ($\hat{b}_{i}$) creates (annihilates) a phonon of the acoustic branch at site $i$, with dispersion relation described by $\hat{H}_{\text{ph}}$, discussed in Sec~\ref{sec:Dyson_equation}.
@@
 
-For mathematical simplicity~\cite{ge.ko.92,ao.ts.14}, 
- we consider the correlated central region as a $d$-dimensional layer and consider the limit of infinite dimensions $d \rightarrow \infty$ by rescaling the hopping as $t_{\text{c}}=t^{\ast}/(2\sqrt{d})$.
-Taking $a=1$, sums over the crystal momentum ${\bf k}$ of a generic quantity $\chi$ read $\sum_{{\bf k}} \chi(\omega,{\bf k}) \rightarrow \int d\epsilon \int   d\overline{\epsilon} \ \rho(\epsilon,\overline{\epsilon}) \chi(\omega;\epsilon,\overline{\epsilon})$ with $\rho(\epsilon,\overline{\epsilon}) = (1/\pi t^{\ast 2}) \exp[-( \epsilon^{2} + \overline{\epsilon}^{2})/t^{\ast 2}]$ as the joint density of states~\cite{ts.ok.08} and with
+For mathematical simplicity~\cite{ge.ko.92,ao.ts.14}, we consider the correlated central region as a $d$-dimensional layer and consider the limit of infinite dimensions $d \rightarrow \infty$ by rescaling the hopping as $t_{\text{c}}=t^{\ast}/(2\sqrt{d})$.
+Taking $a=1$, sums over the crystal momentum $\vec{k}$ of a generic quantity $\chi$ read $\sum_{\vec{k}} \chi(\omega,\vec{k}) \rightarrow \int \dd\epsilon \int   \dd\overline{\epsilon} \ \rho(\epsilon,\overline{\epsilon}) \chi(\omega;\epsilon,\overline{\epsilon})$ with $\rho(\epsilon,\overline{\epsilon}) = (1/\pi t^{\ast 2}) \exp[-( \epsilon^{2} + \overline{\epsilon}^{2})/t^{\ast 2}]$ as the joint density of states~\cite{ts.ok.08} and with
 % 
@@
 \end{align}
-%
 
@@
 
-To correctly describe the nonequilibrium periodic steady state, we use the Floquet generalization of the nonequilibrium Green's function (NEGF) 
-approach~\cite{ts.ok.08,sc.mo.02u,jo.fr.08}.
+To correctly describe the nonequilibrium periodic steady state, we use the Floquet generalization of the nonequilibrium Green's function (NEGF) approach~\cite{ts.ok.08,sc.mo.02u,jo.fr.08}.
 Every function $G(t,t^{\prime})$ satisfying the periodicity relation $G(t,t^{\prime})=G(t+\tau,t^{\prime}+\tau)$, with $\tau=2\pi/\Omega$ as the period related to the external driving frequency $\Omega$, may be represented as~\cite{ts.ok.08,sc.mo.02u,jo.fr.08}
-
+% 
 \begin{equation}
 \label{eq:FloquetGF} 
-\underline{G}_{mn}(\omega) =\int \dd t_{\text{rel}} \int_{-\tau/2}^{\tau/2} \frac{dt_{\text{av}}}{\tau} \ee^{\ii[\left(\omega+m\Omega\right) t -\left( \omega+n\Omega\right)t^{\prime}]} \underline{G}(t,t'),
+\kel{G}_{mn}(\omega) =\int \dd t_{\text{rel}} \int_{-\tau/2}^{\tau/2} \frac{\dd t_{\text{av}}}{\tau} \ee^{\ii[\left(\omega+m\Omega\right) t -\left( \omega+n\Omega\right)t^{\prime}]} \kel{G}(t,t'),
 \end{equation}
+% 
 known as the \emph{Keldysh-Floquet} GF.
 The integration variables $t_{\text{rel}} = t-t^{\prime}$ and $t_{\text{av}} = (t+t^{\prime})/2$ are the relative and average times.
-Within the rest of this work, we denote a Floquet-represented matrix either as $X_{mn}$ with explicit indices, or use a boldface letter $\bf{X}$.
+Within the rest of this work, we denote a Floquet-represented matrix either as $X_{mn}$ with explicit indices, or use a boldface letter $\mat{X}$.
 The underline indicates the overall \emph{Keldysh} structure
@@
 \begin{equation}\label{eq:Keld-structure}
-\underline{{\bf G}} \equiv 
+\kel{\mat{G}} \equiv
 \begin{pmatrix}
-{\bf G}^{\text{R}} & {\bf G}^{\text{K}}\\
-{\bf 0}         & {\bf G}^{\text{A}} \\
+\mat{G}^{\text{R}} & \mat{G}^{\text{K}}\\
+\mat{0}            & \mat{G}^{\text{A}} \\
 \end{pmatrix},
@@
 %
-which contains the \emph{retarded}, \emph{advanced} and \emph{Keldysh} components $\textbf{G}^{\text{R,A,K}}$, where $\textbf{G}^{\text{A}}=(\textbf{G}^{\text{R}})^{\dagger}$.
-The \emph{Keldysh} component is defined as $\textbf{G}^{\text{K}} \equiv \textbf{G}^{>} + \textbf{G}^{<}$, with $\textbf{G}^{\lessgtr}$ as \emph{lesser} and \emph{greater} components~\cite{schw.61,keld.65,ra.sm.86,ha.ja}.
+which contains the \emph{retarded}, \emph{advanced} and \emph{Keldysh} components $\mat{G}^{\text{R,A,K}}$, where $\mat{G}^{\text{A}}=(\mat{G}^{\text{R}})^{\dagger}$.
+The \emph{Keldysh} component is defined as $\mat{G}^{\text{K}} \equiv \mat{G}^{>} + \mat{G}^{<}$, with $\mat{G}^{\lessgtr}$ as \emph{lesser} and \emph{greater} components~\cite{schw.61,keld.65,ra.sm.86,ha.ja}.
 
@@
 The lattice Floquet GF of our setup obeys the Dyson equation 
+% 
 \begin{equation}\label{eq:FullDysonEq}
-\underline{{\bf G}}^{-1}(\omega_n;\epsilon,\overline{\epsilon}) = \underline{{\bf G}}^{-1}_{0}(\omega_n;\epsilon,\overline{\epsilon}) - \underline{{\bf \Sigma}}(\omega_n;\epsilon,\overline{\epsilon}) - \underline{{\bf \Sigma}}_{\text{e-ph}}(\omega_n;\epsilon,\overline{\epsilon}),
+\kel{\mat{G}}^{-1}(\omega_n;\epsilon,\overline{\epsilon}) = \kel{\mat{G}}^{-1}_{0}(\omega_n;\epsilon,\overline{\epsilon}) - \kel{\mat{\Sigma}}(\omega_n;\epsilon,\overline{\epsilon}) - \kel{\mat{\Sigma}}_{\text{e-ph}}(\omega_n;\epsilon,\overline{\epsilon}),
 \end{equation}
-where in our approximation the electron self-energy (SE) $ \underline{{\bf \Sigma}}$ and e-ph SE $\underline{{\bf \Sigma}}_{\text{e-ph}}$ contribute independently to the total SE~\footnote{In fact, there is an indirect feedback via the DMFT self-consistency.}.
-
+% 
+where in our approximation the electron self-energy (SE) $ \kel{\mat{\Sigma}}$ and e-ph SE $\kel{\mat{\Sigma}}_{\text{e-ph}}$ contribute independently to the total SE~\footnote{In fact, there is an indirect feedback via the DMFT self-consistency.}.
 Therein, the lattice GF of the non-interacting part of the Hamiltonian in Eq.~\eqref{eq:Hamiltonian} is
-
+% 
 \begin{equation}\label{eq:non-int_InvGF} 
-\underline{G}^{-1}_{0,mn}(\omega_n;\epsilon,\overline{\epsilon}) =  \underline{g}^{-1}_{0,mn}(\omega_n;\epsilon,\overline{\epsilon}) - \sum_{\rho\in\{\text{l},\text{r}\}}v^2_{\rho}\underline{g}_{\text{b},\rho}(\omega_n;\epsilon)\delta_{mn}
+\kel{G}^{-1}_{0,mn}(\omega_n;\epsilon,\overline{\epsilon}) =  \kel{g}^{-1}_{0,mn}(\omega_n;\epsilon,\overline{\epsilon}) - \sum_{\rho\in\{\text{l},\text{r}\}}v^2_{\rho}\kel{g}_{\text{b},\rho}(\omega_n;\epsilon)\delta_{mn}
 \end{equation}
+% 
 with $v_{\text{l}/\text{r}}$ as lead-layer hybridization, $\omega_n \equiv \omega + n\Omega$, $n\in\mathbbm{Z}$, and 
@@
 where $J_n$ denotes the $n$-th order Bessel function of the first kind, with the argument $\aamp$ defined in Sec.~\ref{sec:Model}.
-The  GF $\underline{g}_{\text{b},\text{l}/\text{r}}$ on the $d$-dimensional boundary of the decoupled leads,  consisting of a single layer coupled to a semi-infinite reservoir in the wide-band limit with broadening $\Gamma_{\text{l}/\text{r}}$ (cf.
+The  GF $\kel{g}_{\text{b},\text{l}/\text{r}}$ on the $d$-dimensional boundary of the decoupled leads,  consisting of a single layer coupled to a semi-infinite reservoir in the wide-band limit with broadening $\Gamma_{\text{l}/\text{r}}$ (cf.
 Fig.~\ref{fig:setup}) is given by
@@
 
-The electron SE $\underline{\bf{\Sigma}}$ is obtained from F-DMFT and therefore, in this approximation, independent of the crystal momentum, i.e.
-$\underline{\bf{\Sigma}}(\omega;\epsilon,\overline{\epsilon}) \simeq \underline{\bf{\Sigma}}(\omega)$.
+The electron SE $\kel{\mat{\Sigma}}$ is obtained from F-DMFT and therefore, in this approximation, independent of the crystal momentum, i.e.
+$\kel{\mat{\Sigma}}(\omega;\epsilon,\overline{\epsilon}) \simeq \kel{\mat{\Sigma}}(\omega)$.
 Further details are given in Sec.~\ref{sec:FDMFT_implementation}.
-In the same spirit, the e-ph SE is included locally as $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega;\epsilon,\overline{\epsilon}) \simeq \underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ ~\footnote{\resub{As explicitly stated in Sec.~\ref{sec:intro}, our analysis provides only qualitative results.
-A more accurate treatment that aims to provide quantitative predictions, should take into account the crystal momentum dependence of $\underline{\bf{\Sigma}}_{\text{e-ph}}$.
-We refer to the review~\cite{gius.17} for a detailed and comprehensive explanation.}}.
+In the same spirit, the e-ph SE is included locally as $\kel{\mat{\Sigma}}_{\text{e-ph}}(\omega;\epsilon,\overline{\epsilon}) \simeq \kel{\mat{\Sigma}}_{\text{e-ph}}(\omega)$~\footnote{\resub{As stated in Sec.~\ref{sec:intro}, our analysis provides only qualitative results.
+A more accurate treatment that aims to provide quantitative predictions, should take into account the crystal momentum dependence of $\kel{\mat{\Sigma}}_{\text{e-ph}}$.
+We refer to the review~\cite{gius.17} which discusses the effects of phonons on the electronic bandstructure and the modelling thereof.}}\vphantom{\cite{gius.17}}.
 In terms of the Keldysh contour time arguments $z$ and $z^\prime$, it has the form
-
+% 
 \begin{equation}\label{eq:backbone_e-ph_SE}
@@
 \end{equation}
-
+% 
 The Keldysh components of the non-interacting phonon GF $\kel{D}_{\text{ph}}(t,t^{\prime})$ are given by~\cite{ao.ts.14}
@@
 For completeness, we now briefly describe the self-consistency F-DMFT scheme used.
-(i) We start from an initial guess for the electron SE $\kel{\mat{\Sigma}}(\omega)$ and set $\kel{\mat \Sigma}_{\text{e-ph}}(\omega)=0$. (ii) Then we compute the local electron GF as 
+(i) We start from an initial guess for the electron SE $\kel{\mat{\Sigma}}(\omega)$ and set $\kel{\mat \Sigma}_{\text{e-ph}}(\omega)=0$.
+(ii) Then we compute the local electron GF as
 %  
@@
 (iii) Using Eq.~\eqref{eq:backbone_e-ph_SE}, we obtain the phonon contribution to the e-ph SE $\kel{\mat{\Sigma}}_{\text{e-ph}}(\omega)$.
-(iv) The problem is mapped onto a single impurity plus bath, whose hybridization function
-is given by
+(iv) The problem is mapped onto a single impurity plus bath, whose hybridization function is given by
 %
@@
 However, in Ref.~\cite{so.do.18} it was argued and shown that for the considered electric field amplitudes, off-diagonal terms in the electron SE $\kel{\mat{\Sigma}}(\omega)$ can be safely neglected with respect to the diagonal ones.
-We follow this argument and adopt here
-this Floquet-diagonal self-energy approximation (FDSA) as well.
-In addition, it turns out that also for the e-ph SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ this approximation is justified~\footnote{More specifically, we verified that in the parameter range in which FDSA is justified for the electron SE $\kel{\mat{\Sigma}}(\omega)$ (Sec.~\ref{sec:results}), the off-diagonal terms of the e-ph SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ are sufficiently suppressed}.
+We follow this argument and adopt here this Floquet-diagonal self-energy approximation (FDSA) as well.
+In addition, it turns out that also for the e-ph SE $\kel{\mat{\Sigma}}_{\text{e-ph}}(\omega)$ this approximation is justified~\footnote{More specifically, we verified that in the parameter range in which FDSA is justified for the electron SE $\kel{\mat{\Sigma}}(\omega)$ (Sec.~\ref{sec:results}), the off-diagonal terms of the e-ph SE $\kel{\mat{\Sigma}}_{\text{e-ph}}(\omega)$ are sufficiently suppressed}.
 Consequently, we solve a nonequilibrium stationary impurity problem, by considering only the $(0,0)$-Floquet matrix element of all the quantities in Eq.~\eqref{eq:imp_Dyson_eq}.
@@
 
-To study direct excitation and II effects in this system,
-we consider the following time-averaged physical quantities.
+To study direct excitation and II effects in this system, we consider the following time-averaged physical quantities.
 
@@
 \begin{align}
-j_{\text{l}\rightarrow\text{r}}&=v^2\int_{-\Omega/2}^{\Omega/2}\frac{\dd\omega}{2\pi} \int \dd\epsilon \int \dd\overline{\epsilon} \rho(\epsilon,\overline{\epsilon}) \rre\Tr(\boldsymbol{J})\label{eq: Current furmula_Omega}\\
+j_{\text{l}\rightarrow\text{r}}&=v^2\int_{-\Omega/2}^{\Omega/2}\frac{\dd\omega}{2\pi} \int \dd\epsilon \int \dd\overline{\epsilon} \rho(\epsilon,\overline{\epsilon}) \rre\Tr(\mat{J})\label{eq: Current furmula_Omega}\\
 &= v^2\int_{-\infty}^{+\infty}\frac{\dd\omega}{2\pi} \int \dd\epsilon \int \dd\overline{\epsilon} \rho(\epsilon,\overline{\epsilon}) \rre(J_{00}),\label{eq: Current furmula_00}
@@
 \begin{equation}
-  \boldsymbol{J}=\left[\boldsymbol{G}^{\text{R}}(\boldsymbol{g}_{\text{b},\text{l}}^{\text{K}}-\boldsymbol{g}_{\text{b},\text{r}}^{\text{K}})+\boldsymbol{G}^{\text{K}}(\boldsymbol{g}_{\text{b},\text{l}}^{\text{A}}-\boldsymbol{g}_{\text{b},\text{r}}^{\text{A}})\right].
+  \mat{J}=\left[\mat{G}^{\text{R}}(\mat{g}_{\text{b},\text{l}}^{\text{K}}-\mat{g}_{\text{b},\text{r}}^{\text{K}})+\mat{G}^{\text{K}}(\mat{g}_{\text{b},\text{l}}^{\text{A}}-\mat{g}_{\text{b},\text{r}}^{\text{A}})\right].
 \end{equation}
 % 
-In our case, it is convenient to use 
-Eq.~\eqref{eq: Current furmula_00}.
+In our case, it is convenient to use Eq.~\eqref{eq: Current furmula_00}.
 
@@
 We follow Ref.~\cite{so.do.18} and take $U=12$ and unless stated otherwise $E_0=2$.
-The fermion leads and the acoustic phonons have temperature $T=0.02$~\footnote{\resub{The chosen value of the temperature is, in comparison with the other paramaters of the system, as e.g.
-$\omega_{\text{ph}}$ and $U$, the smallest energy scale.
+The fermion leads and the acoustic phonons have temperature $T=0.02$~\footnote{\resub{The value chosen for the temperature is the smallest energy scale as compared to the other parameters of the system, e.g.
+$\omega_{\text{ph}}$ and $U$.
 For this reason, we can neglect optical phonons in our qualitative treatment.}}.
@@
 The chemical potentials are set to $\mu_{\text{l}/\text{r}} =\mp 1$, so that a current from left to right is produced by taking energy from the driving.
-
 Due to the hybridization with the leads, the local DOS of the Hubbard layer only features a pseudogap
@@
 \begin{figure}[t]    
-
 \includegraphics[width=0.8\linewidth]{Fig2.pdf}
@@
 Thereby, we partially follow Ref.~\cite{so.do.18} for the electron-only (EO) case and extend the analysis to the case with e-ph interaction.
-In comparison with Ref.~\cite{so.do.18}, here the wide-band leads describe more realistically a metallic structure. This makes the identification of II processes more subtle, as discussed below.
-As in Ref.~\cite{so.do.18} we bypass transient behavior and consider directly the Floquet steady state. In our analysis, we neglect higher-order processes such as multiparticle scattering processes.
+In comparison with Ref.~\cite{so.do.18}, here the wide-band leads describe more realistically a metallic structure.
+This makes the identification of II processes more subtle, as discussed below.
+As in Ref.~\cite{so.do.18} we bypass transient behavior and consider directly the Floquet steady state.
+In our analysis, we neglect higher-order processes such as multiparticle scattering processes.
 
-In order to observe II, the bandwidth of the UHB has to be at least twice the pseudogap~\footnote{Due to the hybridization with the metallic leads 
-only a pseudogap $\Delta_{\text{pg}}$ is present between the LHB and the UHB.} size $\Delta_{\text{pg}}$.
+In order to observe II, the bandwidth of the UHB has to be at least twice the pseudogap~\footnote{Due to the hybridization with the metallic leads only a pseudogap $\Delta_{\text{pg}}$ is present between the LHB and the UHB.} size $\Delta_{\text{pg}}$.
 Only in this case, the photoexcited electron can acquire enough energy to excite a second one across the pseudogap.
@@
 \item For $\Omega<\Delta_{\text{pg}}$, 
-we expect a strong suppression of the current~\footnote{The remaining leak current originates either from multiple-photon absorption processes
-which are strongly suppressed, or from the absence of a true gap.} and
-we do not expect any current if the DOS of the correlated layer has a true gap.
+we expect a strong suppression of the current~\footnote{The remaining leak current originates either from multiple-photon absorption processes which are strongly suppressed, or from the absence of a true gap.} and we do not expect any current if the DOS of the correlated layer has a true gap.
 \item For $\Delta_{\text{pg}}<\Omega<\Delta_{\text{pg}}+2W_{\text{b}}$ as shown in Fig.~\ref{fig:energy_setup}(b), an electron coming from the left lead into the LHB is photoexcited to the UHB and can escape directly into the right lead without additional scattering.
@@
 \end{itemize}
-
+% 
 Notice that in the energy window $\Delta_{\text{pg}}<\Omega<2\Delta_{\text{pg}}$ the only scattering processes taking place are DEs, while for $2\Delta_{\text{pg}}<\Omega<\Delta_{\text{pg}}+2W_{\text{b}}$, both DE and II can occur.
@@
 For $\Omega=5$, in the DE range, the occupation function in the UHB is almost the same for both $v$, while for $\Omega=11$ where the peak in the current occurs, the occupation of the UHB for $v=0.4$ is substantially larger, in line with the behavior of $N_{\text{D}}$.
-
 Further increasing $\Omega$ produces excitations near the border of the UHB where the DOS is reduced and thus  current and double occupation decrease~\footnote{The current $j$ does not approach zero as expected for $\Omega>20$ because of the background current as discussed in Ref.~\cite{so.do.18}.}.
@@
 
+\begin{figure}[b]
+\includegraphics[width=\linewidth]{Fig6.pdf}
+\caption{(Color online) Spectral function $A(\omega)$ (solid line) and occupation function $N(\omega)$ (shaded area) at $\Omega=11$ without and with e-ph interaction, for (a) $v=0.4$ and (b) $v=0.8$.
+Default parameters are specified at the beginning of Sec.~\ref{sec:results}.}
+\label{fig:spec_filling_mu1_v_0.4_0.8_O_11_eph}
+\end{figure}
+
 The double occupation $N_{\text{D}}$  shown in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(b) is larger than and follows the behavior of its EO counterpart within the entire $\Omega$-range considered.
@@
 \ref{fig:spec_filling_mu1_v_0.4_0.8_O_11_eph}.
-
-\begin{figure}[b]
-\includegraphics[width=\linewidth]{Fig6.pdf}
-\caption{(Color online) Spectral function $A(\omega)$ (solid line) and occupation function $N(\omega)$ (shaded area) at $\Omega=11$ without and with e-ph interaction, for (a) $v=0.4$ and (b) $v=0.8$.
-Default parameters are specified at the beginning of Sec.~\ref{sec:results}.}
-\label{fig:spec_filling_mu1_v_0.4_0.8_O_11_eph}
-\end{figure}
 
@@
 
-This behavior is qualitatively valid for different values of the soft cutoff phonon frequency
- $\omega_{\text{ph}}$. It can be seen in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_E0_2_sweep_omegaph}, which shows that the impact of acoustic phonons on 
-current and double occupation is slightly boosted when decreasing $\omega_{\text{ph}}$~\footnote{Reducing $\omega_{\text{ph}}$ has two effects.
+This behavior is qualitatively valid for different values of the soft cutoff phonon frequency $\omega_{\text{ph}}$.
+It can be seen in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_E0_2_sweep_omegaph}, which shows that the impact of acoustic phonons on current and double occupation is slightly boosted when decreasing $\omega_{\text{ph}}$~\footnote{Reducing $\omega_{\text{ph}}$ has two effects.
 First, the phonon spectral function $A_{\text{ph}}(\omega)$ exhibits more weight at low frequencies around $\omega\approx\omega_{\text{ph}}$.
@@
 Fig.~\ref{fig:j_vs_omega_mu1_sweep_v_E0_2_eph} confirms this behavior for intermediate lead-layer hybridizations $v=0.5,0.6,0.7$.
-Also the location of the crossing in the current  between the EO and e-ph case is essentially independent of $v$, as can be seen in
- Fig.~\ref{fig:j_vs_omega_mu1_sweep_v_E0_2_eph}(a).
+Also the location of the crossing in the current  between the EO and e-ph case is essentially independent of $v$, as can be seen in Fig.~\ref{fig:j_vs_omega_mu1_sweep_v_E0_2_eph}(a).
 
@@
 In order to realize a Mott-based photovoltaic setup between metallic leads, we considered a correlated layer coupled to acoustic phonons, located between wide-band fermion leads.
-We studied the influence of the strength 
-of the coupling to the leads on the scattering process occurring at different driving frequencies and observed how the dissipation by acoustic phonons influences the photocurrent and the double occupation.
+We studied the influence of the strength of the coupling to the leads on the scattering process occurring at different driving frequencies and observed how the dissipation by acoustic phonons influences the photocurrent and the double occupation.
 We found evidence of a significant amount of II processes leading to a photocurrent peak at small hybridizations, while these are suppressed  for larger hybridizations.
@@
 Experimentally, the electric field amplitude considered in this paper is several orders of magnitude larger than that of the sunlight, therefore our results are more relevant for photoexcitations produced by intense laser pulses (see also the discussion in~\cite{mu.we.18}) rather than for true photovoltaic systems.
-\resub{We didn't consider smaller electric field amplitudes, because of the slow F-DMFT convergence for such a choice of parameters, that occurs also with weaker hybridization strengths.}
+\resub{We did not consider smaller electric field amplitudes due to the slow F-DMFT convergence for such a choice of parameters.
+This also occurs for smaller hybridization strengths.}
 

### 2022-11-03 resub_PRB/letters/reply_to_referees_jan.txt
intermediate enrico

@@
 The first Referee recommends publication without hesitation.
-The second Referee believes that the paper has to be published in Physical Review B, discussing the points he raised.
+The second Referee believes that the paper has to be published in Physical Review B, after discussing the points she/he raised.
 
@@
 
-A1-A2-A3: We thank the Referee a lot for his remarks on and acknowledgement of our article.
+A1-A2-A3: We thank the Referee for her/his remarks and aprreciation of our article.
 
@@
 
-A4: We will keep this suggestion in mind for our future investigations.
+A4: Thank you for this suggestion, which is an interesting input for  future investigations.
 
@@
 
-A1: The Referee is right, we acknowledge that a discussion on the meaningfulness of the DMFT approximation for the quasi-2D case is missing.
+A1: As the Referee says, the system is not strictly 2D.
+There is a coupling in the third direction due to the hybridisation to the leads.
+Although these are noninteracting, they introduce a dissipation which suppresses 2D coherence and makes nonlocal correlations less relevant.
 
-In the quasi-2D case we address, the use of DMFT which neglects the momentum dependence of the electron self-energy leads to meaningful results for two main reasons.
-
-First: The physical system we want to model with our setup is not "strictly" two dimensional, meaning that there is still some dispersion in the third dimension, even though it may be weak.
-For such quasi-2D systems DMFT can yield useful results (Phys.
-Rev.
-B 97, 115113 (2018)).
-
-Second: In our treatment we do not include nonlocal correlations which give rise to long-ranged collective excitations such as magnons.
-Including nonlocal correlations leads to truly nonlocal effects and therefore nonlocal contributions in the self-energy, whose momentum-dependence then clearly has to be taken into account.
-In low dimensional systems, like the one we are considering, these effects are usually not negligible.
-Yet their inclusion is also a matter of choice, depending on the physics one is interested in: to clearly address the influence of the leads and acoustic phonons on impact ionization processes, spatially nonlocal correlations would complicate the overall picture and understanding.
+On the other hand, antiferromagnetic (even short-range) correlations may play an important role in the spreading of photoexcited carriers, as discussed in prl 113,076405 (2014).
+These nonlocal effects are not taken into account in our paper and certain deserve future investigations.
 
@@
 
-The value of the temperature of T=0.02 is not high compared with the other characteristic energy scales of the system, e.g.
-the soft cutoff of the acoustic phonon frequency w_ph=0.1 and the Hubbard interaction U=12.
-It is actually the smallest chosen energy scale.
-Usually, the optical phonon modes energy is at least twice that of the acoustic phonons one [see Figs.
-4 and 5 in Phys.
-Rev.
-B 102, 245104 (2020)].
-Therefore the choice of a small value for the temperature justifies in our view taking into account only acoustic phonons and neglecting optical phonons.
-
-Just as a remark, we are interested in the effects of phonon-mediated dissipation and for this purpose the acoustic phonons with a finite bandwidth, in contrast to optical phonons, are more effective in energy dissipation, as is already mentioned in Sec.
-II (there optical phonons are denoted Holstein phonons).
+The value of the temperature of T=0.02 is not large as compared with the other characteristic energy scales of the system, e.g.
+the soft cutoff of the acoustic phonon frequency w_ph=0.1 and the Hubbard interaction U=12, as well as the bandwidth.
+In addition taking the energy scale of about 1eV, it roughly corresponds to  room temperature.
+In our simplified model we neglected optical phonons because they are less effective than acoustic ones in dissipating energy, as we mentioned in Sec. II
 
@@
 
-A3: We thank the Referee for pointing out a similar effect of reduced pseudogaps in semiconductors and for the clarification about the phonon renormalization of the band structure due to a momentum-dependent self-energy.
-This is an important point and we address it below.
+A3: We thank the Referee for pointing out this issue, which  we address it below.
 
-The importance of the momentum dependence of the electron self-energy in the 2D case depends on the level of sophistication one wants to achieve in considering acoustic phonons and therefore whether one wants quantitative results or is content with qualitative results.
+The importance of the momentum dependence of the electron self-energy in the 2D case depends on the level of sophistication one wants to achieve in considering acoustic phonons and therefore whether one wants quantitative results or qualitative/semi-quantitative results are sufficient.
 As explicitly stated in Sec.
 I, "...our analysis can only provide qualitative results, while quantitative comparisons with experimental systems require a more realistic setup and are beyond the scope of this work."
-At this level, having used the DMFT approximation and therefore considered momentum-independent self-energies, we cannot quantify the importance of momentum dependencies in the electron self-energy.
-However, as pointed out in the review Rev.
+Let us mentioned that  the Fan (alias  self-energy in the Migdal approximation, see Rev.
 Mod.
 Phys.
-89, 015003 (2017), the Fan term is also "...traditionally referred to as the self-energy in the Migdal approximation".
-This is exactly the term we included, albeit without momentum dependence, to take into account the effect of the acoustic phonons on electrons.
-In the same review it is noted that the Debye-Waller term is static, i.e.
-independent of frequency.
-Hence within DMFT, it would correspond to a change in the chemical potential.
-Since we consider the particle-hole symmetric case, the Debye-Waller term does not contribute.
+89, 015003 (2017)) has been included in our calculation,  albeit without momentum dependence.
+The static Debye-Waller term corresponds in our DMFT case to a shift in the chemical potential, which is zero in the present particle-hole symmetric case.
 
@@
 
-We thank the Referee for having brought up this important point.
-
 We did not consider weaker electric field amplitudes since DMFT only converges slowly for such a choice of parameters.
@@
 
-We followed the suggestion of the Referee, moving the footnote [47] into the main text in Sec. V and extending it to mention smaller hybridizations.
+Prompted by the Referee's comment we moved the footnote [47] into the main text in Sec. V and extending it to mention smaller hybridizations.
 

### 2022-11-04 resub_PRB/letters/reply_to_referees_current.txt
Modified the reply to the referee (which also contains the letter to the editor). I order to avoid confusion of several versions I moved older ones in a directory "oldstuff"  and left only one running version in the "letters" directory.
Since some content of the reply are now canged, please modifiy/include them in the paper accordingly

--- 2022-11-03 resub_PRB/letters/reply_to_referees_jan.txt
@@
 
-A1: As the Referee says, the system is not strictly 2D.
+A1: As the Referee says, the system considered here is not strictly 2D.
 There is a coupling in the third direction due to the hybridisation to the leads.
@@
 
-On the other hand, antiferromagnetic (even short-range) correlations may play an important role in the spreading of photoexcited carriers, as discussed in prl 113,076405 (2014).
+On the other hand, it is true that antiferromagnetic (even short-range) correlations may play an important role in the spreading of photoexcited carriers, as discussed in prl 113,076405 (2014).
 These nonlocal effects are not taken into account in our paper and certain deserve future investigations.
@@
 
-A2:
-
-We thank the Referee for raising this point, giving us the opportunity for further clarification.
-
-The value of the temperature of T=0.02 is not large as compared with the other characteristic energy scales of the system, e.g.
+A2: The value of the temperature of T=0.02 is not large as compared with the other characteristic energy scales of the system, e.g.
 the soft cutoff of the acoustic phonon frequency w_ph=0.1 and the Hubbard interaction U=12, as well as the bandwidth.
@@
 
-A3: We thank the Referee for pointing out this issue, which  we address it below.
+A3: We thank the Referee for pointing out this issue, which  we now address  below and in the paper.
 
@@
 As explicitly stated in Sec.
-I, "...our analysis can only provide qualitative results, while quantitative comparisons with experimental systems require a more realistic setup and are beyond the scope of this work."
-Let us mentioned that  the Fan (alias  self-energy in the Migdal approximation, see Rev.
+I, "...our analysis can only provide qualitative results, while quantitative comparisons with experimental systems require a more realistic setup and are beyond the scope of this work." In this sense, we don't expect a momentum dependent Sigma would change the overall picture obtained in our work.
+We are not looking at a detailed band structure change.
+We have included Fan terms (alias  Migdal terms, see Rev.
 Mod.
 Phys.
-89, 015003 (2017)) has been included in our calculation,  albeit without momentum dependence.
-The static Debye-Waller term corresponds in our DMFT case to a shift in the chemical potential, which is zero in the present particle-hole symmetric case.
+89, 015003 (2017)) in our calculation, although without vertex corrections and momentum dependence.
+Neglecting the DW term, as we do is consistent with neglecting phonon self-consistency and restricting to first order terms in the phonon displacement.
 
-We included a footnote in Sec. III.B addressing the momentum-dependence, together with a reference to the review mentioned above [Rev. Mod. Phys. 89, 015003 (2017)].
+%EACOMM I would discuss this point in the conclusions as further things one could do.
+We included a footnote in Sec. III.B addressing the momentum-dependence, together with a reference to the review mentioned above.
 
@@
 
-Prompted by the Referee's comment we moved the footnote [47] into the main text in Sec. V and extending it to mention smaller hybridizations.
+In connection with the Referee's comment we moved the footnote [47] into the main text in Sec. V and extending it to mention smaller hybridizations.
 

### 2022-11-04 tmp-passexampleexp.sh

@@ -1,0 +1,4 @@
+spawn ssh-add
+expect  "passphrase"
+send -- "$env(PPP)\r"
+interact

### 2022-11-04 resub_PRB/letters/reply_to_referees_current.txt
Version modified following Enrico's suggestions

@@
 
-A1-A2-A3: We thank the Referee for her/his remarks and aprreciation of our article.
+A1-A2-A3: We thank the Referee for her/his remarks and appreciation of our article.
 
@@
 
-A4: Thank you for this suggestion, which is an interesting input for  future investigations.
+A4: We thank the Referee for this suggestion, which is an interesting input for future investigations.
 
@@
 A1: As the Referee says, the system considered here is not strictly 2D.
-There is a coupling in the third direction due to the hybridisation to the leads.
-Although these are noninteracting, they introduce a dissipation which suppresses 2D coherence and makes nonlocal correlations less relevant.
+There is a coupling in the third direction due to the hybridization to the leads.
+Although these are noninteracting, they introduce a dissipation which suppresses 2D-coherence and makes nonlocal correlations less relevant.
 
-On the other hand, it is true that antiferromagnetic (even short-range) correlations may play an important role in the spreading of photoexcited carriers, as discussed in prl 113,076405 (2014).
-These nonlocal effects are not taken into account in our paper and certain deserve future investigations.
+On the other hand, it is true that antiferromagnetic (even short-range) correlations may play an important role in the spreading of photoexcited carriers, as discussed in Phys. Rev. Lett. 113, 076405
+(2014). These nonlocal effects are not taken into account in our paper and certainly deserve future investigations.
 
-As asked, we added in Sec. I a discussion on this point, with a reference to a comprehensive review of nonlocal correlations beyond DMFT [Rev. Mod. Phys. 90, 025003 (2018)].
+As asked, we added in Sec.
+I a discussion on this point, with a reference to the paper mentioned above and to a comprehensive review of nonlocal correlations beyond DMFT [Rev.
+Mod.
+Phys.
+90, 025003 (2018)].
 
@@
 A2: The value of the temperature of T=0.02 is not large as compared with the other characteristic energy scales of the system, e.g.
-the soft cutoff of the acoustic phonon frequency w_ph=0.1 and the Hubbard interaction U=12, as well as the bandwidth.
-In addition taking the energy scale of about 1eV, it roughly corresponds to  room temperature.
-In our simplified model we neglected optical phonons because they are less effective than acoustic ones in dissipating energy, as we mentioned in Sec. II
+the soft cutoff of the acoustic phonon frequency w_ph=0.1 and the Hubbard interaction U=12, as well as the Hubbard bands bandwidth.
+In addition, if one takes the energy scale of about 1eV or less, this would correspond to the room temperature or below.
+In our simplified model, we neglected optical phonons because they are less effective than acoustic ones in dissipating energy, as we mentioned in Sec. II.
 
@@
 As explicitly stated in Sec.
-I, "...our analysis can only provide qualitative results, while quantitative comparisons with experimental systems require a more realistic setup and are beyond the scope of this work." In this sense, we don't expect a momentum dependent Sigma would change the overall picture obtained in our work.
-We are not looking at a detailed band structure change.
-We have included Fan terms (alias  Migdal terms, see Rev.
+I, "...our analysis can only provide qualitative results, while quantitative comparisons with experimental systems require a more realistic setup and are beyond the scope of this work." In this sense, we don't expect that a momentum-dependent Sigma would change the overall picture obtained in our work.
+In fact, we are not looking at a detailed band structure change.
+We have included the Fan term (alias  Migdal term, see Rev.
 Mod.
@@
 89, 015003 (2017)) in our calculation, although without vertex corrections and momentum dependence.
-Neglecting the DW term, as we do is consistent with neglecting phonon self-consistency and restricting to first order terms in the phonon displacement.
+Neglecting the DW term, as we do, is consistent with neglecting phonon self-consistency and restricting to first-order terms in the phonon displacement.
 
-%EACOMM I would discuss this point in the conclusions as further things one could do.
-We included a footnote in Sec. III.B addressing the momentum-dependence, together with a reference to the review mentioned above.
+We included a discussion in Sec. V addressing this issue, together with a reference to the review mentioned above.
 
@@
 We have already discussed this point in the footnote [47].
-The same reasoning applies for smaller hybridization strength which slows down the convergence of the DMFT cycle considerably.
+This holds also for smaller hybridization strengths which slow down the convergence of the DMFT cycle considerably.
 
-In connection with the Referee's comment we moved the footnote [47] into the main text in Sec. V and extending it to mention smaller hybridizations.
+In connection with the Referee's comment we moved the footnote [47] into the main text in Sec. V and we extended it to mention smaller hybridizations.
 
@@
 Modified Sec. I  
-Added reference in Sec. I
-Added footnote in Sec. IIIB
-Added reference in Sec. IIIB
+Added references in Sec. I
 Added footnote in Sec. IV
 Modified Sec. V
+Added reference in Sec. V

### 2022-11-04 resub_PRB/Paper1.tex
Version modified following Enrico's suggestions

@@
 An external periodic electric field induces a Floquet steady state with a current flowing from the lead with the lower to the lead with the higher chemical potential, thus transferring its energy.
-We address this periodic problem via nonequilibrium Floquet dynamical mean-field theory (F-DMFT)\resub{, which has been shown to give meaningful results in similar setups (see, e.g.~\cite{so.do.18}).
-Since we are not interested in capturing long-ranged collective excitations, non-local correlations~\cite{ro.ha.18} are not taken into account.}
+We address this periodic problem via nonequilibrium Floquet dynamical mean-field theory (F-DMFT)\resub{, which has been shown to give meaningful results in quasi-2D setups (see, e.g.~\cite{so.do.18}) as the one considered, in which the coupling in a third direction, due to the hybridization to the leads, introduces a dissipation which suppresses 2D-coherence and makes nonlocal correlations less relevant.
+However, it has been shown that antiferromagnetic (even short-range) correlations may play an important role in the spreading of photoexcited carriers~\cite{ec.we.14}.
+In this paper, we explicitly don't take into account these nonlocal effects~\cite{ro.ha.18}.}
 
 \begin{figure}[b] 
-\includegraphics[width=0.9\linewidth]{Fig1.pdf}
+\includegraphics[width=0.75\linewidth]{Fig1.pdf}
 \caption{(Color online) Schematic representation of the setup.
@@
 Further details are given in Sec.~\ref{sec:FDMFT_implementation}.
-In the same spirit, the e-ph SE is included locally as $\kel{\mat{\Sigma}}_{\text{e-ph}}(\omega;\epsilon,\overline{\epsilon}) \simeq \kel{\mat{\Sigma}}_{\text{e-ph}}(\omega)$~\footnote{\resub{As stated in Sec.~\ref{sec:intro}, our analysis provides only qualitative results.
-A more accurate treatment that aims to provide quantitative predictions, should take into account the crystal momentum dependence of $\kel{\mat{\Sigma}}_{\text{e-ph}}$.
-We refer to the review~\cite{gius.17} which discusses the effects of phonons on the electronic bandstructure and the modelling thereof.}}\vphantom{\cite{gius.17}}.
+In the same spirit, the e-ph SE is included locally as $\kel{\mat{\Sigma}}_{\text{e-ph}}(\omega;\epsilon,\overline{\epsilon}) \simeq \kel{\mat{\Sigma}}_{\text{e-ph}}(\omega)$.
 In terms of the Keldysh contour time arguments $z$ and $z^\prime$, it has the form
@@
 We follow Ref.~\cite{so.do.18} and take $U=12$ and unless stated otherwise $E_0=2$.
-The fermion leads and the acoustic phonons have temperature $T=0.02$~\footnote{\resub{The value chosen for the temperature is the smallest energy scale as compared to the other parameters of the system, e.g.
-$\omega_{\text{ph}}$ and $U$.
-For this reason, we can neglect optical phonons in our qualitative treatment.}}.
+The fermion leads and the acoustic phonons have temperature $T=0.02$~\footnote{\resub{The value chosen for the temperature is small as compared with the other characteristic energy scales of the system, e.g.
+$\omega_{\text{ph}}$, $U$ and $W_{\text{b}}$.}}.
 We consider a particle-hole symmetric system with $\Gamma_{\text{l}}=\Gamma_{\text{r}}=0.37$, $t_{\text{l}}=t_{\text{r}}=1.7$, $\varepsilon_{\text{l}/\text{r}}=\mp 6$ and $v_{\text{l}}=v_{\text{r}}=v$.
@@
 \resub{We did not consider smaller electric field amplitudes due to the slow F-DMFT convergence for such a choice of parameters.
-This also occurs for smaller hybridization strengths.}
+This also occurs for weaker hybridization strengths.}
 
@@
 To address the occurrence of II in such a setup, further extensions such as considering multiple orbitals and impurity scattering should be taken into account.
-These would be interesting for future studies.
+\resub{Finally, a more realistic description of the effects of the electron-phonon interaction on electronic band structure should take into account the crystal momentum dependence of $\kel{\mat{\Sigma}}_{\text{e-ph}}$~\cite{gius.17}.} These would be interesting for future studies.
 
@@
 We thank A.
-Picano for fruitful discussions.
-This work was supported by the Austrian Science Fund (FWF) within Project P 33165-N, as well as NaWi Graz.
+Picano and C.
+Heil for fruitful discussions.
+This work was supported by the Austrian Science Fund (Grant No.
+P 33165-N) and by NaWi Graz.
 The computational results presented have been obtained using the Vienna Scientific Cluster (VSC) and the D-Cluster Graz.

### 2022-11-05 resub_PRB/letters/reply_to_referees_current.txt
Moved the comment on DMFT validity to the conclusions. Also slight modifications. Letter modified accordingly

@@
 
-As asked, we added in Sec.
-I a discussion on this point, with a reference to the paper mentioned above and to a comprehensive review of nonlocal correlations beyond DMFT [Rev.
+As asked, we added in the conclusions a discussion on this point, with a reference to the paper mentioned above and to a comprehensive review of nonlocal correlations beyond DMFT [Rev.
 Mod.
@@
 
-Modified Sec. I  
-Added references in Sec. I
 Added footnote in Sec. IV

### 2022-11-05 resub_PRB/Paper1.tex
Moved the comment on DMFT validity to the conclusions. Also slight modifications. Letter modified accordingly

@@
 An external periodic electric field induces a Floquet steady state with a current flowing from the lead with the lower to the lead with the higher chemical potential, thus transferring its energy.
-We address this periodic problem via nonequilibrium Floquet dynamical mean-field theory (F-DMFT)\resub{, which has been shown to give meaningful results in quasi-2D setups (see, e.g.~\cite{so.do.18}) as the one considered, in which the coupling in a third direction, due to the hybridization to the leads, introduces a dissipation which suppresses 2D-coherence and makes nonlocal correlations less relevant.
-However, it has been shown that antiferromagnetic (even short-range) correlations may play an important role in the spreading of photoexcited carriers~\cite{ec.we.14}.
-In this paper, we explicitly don't take into account these nonlocal effects~\cite{ro.ha.18}.}
+We address this periodic problem via nonequilibrium Floquet dynamical mean-field theory (F-DMFT).
 
@@
 We follow Ref.~\cite{so.do.18} and take $U=12$ and unless stated otherwise $E_0=2$.
-The fermion leads and the acoustic phonons have temperature $T=0.02$~\footnote{\resub{The value chosen for the temperature is small as compared with the other characteristic energy scales of the system, e.g.
+The fermion leads and the acoustic phonons have temperature $T=0.02$~\footnote{\resub{The value chosen for the temperature is much smaller as compared with the other characteristic energy scales of the system, e.g.
 $\omega_{\text{ph}}$, $U$ and $W_{\text{b}}$.}}.
@@
 
+\resub{One should comment on the validity of DMFT, which should be accurate for large dimensions only, for the present quasi 2-D setup.
+As a matter of fact, the hybridization to the leads introduces a dissipation that suppresses 2D-coherence and thus makes nonlocal correlations beyond DMFT less relevant.
+On the other hand, it has been shown that antiferromagnetic (even short-range) correlations may play an important role in the spreading of photoexcited carriers~\cite{ec.we.14}. 
+Thaking into account the effect of such nonlocal correlations (see also ~\cite{ro.ha.18}) could be an interesting extension, although beyond the scope of the present research.}
+
 Experimentally, the electric field amplitude considered in this paper is several orders of magnitude larger than that of the sunlight, therefore our results are more relevant for photoexcitations produced by intense laser pulses (see also the discussion in~\cite{mu.we.18}) rather than for true photovoltaic systems.
 \resub{We did not consider smaller electric field amplitudes due to the slow F-DMFT convergence for such a choice of parameters.
-This also occurs for weaker hybridization strengths.}
+This is also the case for weaker hybridization strengths.}
 
@@
 To address the occurrence of II in such a setup, further extensions such as considering multiple orbitals and impurity scattering should be taken into account.
-\resub{Finally, a more realistic description of the effects of the electron-phonon interaction on electronic band structure should take into account the crystal momentum dependence of $\kel{\mat{\Sigma}}_{\text{e-ph}}$~\cite{gius.17}.} These would be interesting for future studies.
+This aspect could be interesting for future studies.
+ \resub{Finally, a more realistic description of the effects of the electron-phonon interaction on electronic band structure should take into account the crystal momentum dependence of $\kel{\mat{\Sigma}}_{\text{e-ph}}$~\cite{gius.17}.}
 

### 2022-11-05 tmp-passexampleexp.sh

@@ -1,4 +1,0 @@
-spawn ssh-add
-expect  "passphrase"
-send -- "$env(PPP)\r"
-interact

### 2022-11-07 resub_PRB/letters/reply_to_referees_current.txt
Final version resubmitted to PRB

@@
 
-As asked, we added in the conclusions a discussion on this point, with a reference to the paper mentioned above and to a comprehensive review of nonlocal correlations beyond DMFT [Rev.
+As asked, we added in Sec.
+V a discussion on this point, with a reference to the paper mentioned above and to a comprehensive review of nonlocal correlations beyond DMFT [Rev.
 Mod.
@@
 Modified Sec. V
-Added reference in Sec. V
+Added references in Sec. V
+Modified Acknowledgements

### 2022-11-07 resub_PRB/Paper1.tex
typos fixing
Final version resubmitted to PRB

@@
 \begin{figure}[b] 
-\includegraphics[width=0.75\linewidth]{Fig1.pdf}
+\includegraphics[width=0.8\linewidth]{Fig1.pdf}
 \caption{(Color online) Schematic representation of the setup.
@@
 We follow Ref.~\cite{so.do.18} and take $U=12$ and unless stated otherwise $E_0=2$.
-The fermion leads and the acoustic phonons have temperature $T=0.02$~\footnote{\resub{The value chosen for the temperature is much smaller as compared with the other characteristic energy scales of the system, e.g.
+The fermion leads and the acoustic phonons have temperature $T=0.02$~\footnote{\resub{The value chosen for the temperature is much smaller than the other characteristic energy scales of the system, e.g.
 $\omega_{\text{ph}}$, $U$ and $W_{\text{b}}$.}}.
@@
 
-\resub{One should comment on the validity of DMFT, which should be accurate for large dimensions only, for the present quasi 2-D setup.
-As a matter of fact, the hybridization to the leads introduces a dissipation that suppresses 2D-coherence and thus makes nonlocal correlations beyond DMFT less relevant.
+\resub{One should comment on the validity of DMFT, which should be accurate for large dimensions only, for the present quasi two-dimensional (2D) setup.
+As a matter of fact, the hybridization to the leads introduces a dissipation which suppresses 2D-coherence and thus makes nonlocal correlations beyond DMFT less relevant.
 On the other hand, it has been shown that antiferromagnetic (even short-range) correlations may play an important role in the spreading of photoexcited carriers~\cite{ec.we.14}. 
-Thaking into account the effect of such nonlocal correlations (see also ~\cite{ro.ha.18}) could be an interesting extension, although beyond the scope of the present research.}
+Taking into account the effect of such nonlocal correlations (see also~\cite{ro.ha.18}) might be an interesting extension, although beyond the scope of the present research.}
 
@@
 We thank A.
-Picano and C.
-Heil for fruitful discussions.
-This work was supported by the Austrian Science Fund (Grant No.
-P 33165-N) and by NaWi Graz.
+Picano \resub{and C.
+Heil} for fruitful discussions.
+This work was supported by the Austrian Science Fund \resub{(Grant No.
+P 33165-N) and by} NaWi Graz.
 The computational results presented have been obtained using the Vienna Scientific Cluster (VSC) and the D-Cluster Graz.

### 2022-12-20 resub_arXiv/Paper1.tex
final .pdf version PRB + publication + resub_arXiv

--- 2022-11-07 resub_PRB/Paper1.tex
@@
 \definecolor{hblue}{RGB}{0,0,255}
-\newcommand{\resub}[1]{{\color{hblue} #1}}
+% \newcommand{\resub}[1]{{\color{hblue} #1}}
 
@@
 We follow Ref.~\cite{so.do.18} and take $U=12$ and unless stated otherwise $E_0=2$.
-The fermion leads and the acoustic phonons have temperature $T=0.02$~\footnote{\resub{The value chosen for the temperature is much smaller than the other characteristic energy scales of the system, e.g.
-$\omega_{\text{ph}}$, $U$ and $W_{\text{b}}$.}}.
+The fermion leads and the acoustic phonons have temperature $T=0.02$~\footnote{The value chosen for the temperature is much smaller than the other characteristic energy scales of the system, e.g.
+$\omega_{\text{ph}}$, $U$ and $W_{\text{b}}$.}.
 We consider a particle-hole symmetric system with $\Gamma_{\text{l}}=\Gamma_{\text{r}}=0.37$, $t_{\text{l}}=t_{\text{r}}=1.7$, $\varepsilon_{\text{l}/\text{r}}=\mp 6$ and $v_{\text{l}}=v_{\text{r}}=v$.
@@
 
-\resub{One should comment on the validity of DMFT, which should be accurate for large dimensions only, for the present quasi two-dimensional (2D) setup.
+One should comment on the validity of DMFT, which should be accurate for large dimensions only, for the present quasi two-dimensional (2D) setup.
 As a matter of fact, the hybridization to the leads introduces a dissipation which suppresses 2D-coherence and thus makes nonlocal correlations beyond DMFT less relevant.
 On the other hand, it has been shown that antiferromagnetic (even short-range) correlations may play an important role in the spreading of photoexcited carriers~\cite{ec.we.14}. 
-Taking into account the effect of such nonlocal correlations (see also~\cite{ro.ha.18}) might be an interesting extension, although beyond the scope of the present research.}
+Taking into account the effect of such nonlocal correlations (see also~\cite{ro.ha.18}) might be an interesting extension, although beyond the scope of the present research.
 
 Experimentally, the electric field amplitude considered in this paper is several orders of magnitude larger than that of the sunlight, therefore our results are more relevant for photoexcitations produced by intense laser pulses (see also the discussion in~\cite{mu.we.18}) rather than for true photovoltaic systems.
-\resub{We did not consider smaller electric field amplitudes due to the slow F-DMFT convergence for such a choice of parameters.
-This is also the case for weaker hybridization strengths.}
+We did not consider smaller electric field amplitudes due to the slow F-DMFT convergence for such a choice of parameters.
+This is also the case for weaker hybridization strengths.
 
@@
 This aspect could be interesting for future studies.
- \resub{Finally, a more realistic description of the effects of the electron-phonon interaction on electronic band structure should take into account the crystal momentum dependence of $\kel{\mat{\Sigma}}_{\text{e-ph}}$~\cite{gius.17}.}
+Finally, a more realistic description of the effects of the electron-phonon interaction on electronic band structure should take into account the crystal momentum dependence of $\kel{\mat{\Sigma}}_{\text{e-ph}}$~\cite{gius.17}.
 
@@
 We thank A.
-Picano \resub{and C.
-Heil} for fruitful discussions.
-This work was supported by the Austrian Science Fund \resub{(Grant No.
-P 33165-N) and by} NaWi Graz.
+Picano and C.
+Heil for fruitful discussions.
+This work was supported by the Austrian Science Fund (Grant No.
+P 33165-N) and by NaWi Graz.
 The computational results presented have been obtained using the Vienna Scientific Cluster (VSC) and the D-Cluster Graz.
@@
 \bibliographystyle{prsty}   % references in Phys Rev style
-\bibliography{footnotes,references_database}
+\bibliography{references_database}
 
